### 2020-10-29 docs/ms/ms.RMD
Initial commit

---
title: "Manuscript title here"
author: "James R Junker"
date: Dept. of Ecology, Montana State University, Bozeman, MT USA
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

<!--- this is a note in Rmarkdown --->

Abstract
================================================================================

Introduction
================================================================================

Methods
================================================================================

Results
================================================================================

Discussion
================================================================================

References
================================================================================

<div id="refs"></div>

\clearpage

### 2020-12-29 docs/ms/ms.RMD
big commit of work for initial project start.

@@
 title: "Manuscript title here"
-author: "James R Junker"
-date: Dept. of Ecology, Montana State University, Bozeman, MT USA
+author: 
+- name: James R Junker
+  affiliation: Dept. of Ecology, Montana State University, Bozeman, MT USA
 output:
@@
 - \usepackage{lineno}
+- \usepackage{amsmath}
 - \linenumbers
@@
 
-Abstract
-================================================================================
+# Abstract
 
-Introduction
-================================================================================
+# Introduction
 
-Methods
-================================================================================
+Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@Brose2012][@walther2002][@Woodward_Dybkjær_Ólafsson_eta2010].
+The effects of this warming manifest through shifting species ranges [],
 
-Results
-================================================================================
+The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged [@deRuiter1995][@thompson2012].
+Specifically, warming can directly alter , is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018].
 
-Discussion
-================================================================================
+Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (~5 - 28$^\circ$C).
+Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011][@padfield2017] and within streams seasonally [@gorman2012][@hood2018].
+The dynamics of basal resource supply has a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumer to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
+Further, we predicted that food web OM fluxes will 'speed up' with increasing temperature through increases in the importance of relatively faster, higher turnover consumers.
+Within streams, the speeding up of ecosystems will lead to earlier food web fluxes in warmer compared to colder streams.
 
-References
-================================================================================
+# Methods
 
-<div id="refs"></div>
+We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N  021$^\circ$ 18'W) that varied in mean annual temperature.
+Hengill is characterized by indirect geothermal heating of groundwater [@arnason_hengill_1969], leading to a natural variability in water temperatures (4.5–54.0 $^\circ$C), but similar solute chemistries [@friberg_relationships_2009].
+These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman_climate_2014; @nelson_experimental_2017].
+We selected streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers.
+In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp.
+Pocasset, MA, USA).
+Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp.
+Pocasset, MA, USA).
 
-\clearpage
+## Invertebrate sampling
+
+We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous study (*n* = 6 streams).
+The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental manipulation [see @nelson_experimental_2017; -@nelson_shifts_2017].
+Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson_experimental_2017; @hood_increased_2018].
+We collected fiver Surber samples (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream.
+Within the sampler, inorganic substrates were disturbed to ~10 cm depth and invertebrates and organic matter were removed from stones with a brush.
+Samples were then preserved with 5% formaldehyde until laboratory analysis.
+In the laboratory, we split samples into coarse (>1 mm) and fine (<1 mm but >250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10–15 x magnification).
+For particularly large samples, fine fractions were subsampled (1/2–1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates.
+Subsamples were scaled to the rest of the sample assuming similar abundance and body size distributions.
+Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson_black_1977; @merritt_introduction_2008; @andersen_chironomidae_2013].
+Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
+
+## Secondary Production
+
+Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @Benke_Huryn2017].
+Growth rates were determined using taxon appropriate approaches described in [@junker_resource_nodate].
+Briefly, growth rates of common taxa (e.g., Chironomidae spp., Radix balthica, etc.) were determined using *in situ* chambers [@huryn_method_1986].
+Multiple individuals  (*n* = 5–15) within small size categories (~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned chambers for 7–15 days, after which they were again photographed.
+Individual lengths were measured from field pictures using image analysis software [@Schindelin_Arganda-Carreras_Frise_Kaynig_Longair_Pietzsch_Preibisch_Rueden_Saalfeld_Schmid_et al.2012], and body lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke_length-mass_1999; @ogorman_impacts_2012; @hannesdottir_increased_2013].
+Growth rates (*g*, d^-1^) were calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:
+
+$$g = log_e ( W_{t+\Delta t} / W_t) / \Delta t$$
+
+Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500).
+For taxa which exhibit synchronous growth and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty using a bootstrap technique similar to that described in Benke and Huryn [-@benke_secondary_2017].
+Individual Lengths were converted to mg AFDM using published length-mass regression cited above and size-frequency histograms were visually inspected for directional changes in body size through time.
+For each date, size-frequency distributions were resampled with replacement (*n* = 500) and growth rates estimated from equation 1.
+We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ > $W_t$.
+To estimate growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of empirical growth data against body size and temperature within each stream.
+To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled measured growth rates, in addition to abundance and size distributions from individual samples.
+For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean interval biomass for each size class and the number of days between sample dates to estimate size class-specific production.
+For each interval, size classes were summed for each taxon to calculate total population-level production.
+Intervals were summed to estimate annual secondary production.
+
+## Gut Content Analysis
+
+Macroinvertebrate diets were quantified for dominant taxa in each stream.
+We focused on numerically abundant taxa and/or taxa with relatively high annual production.
+A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic shifts in diet.
+We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes.
+For small-bodied taxa, we combined multiple individuals (*n* = 3–5) to ensure samples contained enough material for quantification.
+We used methods outlined in Rosi-Marshall [-@Rosi-Marshall_Wellard Kelly_Hall_Vallis2016] to remove gut tracts and prepare gut content slides.
+Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds.
+Gut content slurries were filtered onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a microscope slide, cleared with Type B immersion old, and covered with a cover slip.
+We took 5–10 random photographs under 200–400x magnification, depending on the density of particles, using a digital camera mounted on a compound microscope.
+From these photographs we identified all particles within each field and measured the relative area of particles using image analysis software [@schindelin_fiji_2012].
+We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular plants (bryophytes), and animal material.
+We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles.
+Gut contents of many predators were empty or contained unidentifiable, macerated prey.
+For these taxa, we assumed 100% animal material.
+
+## Organic Matter Consumption Estimates
+
+Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@Benke_Wallace1980].
+Taxon-specific secondary production estimates were combined with measured diet proportions, diet-specific assimilation efficiencies, AE[i], and assumed net production efficiencies, NPE, to estimate consumption of organic matter.
+For each food category, i, diet proportions were multiplied by the gross growth efficiency (GGE[i] = AE[i] * NPE) to calculate the relative production attributable to each food category.
+The relative production from each food type was then multiplied by the interval-level production and finally divided by GGE[i] to estimate consumption of organic matter from each food category by a consumer [@benke_trophic_1980].
+Consumption was calculated for each taxon across sampling intervals (typically ~1 month).
+Total interval consumption was calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and inte(rvals.
+Variability in consumption estimates was estimated through bootstrapping, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and the consumption estimated using the TBP method.
+Variability in AE[i] was incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36), filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@Welch1968][@Cross_Wallace_Rosemond2007][@Cross_Baxter_Donner_et al.2011][@Benke_Wallace1980][@Benke1997].
+Variability in NPE was incorporated by resampling values from an assumed beta distribution with median NPE = 0.45 (95% PI = 0.4-0.5).
+Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@Belgorodski_Greiner_Tolksdorf_Schueller2017].
+
+## Quantifying the distribution of food web fluxes
+
+### Evenness Among consumers
+
+To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@Lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+p_S$.
+The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
+In a community with perfectly equal distribution of OM consumption, the Lorenz curve is simply a straight diagonal line.
+Deviation from perfect equality was calculated as the Gini coefficient [@Gini1921], normalized for differences in $S$ among streams, $G^*$ [@Solomon1979][@Chao_Ricotta2019]:
+$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+### Distribution along species trait axes
+
+To explore how
+
+### Through time
+
+To qu
+
+## Statistical Analyses
+
+# Results
+
+# Discussion
+
+\newpage
+
+# References

### 2020-12-29 docs/prelim-doc.Rmd
big commit of work for initial project start.

---
title: "Prelim report"
author: "Junker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source("./packages.R")
stream_order = factor(c("hver", "st6","st9", "st7","oh2","st14"))#stream ordering
stream_temp_labels = c("27.2","17.6","11.2","5.8","5.5","5.0")#stream annual temperature labels
oce_temp_pos = c(256,212,168,124,80,1)#color positions in 'temperature' list of ocecolors

drake::loadd("spp_rankings")

```

## Analysis

Preliminary figures for exploring data analyses and figures.

### Histograms of PB, M, and Biomass among streams.

```{r pb historgram, echo = FALSE, warnings = FALSE}
pb_df = spp_rankings[['PB_spp_rank']] %>% bind_rows %>% dplyr::filter(pb_y_mean >0) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))
bio_df = spp_rankings[['bio_spp_rank']] %>% bind_rows %>% dplyr::filter(bio_mg_m_mean >0 | is.na(bio_mg_m_mean)) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))
M_df = spp_rankings[['M_spp_rank']] %>% bind_rows %>% dplyr::filter(M_mg_ind_mean >0 | is.na(M_mg_ind_mean)) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))

pb_boxplot = ggplot(pb_df,aes(x = site_id, y = log10(pb_y_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = c(0,0), legend.justification = c(0,0),
        legend.background = element_rect(fill = 'transparent', colour = NA))
# pb_boxplot

M_boxplot = ggplot(M_df,aes(x = site_id, y = log10(M_mg_ind_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = "none")

bio_boxplot = ggplot(bio_df,aes(x = site_id, y = log10(bio_mg_m_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
  theme(axis.title.x = element_blank(), legend.title = element_blank(),legend.position = "none")

grid.arrange(pb_boxplot, M_boxplot, bio_boxplot, ncol = 3)

```

### Rank plots

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>

### 2020-12-29 R/analyze_gini.R

@@ -1,0 +1,16 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param spp_rankings
+analyze_gini <- function(spp_rankings) {
+
+  spp_ginis = spp_rankings %>%
+    map(~.x %>% 
+          map(~.x %>% group_by(site_id) %>%
+          dplyr::mutate(across(contains('mean'),  ~ .x/sum(.x), .names = "{.col}_relative")) %>%
+            dplyr::arrange(across(contains('rank'))) %>%
+            dplyr::mutate(across(contains('relative'), ~cumsum(.x), .names = "{.col}_cumulative"))))
+  
+}

### 2020-12-29 R/create_diet_matrices.R

@@ -1,0 +1,75 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param gut_lists
+##' @param spp_list
+create_diet_matrices <- function(gut_lists, spp_list = production_summaries[["production_spp_list"]]) {
+## ++++ Helper functions ++++ ##
+  create_matrix = function(spp_list, resource_list){
+    # create three matrices for 1:4. 5:8, 9:12 months
+    spp_matrix = matrix(0, nrow = nrow(spp_list), ncol = nrow(spp_list))
+    rownames(spp_matrix) <- colnames(spp_matrix) <- unlist(spp_list)
+    res_matrix = matrix(0, nrow = nrow(resource_list), ncol = nrow(resource_list))
+    rownames(res_matrix) <- colnames(res_matrix) <- unlist(resource_list)
+    
+    # create combined lists
+    full_matrix = as.matrix(gtools::smartbind(spp_matrix, res_matrix, fill = 0))
+    rownames(full_matrix)<- colnames(full_matrix)
+    return(full_matrix)
+  }
+  
+  
+## ++++ End Helper functions ++++ ##
+  
+  spp_list = spp_list %>% rlist::list.subset(names(stream_order_list))
+  
+  resource_list = gut_lists[["resource_list"]] %>% rlist::list.subset(names(stream_order_list))
+  
+  predator_lists = list(hver = c("Limnophora.riparia","Sperchon.glandulosus"),
+                        st6 = c("Limnophora.riparia","Sperchon.glandulosus","Macropelopia", "Antocha.sp.","Ephydridae.sp."),
+                        st9 = c("Limnophora.riparia","Sperchon.glandulosus","Macropelopia", "Antocha.sp.","Ephydridae.sp.", "Clinocera.stagnalis"),
+                        st7 = c("Limnophora.riparia","Sperchon.glandulosus"),
+                        oh2 = c("Limnophora.riparia","Sperchon.glandulosus", "Macropelopia"),
+                        st14 = c("Limnophora.riparia","Sperchon.glandulosus", "Antocha.sp.")) %>% 
+    rlist::list.subset(names(stream_order_list))
+  
+  predator_diet_lists = list(hver = list(c("Simulium.vittatum","Cricotopus.sylvestris","Nais.spp.", "Naididae 1"),c("Nais.spp.","Naididae 1")),
[…]

### 2020-12-29 R/estimate_flux.R

@@ -1,0 +1,50 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param diet_matrices
+##' @param seasonal_fluxes
+estimate_flux <- function(diet_matrices, seasonal_fluxes) {
+ 
+  # resource date frame with efficiences
+  diet_item = list("amorphous_detritus",
+                "cyanobacteria",
+                "diatom",
+                "filamentous",
+                "green_algae",
+                "plant_material",
+                "animal")
+ 
+   efficiencies = list(
+     c(0.08, 0.1, 0.12),
+     c(0.08, 0.1, 0.12),
+     c(0.24, 0.3, 0.36),
+     c(0.24, 0.3, 0.36),
+     c(0.24, 0.3, 0.36),
+     c(0.08, 0.1, 0.12),
+     c(0.56, 0.7, 0.84)
+  )
+  resource_keyval = setNames(efficiencies, nm = unlist(diet_item))
+
+ # estimate the beta distributions to draw diet AEs from
+   set.seed(123)
+   beta_dist.pars = map(efficiencies, ~rriskDistributions::get.beta.par(p = c(0.025,0.5,0.975), q = unlist(.x), plot = FALSE, show.output = FALSE))
+   res_effs = map(beta_dist.pars, ~rbeta(1e3, shape1 = .x[1], shape2 = .x[2])) %>% setNames(., nm = unlist(diet_item))
+
+ #NPE quantile 0.025,0.5,0.975
+   NPE_dist.pars = rriskDistributions::get.beta.par(p = c(0.025,0.5,0.975),q = c(0.4,0.45,0.5), show.output = FALSE, plot = FALSE)
+   NPE = rbeta(1e3, shape1 = NPE_dist.pars[1], shape2 = NPE_dist.pars[2])
+ # combined the production from Jan-Apr, May-Aug, Sep-Dec
+  boot_flux_function = function(mat_list, losses,resources_mat, efficiences_vct, NPE,...){
+     
+     
+    colnames(mat_list) %>% tibble %>%
+      setNames(., nm = 'matrix_name') %>%
+      dplyr::mutate(efficiencies = dplyr::recode(matrix_name, !!!resource_keyval),
+                    efficiencies = tidyr::replace_na(efficiencies, 0.7)) -> matrix_effiencies
+    boots = mat_list
+    
+  }
+
+}

### 2020-12-29 R/fluxweb_mod_function.R

@@ -1,0 +1,119 @@
+fluxing = function (mat, biomasses = NULL, losses, efficiencies, bioms.prefs = TRUE, 
+          bioms.losses = TRUE, ef.level = "prey", method = "straight_flux") # simple addition of the 'method' term
+{
+  if (!is.numeric(mat)) {
+    stop("'mat' must be numeric")
+  }
+  if (dim(mat)[1] != dim(mat)[2]) {
+    stop("mat should be a square matrix")
+  }
+  if (!is.null(biomasses)) {
+    if (!is.vector(biomasses)) {
+      stop("biomasses should be a vector")
+    }
+    else {
+      if (length(biomasses) != dim(mat)[1]) {
+        stop("length of biomasses vector should equal to dimensions of mat")
+      }
+    }
+    if (!is.numeric(biomasses)) {
+      stop("'biomasses' must be numeric")
+    }
+    else if (any(biomasses < 0)) {
+      stop("'biomasses' must be all >=0")
+    }
+  }
+  else if (bioms.prefs) {
+    stop("bioms.prefs set to TRUE but no biomasses provided")
+  }
+  if (!is.numeric(losses)) {
+    stop("'losses' should be numeric")
+  }
+  else if (any(losses < 0)) {
+    stop("'losses' contain negative value(s)")
+  }
+  if (!is.numeric(efficiencies)) {
+    stop("'efficiencies' must be numeric")
+  }
+  if (ef.level == "pred") {
+    colsums = colSums(mat)
+    if (sum(is.na(efficiencies[colsums == 0])) > 0) {
+      efficiencies[colsums == 0] = 1
+    }
+  }
+  if (ef.level == "prey") {
+    rowsums = rowSums(mat)
+    if (sum(is.na(efficiencies[rowsums == 0])) > 0) {
+      efficiencies[rowsums == 0] = 1
+    }
+  }
+  if (ef.level == "link.specific") {
+    if (sum(efficiencies[mat == 0]) > 0) {
+      warning("Efficiencies of some non existing links are not 0")
+    }
+  }
+  if (!(ef.level %in% c("prey", "pred", "link.specific"))) {
+    stop("ef.level should be set to 'pred', 'prey' or 'link.specific'")
+  }
+  if (ef.level == "prey" && is.matrix(efficiencies)) {
+    warning("'ef.level' is set to 'prey' and expect a vector of efficiencies but get a matrix instead.\n ef.level was then set to 'link.specific'")
+    ef.level = "link.specific"
+  }
[…]

### 2020-12-29 R/plan.R

@@ -1,0 +1,38 @@
+the_plan <-
+  drake_plan(
+   ## Plan targets in here.
+   ### environmental data
+  environment_data = read_clean_temperature(),
+  
+   ### production data
+  production_boots = read_production(),
+  
+  production_summaries = summarise_production(production_boots),
+  
+  seasonal_fluxes = summarise_seasonal_fluxes(production_boots[["int_spp_boots"]]),
+  
+   ### diet data
+  gut_lists = read_clean_guts(),
+  
+  # gut_df = create_gut_df(gut_lists),
+  
+  # gut_summaries = summarise_guts(gut_df),
+  
+  diet_matrices = create_diet_matrices(gut_lists, production_summaries[["production_spp_list"]]),
+  
+  # flux_estimates = estimate_flux(diet_matrices, seasonal_fluxes),
+  
+  # spp_rankings = rank_spp_traits(flux_estimates, production_summaries),
+  
+   ### trait analyses
+  spp_rankings = rank_spp_traits(production_summaries),
+  
+  # gini_analysis = analyze_gini(spp_rankings),
+
+  # target_name = target(
+  #   command = {
+  #     rmarkdown::render(knitr_in("docs/prelim-doc.Rmd"))
+  #     file_out("docs/prelim-doc.html")
+  #   }
+  # )  
+)

### 2020-12-29 R/read_clean_guts.R

@@ -1,0 +1,181 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+
+read_clean_guts <- function() {
+
+  #####    Gut Content Data Import ####
+  ##read in gut data
+  hver_path = "./data/raw-data/gut_data/hver/"
+  hver_gut_paths = as.list(dir(hver_path, pattern ="full.csv", full.names = FALSE, include.dirs = FALSE, recursive = TRUE))
+  hver_gut_files= suppressMessages(map(hver_gut_paths, ~read_csv(file = paste0(hver_path, .x))))
+  hver_gut_files = map(hver_gut_files, function(x){ if(dim(x)[2] > 2){
+    x = x[,-1];return(x)} else{return(x)}})
+  
+  hver_gut_columns = map(hver_gut_paths, ~.x %>%
+                           str_replace(.,pattern = "IMG_", "IMG") %>%
+                           strsplit(., '[/_.][[:space:]]*') %>%
+                           as.data.frame() %>%
+                           .[c(2,4,5,7),] %>%
+                           set_names(c("site","date","taxon","pic")))
+  hver_gut_columns = bind_rows(hver_gut_columns)
+  hver_gut_columns = split(hver_gut_columns, seq(nrow(hver_gut_columns)))
+  hver_gut_contents = map2(hver_gut_columns, hver_gut_files, ~.x %>%
+                             rowr::cbind.fill(.y))
+  
+  names = c("site","date","taxon","pic","diet_item","area")
+  hver_gut_contents = lapply(hver_gut_contents, setNames, names)
+  
+  hver_gut_df = bind_rows(hver_gut_contents)
+  
+  hver_gut_summ <<- hver_gut_df %>%
+   dplyr::mutate(diet_item = str_replace(diet_item, ".*ga.*", "green_algae"),
+           diet_item = str_replace(diet_item, ".*cyano.*", "cyanobacteria"),
+           diet_item = str_replace(diet_item, ".*vascular.*", "plant_material"),
+           diet_item = str_replace(diet_item, ".*dino.*","green_algae"),
+           diet_item = str_replace(diet_item, ".*microcystis.*", "cyanobacteria"),
+           diet_item = str_replace(diet_item, ".*chaeto.*","green_algae"),
+           diet_item = recode(diet_item, amdet = "amorphous_detritus", dia = "diatom",
[…]

### 2020-12-29 R/read_clean_temperature.R

@@ -1,0 +1,22 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+
+read_clean_temperature <- function() {
+
+  ####    import temperature data    ####
+    ann_stream_temps = readRDS(file = "./data/derived-data/annual_tempkt.rds") #annual mean boltzmann temperature
+  names(ann_stream_temps) =  tolower(gsub("(.*)_.*$", "\\1", names(ann_stream_temps))) #setting names of annual temps
+  ann_stream_temps = data.frame(t(ann_stream_temps)) %>% rownames_to_column("SITE") %>% 
+    dplyr::rename(tempkt =  starts_with('t')) %>% dplyr::mutate(SITE = factor(SITE, levels = stream_order)) #rename to annual temperature to 'tempkt'
+  stream_temps_list = readRDS(file = "./data/derived-data/stream_temps_full.rds") %>% rlist::list.subset(names(stream_order_list)) #interval temperature list
+  stream_temps_bound = stream_temps_list %>% bind_rows() %>% dplyr::mutate(SITE = factor(SITE, levels = stream_order)) #interval temperature df
+  
+  ####    End Temperature data import    ####
+  
+  return(list(stream_order = stream_order, stream_order_list = stream_order_list, stream_temp_labels = stream_temp_labels, 
+              ann_stream_temps = ann_stream_temps, stream_temps_list = stream_temps_list, stream_temps_bound = stream_temps_bound))
+
+}

### 2020-12-29 R/read_production.R

@@ -1,0 +1,99 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+
+read_production <- function() {
+
+  ####    full raw production, biomass, abundance import and clean    ####
+  prod_full_list = readRDS(file = "./data/derived-data/prod_full_fin.rds") %>%
+    #rename Tubificid update to Naidid to recognize taxon changes
+    purrr::map(~.x %>% purrr::map(~.x %>% dplyr::mutate(taxon_id = case_when(stringr::str_detect("Tubificid 1",taxon_id) ~ "Naidid 1",
+                                                                             stringr::str_detect("Tub. 2", taxon_id) ~ "Naidid 2", 
+                                                                             TRUE ~ taxon_id )))) %>%
+    rlist::list.subset(names(stream_order_list))
+  
+  spp_removals = list(hver = c('Homoptera', 'Lepidoptera', 'Limnophora.pupa', 'Midge.pupa', 
+                               'Slug', 'Snail.egg', 'Thrips'),
+                      st6 = c("Homoptera", "Limnophora.pupa", "Midge.pupa", "S..vittatum.pupa"), 
+                      st9 = c('Clinocera.pupa','Homoptera', 'Limnophora.pupa',
+                              'Limnophora.egg', 'Midge.pupa', 'S..vittatum.pupa', 'Slug',
+                              'Snail.egg','Thrips'),
+                      oh2 = c(),
+                      st7 = c(),
+                      st14 = c('Homoptera', 'S..vernum.pupa', 'S..vitattum.pupa', 'Spider..terr..','Thrips')) %>%
+    rlist::list.subset(names(stream_order_list))
+  
+  ## remove species with no 
+  
+  prod_full_list = purrr::map2(prod_full_list, spp_removals, function(prod, removals){
+    map(prod, ~.x %>% dplyr::filter(taxon_id %ni% removals))})
+    
+  ##  
+  int_spp_boots = prod_full_list %>% map(~rlist::list.subset(.,grepl("Pint", names(.))) %>% flatten_df)%>%
+    rlist::list.subset(names(stream_order_list))
+  
+  # stream community-level summaries 
+  # interval level community summary
+  int_comm_boots = map(prod_full_list, ~.x %>%
+                           map(~.x %>%
+                                 group_by(site_id, date_id, boot_id) %>% 
+                                 dplyr::select(-taxon_id) %>%
[…]

### 2020-12-29 R/summarise_production.R

@@ -1,0 +1,52 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param production_boots
+summarise_production <- function(production_boots) {
+  # stream community-level summaries 
+  # interval level community summary
+  int_comm_summary = production_boots[["int_comm_boots"]] %>%
+                             map(~.x %>%
+                             ungroup %>% group_by(site_id, date_id) %>%
+                             dplyr::summarise(across(matches('prod|bio|ind|pb'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                                               quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                                               quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                                               quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                                               quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                                               quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))) %>%
+    bind_rows
+  
+  # annual community summaries
+    ann_comm_summary = production_boots[["ann_comm_boots"]] %>%
+                             map( ~.x %>%
+                             ungroup %>% group_by(site_id) %>%
+                             dplyr::summarise(across(matches('prod|bio|ind|pb'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                                               quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                                               quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                                               quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                                               quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                                               quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))) %>%
+    bind_rows
+  
+  
+  # stream species summaries 
+   int_spp_summary = production_boots[["int_spp_summary"]] 
+    
+   ann_spp_summary = production_boots[["ann_spp_boots"]] %>%
+                           map(~.x %>%
+                           group_by(site_id, taxon_id) %>%
+                           dplyr::summarise(across(matches('prod|bio|ind|pb'), list(mean = ~mean(.x, na.rm = TRUE),
[…]

### 2020-12-29 R/summarise_seasonal_fluxes.R

@@ -1,0 +1,40 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param int_spp_boots
+summarise_seasonal_fluxes <- function(int_spp_boots =
+                                      production_boots[["int_spp_boots"]]) {
+# combine produciton into Jan-Apr, May-Aug, Sep-Dec
+  
+ season_spp_boots_full = future_map(int_spp_boots, ~.x %>%
+                           dplyr::mutate(month_id = lubridate::month(as.Date(date_id)),
+                                                       yr_third = case_when(month_id %in% 1:4 ~ "first",
+                                                                             month_id %in% 5:8 ~ "second",
+                                                                             month_id %in% 9:12 ~ "third"),
+                                         jul_day = julian(as.Date(date_id), origin = as.Date("2010-01-01")),
+                                         y_day = lubridate::yday(date_id)) %>%
+                           group_by(site_id, taxon_id, boot_id,  yr_third) %>%
+                           dplyr::summarise(prod_mg_m_int = sum(prod_mg_m_int),
+                                            start_date = as.Date(min(jul_day), origin = as.Date("2010-01-01")),
+                                            end_date = as.Date(max(y_day), origin = as.Date("2010-01-01")))) %>%
+                               rlist::list.subset(names(stream_order_list))
+ 
+ season_spp_summaries = season_spp_boots_full %>% 
+   map(~.x %>% ungroup %>%
+         group_by(site_id, taxon_id, start_date, end_date) %>%
+         dplyr::summarise(across(matches('prod'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                       quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                       quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                       quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                       quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                       quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))) %>% 
+  bind_rows %>% dplyr::mutate(site_id = factor(site_id, levels = stream_order))
+ 
+season_spp_boots_split = season_spp_boots_full %>%
+  map(~.x %>% ungroup %>% named_group_split(yr_third)) %>%
+  rlist::list.subset(names(stream_order_list))
+
[…]

### 2020-12-29 packages.R

@@ -1,0 +1,61 @@
+## library() calls go here
+###load packages and functions
+  if(!require("pacman")) install.packages("pacman")
+  library(pacman)
+  package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
+                    "RCurl","plyr","tidyverse","furrr", "fnmate", "rowr",
+                    "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
+                    "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
+                    "viridis", "broom","bbmle","ggthemes", "ggeffects",
+                    "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions")
+  p_load(char = package.list, install = TRUE, character.only = TRUE)
+  p_load_gh("jimjunker1/junkR")
+  p_load_gh("milesmcbain/dflow")
+  rm("package.list" )
+  # ins_julian_path = getURL("https://raw.githubusercontent.com/jimjunker1/secprod_workflow/master/len_freq/ins_julian_function.txt",ssl.verifypeer = FALSE)
+  # ins_julian <<- eval(parse(text = ins_julian_path))
+  #  len_freq_path = getURL("https://raw.githubusercontent.com/jimjunker1/secprod_workflow/master/len_freq/len_freq_function.R",ssl.verifypeer = FALSE)
+  #  len_freq <<- eval(parse(text = len_freq_path))
+  cbbPalette <<- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+  # load("./object_files/ocecolors.rda")
+  theme_mod = function(){theme_bw() %+replace% theme(panel.grid = element_blank())}
+  theme_black = function() {theme_bw() %+replace% theme(panel.background = element_rect(fill = 'transparent', colour = NA),panel.grid = element_blank(), axis.ticks = element_line(color = 'white'),
+                                                          axis.title = element_text(color = 'white'), axis.text = element_text(color = 'white'), plot.background =element_rect(fill = 'transparent', colour = NA),
[…]

### 2021-01-05 docs/ms/ms.RMD
updated and filxed issue with cbind.fill recognition with Roxygen

@@
 # Introduction
-
-Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@Brose2012][@walther2002][@Woodward_Dybkjær_Ólafsson_eta2010].
-The effects of this warming manifest through shifting species ranges [],
-
-The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged [@deRuiter1995][@thompson2012].
-Specifically, warming can directly alter , is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018].
-
+<!--- warming and effects in food webs --->
+Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
+While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
+This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, such as shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].
+Identifying general effects of temperature is further complicated by the fact that natural variation in temperature often exists concurrently with other environmental gradients (e.g., light, water, and/or nutrient availability).
+Understanding the effects of temperature...alterations to ecosystem function and the services they provide.
+<!--- Speeding up of food web: Species levels--->
+The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged (e.g., food webs; [@deruiter1995][@thompson2012].
+Characteristics The magnitude The response of ecosystem function to environmental drivers and variability <!---Ecosystem functionality---> is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018].
+The complexity in responses to warming arise from
+<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
 Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (~5 - 28$^\circ$C).

### 2021-01-05 R/Lorenz.R

@@ -54,11 +54,11 @@ lcs_plot = function(curves){
 
 #====Example====
 #the input must be a list of observed abundance/frequency vectors corresponding to multiple assemblages
-com_1 = c(10, 2)
-com_2 = c(10, 10, 2, 1, 1)
-ps = list(com_1=com_1, com_2 = com_2)
-result_table = lcs_table(ps)
-lcs_plot(result_table)
+# com_1 = c(10, 2)
+# com_2 = c(10, 10, 2, 1, 1)
+# ps = list(com_1=com_1, com_2 = com_2)
+# result_table = lcs_table(ps)
+# lcs_plot(result_table)
 
 
 #' This code is modified from Chao and Ricotta 2019 (Ecology)

### 2021-01-05 R/create_gut_dists.R

@@ -1,0 +1,15 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param gut_lists
+create_gut_dists <- function(gut_lists = gut_lists[['diet_list']]) {
+
+  gut_matrices = gut_lists[[1]] %>% map(~.x %>% 
+                                     dplyr::select(site, date, taxon, diet_item, rel_area) %>%
+                                     group_by(site,date, taxon) %>%
+                                     pivot_wider(names_from = 'diet_item',values_from = 'rel_area')
+                                     )
+
+}

### 2021-01-05 R/create_seasonal_matrices.R

@@ -1,0 +1,70 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param blank_diet_matrices
+##' @param gut_lists
+create_seasonal_matrices <- function(blank_diet_matrices, gut_lists) {
+  ## ++++ Helper functions ++++ ##
+  
+  split_diets <- function(x){
+    
+    if(any(is.na(x$date))){
+      diet_list = vector('list',3L)
+      for(i in 1:3){
+        diet_list[[i]] <- x
+      }
+      return(diet_list)
+    } else {
+      diet_list = x %>%
+        dplyr::mutate(month_id = match(month_id, month.abb),
+                      yr_third = case_when(month_id %in% 1:4 ~ "first",
+                                           month_id %in% 5:8 ~ "second",
+                                           month_id %in% 9:12 ~ "third")) %>%
+        ungroup %>% group_split(yr_third)
+      
+      if(length(diet_list) < 3){
+        list.length = length(diet_list)
+        to_add = 3-list.length
+        for(i in 1:to_add){
+          diet_list[[(i+list.length)]] <- x %>% 
+            group_by(site, date, taxon, diet_item) %>% 
+            dplyr::summarise(rel_area = mean(rel_area))
+        }
+      }
+      
+      return(diet_list)
+    }
+  }
+  
+  merge_matrices = function(diet,mat,...){
+    tax_diet = diet %>%
+      group_by(taxon, diet_item) %>%
+      dplyr::summarise(rel_area = mean(rel_area))
+    
+    for(i in 1:nrow(tax_diet)){
+      taxon = tax_diet$taxon[i]
+      taxa_list = agrep(taxon, colnames(mat))
+      diet_item = tax_diet$diet_item[i]
+      mat[rownames(mat) %in% diet_item, taxa_list] <- tax_diet$rel_area[i]
+    }
+    return(mat)
+  }
+  
+  ## ++++ End Helper functions ++++ ##
+  diets = gut_lists[['diet_list']]
+  diet_splits = diets %>% map(~split_diets(.x))
+  
+  ## combine the blank matrices and the seasonal matrices
+  filled_matrices = vector('list', length = length(diet_splits))
+  filled_matrices = filled_matrices %>% setNames(., nm = levels(stream_order)) %>% rlist::list.subset(names(stream_order_list))
[…]

### 2021-01-05 R/estimate_flux.R

@@ -5,8 +5,23 @@
 ##' @title
 ##' @param diet_matrices
 ##' @param seasonal_fluxes
-estimate_flux <- function(diet_matrices, seasonal_fluxes) {
- 
+estimate_flux <- function(diet_matrices, seasonal_fluxes = seasonal_fluxes[["seasonal_spp_boots_split"]]) {
+  ## ++++ Helper functions ++++ ##
+  
+  boot_flux_function = function(mat_list, losses, resources_mat, efficiences_vct, NPE,...){
+    
+    
+    colnames(mat_list) %>% tibble %>%
+      setNames(., nm = 'matrix_name') %>%
+      dplyr::mutate(efficiencies = dplyr::recode(matrix_name, !!!resource_keyval),
+                    efficiencies = tidyr::replace_na(efficiencies, 0.7)) -> matrix_effiencies
+    boots = mat_list
+    
+  }
+  ## ++++ End Helper functions ++++ ##
+   prod_list_split = 
+  
+  
   # resource date frame with efficiences
   diet_item = list("amorphous_detritus",
                 "cyanobacteria",
@@ -36,15 +51,6 @@ estimate_flux <- function(diet_matrices, seasonal_fluxes) {
    NPE_dist.pars = rriskDistributions::get.beta.par(p = c(0.025,0.5,0.975),q = c(0.4,0.45,0.5), show.output = FALSE, plot = FALSE)
    NPE = rbeta(1e3, shape1 = NPE_dist.pars[1], shape2 = NPE_dist.pars[2])
  # combined the production from Jan-Apr, May-Aug, Sep-Dec
-  boot_flux_function = function(mat_list, losses,resources_mat, efficiences_vct, NPE,...){
-     
-     
-    colnames(mat_list) %>% tibble %>%
-      setNames(., nm = 'matrix_name') %>%
-      dplyr::mutate(efficiencies = dplyr::recode(matrix_name, !!!resource_keyval),
-                    efficiencies = tidyr::replace_na(efficiencies, 0.7)) -> matrix_effiencies
-    boots = mat_list
-    
-  }
+
 
 }

### 2021-01-05 R/read_clean_guts.R

@@ -10,11 +10,11 @@ read_clean_guts <- function() {
   ##read in gut data
   hver_path = "./data/raw-data/gut_data/hver/"
   hver_gut_paths = as.list(dir(hver_path, pattern ="full.csv", full.names = FALSE, include.dirs = FALSE, recursive = TRUE))
-  hver_gut_files= suppressMessages(map(hver_gut_paths, ~read_csv(file = paste0(hver_path, .x))))
-  hver_gut_files = map(hver_gut_files, function(x){ if(dim(x)[2] > 2){
+  hver_gut_files= suppressMessages(purrr::map(hver_gut_paths, ~read_csv(file = paste0(hver_path, .x))))
+  hver_gut_files = purrr::map(hver_gut_files, function(x){ if(dim(x)[2] > 2){
     x = x[,-1];return(x)} else{return(x)}})
   
-  hver_gut_columns = map(hver_gut_paths, ~.x %>%
+  hver_gut_columns = purrr::map(hver_gut_paths, ~.x %>%
                            str_replace(.,pattern = "IMG_", "IMG") %>%
                            strsplit(., '[/_.][[:space:]]*') %>%
                            as.data.frame() %>%
@@ -23,7 +23,7 @@ read_clean_guts <- function() {
   hver_gut_columns = bind_rows(hver_gut_columns)
   hver_gut_columns = split(hver_gut_columns, seq(nrow(hver_gut_columns)))
   hver_gut_contents = map2(hver_gut_columns, hver_gut_files, ~.x %>%
-                             rowr::cbind.fill(.y))
+                            junkR::cbind.fill(.y))
   
   names = c("site","date","taxon","pic","diet_item","area")
   hver_gut_contents = lapply(hver_gut_contents, setNames, names)
@@ -39,11 +39,12 @@ read_clean_guts <- function() {
            diet_item = str_replace(diet_item, ".*chaeto.*","green_algae"),
            diet_item = recode(diet_item, amdet = "amorphous_detritus", dia = "diatom",
                               dino = "dinoflaggelate", fila = "filamentous")) %>%
+    tidyr::complete(diet_item, nesting(site, date, taxon, pic), fill = list(area = 0)) %>%
     group_by(site,date,taxon,diet_item) %>%
     dplyr::summarise(item_area = sum(area)) %>%
     ungroup() %>% group_by(site, date, taxon) %>%
     dplyr::mutate(rel_area = item_area/sum(item_area), 
-                  month_id = stringr::str_extract(date, "\\D{3,4}"))
[…]

### 2021-01-05 R/split_seasonal_fluxes.R

@@ -1,0 +1,14 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param season_spp_split
+split_seasonal_fluxes <- function(season_spp_split =
+                                  seasonal_fluxes[["season_spp_boots_split"]]) {
+
+ flux_boot_split = map(season_spp_split, ~.x %>% map(~.x %>% group_split(boot_id)))
+ 
+ return(flux_boot_split)
+ 
+}

### 2021-01-09 docs/ms/ms.RMD
modeled diets, moving to create model matrices to complete full flux boot strapped estimates

@@
 <!--- warming and effects in food webs --->
-Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
-While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
-This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, such as shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].
-Identifying general effects of temperature is further complicated by the fact that natural variation in temperature often exists concurrently with other environmental gradients (e.g., light, water, and/or nutrient availability).
+Temperature is an important abiotic variable with increasing relevance as increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
+Temperature'smak effect on ecosystem manifest through complex of direct and indirect pathways such as, shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
+This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, s Identifying general effects of temperature is further complicated by the fact that natural variation in temperature often exists concurrently with other environmental gradients (e.g., light, water, and/or nutrient availability).
 Understanding the effects of temperature...alterations to ecosystem function and the services they provide.

### 2021-01-09 R/create_diet_df.R

@@ -1,0 +1,29 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param gut_lists
+##' @param spp_list
+##' @param diet_model
+create_diet_df <- function(gut_lists, spp_list =
+                           production_summaries[["production_spp_list"]],
+                           diet_model = modeled_diets[["diet_model"]]) {
+
+  # period list 
+  period_list = list(c('first','second','third'))
+  
+  spp_list = spp_list %>% rlist::list.subset(names(stream_order_list))
+  
+  resource_list = gut_lists[["resource_list"]] %>% rlist::list.subset(names(stream_order_list))
+  
+  stream_diet_dfs = pmap(list(spp_list, resource_list, period_list), ~expand.grid(taxon = unlist(..1),
+                                                                                  diet_item = unlist(..2), 
+                                                                                  yr_third = unlist(..3),
+                                                                                  KEEP.OUT.ATTRS = FALSE,
+                                                                                  stringsAsFactors = FALSE) %>%
+                           dplyr::mutate(value = NA_real_))
+  
+  return(stream_diet_dfs = stream_diet_dfs)
+  
+}

### 2021-01-09 R/model_diet_props.R

@@ -1,0 +1,55 @@
+##' This code builds a multilevel model for diet proportions across sites. It allows for species- and period-level
+##' modifications. To allow for uncertainty to be propagated through to OM flux estimates, it employs a hierarchical 
+##' bayesian model in brms
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param gut_lists
+model_diet_props <- function(gut_lists) {
+  
+  ## ++++ Helper functions ++++ ##
+  convert_month_num <- function(x){
+    x %>% dplyr::mutate(month_id = match(month_id, month.abb),
+                        yr_third = case_when(month_id %in% 1:4 ~ 'first',
+                                             month_id %in% 5:8 ~ 'second',
+                                             month_id %in% 9:12 ~ 'third'))
+  }
+
+  ## ++++ End Helper functions ++++ ##
+  
+    # convert gut lists into wide format for each site
+  wide_gut_lists = gut_lists[["diet_list"]] %>% 
+    map(~convert_month_num(.x)) %>%
+    map(~.x %>% ungroup %>% 
+          select(site, yr_third, taxon, id, diet_item, rel_area) %>%
+          group_by(site, yr_third, id, taxon) %>% 
+          pivot_wider(names_from = 'diet_item', values_from = 'rel_area', values_fn = max)) %>%
+    rlist::list.subset(names(stream_order_list))
+  
+  wide_guts_lists_nopred = wide_gut_lists %>%
+    map(~.x %>%
+          dplyr::filter(animal <= 0.99)) %>%
+    # map( ~ if(length(.x) == 10){.x %>% dplyr::mutate(green_algae = NA_real_)} else{.x = .x}) %>% 
+    bind_rows %>%
+    ungroup %>% select(-id) %>% dplyr::filter(site %ni% c('st7','oh2'))
+  
+  diet_meta = wide_guts_lists_nopred %>% ungroup %>% select(site, yr_third, taxon)
+  diet_props = wide_guts_lists_nopred %>% ungroup %>% select(-site:-taxon) %>% as.matrix
+  apply(diet_props,1,sum)
+  
+  diet_df = diet_meta;diet_df$props = diet_props
+  
+  #### full brm diet model ###
+  model_formula <- brms::bf(props ~ site + yr_third + taxon)
+  model_prior = brms::get_prior(model_formula, 
+                    data = diet_df,
+                    family = dirichlet())
+  conflicted:::conflicts_reset()
+    set.seed(123)
[…]

### 2021-01-09 R/plan.R

@@ -19,7 +19,17 @@ the_plan <-
   # gut_df = create_gut_dists(gut_lists),
   
   # gut_summaries = summarise_guts(gut_df),
+  # 
+  modeled_diets = model_diet_props(gut_lists),
   
+  # re-establish conflicts
+  conflicted:::conflicts_register(),
+  
+  #create full data frame of site x yr_third x taxon for diet proportions
+  full_diet_df = create_diet_df(gut_lists, production_summaries[["production_spp_list"]]),
+  # predict diets 
+  predicted_diets = predict_diets(full_diet_df, modeled_diets),
+  #create blank diet matrices to fill in  
   blank_diet_matrices = create_diet_matrices(gut_lists, production_summaries[["production_spp_list"]]),
   
   seasonal_diet_matrices = create_seasonal_matrices(blank_diet_matrices, gut_lists),

### 2021-01-09 R/predict_diets.R

@@ -1,0 +1,14 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param full_diet_df
+##' @param modeled_diets
+predict_diets <- function(full_diet_df, modeled_diets) {
+
+  diet_model = modeled_diets[["diet_model"]]
+  
+  model_predict = predict(diet_model, newdata = bind_rows(full_diet_df))
+
+}

### 2021-01-09 R/read_clean_guts.R

@@ -6,6 +6,33 @@
 
 read_clean_guts <- function() {
 
+  #####    Create taxon rename lists   #####
+  
+  old_names <- list(c("Csylvestris"),
+                    c("Radix", "RadixBalthica"),
+                    c("Eukie","Eminor"),
+                    c("Ooblidens"),
+                    c("Tany"),
+                    c("Theinem"),
+                    c("Simuliumvittatum", "Svitt"),
+                    c("Oligo"), 
+                    c("Ofridgidus"),
+                    c("Rhecricotopus","Rheocricotpus"),
+                    c("Orthoclad", "Odentiformes"))
+  
+  new_names <- list("Cricotopus sylvestris",
+                    "Radix balthica",
+                    "Eukiefferiella",
+                    "Orthocladius oblidens",
+                    "Macropelopia",
+                    "Thienemanniella sp.",
+                    "Simulium vittatum",
+                    "Lumbricidae",
+                    "Orthocladius fridgidus",
+                    "Rheocricotopus",
+                    "Orthocladius")
+  
+  taxon_name_keyval = setNames(rep(new_names, lengths(old_names)), unlist(old_names))
   #####    Gut Content Data Import ####
   ##read in gut data
   hver_path = "./data/raw-data/gut_data/hver/"
@@ -18,14 +45,14 @@ read_clean_guts <- function() {
                            str_replace(.,pattern = "IMG_", "IMG") %>%
                            strsplit(., '[/_.][[:space:]]*') %>%
                            as.data.frame() %>%
-                           .[c(2,4,5,7),] %>%
-                           set_names(c("site","date","taxon","pic")))
+                           .[c(2,4:7),] %>%
+                           set_names(c("site","date","taxon","id", "pic")))
   hver_gut_columns = bind_rows(hver_gut_columns)
   hver_gut_columns = split(hver_gut_columns, seq(nrow(hver_gut_columns)))
   hver_gut_contents = map2(hver_gut_columns, hver_gut_files, ~.x %>%
-                            junkR::cbind.fill(.y))
+                            junkR::cbind_fill(.y))
   
-  names = c("site","date","taxon","pic","diet_item","area")
+  names = c("site","date","taxon","id", "pic", "diet_item","area")
[…]

### 2021-01-09 packages.R

@@ -3,15 +3,17 @@
   if(!require("pacman")) install.packages("pacman")
   library(pacman)
   package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
-                    "RCurl","plyr","tidyverse","furrr", "fnmate",
+                    "RCurl","plyr","tidyverse","furrr", "fnmate", 
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
                     "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
                     "viridis", "broom","bbmle","ggthemes", "ggeffects",
-                    "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions")
+                    "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
+                    "rstan", "brms", "tidybayes", "parallel")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
   # p_load_gh("jimjunker1/junkR")
   devtools::install_github("jimjunker1/junkR")
   library(junkR)
+  conflict_prefer('count', 'dplyr')
   p_load_gh("milesmcbain/dflow")
   rm("package.list" )
   # len <<- function(data)
@@ -43,50 +45,30 @@
   #   do.call(cbind, lapply(nm, function (x)
   #     rbind(x, matrix(, n-nrow(x), ncol(x)))))
   # }
-  # ins_julian_path = getURL("https://raw.githubusercontent.com/jimjunker1/secprod_workflow/master/len_freq/ins_julian_function.txt",ssl.verifypeer = FALSE)
-  # ins_julian <<- eval(parse(text = ins_julian_path))
-  #  len_freq_path = getURL("https://raw.githubusercontent.com/jimjunker1/secprod_workflow/master/len_freq/len_freq_function.R",ssl.verifypeer = FALSE)
-  #  len_freq <<- eval(parse(text = len_freq_path))
-  cbbPalette <<- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+  cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
   # load("./object_files/ocecolors.rda")
   theme_mod = function(){theme_bw() %+replace% theme(panel.grid = element_blank())}
[…]

### 2021-02-04 docs/ms/ms.RMD
flux is finalized. Moving on the figure creation.

@@
 We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N  021$^\circ$ 18'W) that varied in mean annual temperature.
-Hengill is characterized by indirect geothermal heating of groundwater [@arnason_hengill_1969], leading to a natural variability in water temperatures (4.5–54.0 $^\circ$C), but similar solute chemistries [@friberg_relationships_2009].
-These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman_climate_2014; @nelson_experimental_2017].
+Hengill is characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5–54.0 $^\circ$C), but similar solute chemistries [@friberg_relationships_2009].
+These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014][@nelson2017a].
 We selected streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers.
@@
 We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous study (*n* = 6 streams).
-The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental manipulation [see @nelson_experimental_2017; -@nelson_shifts_2017].
-Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson_experimental_2017; @hood_increased_2018].
+The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental manipulation [see @nelson2017][@nelson2017a].
+Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018].
 We collected fiver Surber samples (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream.
@@
 Subsamples were scaled to the rest of the sample assuming similar abundance and body size distributions.
-Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson_black_1977; @merritt_introduction_2008; @andersen_chironomidae_2013].
+Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson1977][@merritt2008][@andersen2013].
 Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
@@
 Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500).
-For taxa which exhibit synchronous growth and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty using a bootstrap technique similar to that described in Benke and Huryn [-@benke_secondary_2017].
+For taxa which exhibit synchronous growth and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017].
 Individual Lengths were converted to mg AFDM using published length-mass regression cited above and size-frequency histograms were visually inspected for directional changes in body size through time.
@@
 
-## Gut Content Analysis
+## Diet analysis
 
+**Come back and confirm this section**
 Macroinvertebrate diets were quantified for dominant taxa in each stream.
@@
 For small-bodied taxa, we combined multiple individuals (*n* = 3–5) to ensure samples contained enough material for quantification.
-We used methods outlined in Rosi-Marshall [-@Rosi-Marshall_Wellard Kelly_Hall_Vallis2016] to remove gut tracts and prepare gut content slides.
+We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content slides.
 Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds.
@@
 We took 5–10 random photographs under 200–400x magnification, depending on the density of particles, using a digital camera mounted on a compound microscope.
-From these photographs we identified all particles within each field and measured the relative area of particles using image analysis software [@schindelin_fiji_2012].
+From these photographs we identified all particles within each field and measured the relative area of particles using image analysis software [@schindelin2012].
 We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular plants (bryophytes), and animal material.
@@
 
+To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a hierarchical multivariate model [@fordyce2011].
+Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
+$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$
+$$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$
+where, $\overrightarrow{p_i}$, is a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
+We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$,
+$$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$
+$$\alpha \sim Uniform(0,\textit{c})$$
+where, $\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value.
+**add in site-level model parameter and model fitting language**.
+Models were fit in Stan with the 'brms' package in R [@burkner2017].
+For non-dominant taxa, diet proportions were imputed from the hierarchical model by resampling from posterior distributions.
+Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.
+
 ## Organic Matter Consumption Estimates
 
-Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@Benke_Wallace1980].
-Taxon-specific secondary production estimates were combined with measured diet proportions, diet-specific assimilation efficiencies, AE[i], and assumed net production efficiencies, NPE, to estimate consumption of organic matter.
-For each food category, i, diet proportions were multiplied by the gross growth efficiency (GGE[i] = AE[i] * NPE) to calculate the relative production attributable to each food category.
-The relative production from each food type was then multiplied by the interval-level production and finally divided by GGE[i] to estimate consumption of organic matter from each food category by a consumer [@benke_trophic_1980].
+Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980].
+Taxon-specific secondary production estimates were combined with diet proportions, diet-specific assimilation efficiencies, $AE_{i}$, and assumed net production efficiencies, $NPE$, to estimate consumption of organic matter.
+For each food category, $\textit{i}$, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food category.
+The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic matter from each food category by a consumer [@benke1980].
 Consumption was calculated for each taxon across sampling intervals (typically ~1 month).
 Total interval consumption was calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and inte(rvals.
-Variability in consumption estimates was estimated through bootstrapping, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and the consumption estimated using the TBP method.
-Variability in AE[i] was incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36), filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@Welch1968][@Cross_Wallace_Rosemond2007][@Cross_Baxter_Donner_et al.2011][@Benke_Wallace1980][@Benke1997].
-Variability in NPE was incorporated by resampling values from an assumed beta distribution with median NPE = 0.45 (95% PI = 0.4-0.5).
-Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@Belgorodski_Greiner_Tolksdorf_Schueller2017].
+Variability in consumption estimates was estimated through a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with the TBP method using simulated diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency.
+Variability in $AE_{i}$ was incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36), filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968][@cross2007][@cross2011][@benke1980][@benke1997].
+Variability in $NPE$ was incorporated by resampling values from an assumed beta distribution with median $NPE$ = 0.45 (95% PI = 0.4-0.5).
+Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@belgorodski2017].
 
@@
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@Lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
 p_S$.
 The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
-In a community with perfectly equal distribution of OM consumption, the Lorenz curve is simply a straight diagonal line.
-Deviation from perfect equality was calculated as the Gini coefficient [@Gini1921], normalized for differences in $S$ among streams, $G^*$ [@Solomon1979][@Chao_Ricotta2019]:
+In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is simply a straight diagonal line.
+Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1979][@chao2019]:
 $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
-### Distribution along species trait axes
+### Distribution along species' trait axes
 
-To explore how
+We were interested in how OM fluxes were distributed (random vs. non-random) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass), to explore
 
@@
 
+# Acknowledgements
+
+Jeff Wesner and Abe Kanz for code sharing and discussions on modeling diet proportions.
+
 \newpage

### 2021-02-04 R/Lorenz.R

@@ -16,8 +16,9 @@ library(ggplot2)
 #'lcs_table is used to compute the values of each Lorenz curve
 #' @param ps is a list of observed abundance/frequency vectors corresponding to multiple assemblages. 
 #' @return the values for plotting the Lorenz curve of each assemblage.
-lcs_table = function(ps){
+lcs_table = function(ps, resp_var = NULL, sort_var = NULL,...){
   lc = function(p,j){
+    if(is.vector(p)){
     p = p[p>0]
     s = length(p)
     p = p/sum(p)
@@ -25,7 +26,17 @@ lcs_table = function(ps){
     out_x = sapply(1:s, function(i){i/s})
     out_y = sapply(1:s, function(i){sum(p[1:i])})
     out = data.frame(x = c(0,out_x),y = c(0,out_y),source = names(ps)[j])
-  }
+    } else{ p <- data.frame(p)
+    p <- p[resp_var > 0,]
+    s <- nrow(p)
+    resp_string = paste0("relative_",resp_var)
+    # resp_var = as.name(resp_var)
+    p[[resp_string]] <- with(p, resp_var/sum(resp_var)) -> p.rel
+    p.rel = p.rel %>% dplyr::arrange(sort_var)
+    out_x <- sapply(1:s, function(i){i/s})
+    out_y <- sapply(1:s, function(i){sum(p.rel[1:i,resp_var])})
+    out <- data.frame(x = c(0,out_x), y = c(0,out_y), source = names(ps)[j])
+  }};debugonce(lc)
   curves = lapply(1:length(ps),function(j){lc(ps[[j]],j)})
   curves = do.call(rbind,curves)
 }
@@ -63,11 +74,11 @@ lcs_plot = function(curves){
 
 #' This code is modified from Chao and Ricotta 2019 (Ecology)
 #' source: https://github.com/AnneChao/Evenness/blob/master/Evenness.R
-#' Gini_even computes the two Gini evenness indices mentioned in the Discussion section and in Appendix S4.
+#' gini_even computes the two Gini evenness indices mentioned in the Discussion section and in Appendix S4.
 #' 
 #' @param x is an observed species abundance or frequency or production vector. 
 #' @return a vector of two Gini evenness indices (non-normalized and normalizd).
-Gini_even <- function(x){
+gini_even <- function(x){
   x <- sort(x[x>0], decreasing = T)/sum(x)
   S <- length(x)
   ipi <- sapply(1:S, function(i) i*x[i]) %>% sum

### 2021-02-04 R/create_diet_matrices.R

@@ -3,33 +3,40 @@
 ##' .. content for \details{} ..
 ##'
 ##' @title
-##' @param gut_lists
-##' @param spp_list
-create_diet_matrices <- function(gut_lists, spp_list = production_summaries[["production_spp_list"]]) {
-## ++++ Helper functions ++++ ##
-  create_matrix = function(spp_list, resource_list){
-    # create three matrices for 1:4. 5:8, 9:12 months
-    spp_matrix = matrix(0, nrow = nrow(spp_list), ncol = nrow(spp_list))
-    rownames(spp_matrix) <- colnames(spp_matrix) <- unlist(spp_list)
-    res_matrix = matrix(0, nrow = length(resource_list), ncol = length(resource_list))
-    rownames(res_matrix) <- colnames(res_matrix) <- unlist(resource_list)
-    
-    # create combined lists
-    full_matrix = as.matrix(gtools::smartbind(spp_matrix, res_matrix, fill = 0))
-    rownames(full_matrix)<- colnames(full_matrix)
+##' @param diet_df
+##' @param seasonal_boot_list
+##' 
+create_diet_matrices <- function(diet_df = modeled_diets[['diet_seasonal_boot_split']], seasonal_boot_split) {
+ 
+  ## ++++ Helper functions ++++ ##
+  
+  create_matrix = function(single_diet_df, name_order){
+    # create matrix from full diet proportion data.frame
+    # this function takes a single_diet_df, so it must be mapped
+    # if converting a list
+    spp_names = unique(single_diet_df$taxon)
+    spp_names = spp_names[spp_names %in% name_order]
+    res_names = unique(single_diet_df$diet_item)
+    full_names = c(spp_names, res_names)
+    full_long_df = expand.grid(taxon = full_names, diet_item = full_names)
+    res_long_df = single_diet_df %>% select(taxon, diet_item, rel_area)
+    filled_long_df = join(full_long_df, res_long_df) %>% dplyr::mutate(rel_area = tidyr::replace_na(rel_area, 0))
+    # create matrix from long data frame
+    full_matrix = filled_long_df %>% pivot_wider(names_from = 'taxon', values_from = 'rel_area', values_fn = mean) %>%
+      column_to_rownames('diet_item') %>% as.matrix
+
     return(full_matrix)
   }
   
-  
-## ++++ End Helper functions ++++ ##
-  
[…]

### 2021-02-04 R/estimate_flux.R

@@ -3,24 +3,34 @@
 ##' .. content for \details{} ..
 ##'
 ##' @title
-##' @param diet_matrices
+##' @param seasonal_diets
 ##' @param seasonal_fluxes
-estimate_flux <- function(diet_matrices, seasonal_fluxes = seasonal_fluxes[["seasonal_spp_boots_split"]]) {
+estimate_flux <- function(seasonal_diets = diet_matrices, seasonal_fluxes = seasonal_boot_split) {
   ## ++++ Helper functions ++++ ##
+  prod_to_met <- function(production, NPE,...){
+    production %>% 
+      dplyr::mutate(across(contains("prod"), list(loss = ~.x/NPE), .names = "{.fn}")) %>% 
+      dplyr::select(taxon_id, loss) %>% tibble::deframe() -> losses
+  }
   
-  boot_flux_function = function(mat_list, losses, resources_mat, efficiences_vct, NPE,...){
+  boot_flux_function = function(mat, losses, resource_effs_vct,...){
     
-    
-    colnames(mat_list) %>% tibble %>%
+    colnames(mat) %>% tibble %>%
       setNames(., nm = 'matrix_name') %>%
-      dplyr::mutate(efficiencies = dplyr::recode(matrix_name, !!!resource_keyval),
-                    efficiencies = tidyr::replace_na(efficiencies, 0.7)) -> matrix_effiencies
-    boots = mat_list
+      dplyr::mutate(efficiencies = dplyr::recode(matrix_name, !!!resource_effs_vct, .default = 0.7)) -> x 
+   
+      setNames(x$efficiencies, nm = x$matrix_name)-> matrix_efficiencies
+      
+      resource_losses = setNames(rep(0, length(resource_effs_vct)), nm = names(resource_effs_vct))
+      losses = c(losses,resource_losses)
+    
+    flux_obj = fluxing(mat = mat, losses = losses, efficiencies =  matrix_efficiencies,
+                                bioms.losses = FALSE, bioms.prefs = FALSE, ef.level = 'prey', method = 'tbp')
+    return(flux_obj)
     
   }
   ## ++++ End Helper functions ++++ ##
-   prod_list_split = 
-  
+
   
   # resource date frame with efficiences
   diet_item = list("amorphous_detritus",
[…]

### 2021-02-04 R/model_diet_props.R

@@ -5,51 +5,149 @@
 ##' .. content for \details{} ..
 ##'
 ##' @title
-##' @param gut_lists
-model_diet_props <- function(gut_lists) {
+##' @param full_diet_df
+model_diet_props <- function(full_diet_df = full_diet_df, model = "dirichlet",...) {
   
   ## ++++ Helper functions ++++ ##
-  convert_month_num <- function(x){
-    x %>% dplyr::mutate(month_id = match(month_id, month.abb),
-                        yr_third = case_when(month_id %in% 1:4 ~ 'first',
-                                             month_id %in% 5:8 ~ 'second',
-                                             month_id %in% 9:12 ~ 'third'))
-  }
-
+  expand.grid.df <- function(...) Reduce(function(...) merge(..., by=NULL), list(...))
   ## ++++ End Helper functions ++++ ##
-  
+  full_diet_count_df = full_diet_df %>% dplyr::mutate(rel_area = round(rel_area*1000,0))
+  full_diet_prop_df = full_diet_df
     # convert gut lists into wide format for each site
-  wide_gut_lists = gut_lists[["diet_list"]] %>% 
-    map(~convert_month_num(.x)) %>%
-    map(~.x %>% ungroup %>% 
+  wide_gut_lists = full_diet_df %>% 
           select(site, yr_third, taxon, id, diet_item, rel_area) %>%
           group_by(site, yr_third, id, taxon) %>% 
-          pivot_wider(names_from = 'diet_item', values_from = 'rel_area', values_fn = max)) %>%
+          pivot_wider(names_from = 'diet_item', values_from = 'rel_area') %>%
+  named_group_split(site) %>%
     rlist::list.subset(names(stream_order_list))
   
+  # # remove predators from lists
+  # # name predators 
+  predator_lists = list(hver = c("Limnophora riparia"),
+                        st6 = c("Limnophora riparia", "Antocha sp.", "Ephydridae.sp.", "Clinocera stagnalis"),
+                        st9 = c("Limnophora riparia", "Antocha sp.", "Ephydridae.sp.", "Clinocera stagnalis"),
+                        st7 = c("Limnophora riparia", "Macropelopia", "Dicranota", "Clinocera stagnalis"),
+                        oh2 = c("Limnophora riparia", "Macropelopia", "Dicranota", "Clinocera stagnalis"),
+                        st14 = c("Limnophora riparia", "Antocha sp.")) %>%
[…]

### 2021-02-04 R/read_clean_guts.R

@@ -9,28 +9,56 @@ read_clean_guts <- function() {
   #####    Create taxon rename lists   #####
   
   old_names <- list(c("Csylvestris"),
-                    c("Radix", "RadixBalthica"),
-                    c("Eukie","Eminor"),
+                    c("Radix", "RadixBalthica","Radix.Balthica","Radix.balthica"),
+                    c("Eukie","Eminor","Eukiefferiella sp."),
                     c("Ooblidens"),
                     c("Tany"),
-                    c("Theinem"),
-                    c("Simuliumvittatum", "Svitt"),
-                    c("Oligo"), 
-                    c("Ofridgidus"),
-                    c("Rhecricotopus","Rheocricotpus"),
-                    c("Orthoclad", "Odentiformes"))
+                    c("Theinem","Theinemanniella"),
+                    c("Simuliumvittatum", "Svitt", "Simulium.vittatum"),
+                    c("Oligo", "Lumb 3","Lumb"), 
+                    c("Ofridgidus", "Orthocladius fridgidus","Orthocladius.fridgidus"),
+                    c("Rhecricotopus","Rheocricotpus","Rheocricotopus.effusus","Rheocricotopus"),
+                    c("Orthoclad"),
+                    c("Ceratopegonid"),
+                    c("Chaetocladius dentiforceps","Odentiformes"),
+                    c("Diamesa.bohemani_zernyi"),
+                    c("Diamesa.bertrami"),
+                    c("Eukiefferiella.claripennis"),
+                    c("Eukiefferiella.minor","Eukiefferiella.mino"),
+                    c("Micropsectra", "Micropsectra.sp."),
+                    c("Parochlus"),
+                    c("Potomaphylax.cingulatus"),
+                    c("Prosimulium","Prosimulium.ursinum"),
+                    c("Simulium.vernum"),
+                    c("Sperchon"),
+                    c("Oligochaeta.A"),
+                    c("Clinocera"))
   
   new_names <- list("Cricotopus sylvestris",
                     "Radix balthica",
-                    "Eukiefferiella",
+                    "Eukiefferiella sp.",
                     "Orthocladius oblidens",
                     "Macropelopia",
                     "Thienemanniella sp.",
                     "Simulium vittatum",
                     "Lumbricidae",
-                    "Orthocladius fridgidus",
-                    "Rheocricotopus",
-                    "Orthocladius")
[…]

### 2021-02-04 R/split_seasonal_diets.R

@@ -1,0 +1,44 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param gut_lists
+split_seasonal_diets <- function(gut_lists) {
+  ## ++++ Helper functions ++++ ##
+  
+  split_diets <- function(x){
+    
+    if(any(is.na(x$date))){
+      diet_list = vector('list',3L)
+      for(i in 1:3){
+        diet_list[[i]] <- x
+      }
+      return(diet_list)
+    } else {
+      diet_list = x %>%
+        dplyr::mutate(month_id = match(month_id, month.abb),
+                      yr_third = case_when(month_id %in% 1:4 ~ "first",
+                                           month_id %in% 5:8 ~ "second",
+                                           month_id %in% 9:12 ~ "third")) %>%
+        ungroup %>% group_split(yr_third)
+      
+      if(length(diet_list) < 3){
+        list.length = length(diet_list)
+        to_add = 3-list.length
+        for(i in 1:to_add){
+          diet_list[[(i+list.length)]] <- x %>% 
+            group_by(site, date, taxon, diet_item) %>% 
+            dplyr::summarise(rel_area = NA)
+        }
+      }
+      
+      return(diet_list)
+    }
+  }
+  ## ++++ End Helper functions ++++ ##
+  debugonce(split_diets)
+  diets = gut_lists[['diet_list']]
+  diet_splits = diets %>% map(~split_diets(.x))
+
+}

### 2021-02-04 R/split_seasonal_production.R

@@ -1,0 +1,14 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param season_spp_split
+split_seasonal_production <- function(season_spp_split =
+                                  seasonal_production[["season_spp_boots_split"]]) {
+
+ prod_boot_split = map(season_spp_split, ~.x %>% map(~.x %>% group_split(boot_id)))
+ 
+ return(prod_boot_split)
+ 
+}

### 2021-02-04 R/summarise_production.R

@@ -45,7 +45,7 @@ summarise_production <- function(production_boots) {
                                                                              quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))) %>% 
    bind_rows
   
-   production_spp_list = ann_spp_summary %>% named_group_split(site_id) %>% map(~.x %>% select(taxon_id))
+   production_spp_list = ann_spp_summary %>% named_group_split(site_id) %>% map(~.x %>% select(taxon_id)) %>% rlist::list.subset(names(stream_order_list))
    
    return(list(int_comm_summary = int_comm_summary, ann_comm_summary = ann_comm_summary, ann_spp_summary = ann_spp_summary, int_spp_summary= int_spp_summary, production_spp_list = production_spp_list))
 

### 2021-02-10 docs/ms/ms.RMD
preliminary documents and first draft of figures.

@@
 <!--- warming and effects in food webs --->
-Temperature is an important abiotic variable with increasing relevance as increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
-Temperature'smak effect on ecosystem manifest through complex of direct and indirect pathways such as, shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
-This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, s Identifying general effects of temperature is further complicated by the fact that natural variation in temperature often exists concurrently with other environmental gradients (e.g., light, water, and/or nutrient availability).
-Understanding the effects of temperature...alterations to ecosystem function and the services they provide.
+Temperature is an important abiotic variable with increasing relevance  increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
+Temperature's effect on ecosystems manifest through complex of direct and indirect pathways such as, shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
+This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, which are concurrently influenced by other environmental gradients (e.g., light, water, and/or nutrient availability).
+Yet, identifying general effects of temperature is a necessary step ...alterations to ecosystem function and the services they provide.
 <!--- Speeding up of food web: Species levels--->

### 2021-02-10 docs/prelim-doc.Rmd
preliminary documents and first draft of figures.

@@
   html_document: 
-      keep_md: true
-      toc: true
-      toc_float: true
-      toc_depth: 3
-      numbered_sections: true
+    keep_md: yes
+    toc: yes
+    toc_float: yes
+    numbered_sections: yes
+bibliography: refs.bib
 ---
@@
 oce_temp_pos = c(256,212,168,124,80,1)#color positions in 'temperature' list of ocecolors
-
-drake::loadd("spp_rankings")
+library(knitr)
 
@@
 
-### Histograms of PB, M, and Biomass among streams.
+First, thing I did was find a way to model and propagate error of diets across sites.
+To do so, I build a bayesian random effects model that incorporated varying seasons, taxon, and streams and modeled the multinomial diet response using a dirichlet family distributional model.
+The model priors assume equal contribution of all diet items, which is conservative, but it outputs posterior distributions of diet proportions.
+These we can draw from for each taxa and each bootstrap to incorporate uncertainty through the flux estimates.
+I only estimated this for non-predators and then predators assumed to have a diet of 100% animal material.
+The posterior distributions look something like the plot below.
+This is subsampled to allow for a more manageable plot file size, but it captures the distributions.
 
-```{r pb historgram, echo = FALSE, warnings = FALSE}
-pb_df = spp_rankings[['PB_spp_rank']] %>% bind_rows %>% dplyr::filter(pb_y_mean >0) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))
-bio_df = spp_rankings[['bio_spp_rank']] %>% bind_rows %>% dplyr::filter(bio_mg_m_mean >0 | is.na(bio_mg_m_mean)) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))
-M_df = spp_rankings[['M_spp_rank']] %>% bind_rows %>% dplyr::filter(M_mg_ind_mean >0 | is.na(M_mg_ind_mean)) %>% dplyr::mutate(site_id = factor(site_id, levels = rev(stream_order)))
+### Stream-level posterior distributions of diet contributions
 
-pb_boxplot = ggplot(pb_df,aes(x = site_id, y = log10(pb_y_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
-  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
-  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
-  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = c(0,0), legend.justification = c(0,0),
-        legend.background = element_rect(fill = 'transparent', colour = NA))
-# pb_boxplot
+```{r diet plots, echo = FALSE, warning=FALSE}
 
-M_boxplot = ggplot(M_df,aes(x = site_id, y = log10(M_mg_ind_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
-  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
-  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
-  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = "none")
+drake::loadd(prelim_diet_figures)
 
-bio_boxplot = ggplot(bio_df,aes(x = site_id, y = log10(bio_mg_m_mean))) + geom_violin(aes(fill = site_id), alpha = 0.5) +
-  geom_jitter(aes( fill = site_id),color = 'black', size = 2, shape = 21, alpha = 0.5) +
-  scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
-  theme(axis.title.x = element_blank(), legend.title = element_blank(),legend.position = "none")
-
-grid.arrange(pb_boxplot, M_boxplot, bio_boxplot, ncol = 3)
+prelim_diet_figures
 
@@
 
+When we look at the distribution of OM flux to taxa, we see varying evenness in the distributions of OM fluxes. One way to view this is rank-production plots:
+
+```{r rank-production plots, echo = FALSE, warning=FALSE, height = 8, width = 8, units = 'in'}
+drake::loadd(annual_spp_flux_fig)
+
+annual_spp_flux_fig
+
+```
+
+This gives the impression that the evenness of production is highest in the mid range temperatures.
+However, evenness is not as straightforward because evenness is related to species richness in almost all formulations of it.
+A consensus seems to be emerging that evenness must be corrected for richness to compare across sites [@chao2019].
+Once we correct for this we see evenness is not lowest at higher temperatures, but in the middle when we account for species richness.
+This is based on the Gini index which measures inequality and when standardized ranges from 0 to 1.
+
+```{r gini table, echo = FALSE, warning=FALSE}
+
+drake::loadd(gini_analysis)
+drake::loadd(environment_data)
+
+ann_temps = environment_data[["ann_stream_temps"]]
+
+gini_summ = gini_analysis[["stream_gini_summary"]] %>% dplyr::select(c(site, contains("mean"), contains("quant2.5"), contains("quant97.5"))) %>% left_join(ann_temps %>% dplyr::select(site = "SITE", tempC), by = "site") %>% dplyr::mutate(tempc = round(tempC, 1)) %>% dplyr::select(site, tempC, contains('Non-normalized'), contains("Normalized")) %>% dplyr::arrange(desc(tempC))
+knitr::kable(gini_summ, digits = 2)
+```
+
+Another way to view this is to look at the accumulation of flux across the accumulation of species standardize 0-1.
+This is often viewed as a Lorenz curve.
+Here we order species by annual flux, $x_i$ is the annual flux of species *i*, such that $x_1 < x_2 < ...
+< x_n$.
+If every species contributes an equal amount to production the Lorenz curve falls along the solid 1:1 line on the plot.
+The bold colored lines represent the mean value and each grey line is an individual bootstrapped estimate.
+
+### Lorenz curves of cumulative flux with species
+
+```{r lorenz of flux, echo = FALSE, warning=FALSE}
+drake::loadd(lorenz_trait_fig)
+
+lorenz_trait_fig[[1]]
+
+```
+
+Here we see that total community flux accumulates differently across the streams.
+There are a few instances when it looks like abrupt 'jumps' in cumulative flux.
+These are mostly driven by species that dominate biomass.
+When we look at how flux accumulates with biomass we see the curves fall near the 1:1 lines, which is expected since standing biomass strongly influences production.
+In st14 we see lots of variation driven by empty samples and low sample size in the winter.
+
+### Lorenz curve of cumulative flux v. biomass
+
+```{r lorenz biomass, echo = FALSE, warning=FALSE}
+
+lorenz_trait_fig[[4]]
+
+```
+
+This allows us an opportunity to look how total community flux accumulates across different species traits in a standardized way.
+So rather than the distribution differences attributed to different absolute magnitudes they are attributed to the relative magnitudes.
+So how does temperature modify how flux accumulates with species traits such as annual P:B and mean body size.
+First, a look at the distribution of traits across taxa in the streams.
+
+### Histograms of PB, M, and Biomass among streams.
+
+```{r pb histogram, echo = FALSE, warnings = FALSE}
+
+drake::loadd(spp_trait_histograms)
+
+grid.draw(spp_trait_histograms)
+
+```
+
+So how does flux accumulate with annual *P:B* across sites?
+Here, we order each species by *P:B*, such that $pb_1 < pb_2 < ...
+< pb_n$.
+We see the most striking differences at the warmest and coldest sites.
+At hver, OM flux is disproportionately skewed towards taxa with higher annual *P:B* and in st14 flux is disproportionately skewed towards low *P:B* taxa.
+
+### Accumulation of flux with P:B across sites
+
+```{r pb lorenz, echo = FALSE, warning=FALSE}
+lorenz_trait_fig[[2]]
+```
+
+So how does flux accumulate with mean body size, *M*, across sites?
+Here, we order each species by *M*, such that $M_1 < M_2 < ...
+< M_n$.
+This give a complementary story to *P:B*, flux in hver is disproportionately skewed towards lower *M*, and st14 skewed towards larger relative *M*.
+We are also able to glean a bit more information from some of the mid temperature streams.
+In st9 (11.2 $^\circ$C) the largest taxa also has the largest flux (and biomass)
+
+### Accumulation of flux with M across sites
+
+```{r M lorenz, echo = FALSE, warning=FALSE}
+lorenz_trait_fig[[3]]
+```
+
 ## Reproducibility
 
-<details><summary>Reproducibility receipt</summary>
+<details>
+
+<summary>
+
+Reproducibility receipt
+
+</summary>
 
@@
 </details>
+
+## References

### 2021-02-10 R/plan.R

@@ -48,16 +48,18 @@ the_plan <-
    
    ### figures
   #
+  prelim_diet_figures = plot_stream_diets(modeled_diets[["diet_predictions"]]),
+  #
   annual_spp_flux_fig = plot_spp_flux(flux_summaries[["annual_spp_flux_summary"]], environment_data[["stream_temp_labels"]]),
   #
   spp_trait_histograms = plot_trait_histogram(spp_rankings_summary),
   #
   lorenz_trait_fig = plot_trait_lorenz(lorenz_analysis, spp_rankings_summary),
   
-  # target_name = target(
-  #   command = {
-  #     rmarkdown::render(knitr_in("docs/prelim-doc.Rmd"))
-  #     file_out("docs/prelim-doc.html")
-  #   }
-  # )  
+  target_name = target(
+    command = {
+      rmarkdown::render(knitr_in("docs/prelim-doc.Rmd"))
+      file_out("docs/prelim-doc.html")
+    }
+  )
 )

### 2021-02-10 R/plot_stream_diets.R

@@ -1,0 +1,22 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param diet_predictions
+plot_stream_diets <- function(diet_predictions = modeled_diets[["diet_predictions"]]) {
+
+  diet_predictions %>%
+    dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+    group_by(site, diet_item) %>%
+    sample_n(size = 2000, replace = FALSE) %>%
+    ggplot(aes(x = rel_area)) + geom_density(aes(group = diet_item, color = diet_item, fill = diet_item), alpha = 0.5) +
+    scale_color_viridis_d(option = 'plasma')+
+    scale_fill_viridis_d(option = 'plasma')+
+    theme_tufte(ticks = TRUE) +
+    geom_rangeframe(sides = "lb")+
+    facet_wrap(~site, ncol = 2) -> stream_diets_plot
+  
+  return(stream_diets_plot)
+
+}

### 2021-02-10 R/rank_spp_boots.R

@@ -13,7 +13,7 @@ rank_spp_boots <- function(ann_spp_boots = production_boots[["ann_spp_boots"]]) 
     junkR::named_group_split(boot_id) %>%
     purrr::map(~.x %>%
                  dplyr::select(site_id, taxon_id, matches('bio.*')) %>%
-                 dplyr::mutate(bio_ann_rank = dense_rank(desc(bio_mg_m)))) %>%
+                 dplyr::mutate(bio_ann_rank = dense_rank(bio_mg_m))) %>%
     bind_rows(.id = 'boot_id'))
   # abundance
   # # sum across intervals for each stream
@@ -22,7 +22,7 @@ rank_spp_boots <- function(ann_spp_boots = production_boots[["ann_spp_boots"]]) 
     junkR::named_group_split(boot_id) %>%
     purrr::map(~.x %>%
                  dplyr::select(site_id, taxon_id, matches('n_ind.*')) %>%
-                 dplyr::mutate(n_ann_rank = dense_rank(desc(n_ind_m)))) %>%
+                 dplyr::mutate(n_ann_rank = dense_rank(n_ind_m))) %>%
   bind_rows(.id = 'boot_id'))
   # body size, *M*
   M_spp_rank_boots = ann_spp_boots %>%
@@ -30,7 +30,7 @@ rank_spp_boots <- function(ann_spp_boots = production_boots[["ann_spp_boots"]]) 
     junkR::named_group_split(boot_id) %>%
     purrr::map(~.x %>%
                  dplyr::select(site_id, taxon_id, matches('M.*_ind')) %>%
-                 dplyr::mutate(M_ann_rank = dense_rank(desc(M_mg_ind)))) %>%
+                 dplyr::mutate(M_ann_rank = dense_rank(M_mg_ind))) %>%
     bind_rows(.id = 'boot_id'))
   
   # PB ratio
@@ -39,7 +39,7 @@ rank_spp_boots <- function(ann_spp_boots = production_boots[["ann_spp_boots"]]) 
     junkR::named_group_split(boot_id) %>%
     purrr::map(~.x %>%
                  dplyr::select(site_id, taxon_id, matches('pb.*')) %>%
-                 dplyr::mutate(pb_ann_rank = dense_rank(desc(pb_y)))) %>%
+                 dplyr::mutate(pb_ann_rank = dense_rank(pb_y))) %>%
     bind_rows(.id = 'boot_id'))
   
[…]

### 2021-03-10 docs/ms/ms.RMD
skew analysis updated

@@
 csl: ecology.csl
+editor_options: 
+  markdown: 
+    wrap: 180
 ---
+
+```{r import general objects, echo=FALSE, warning=FALSE, message=FALSE}
+
+source("./packages.R")
+
+```
+<!--- Title page details --->
+
+\newpage
 
@@
 
+\newpage
+
 # Introduction
+
 <!--- warming and effects in food webs --->
-Temperature is an important abiotic variable with increasing relevance  increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][].
-Temperature's effect on ecosystems manifest through complex of direct and indirect pathways such as, shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18].While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010].
-This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, which are concurrently influenced by other environmental gradients (e.g., light, water, and/or nutrient availability).
-Yet, identifying general effects of temperature is a necessary step ...alterations to ecosystem function and the services they provide.
+
+Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
+[@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges [][] and subsequent changes to local and
+regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001]. While a growing body of theoretical and
+empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [@oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017],
+especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010b]. Yet, identifying general effects of temperature is a necessary step
+towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
+
 <!--- Speeding up of food web: Species levels--->
-The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged (e.g., food webs; [@deruiter1995][@thompson2012].
-Characteristics The magnitude The response of ecosystem function to environmental drivers and variability <!---Ecosystem functionality---> is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018].
-The complexity in responses to warming arise from
+
+Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010b] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distributions among species and trophic levels [@may1972; @mccann1998; @barnes2018].
+Direct changes through species richness effects [@gibert2019].
+Indirect through the distribution of consumer and prey species and it effects on the acquisition and allocation of resources among species [@zhang2017] --macroecology of food web dynamics and stability are controlled by the .
+
+Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
+etc.; @dell2014].
+
 <!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (~5 - 28$^\circ$C).
-Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011][@padfield2017] and within streams seasonally [@gorman2012][@hood2018].
-The dynamics of basal resource supply has a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumer to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
-Further, we predicted that food web OM fluxes will 'speed up' with increasing temperature through increases in the importance of relatively faster, higher turnover consumers.
-Within streams, the speeding up of ecosystems will lead to earlier food web fluxes in warmer compared to colder streams.
+
+Metabolic rates
+
+acquisition of resources by consumer Generally, temperature is predicted to have disproportionately higher effects on consumers relative to resources [@allen2005; @vasseur2005;
+@oconnor2011]
+
+Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous
+research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
+[@ogorman2012; @hood2018].
+Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2019] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to
+consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
+We, further expected that increasing temperature would reduce consumer species [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
+The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
+Seasonally, warmer streams will lead to earlier food web fluxes in warmer compared to colder streams.
 
@@
 
-We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N  021$^\circ$ 18'W) that varied in mean annual temperature.
-Hengill is characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5–54.0 $^\circ$C), but similar solute chemistries [@friberg_relationships_2009].
-These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014][@nelson2017a].
-We selected streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers.
-In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp.
-Pocasset, MA, USA).
-Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp.
-Pocasset, MA, USA).
+We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
+characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
+chemistries [@friberg2009]. These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a]. We selected
+streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers. In each stream, we measured temperature and water depth
+every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp. Pocasset, MA, USA). Light availability in the watershed was measured every 15
+min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp. Pocasset, MA, USA).
 
@@
 
-We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous study (*n* = 6 streams).
-The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental manipulation [see @nelson2017][@nelson2017a].
-Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018].
-We collected fiver Surber samples (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream.
-Within the sampler, inorganic substrates were disturbed to ~10 cm depth and invertebrates and organic matter were removed from stones with a brush.
-Samples were then preserved with 5% formaldehyde until laboratory analysis.
-In the laboratory, we split samples into coarse (>1 mm) and fine (<1 mm but >250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10–15 x magnification).
-For particularly large samples, fine fractions were subsampled (1/2–1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates.
-Subsamples were scaled to the rest of the sample assuming similar abundance and body size distributions.
-Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson1977][@merritt2008][@andersen2013].
-Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
+We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
+study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
+manipulation [see @nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
+unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
+(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
+organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
+(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
+For particularly large samples, fine fractions were subsampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
+the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
+taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
 
@@
 
-Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @Benke_Huryn2017].
-Growth rates were determined using taxon appropriate approaches described in [@junker_resource_nodate].
-Briefly, growth rates of common taxa (e.g., Chironomidae spp., Radix balthica, etc.) were determined using *in situ* chambers [@huryn_method_1986].
-Multiple individuals  (*n* = 5–15) within small size categories (~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned chambers for 7–15 days, after which they were again photographed.
-Individual lengths were measured from field pictures using image analysis software [@Schindelin_Arganda-Carreras_Frise_Kaynig_Longair_Pietzsch_Preibisch_Rueden_Saalfeld_Schmid_et al.2012], and body lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke_length-mass_1999; @ogorman_impacts_2012; @hannesdottir_increased_2013].
-Growth rates (*g*, d^-1^) were calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:
+Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @benke2017]. Growth rates were determined using taxon appropriate
+approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., Radix balthica, etc.) were determined using *in situ* chambers [@huryn1986].
+Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned
+chambers for 7--15 days, after which they were again photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
+lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke1999; @ogorman2012; @hannesdottir2013]. Growth rates (*g*, d^-1^) were
+calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:
 
@@
 
-Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500).
-For taxa which exhibit synchronous growth and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017].
-Individual Lengths were converted to mg AFDM using published length-mass regression cited above and size-frequency histograms were visually inspected for directional changes in body size through time.
-For each date, size-frequency distributions were resampled with replacement (*n* = 500) and growth rates estimated from equation 1.
-We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ > $W_t$.
-To estimate growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of empirical growth data against body size and temperature within each stream.
-To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled measured growth rates, in addition to abundance and size distributions from individual samples.
-For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean interval biomass for each size class and the number of days between sample dates to estimate size class-specific production.
-For each interval, size classes were summed for each taxon to calculate total population-level production.
-Intervals were summed to estimate annual secondary production.
+Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500). For taxa which exhibit synchronous growth
+and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
+using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
+above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
+replacement (*n* = 500) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
+growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
+empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
+measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean
+interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
+taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.
 
@@
 
-**Come back and confirm this section**
-Macroinvertebrate diets were quantified for dominant taxa in each stream.
-We focused on numerically abundant taxa and/or taxa with relatively high annual production.
-A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic shifts in diet.
-We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes.
-For small-bodied taxa, we combined multiple individuals (*n* = 3–5) to ensure samples contained enough material for quantification.
-We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content slides.
-Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds.
-Gut content slurries were filtered onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a microscope slide, cleared with Type B immersion old, and covered with a cover slip.
-We took 5–10 random photographs under 200–400x magnification, depending on the density of particles, using a digital camera mounted on a compound microscope.
-From these photographs we identified all particles within each field and measured the relative area of particles using image analysis software [@schindelin2012].
-We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular plants (bryophytes), and animal material.
-We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles.
-Gut contents of many predators were empty or contained unidentifiable, macerated prey.
-For these taxa, we assumed 100% animal material.
+**Come back and confirm this section** Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
+high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
+shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
+= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content
+slides. Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds. Gut content slurries were filtered
+onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
+microscope slide, cleared with Type B immersion old, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
+particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
+using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
+plants (bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
+contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.
 
-To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a hierarchical multivariate model [@fordyce2011].
-Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
-$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$
-$$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$
-where, $\overrightarrow{p_i}$, is a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
-We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$,
-$$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$
-$$\alpha \sim Uniform(0,\textit{c})$$
-where, $\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value.
-**add in site-level model parameter and model fitting language**.
-Models were fit in Stan with the 'brms' package in R [@burkner2017].
-For non-dominant taxa, diet proportions were imputed from the hierarchical model by resampling from posterior distributions.
-Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.
+To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
+hierarchical multivariate model [@fordyce2011]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
+$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
+a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
+We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
+$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
+site-level model parameter and model fitting language**. Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
+from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
+values.
 
@@
 
-Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980].
-Taxon-specific secondary production estimates were combined with diet proportions, diet-specific assimilation efficiencies, $AE_{i}$, and assumed net production efficiencies, $NPE$, to estimate consumption of organic matter.
-For each food category, $\textit{i}$, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food category.
-The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic matter from each food category by a consumer [@benke1980].
-Consumption was calculated for each taxon across sampling intervals (typically ~1 month).
-Total interval consumption was calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and inte(rvals.
-Variability in consumption estimates was estimated through a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with the TBP method using simulated diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency.
-Variability in $AE_{i}$ was incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36), filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968][@cross2007][@cross2011][@benke1980][@benke1997].
-Variability in $NPE$ was incorporated by resampling values from an assumed beta distribution with median $NPE$ = 0.45 (95% PI = 0.4-0.5).
-Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@belgorodski2017].
+Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
+diet proportions, diet-specific assimilation efficiencies, $AE_{i}$, and assumed net production efficiencies, $NPE$, to estimate consumption of organic matter. For each food
+category, $\textit{i}$, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
+category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
+matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
+calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
+a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
+the TBP method using simulated diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in $AE_{i}$ was
+incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
+filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
+(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in $NPE$ was
+incorporated by resampling values from an assumed beta distribution with median $NPE$ = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
+within the *rriskDistributions* package [@belgorodski2017].
 
@@
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
-p_S$.
-The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
-In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is simply a straight diagonal line.
-Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1979][@chao2019]:
-$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
+such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
+case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
+simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
+[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+
 ### Distribution along species' trait axes
 
-We were interested in how OM fluxes were distributed (random vs. non-random) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass), to explore
+We were interested in how OM fluxes were distributed (randomly vs.
+non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient.
+We used a permutation analyses to test for non-random patterns in OM flux with species traits.
+First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$).
+We then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
 
-### Through time
+$$Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}$$
 
-To qu
+where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
+To determine the probability of observing the skewness we observe in the data compared to random ordering, we constructed a distribution of skewness estimates from random species ordering while maintaining the relative distribution of OM fluxes.
+The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore we permuted 1,000,000 random species orderings and calculating the skew in the cumulative distribution of annual OM fluxes.
+We then use this random distribution to estimate the probability of observing a skewness as extreme or greater.
 
@@
 # Results
+
+```{r load objects from cache, echo = FALSE, warning = FALSE, message=FALSE}
+library(tidyverse)
+ drake::loadd(flux_estimates)
+ energy_demand = flux_estimates[["energy_demand"]]
+ comm_energy_demand_summary = energy_demand %>%
+    group_by(site, boot_id) %>% 
+    dplyr::summarise(flux_mg_m_y = sum(flux_mg_m_y)) %>%
+    ungroup %>% group_by(site) %>%
+    dplyr::summarise(across(matches('flux'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+  bind_rows
+  min_demand = comm_energy_demand_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
+  max_demand = comm_energy_demand_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))
+
+drake::loadd(flux_summaries)
+annual_comm_flux_summary = flux_summaries[["annual_comm_flux_summary"]]
+min_flux = annual_comm_flux_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
+max_flux = annual_comm_flux_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))
+
+```
+## Community OM fluxes
+
+Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),2)`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),2)`].
+
+```{r diet import, echo = FALSE, include = TRUE, message=FALSE, warning = FALSE}
+drake::loadd(modeled_diets)
+diet_predictions_site = modeled_diets[["diet_predictions"]] %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+    group_by(site, diet_item) %>%
+    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
+                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
+
+diet_predictions_item = modeled_diets[["diet_predictions"]] %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+    group_by(diet_item) %>%
+    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
+                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
+```
+
+Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]).
+Calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.
+
+## Evenness of OM fluxes within streams
+
+```{r species richness, echo = FALSE, warning=FALSE, message=FALSE}
+spp_richness = energy_demand %>% group_by(site) %>% dplyr::summarise(taxon_n = n_distinct(taxon))
+
+drake::loadd(gini_analysis)
+gini_summary = gini_analysis[["stream_gini_summary"]]
+
+```
+
+Generally, the material fluxes within a stream were distributed unevenly among consumers, however, this varied among streams (Figure X).
+This was partly due to marked differences in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
+After accounting for species richness material fluxes were unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant97.5') %>% round(2)`])
 

### 2021-03-10 R/Evenness.R

@@ -1,0 +1,79 @@
+#*******************************************************************************
+#********************************************************************************
+# 
+## R scipts "Evenness" for Chao and Ricotta (2019) Ecology paper. 
+## This R code is for computing Figures 2, 3 and 4 of Chao and Ricotta (2019) paper.
+# NOTE: The packages "ggplot2", "dplyr", "ade4", "reshape2", "ggpubr", "phytools", "ape" must be 
+# installed and loaded before running the scripts. 
+# 
+#
+# The following R scripts include two parts:  
+# (1). Script for computing the profiles for six classes of evenness measures (see Figure 2 in Chao and Ricotta's paper).
+# (2). Script for computing the contribution of each species/node to taxonomic dissimarity and/or phylogenetic
+#      dissimarity measures (see Figures 3 and 4 in Chao and Ricotta's paper)
+# 
+#
+#*******************************************************************************
+#*******************************************************************************
+
+# library(ggplot2)
+# library(dplyr)
+# library(ade4)
+# library(reshape2)
+library(ggpubr)
+# library(phytools)
+# library(ape)
+
+####################################################################################
+#
+# (1). Computing the profiles for six classes of evenness measures (Table 1 and Figure 2)
+#
+####################################################################################
+
+qD <- function(p,q){
+  p <- p[p>0]
+  if(q!=1){
+    (sum(p^q))^(1/(1-q))
+  }else{
+    exp(-sum(p*log(p)))
+  }
+}
+
+#' new_fun computes all six classes of evenness measures.
+#' @param x is an observed species abundance or frequency vector. 
+#' @param q.order is a vector of diversity orders: user must specify a sequence (suggested range is from 0 to 2 in an increment of 0.05).
+#' @return the profiles of all six classes of evenness indices listed in Table 1; see Figure 2 for output.
+new_fun <- function(x,q.order,evenness.type,...){
+  FUN <- qD
+  n <- sum(x)
+  p <- x/n
[…]

### 2021-03-10 R/analyze_skew.R

@@ -1,0 +1,55 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param lorenz_analysis
+##' @param random_rankings
+analyze_skew <- function(lorenz_analysis, random_rankings) {
+
+  ## ++++ Helper functions ++++ ##
+  skew_est = function(df, x,y){
+    site_name = unique(df$site)
+    # boot_id = unique(df$boot_id)
+    skew_name = paste0(as.character(y),'_skew')
+    y = df %>% dplyr::select(all_of(y)) %>% na.omit %>% unlist
+    x = df %>% dplyr::select(all_of(x)) %>% na.omit %>% dplyr::filter(. > 0) %>% unlist
+    
+    y1 = quantile(y, 0.25, na.rm = TRUE)
+    y2 = quantile(y, 0.5, na.rm = TRUE)
+    y3 = quantile(y, 0.75, na.rm = TRUE)
+    
+    y1_min = which.min(abs(y - y1))
+    y2_min = which.min(abs(y - y2))
+    y3_min = which.min(abs(y - y3))
+    
+    x1 = unname(x[y1_min])
+    x2 = unname(x[y2_min])
+    x3 = unname(x[y3_min])
+    
+    skew = (x3 - 2*x2 + x1)/(x3-x1)
+    assign(skew_name, skew)
+    z = data.frame(site = site_name, eval(as.symbol(skew_name)))
+    colnames(z)[2] <- skew_name 
+    return(z)
+  }
+  
+  ## ++++ End Helper functions ++++ ##
+   # debugonce(skew_est)
+ 
+  PB_skew_boots = lorenz_analysis[["pb_ranking_boots"]] %>%
+    named_group_split(site) %>%
+    map(~.x %>% named_group_split(boot_id) %>%
+          map(~.x %>% skew_est(., 'rel_flux', 'pb_y')) %>% 
+          bind_rows(.id = 'boot_id')) %>%
+    bind_rows(.id = 'site')
+  
+  M_skew_boots = lorenz_analysis[["M_ranking_boots"]] %>%
+    named_group_split(site) %>%
+    map(~.x %>% named_group_split(boot_id) %>%
+          map(~.x %>% skew_est(., 'rel_flux', 'M_mg_ind')) %>%
+          bind_rows(.id = 'boot_id')) %>%
+    bind_rows(.id = 'site')
+  
[…]

### 2021-03-10 R/create_random_ranks.R

@@ -1,0 +1,64 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param ann_spp_flux
+##' @param n
+create_random_ranks <- function(ann_spp_flux = flux_summaries[["annual_spp_flux_boots"]], n = 1e6,...) {
+
+  #'
+  #'
+  ## ++++ Helper functions ++++ ##
+  random_ordering = function(x, n){
+    x = vector('list', length = n)
+    taxa_list = unique(x$taxon)
+    random_spp = lapply(x, sample(taxa_list, replace = FALSE))
+    return(random_spp)
+  }
+  
+  skew_est = function(df, x,y){
+    site_name = unique(df$site)
+    skew_name = paste0(as.character(y),'_skew')
+    df = df %>% dplyr::filter(flux_mg_m_y > 0)
+    y = df %>% dplyr::select(all_of(y)) %>% na.omit %>% unlist
+    x = df %>% dplyr::select(all_of(x)) %>% na.omit %>% dplyr::filter(. > 0) %>% unlist
+    
+    y1 = quantile(y, 0.25, na.rm = TRUE)
+    y2 = quantile(y, 0.5, na.rm = TRUE)
+    y3 = quantile(y, 0.75, na.rm = TRUE)
+    
+    y1_min = which.min(abs(y - y1))
+    y2_min = which.min(abs(y - y2))
+    y3_min = which.min(abs(y - y3))
+    
+    x1 = unname(x[y1_min])
+    x2 = unname(x[y2_min])
+    x3 = unname(x[y3_min])
+    
+    skew = (x3 - 2*x2 + x1)/(x3-x1)
+    assign(skew_name, skew)
+    z = data.frame(site = site_name, eval(as.symbol(skew_name)))
+    colnames(z)[2] <- skew_name 
+    return(z)
+  }
+  ## ++++ End Helper functions ++++ ##
+  
+  set.seed(42);boot_n = sample(unique(ann_spp_flux$boot_id), n, replace = TRUE)
+ 
+  # debugonce(skew_est)
+  spp_rank_list = boot_n %>% 
+    map(., ~ann_spp_flux %>%
+          dplyr::filter(boot_id == .x) %>%
+          group_by(site) %>%
+          slice_sample(prop = 1.0, replace = FALSE) %>%
+          dplyr::filter(flux_mg_m_y > 0) %>% 
[…]

### 2021-03-10 R/estimate_flux.R

@@ -74,6 +74,9 @@ estimate_flux <- function(seasonal_diets = diet_matrices, seasonal_fluxes = seas
      map2(x, y, function(a,b){
    pmap(list(a,b,res_effs), ~boot_flux_function(mat =..1, losses = ..2, resource_effs_vct = ..3))
      })})
+   
+   ann_fluxes = fluxes %>% map(~.x %>% map(~.x %>% bind_rows(.id = 'boot_id')) %>% bind_rows(.id = 'yr_third') %>% pivot_longer(-boot_id:-yr_third, names_to = 'taxon', values_to = 'flux_mg_m') %>%
+                                             group_by(taxon, boot_id) %>% dplyr::summarise(flux_mg_m_y = sum(flux_mg_m, na.rm = TRUE))) %>% bind_rows(.id = 'site')
        
-   return(flux_full)
+   return(list(energy_demand= ann_fluxes, flux_full = flux_full))
 }

### 2021-03-10 packages.R

@@ -3,12 +3,12 @@
   if(!require("pacman")) install.packages("pacman")
   library(pacman)
   package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
-                    "RCurl","plyr","tidyverse","furrr", "fnmate", 
+                    "RCurl","plyr","tidyverse","furrr", "fnmate", "moments",
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
                     "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
                     "viridis", "broom","bbmle","ggthemes", "ggeffects",
                     "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
-                    "rstan", "brms", "tidybayes", "parallel")
+                    "rstan", "brms", "tidybayes", "parallel", "hillR")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
   # p_load_gh("jimjunker1/junkR")
   devtools::install_github("jimjunker1/junkR")
@@ -70,6 +70,7 @@
   
 source("./R/fluxweb_mod_function.R")
 source("./R/Lorenz.R")
+source("./R/Evenness.R")
 nboot = 1e3
 theme_set(theme_mod())
 options(mc.cores = parallel::detectCores()-1)

### 2021-03-10 working.R

@@ -1,0 +1,16 @@
+x = x %>% dplyr::filter(site == 'hver')
+y = spp_rankings_summary[[5]] %>% dplyr::filter(site == 'hver')
+z = spp_rankings_summary[[5]] %>% dplyr::filter(site == "st14")
+
+mu = mean(y$pb_y_mean, na.rm = TRUE)
+
+sum(na.omit(y$pb_y_mean < mu))
+
+mu_z = mean(z$pb_y_mean, na.rm = TRUE)
+
+sum(na.omit(z$pb_y_mean < mu_z))
+21/27
+22/27
+
+(mu_z- 0.7778)/(0.786-0.7778)
+21+

### 2021-04-18 doc/ms/ms.Rmd
commit to fix f'in Dropbox sync/backup issues. Hopefully doesn't mess it up further.

--- 2021-03-10 docs/ms/ms.RMD
@@
 
-```{r import general objects, echo=FALSE, warning=FALSE, message=FALSE}
+```{r import general objects, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),2)`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),2)`].
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.
 
@@
 drake::loadd(gini_analysis)
-gini_summary = gini_analysis[["stream_gini_summary"]]
+gini_summary = gini_analysis[["stream_gini_summary"]] %>% set_names(make.names(names(.)))
 
@@
 
-Generally, the material fluxes within a stream were distributed unevenly among consumers, however, this varied among streams (Figure X).
-This was partly due to marked differences in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-After accounting for species richness material fluxes were unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant97.5') %>% round(2)`])
+Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1).
+The calculated inequality, i.e.
+Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Differences in inequality were partly attributed to consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
+Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+
+```{r spp flux summaries, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(spp_rankings_summary)
+spp_flux_summary = spp_rankings_summary[["prod_spp_rank"]]
+select_dom = function(x){
+  x= x[which(!is.na(x$taxon)),]
+  x = x %>% dplyr::mutate(tot_n = max(prod_ann_rank, na.rm = TRUE))
+  if(sum(x$rel_flux >= 0.15) > 1){
+    y = x[which(x$rel_flux >= 0.15),]
+    } else{
+      y = x[which(x$prod_ann_rank >= (max(x$prod_ann_rank)-1)),]
+   }
+  return(y)
+}
+
+spp_dominance = spp_flux_summary %>% named_group_split(site) %>% map(.,~select_dom(.x)) %>% bind_rows(.id = 'site') %>% 
+  group_by(site) %>%
+  dplyr::summarise(n_dom = n(), 
+                   tot_n = unique(tot_n),
+                   dom_flux = 1-min(rel_flux, na.rm = TRUE), 
+                   dom_spp = 1-min(rel_spp))
+
+n_dom_min = spp_dominance %>% dplyr::slice(which.min(n_dom))
+n_dom_max = spp_dominance %>% dplyr::slice(which.max(n_dom))
+
+perc_dom_min = spp_dominance %>% dplyr::slice(which.min(dom_spp))
+perc_dom_max = spp_dominance %>% dplyr::slice(which.max(dom_spp))
+
+```
+
+Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a).
+For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
+Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblage.
+
+## Trait distributions among sites and taxa
+
+```{r trait summary, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(spp_rankings_summary)
+pb_summ = spp_rankings_summary[["PB_spp_rank"]] %>% na.omit %>% group_by(site) %>% dplyr::summarise(across(matches("pb.*mean"), ~mean(.x,na.rm = TRUE)))
+
+m_summ = spp_rankings_summary[["M_spp_rank"]] %>% na.omit %>% group_by(site) %>% dplyr::summarise(across(matches(".*ind_mean"), ~mean(.x,na.rm = TRUE)))
+
+drake::loadd(skew_analysis)
+
+pb_summ = skew_analysis[["PB_skew_summ"]]
+
+m_summ = skew_analysis[["M_skew_summ"]]
+```
+
+The fluxes of OM were distributed differently across body sizes and turnover rates (**P:B**) among and within streams.
+Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
+Fluxes were skewed differentially towards larger body sizes (positive skew) among streams, with skew estimates with body size (**M**) ranging from `r m_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
+Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
+
+When compared to random
+
+-- mean skew with M ranged from
+
+-- The probability of observing these values of skew with pb `r pb_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`
+
+-- The probability of observing these values of skew with M `r m_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`
 
@@
 
-\newpage
-
 # References

### 2021-04-18 doc/ms/tables-figures.Rmd
commit to fix f'in Dropbox sync/backup issues. Hopefully doesn't mess it up further.

---
title: ""
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("./packages.R")
library(knitr)
```

## Tables
\newpage

Table 1.

```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(gini_analysis)
gini_analysis[["stream_gini_summary"]] %>% dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>% knitr::kable(align = "lrr")

```

\newpage

Table 2.

\newpage

Figure descriptions

Figure 1. Species rank-flux plots among streams. Within each stream, species are ranked by descending annual total organic matter flux (mg AFDM $m^{-2} y^{-1}$).

```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(annual_spp_flux_fig)
annual_spp_flux_fig
```

\newpage

Figure 2. Evenness profiles of species' relatives fluxes among streams.

```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE,  fig.width=5, fig.height=5, dpi = 450}
loadd(hill_diversity_analysis)
hill_diversity_analysis

```

\newpage

Figure 3. Histograms of species trait distributions of (a) log~10~ annual production:biomass ratio (y^-1^), (b) log~10~ mean body mass (mg ind^-1^), and (c) log~10~ annual mean population biomass (mg m^-2^).

```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(spp_trait_histograms)
grid.draw(spp_trait_histograms)
```

\newpage

Figure 4. Relative cumulative fluxes among species in relation to ranked order of (a) annual production:biomass ratio (y^-1^) and (b) mean body size (mg ind^-1^).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(lorenz_trait_fig)
grid.arrange(lorenz_trait_fig[["pb_lorenz_flux_plot"]], lorenz_trait_fig[["M_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))

```

\newpage

Figure S1. Modeled diet proportions among streams

```{r diets, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(prelim_diet_figures)
prelim_diet_figures

```

\newpage

Figure S2. Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (mg AFDM m^-2^ y^-1^).

```{r lorenz flux, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
lorenz_trait_fig[["lorenz_flux_plot"]]

```

\newpage

Figure S3. Cumulative plot of relative community flux by species in relation to mean annual population biomass (mg m^-2^).

```{r biomass flux, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
lorenz_trait_fig[["bio_lorenz_flux_plot"]]
```

### 2021-04-18 docs/ms/ms.RMD
commit to fix f'in Dropbox sync/backup issues. Hopefully doesn't mess it up further.

@@
 
-```{r import general objects, echo=FALSE, warning=FALSE, message=FALSE}
-
-source("./packages.R")
-
-```
 <!--- Title page details --->
@@
 
-## Diet analysis
+## **Diet analysis**
 
@@
 We used a permutation analyses to test for non-random patterns in OM flux with species traits.
-First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$).
-We then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
-
-$$Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}$$
-
-where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine the probability of observing the skewness we observe in the data compared to random ordering, we constructed a distribution of skewness estimates from random species ordering while maintaining the relative distribution of OM fluxes.
-The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore we permuted 1,000,000 random species orderings and calculating the skew in the cumulative distribution of annual OM fluxes.
-We then use this random distribution to estimate the probability of observing a skewness as extreme or greater.
+First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and measured the asymmetry in the distribution of annual OM flux with species traits.
+To determine the probability of observing the empirical asymmetry we constructed a random distribution of asymmetry values.
+The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore chose to permute estimated this by randomly ordering species 10,000,000 times and calculating the skew in the cumulative distribution of annual OM fluxes.
+We then use this random distribution to estimate the probability of observing
 
@@
  drake::loadd(flux_estimates)
- energy_demand = flux_estimates[["energy_demand"]]
- comm_energy_demand_summary = energy_demand %>%
-    group_by(site, boot_id) %>% 
-    dplyr::summarise(flux_mg_m_y = sum(flux_mg_m_y)) %>%
-    ungroup %>% group_by(site) %>%
-    dplyr::summarise(across(matches('flux'), list(mean = ~mean(.x, na.rm = TRUE),
-                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
-                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
-                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
-                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
-                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
-  bind_rows
-  min_demand = comm_energy_demand_summary %>% dplyr::slice(which.min(flux_mg_m_y_mean))
-  max_demand = comm_energy_demand_summary %>% dplyr::slice(which.max(flux_mg_m_y_mean))
-
+ # energy_demand = flux_estimates[["energy_demand"]]
+ # comm_energy_demand_summary = energy_demand %>%
+ #    bind_rows
+ # min_demand = comm_energy_demand_summary %>% dplyr::slice(which.min())
 drake::loadd(flux_summaries)
@@
 
-Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),2)`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),2)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),2)`].
-
-```{r diet import, echo = FALSE, include = TRUE, message=FALSE, warning = FALSE}
-drake::loadd(modeled_diets)
-diet_predictions_site = modeled_diets[["diet_predictions"]] %>%
-   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
-    group_by(site, diet_item) %>%
-    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
-                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
-                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
-                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
-                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
-                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
-
-diet_predictions_item = modeled_diets[["diet_predictions"]] %>%
-   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
-    group_by(diet_item) %>%
-    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
-                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
-                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
-                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
-                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
-                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
-```
+Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
+Community energy demand varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),1)`-fold across streams () and was positively related to temperature.
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),2)` [`r paste0(round((min_flux$flux_mg_m_y_quant2.5/1000),2)," - ",round((min_flux$flux_mg_m_y_quant97.5/1000),2))`] to `r round((max_flux$flux_mg_m_y_mean/1000),2)`[`r paste0(round((max_flux$flux_mg_m_y_quant2.5/1000),2)," - ",round((max_flux$flux_mg_m_y_quant97.5/1000),2))`] $g AFDM m^{-2} y^{-1}$ (mean $\pm$ 95% percentile interval [PI]).
 
 Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]).
-Calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.
+Diets composition among all streams were dominated by diatoms (X% $\pm$ XX), amorphous detritus (X% $\pm$ XX), and green algae (X% $\pm$ XX).
+Calculated percent similarity among streams ranged from XX to XX.
 
@@
 
-```{r species richness, echo = FALSE, warning=FALSE, message=FALSE}
-spp_richness = energy_demand %>% group_by(site) %>% dplyr::summarise(taxon_n = n_distinct(taxon))
-
-drake::loadd(gini_analysis)
-gini_summary = gini_analysis[["stream_gini_summary"]]
-
-```
-
-Generally, the material fluxes within a stream were distributed unevenly among consumers, however, this varied among streams (Figure X).
-This was partly due to marked differences in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-After accounting for species richness material fluxes were unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>%  select('Normalized Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice(which.min("Normalized.Gini_mean")) %>% select('Normalized.Gini_quant97.5') %>% round(2)`])
+Ranked
 

### 2021-04-18 R/analyze_dominance.R

@@ -36,6 +36,7 @@ analyze_dominance <- function(ann_spp_flux_boots = flux_summaries[["annual_spp_f
     group_by(site) %>% select(contains('mean')) %>%
     dplyr::arrange(desc(flux_mg_m_y_mean)) %>%
     dplyr::mutate(rel_flux = flux_mg_m_y_mean/sum(flux_mg_m_y_mean),
+                  spp_rank = dense_rank(rel_flux),
                   partial_dominance = part_dominance(rel_flux))
     
 

### 2021-04-18 R/analyze_skew.R

@@ -34,22 +34,87 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
     return(z)
   }
   
+  skew_probs = function(emp_skew, rand_skew, skew_var = NULL,...){
+    if(is.null(var)) stop("Error: Must define the skew variable.")
+    rand_tot = nrow(rand_skew)
+    rand_skew = rand_skew[,grepl("skew",colnames(rand_skew))]
+    skew = unlist(emp_skew[,grepl(skew_var, colnames(emp_skew))])
+    extreme_vec = sapply(skew, FUN = function(x){
+      if(x > 0){
+        y = sum(rand_skew >= x, na.rm = TRUE)/rand_tot
+      } else if( x < 0){
+        y = sum(rand_skew <= x, na.rm = TRUE)/rand_tot
+      } else{
+        y = sum(rand_skew ==0, na.rm =TRUE)/rand_tot
+      }
+      y
+    })
+    extreme_vec
+  }
+  
   ## ++++ End Helper functions ++++ ##
    # debugonce(skew_est)
  
   PB_skew_boots = lorenz_analysis[["pb_ranking_boots"]] %>%
     named_group_split(site) %>%
-    map(~.x %>% named_group_split(boot_id) %>%
+    future_map(~.x %>% named_group_split(boot_id) %>%
           map(~.x %>% skew_est(., 'rel_flux', 'pb_y')) %>% 
           bind_rows(.id = 'boot_id')) %>%
     bind_rows(.id = 'site')
   
   M_skew_boots = lorenz_analysis[["M_ranking_boots"]] %>%
     named_group_split(site) %>%
-    map(~.x %>% named_group_split(boot_id) %>%
+    future_map(~.x %>% named_group_split(boot_id) %>%
           map(~.x %>% skew_est(., 'rel_flux', 'M_mg_ind')) %>%
           bind_rows(.id = 'boot_id')) %>%
     bind_rows(.id = 'site')
   
-  return(list(pb_skew_boots = PB_skew_boots, M_skew_boots = M_skew_boots))
+  stream_PB_boots = PB_skew_boots %>%
+    named_group_split(site) %>% rlist::list.subset(names(stream_order_list))
+  stream_M_boots = M_skew_boots %>%
+    named_group_split(site) %>% rlist::list.subset(names(stream_order_list))
+  stream_rand_boots = random_rankings %>%
[…]

### 2021-04-18 R/rank_spp_traits.R

@@ -16,6 +16,7 @@ rank_spp_traits <- function(ann_spp_summary = production_summaries[["ann_spp_sum
     left_join(ann_flux_summary, by = c('site', 'taxon')) %>%
     # purrr::map(~.x %>%
                  dplyr::select(site, taxon, matches('prod.*_mean'), matches('flux')) %>%
+                 dplyr::filter_at(vars(matches('flux')), all_vars(. > 0)) %>% 
                  dplyr::mutate(prod_ann_rank = dense_rank(prod_mg_m_y_mean)) %>%
                  dplyr::arrange(across(matches('.*ann_rank'))) %>%
                  dplyr::mutate(cumul_flux = cumsum(flux_mg_m_y_mean),
@@ -32,7 +33,8 @@ rank_spp_traits <- function(ann_spp_summary = production_summaries[["ann_spp_sum
     left_join(ann_flux_summary, by = c('site', 'taxon')) %>%
     # purrr::map(~.x %>%
           dplyr::select(site, taxon, matches('bio.*_mean'), matches('flux')) %>%
-          dplyr::mutate(bio_ann_rank = dense_rank(bio_mg_m_mean)) %>%
+    dplyr::filter_at(vars(matches('flux')), all_vars(. > 0)) %>% 
+    dplyr::mutate(bio_ann_rank = dense_rank(bio_mg_m_mean)) %>%
             dplyr::arrange(across(matches('.*ann_rank'))) %>%
             dplyr::mutate(cumul_flux = cumsum(flux_mg_m_y_mean),
                           cumul_bio = cumsum(bio_mg_m_mean),
@@ -50,7 +52,8 @@ rank_spp_traits <- function(ann_spp_summary = production_summaries[["ann_spp_sum
     left_join(ann_flux_summary, by = c('site', 'taxon')) %>%
     # purrr::map(~.x %>%
           dplyr::select(site, taxon, matches('n.*_mean'), matches('flux')) %>%
-          dplyr::mutate(n_ann_rank = dense_rank(n_ind_m_mean)) %>%
+    dplyr::filter_at(vars(matches('flux')), all_vars(. > 0)) %>% 
+    dplyr::mutate(n_ann_rank = dense_rank(n_ind_m_mean)) %>%
             dplyr::arrange(across(matches('.*ann_rank'))) %>%
             dplyr::mutate(cumul_flux = cumsum(flux_mg_m_y_mean),
[…]

### 2021-04-27 doc/ms/ms.Rmd
updated analysis and ms

@@
 To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
-hierarchical multivariate model [@fordyce2011]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
+hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
 $$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
@@
 $\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
-site-level model parameter and model fitting language**. Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
+site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
 from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
 values.
+
+From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials).
+Proportional similarities were calculated as:
+
+$$ PS = 1 - 0.5 \sum_{j=1}^S|p_{x,i} - p_{y,i}|$$
+
+where, *p~x,i~* is the proportion of food resource *i* in the diet of taxon *x*, *p~y,i~* is the proportion of food resource *i* in the diet of taxon *y*, and there are *S* food categories.
+Proportional similarity was calculated across all taxa within a stream based on modeled diet contributions from each taxon.
+To calculate *PS* among streams we sampled 1000 estimates of the mean stream-level diet proportions for each stream and calculated *PS* for each.
 
@@
 Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
-diet proportions, diet-specific assimilation efficiencies, $AE_{i}$, and assumed net production efficiencies, $NPE$, to estimate consumption of organic matter. For each food
-category, $\textit{i}$, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
+diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
+category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
 category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
@@
 a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
-the TBP method using simulated diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in $AE_{i}$ was
-incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
+the TBP method using modeled diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
+incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
 filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
-(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in $NPE$ was
-incorporated by resampling values from an assumed beta distribution with median $NPE$ = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
+(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
+incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
 within the *rriskDistributions* package [@belgorodski2017].
@@
 
-Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
+Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
+Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
 Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.
@@
                                                             quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
+
+drake::loadd(diet_similarity)
+min_within_overlap = diet_similarity[['within_overlap_summ']] %>% dplyr::slice_min(meanoverlap_mean)
+max_within_overlap = diet_similarity[['within_overlap_summ']] %>% dplyr::slice_max(meanoverlap_mean)
+
+# min_among_overlap = diet_similarity[[]]
+
+among_overlap_mean = mean(diet_similarity[['among_overlap_mean']], na.rm = TRUE)
+among_overlap_quant2.5 = quantile(diet_similarity[['among_overlap_mean']], 0.025, na.rm = TRUE)
+among_overlap_quant97.5 = quantile(diet_similarity[['among_overlap_mean']], 0.975, na.rm = TRUE)
+
 ```
 
-Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX).
+Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX).
 Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]).
-Calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.
+Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`).
+Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
+Diet similarity of pairwise comparisons among streams showed Pairwise comparisons among streams calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.
 
@@
 
-n_dom_min = spp_dominance %>% dplyr::slice(which.min(n_dom))
-n_dom_max = spp_dominance %>% dplyr::slice(which.max(n_dom))
+n_dom_min = spp_dominance %>% dplyr::slice_min(n_dom)
+n_dom_max = spp_dominance %>% dplyr::slice_max(n_dom)
 
@@
 
-## Trait distributions among sites and taxa
+## OM fluxes along species trait distributions among sites and taxa
 
@@
 
-pb_summ = skew_analysis[["PB_skew_summ"]]
+pb_skew_summ = skew_analysis[["PB_skew_summ"]]
 
-m_summ = skew_analysis[["M_skew_summ"]]
+m_skew_summ = skew_analysis[["M_skew_summ"]]
 ```
 
-The fluxes of OM were distributed differently across body sizes and turnover rates (**P:B**) among and within streams.
+The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
 Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
-Fluxes were skewed differentially towards larger body sizes (positive skew) among streams, with skew estimates with body size (**M**) ranging from `r m_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
-Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
+Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
+Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
 
-When compared to random
-
--- mean skew with M ranged from
-
--- The probability of observing these values of skew with pb `r pb_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`
-
--- The probability of observing these values of skew with M `r m_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`
+When compared to a random ordering while also preserving the relative distribution of fluxes among taxa, the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
+Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.
 

### 2021-04-27 doc/ms/tables-figures.Rmd
updated analysis and ms

@@
 
-\newpage
+<!-- \newpage -->
 
-Figure 2. Evenness profiles of species' relatives fluxes among streams.
+<!-- Figure 2. Evenness profiles of species' relatives fluxes among streams. -->
 
-```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE,  fig.width=5, fig.height=5, dpi = 450}
-loadd(hill_diversity_analysis)
-hill_diversity_analysis
+<!-- ```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE,  fig.width=5, fig.height=5, dpi = 450} -->
+<!-- loadd(hill_diversity_analysis) -->
+<!-- hill_diversity_analysis -->
 
-```
+<!-- ``` -->
 
@@
 
+Figure 4.
+Bootstrapped distribution of skew statistics from OM fluxes with body size, *M*, and (b) population annual production:biomass ratio relative to the distribution of skew statistics of 100,000 random orderings.
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(random_skew_fig)
+grid.draw(random_skew_fig)
+
+```
+
+\newpage
 Figure S1. Modeled diet proportions among streams

### 2021-04-27 R/analyze_diet_similarity.R

@@ -1,0 +1,101 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param full_diet_df
+##' @param modeled_diets
+analyze_diet_similarity <- function(gut_df = gut_lists[["diet_list"]], diet_predictions = modeled_diets[["diet_predictions"]]) {
+  ## ++++ Helper functions ++++ ## 
+  
+  ## ++++ End Helper functions ++++ ##
+  
+  wide_diets_list = gut_df %>% bind_rows %>% ungroup %>% select(site, month_id, taxon, id, diet_item, rel_area) %>%
+    group_by(site, month_id, taxon, id) %>%
+    pivot_wider( names_from = 'diet_item', values_from = 'rel_area') %>% 
+    named_group_split(site) %>%
+    rlist::list.subset(names(stream_order_list))
+  
+  RInSp_lists = wide_diets_list %>% map(~RInSp::import.RInSp(.x, col.header = TRUE, info.cols = c(1:4), data.type = 'double'))
+  
+  within_empirical_overlap = RInSp_lists %>% map(function(x){
+    y = RInSp::overlap(x)
+    diag(y[['overlapmatrix']]) <- NA
+    y = append(y, list(min_overlap = min(y[['overlapmatrix']], na.rm = TRUE),
+                       max_overlap = max(y[['overlapmatrix']], na.rm = TRUE)))
+    })
+  
+  within_diet_overlap_minmax = within_empirical_overlap %>% 
+    map(~.x %>% .[grepl("min|max", names(.))]) %>%
+    bind_rows(.id = 'site')
+  
+  # estimate across stream diet overlaps from modeled diets
+  
+  diet_predictions %>%
+    dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+    group_by(site, taxon, boot_id, diet_item) %>%
+    dplyr::summarise(summed_area = sum(rel_area, na.rm = TRUE)) %>%
+    dplyr::mutate(rel_area = summed_area/sum(summed_area, na.rm = TRUE)) %>%
+    select(site, taxon, boot_id, diet_item, rel_area) %>%
+    ungroup -> annual_diet_predictions
+  
+  annual_diet_predictions %>% pivot_wider(names_from = 'diet_item', values_from = 'rel_area') %>%
+    named_group_split(site) %>%
+    future_map(~.x %>% named_group_split(boot_id) %>%
[…]

### 2021-04-27 R/analyze_temp_stats.R

@@ -1,0 +1,23 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param ann_comm_boots
+##' @param stream_gini_df
+##' @param diet_similarity
+analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boots"]],
+                               stream_gini_df = gini_analysis[["stream_gini_df"]],
+                               diet_similarity, n_boot = 1e5) {
+  
+  stream_temps = stream_temp_labels %>% data.frame %>%
+    rownames_to_column('site_id') %>% setNames(., c('site_id', 'tempC'))
+
+  pb_temp_boots = ann_comm_boots %>%
+    map(~.x %>% slice_sample(n = n_boot, replace = TRUE) %>%
+          dplyr::select(site_id, pb_y)) %>%
+    bind_rows %>% left_join(stream_temps) #%>%
+    apply(.,1,function(x)
+    
+
+}

### 2021-04-27 R/plot_random_skew.R

@@ -6,41 +6,76 @@
 ##' @param skew_analysis
 ##' @param random_rankings
 plot_random_skew <- function(skew_analysis, random_rankings) {
-  
-  random_summ_pb = random_rankings %>% group_by(site) %>%
-    dplyr::summarise(across(.fns = list(mean = ~mean(.x, na.rm = TRUE),
-                                             quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
-                                             quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
-                                             quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
-                                             quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
-                                             quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
-    dplyr::select(site, matches("mean|quant2.5|quant50|quant97.5")) %>%
-    pivot_longer(-site,names_to = 'variable', values_to = 'value') %>%
-    dplyr::mutate(stat = stringr::str_extract_all(variable, '(?<=skew_)(.*)','\\1'),
-                  group = "random", 
-                  measure = "pb" )
-  random_summ_M = random_summ_pb %>% dplyr::mutate(measure = "M")
-  random_summ = random_summ_M %>% bind_rows(random_summ_pb)
+  # 
+  # random_summ_pb = random_rankings %>% group_by(site) %>%
+  #   dplyr::summarise(across(.fns = list(mean = ~mean(.x, na.rm = TRUE),
+  #                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+  #                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+  #                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+  #                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+  #                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+  #   dplyr::select(site, matches("mean|quant2.5|quant25|quant50|quant75|quant97.5")) %>%
+  #   pivot_longer(-site,names_to = 'variable', values_to = 'value') %>%
[…]

### 2021-04-27 R/plot_stream_diets.R

@@ -9,7 +9,7 @@ plot_stream_diets <- function(diet_predictions = modeled_diets[["diet_prediction
   diet_predictions %>%
     dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
     group_by(site, diet_item) %>%
-    sample_n(size = 2000, replace = FALSE) %>%
+    sample_n(size = 5000, replace = FALSE) %>%
     ggplot(aes(x = rel_area)) + geom_density(aes(group = diet_item, color = diet_item, fill = diet_item), alpha = 0.5) +
     scale_color_viridis_d(option = 'plasma')+
     scale_fill_viridis_d(option = 'plasma')+

### 2021-04-27 packages.R

@@ -8,14 +8,14 @@
                     "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
                     "viridis", "broom","bbmle","ggthemes", "ggeffects",
                     "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
-                    "rstan", "brms", "tidybayes", "parallel", "hillR")
+                    "rstan", "brms", "tidybayes", "parallel", "hillR", "RInSp")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
   # p_load_gh("jimjunker1/junkR")
   remotes::install_github("jimjunker1/junkR")
   library(junkR)
   conflict_prefer('count', 'dplyr')
   remotes::install_github("milesmcbain/dflow")
-  remotes::install_github("MilesMcBain/breakerofchains")
+  # remotes::install_github("MilesMcBain/breakerofchains")
   library(dflow)
   rm("package.list" )
   # len <<- function(data)

### 2021-05-14 doc/ms/ms.Rmd
Jules committed this for you. Respect.

@@
 source("./packages.R")
+drake::loadd(temperature_stats)
 
@@
 
+Relationships between mean annual temperature ($^\circ$C) and mean community *M* and *P:B* were assessed with bootstrapped linear regressions.
+Here, `r temperature_stats[['n_boot']]` values of mean *M* or *P:B* were resampled with replacement from each stream.
+For each resampling event, a linear model was fit between *log~e~*-transformed *M* or *P:B* and mean annual temperature.
+Response variables *M* and *P:B* were transformed to meet assumptions of normality of residuals variation.
+
 # Results
@@
 Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
 Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`).
 Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
-Diet similarity of pairwise comparisons among streams showed Pairwise comparisons among streams calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.
+Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature (Supporting Materials).
 
@@
 
+M_temp_coefs = temperature_stats[["M_temp_coefs"]]
+M_temp_coef_mean = round((exp(mean(M_temp_coefs, na.rm = TRUE)) -1)*100,1)
+M_temp_coef_quant2.5 = round((exp(quantile(M_temp_coefs, 0.025, na.rm = TRUE))-1)*100,1)
+M_temp_coef_quant97.5 = round((exp(quantile(M_temp_coefs, 0.975, na.rm = TRUE))-1)*100,1)
+
+pb_temp_coefs = temperature_stats[["pb_temp_coefs"]]
+pb_temp_coef_mean = round((exp(mean(pb_temp_coefs, na.rm = TRUE))-1)*100,1)
+pb_temp_coef_quant2.5 = round((exp(quantile(pb_temp_coefs, 0.025, na.rm = TRUE))-1)*100,1)
+pb_temp_coef_quant97.5 = round((exp(quantile(pb_temp_coefs, 0.975, na.rm = TRUE))-1)*100,1)
+
 drake::loadd(skew_analysis)
@@
 Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
+Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
+Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
+In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% IP, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
 Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).

### 2021-05-14 R/analyze_diet_similarity.R

@@ -95,7 +95,8 @@ analyze_diet_similarity <- function(gut_df = gut_lists[["diet_list"]], diet_pred
    apply(., c(1,2), function(x) quantile(x,probs = c(0.025, 0.5, 0.975), na.rm = TRUE))
   
   return(list(within_diet_overlap = within_empirical_overlap, within_diet_overlap_minmax = within_diet_overlap_minmax,
-              within_overlap_summ = within_overlap_summ, among_modeled_overlap = among_modeled_overlap, among_overlap_mean = among_overlap_mean,
+              within_overlap_summ = within_overlap_summ, among_modeled_overlap = among_modeled_overlap,
+              among_overlap_array = among_overlap_array, among_overlap_mean = among_overlap_mean, 
               pair_overlap_mean = pair_overlap_mean, pair_overlap_quantiles = pair_overlap_quantiles))
   
 }

### 2021-05-21 doc/ms/ms.Rmd
updated ms to attempt to get indent...not working yet. Pushing to other comp.

@@
 - \usepackage{amsmath}
+- \usepackage{indentfirst}
 - \linenumbers
+- \setlength\parindent{24pt}\setlength{\parskip}{0.0pt plus 1.0pt}
+indent: true
 linestretch: 1
@@
 
-Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
+|   Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
 [@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges [][] and subsequent changes to local and
@@
 
-Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010b] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+| Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010b] that underpin ecosystem functions [@deruiter1995; @thompson2012].
 The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distributions among species and trophic levels [@may1972; @mccann1998; @barnes2018].
@@
 
-Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
+|  Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
 etc.; @dell2014].
@@
 
-acquisition of resources by consumer Generally, temperature is predicted to have disproportionately higher effects on consumers relative to resources [@allen2005; @vasseur2005;
+|   acquisition of resources by consumer Generally, temperature is predicted to have disproportionately higher effects on consumers relative to resources [@allen2005; @vasseur2005;
 @oconnor2011]
 
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous
+|    Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous
 research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
@@
 
-We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
+|     We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
 characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
@@
 
-To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
+| To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
 hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
@@
 
-From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials).
+| From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials).
 Proportional similarities were calculated as:
@@
 
-Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
+| Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
 diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
@@
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
-such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
+| To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+p_S$.
+The Lorenz curve plots how a value, in this
 case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
@@
 
-Relationships between mean annual temperature ($^\circ$C) and mean community *M* and *P:B* were assessed with bootstrapped linear regressions.
+| Relationships between mean annual temperature ($^\circ$C) and mean community *M* and *P:B* were assessed with bootstrapped linear regressions.
 Here, `r temperature_stats[['n_boot']]` values of mean *M* or *P:B* were resampled with replacement from each stream.
@@
 
-Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
+| Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
 Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX).
+| Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX).
 Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
@@
 
-Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1).
+| Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1).
 The calculated inequality, i.e.
@@
 
-Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a).
+| Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a).
 For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
@@
 
-The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
+| The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
 Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
@@
 
-When compared to a random ordering while also preserving the relative distribution of fluxes among taxa, the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
+| When compared to a random ordering while also preserving the relative distribution of fluxes among taxa, the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
 Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.

### 2021-05-30 doc/coherence_ms/coherence_ms.Rmd
finalized results. start work on discussion.

---
title: "Manuscript title here"
author: 
- name: James R Junker
  affiliation: Dept. of Ecology, Montana State University, Bozeman, MT USA
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \usepackage{indentfirst}
- \linenumbers
# - \setlength\parindent{24pt}\setlength{\parskip}{0.0pt plus 1.0pt}
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
editor_options: 
  markdown: 
    wrap: 180
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Analysis

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>

### 2021-05-30 doc/ms/ms.Rmd
finalized results. start work on discussion.

--- 2021-05-14 doc/ms/ms.Rmd
@@
 - \usepackage{amsmath}
+- \usepackage{indentfirst}
 - \linenumbers
+indent: true
 linestretch: 1
@@
 csl: ecology.csl
-editor_options: 
-  markdown: 
-    wrap: 180
 ---
@@
 <!--- Title page details --->
+<!-- \setlength\parindent{24pt}\setlength{\parskip}{0.0pt plus 1.0pt} -->
 
@@
 
+Energy fluxes through invertebrate food webs restructured in response to temperature.
+Specifically, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
+Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense/both across and within communities.
+
 \newpage
@@
 <!--- warming and effects in food webs --->
-
+\setlength\parindent{24pt}
 Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
@@
 especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010b]. Yet, identifying general effects of temperature is a necessary step
-towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
+towards understanding how future warming may alter the functioning of ecosystems and the services they provide.\par
 
 <!--- Speeding up of food web: Species levels--->
-
+\setlength\parindent{24pt}
 Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010b] that underpin ecosystem functions [@deruiter1995; @thompson2012].
@@
 Direct changes through species richness effects [@gibert2019].
-Indirect through the distribution of consumer and prey species and it effects on the acquisition and allocation of resources among species [@zhang2017] --macroecology of food web dynamics and stability are controlled by the .
+Indirect through the distribution of consumer and prey species and it effects on the acquisition and allocation of resources among species [@zhang2017] --macroecology of food web dynamics and stability are controlled by the .\par
 
+\setlength\parindent{24pt}
 Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
@@
 
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous
-research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
+Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C).
+Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
 [@ogorman2012; @hood2018].
-Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2019] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to
-consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
+Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2019] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
 We, further expected that increasing temperature would reduce consumer species [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
@@
 For each resampling event, a linear model was fit between *log~e~*-transformed *M* or *P:B* and mean annual temperature.
-Response variables *M* and *P:B* were transformed to meet assumptions of normality of residuals variation.
+Response variables *M* and *P:B* were transformed to meet the assumption of normally distributed residual variation.
 
@@
 For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
-Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblage.
+Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams.
+Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences among the temperature gradient.
 
@@
 
+# analyze skewness with temperature
+M_skew_temp_coefs = temperature_stats[["M_skew_temp_coefs"]]
+M_skew_temp_coef_mean = round(mean(M_skew_temp_coefs, na.rm = TRUE), 2)
+M_skew_temp_coef_quant2.5 = round(quantile(M_skew_temp_coefs, 0.025, na.rm = TRUE),2)
+M_skew_temp_coef_quant97.5 = round(quantile(M_skew_temp_coefs, 0.975, na.rm = TRUE),2)
+
+pb_skew_temp_coefs = temperature_stats[["pb_skew_temp_coefs"]]
+pb_skew_temp_coef_mean = round(mean(pb_skew_temp_coefs, na.rm = TRUE),2)
+pb_skew_temp_coef_quant2.5 = round(quantile(pb_skew_temp_coefs, 0.025, na.rm = TRUE),2)
+pb_skew_temp_coef_quant97.5 = round(quantile(pb_skew_temp_coefs, 0.975, na.rm = TRUE),2)
+
 drake::loadd(skew_analysis)
@@
 
-When compared to a random ordering while also preserving the relative distribution of fluxes among taxa, the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
+We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
+non-random structure in the community energy fluxes.
+the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
 Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.
+The probability that
+
+The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure XX).
+Skew towards larger body sizes was negatively association with stream temperature.
+The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` to `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C .
+The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r ((sum(M_skew_temp_coefs < 0)/n_boot)*100)`% of values fell below zero.
+Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
+The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` to `r pb_skew_temp_coef_quant97.5` 95% PI).
 

### 2021-05-30 doc/ms/ms.tex
finalized results. start work on discussion.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript title here},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{indentfirst}
\linenumbers
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Manuscript title here}
\author{true}
\date{}

\begin{document}
\maketitle

\setstretch{1}
\newpage

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\setlength\parindent{24pt}

Temperature is an important abiotic variable with increasing relevance
as warming global temperatures alter the diversity, structure, and
functioning of Earth's ecosystems (Walther et al. 2002). Temperature's
effect on ecosystems manifest through complex direct and indirect
pathways such as shifting species ranges {[}{]}{[}{]} and subsequent
changes to local and regional communities {[}{]}, species adaptations
(Gibert and DeLong 2017), and through effects on individual metabolic
rates (Gillooly et al. 2001, Brown et al. 2004). While a growing body of
theoretical and empirical study has enhanced our knowledge of
temperature-mediated changes to ecosystems (O'Connor et al. 2009),
general patterns are uncertain and empirical studies often idiosyncratic
(Nelson et al. 2017a, Zhang et al. 2017), especially at higher levels of
organizations such as communities and food webs (Walther et al. 2002,
Woodward et al. 2010). Yet, identifying general effects of temperature
is a necessary step towards understanding how future warming may alter
the functioning of ecosystems and the services they provide.

\par

\setlength\parindent{24pt}

Temperature has the potential to alter the provision and maintenance of
ecosystem services by modifying the interactions among species (Woodward
et al. 2010, Brose et al. 2012) that underpin ecosystem functions (de
Ruiter et al. 1995, Thompson et al. 2012). The signature of temperature
on the stability and dynamics of food webs is present across global
climate gradients (Baiser et al. 2019) where its direct and indirect
effects alter the magnitudes and relative distributions among species
and trophic levels (May 1972, McCann et al. 1998, Barnes et al. 2018).
Direct changes through species richness effects (Gibert 2019). Indirect
through the distribution of consumer and prey species and it effects on
the acquisition and allocation of resources among species (Zhang et al.
2017) --macroecology of food web dynamics and stability are controlled
by the .

\par

\setlength\parindent{24pt}

Temperature can directly alter the distribution of species interactions
by asymmetric responses in organismal traits among species {[}e.g.,
attack rate, handling time, growth rates, etc.; Dell et al. (2014){]}.

Metabolic rates

acquisition of resources by consumer Generally, temperature is predicted
to have disproportionately higher effects on consumers relative to
resources (Allen et al. 2005, Vasseur and McCann 2005,
\textbf{oconnor2011?})

Here, we measured the patterning and distribution of organic matter
fluxes within invertebrate food webs across a natural stream temperature
gradient (\textasciitilde5 - 28\(^\circ\)C). Previous research in these
streams has shown a strong positive effect of temperature on primary
production both among streams (Padfield et al. 2017,
\textbf{demars2011?}) and within streams seasonally (O'Gorman et al.
2012, Hood et al. 2018). Consumers rely largely on autochthonous
resource (O'Gorman et al. 2012, \textbf{nelson2019?}) and therefore the
dynamics of primary production have a strong control on consumer energy
demand (Junker et al. 2020), as such, we predicted total annual OM
fluxes to consumers to scale with among stream patterns in primary
production and consumer energy demand, and therefore, increase with
temperature across streams. We, further expected that increasing
temperature would reduce consumer species (\textbf{ogorman2019?}),
thereby altering how OM fluxes are distributed within and across
communities. The distribution of OM fluxes to consumers will shift
towards relatively faster, higher turnover consumer at higher
temperatures, `speeding up' consumer dynamics both through direct
effects on consumer turnover and through a decrease in mean body size.
Seasonally, warmer streams will lead to earlier food web fluxes in
warmer compared to colder streams.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We studied six streams within the Hengill geothermal field of
southwestern Iceland (64\(^\circ\) 03'N 021\(^\circ\) 18'W) that varied
in mean annual temperature. Hengill is characterized by indirect
geothermal heating of groundwater (Arnason et al. 1969), leading to a
natural variability in water temperatures (4.5--54.0 \(^\circ\)C), but
similar solute chemistries (Friberg et al. 2009). These conditions
create a ``natural laboratory'' for isolating the effects of temperature
on ecosystem processes (O'Gorman et al. 2014, Nelson et al. 2017b). We
selected streams to maximize the temperature range, while minimizing
differences in the structural aspects of primary producers. In each
stream, we measured temperature and water depth every 15 min from July
2010 through August 2012 (U20-001-01 water-level logger, Onset Computer
Corp.~Pocasset, MA, USA). Light availability in the watershed was
measured every 15 min from atmospheric stations (HOBO pendant
temperature/light UA-002-64, Onset Computer Corp.~Pocasset, MA, USA).

\hypertarget{invertebrate-sampling}{%
\subsection{Invertebrate sampling}\label{invertebrate-sampling}}

We sampled macroinvertebrate communities approximately monthly from July
2011 to August 2012 in four streams and from October 2010 to October
2011 in two streams used in a previous study (\emph{n} = 6 streams). The
two streams were part of an experiment beginning October 2011, therefore
overlapping years were not used to exclude the impact of experimental
manipulation (see Nelson et al. 2017a, 2017b). Inter-annual comparisons
of primary and secondary production in previous studies showed minimal
differences among years in unmanipulated streams, suggesting that
combining data from different years would not significantly bias our
results (Nelson et al. 2017a, Hood et al. 2018). We collected fiver
Surber samples (0.023 m\textsuperscript{2}, 250 \(\mu\)m mesh) from
randomly selected locations within each stream. Within the sampler,
inorganic substrates were disturbed to \textasciitilde10 cm depth and
invertebrates and organic matter were removed from stones with a brush.
Samples were then preserved with 5\% formaldehyde until laboratory
analysis. In the laboratory, we split samples into coarse (\textgreater1
mm) and fine (\textless1 mm but \textgreater250 \(\mu\)m) fractions
using nested sieves and then removed invertebrates form each fraction
under a dissecting microscope (10--15 x magnification). For particularly
large samples, fine fractions were subsampled (1/2--1/16th) using a
modified Folsom plankton splitter prior to removal of invertebrates.
Subsamples were scaled to the rest of the sample assuming similar
abundance and body size distributions. Macroinvertebrates were
identified to the lowest practical taxonomic level (usually genus) with
taxonomic keys (Peterson 1977, Merritt et al. 2008, Andersen et al.
2013). Taxon-specific abundance and biomass were scaled to a per meter
basis by dividing by the Surber sampler area.

\hypertarget{secondary-production}{%
\subsection{Secondary Production}\label{secondary-production}}

Daily secondary production of invertebrate taxa was calculated using the
instantaneous growth rate method {[}IGR; Benke and Huryn (2017){]}.
Growth rates were determined using taxon appropriate approaches
described in (Junker et al. 2020). Briefly, growth rates of common taxa
(e.g., Chironomidae spp., Radix balthica, etc.) were determined using
\emph{in situ} chambers (Huryn and Wallace 1986). Multiple individuals
(\emph{n} = 5--15) within small size categories (\textasciitilde1 mm
length range) were photographed next to a field micrometer, placed into
the stream within pre-conditioned chambers for 7--15 days, after which
they were again photographed. Individual lengths were measured from
field pictures using image analysis software (Schindelin et al. 2012),
and body lengths were converted to mass (mg ash-free dry mass
{[}AFDM{]}) using published length-mass regressions (Benke et al. 1999,
O'Gorman et al. 2012, Hannesdóttir et al. 2013). Growth rates (\emph{g},
d\textsuperscript{-1}) were calculated by the changes in mean body size
(\emph{W}) over a given time interval (\emph{t}) with the following
equation:

\[g = log_e ( W_{t+\Delta t} / W_t) / \Delta t\]

Variability in growth rates was estimated by bootstrapping through
repeated resampling of individual lengths with replacement (\emph{n} =
500). For taxa which exhibit synchronous growth and development (e.g.,
Simuliidae spp., some Chironomidae spp., etc.), we examined temporal
changes in length-frequency distributions and calculated growth rates
and uncertainty using a bootstrap technique similar to that described in
Benke and Huryn (2017). Individual Lengths were converted to mg AFDM
using published length-mass regression cited above and size-frequency
histograms were visually inspected for directional changes in body size
through time. For each date, size-frequency distributions were resampled
with replacement (\emph{n} = 500) and growth rates estimated from
equation 1. We prevented the calculation of negative growth rates by
requiring \(W_{t + \Delta t}\) \textgreater{} \(W_t\). To estimate
growth rates of taxa for which growth could not be estimated
empirically, we developed stream-specific growth rate models by
constructing multivariate linear regressions of empirical growth data
against body size and temperature within each stream. To estimate
uncertainty in production of each taxon, we used a bootstrapping
technique that resampled measured growth rates, in addition to abundance
and size distributions from individual samples. For each iteration
(\emph{n} = 1000), size-specific growth rates were multiplied by mean
interval biomass for each size class and the number of days between
sample dates to estimate size class-specific production. For each
interval, size classes were summed for each taxon to calculate total
population-level production. Intervals were summed to estimate annual
secondary production.

\hypertarget{diet-analysis}{%
\subsection{Diet analysis}\label{diet-analysis}}

\textbf{Come back and confirm this section} Macroinvertebrate diets were
quantified for dominant taxa in each stream. We focused on numerically
abundant taxa and/or taxa with relatively high annual production. A
minimum of five individuals were selected from samples, and, when
possible included individuals of different size classes to account for
ontogenetic shifts in diet. We included individuals from different
seasons to capture concurrent ontogenetic and seasonal changes. For
small-bodied taxa, we combined multiple individuals (\emph{n} = 3--5) to
ensure samples contained enough material for quantification. We used
methods outlined in Rosi-Marshall (2016) to remove gut tracts and
prepare gut content slides. Briefly, we removed the foregut from each
individual or collection of individuals and sonicated gut contents in
water for 30 seconds. Gut content slurries were filtered onto gridded
nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 \(\mu\)m
pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 \(^\circ\)C
for 15 min, placed on a microscope slide, cleared with Type B immersion
old, and covered with a cover slip. We took 5--10 random photographs
under 200--400x magnification, depending on the density of particles,
using a digital camera mounted on a compound microscope. From these
photographs we identified all particles within each field and measured
the relative area of particles using image analysis software (Schindelin
et al. 2012). We identified particles as diatoms, green and filamentous
algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (bryophytes), and animal material. We calculated the proportion
of each food category in the gut by dividing their summed area by the
total area of all particles. Gut contents of many predators were empty
or contained unidentifiable, macerated prey. For these taxa, we assumed
100\% animal material.

To estimate variability in diet compositions and to impute missing
values for non-dominant, yet present, taxa, we modeled the diet
proportions within each stream using a

hierarchical multivariate model (\textbf{coblentz2017?}). Here, the diet
of a consumer population, \emph{i}, is a multinomial
vector,\(\overrightarrow{y_i}\), of
\[\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)\]
\[\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) \]
where, \(\overrightarrow{p_i}\), is a vector of consumer diet
proportions, \(\overrightarrow{q_i}\) is a vector of the population's
diet proportions and \(\alpha\) is a concentration parameter of the
Dirichlet process. We used uniform priors for \(\overrightarrow{q_i}\)
and \(\alpha\),
\[\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})\]
\[\alpha \sim Uniform(0,\textit{c})\] where,
\(\overrightarrow{\textbf{1}}\) is a vector of ones the same length of
basal resource types and \(\textit{c}\) is the presumed maximum value
the concentration value. \textbf{add in site-level model parameter and
model fitting language} . Models were fit in Stan with the `brms'
package in R (Bürkner 2017). For non-dominant taxa, diet proportions
were imputed from the hierarchical model by resampling from posterior
distributions. Importantly, this process allowed to maintain the
hierarchical structure of the data when imputing missing values.

From modeled diet compositions, we estimated trophic redundancy within
and across stream food webs by calculating proportional similarities
{[}\emph{PS}; (\textbf{whittaker1952?}){]} among modeled diet estimates
(proportional similarity estimates from empirical diets give similar
results to modeled estimates; Supporting Materials). Proportional
similarities were calculated as:

\[ PS = 1 - 0.5 \sum_{j=1}^S|p_{x,i} - p_{y,i}|\]

where, \emph{p\textsubscript{x,i}} is the proportion of food resource
\emph{i} in the diet of taxon \emph{x}, \emph{p\textsubscript{y,i}} is
the proportion of food resource \emph{i} in the diet of taxon \emph{y},
and there are \emph{S} food categories. Proportional similarity was
calculated across all taxa within a stream based on modeled diet
contributions from each taxon. To calculate \emph{PS} among streams we
sampled 1000 estimates of the mean stream-level diet proportions for
each stream and calculated \emph{PS} for each.

\hypertarget{organic-matter-consumption-estimates}{%
\subsection{Organic Matter Consumption
Estimates}\label{organic-matter-consumption-estimates}}

Consumption fluxes (g m\textsuperscript{-2} t\textsuperscript{-1}) were
calculated using the trophic basis of production method (TBP; (Benke and
Wallace 1980). Taxon-specific secondary production estimates were
combined with

diet proportions, diet-specific assimilation efficiencies,
\emph{AE\textsubscript{i}}, and assumed net production efficiencies,
\emph{NPE}, to estimate consumption of organic matter. For each food
category, \emph{i}, diet proportions were multiplied by the gross growth
efficiency (\(GGE_{i} = AE_{i} * NPE\)) to calculate the relative
production attributable to each food category. The relative production
from each food type was then multiplied by the interval-level production
and finally divided by \(GGE_{i}\) to estimate consumption of organic
matter from each food category by a consumer (Benke and Wallace 1980).
Consumption was calculated for each taxon across sampling intervals
(typically \textasciitilde1 month). Total interval consumption was
calculated by summing across all taxa, while annual consumption was
calculated by summing across all taxa and intervals. Variability in
consumption estimates was estimated through a Monte Carlo approach,
wherein bootstrapped vectors of secondary production for each taxon (see
\emph{Secondary production} methods above) were resampled and
consumption estimated with the TBP method using modeled diet proportions
(see \emph{Diet analysis} above), diet-specific assimilation
efficiencies, and net production efficiency. Variability in
\emph{AE\textsubscript{i}} was incorporated by resampling values from
beta distributions fit to median and 2.5\% and 97.5\% percentiles for
each diet item: diatoms = 0.30 (95\% percentile interval (PI):
0.24-0.36), filamentous and green algae = 0.30 (95\% PI: 0.24-0.36),
cyanobacteria = 0.10 (95\% PI: 0.08-0.12), amorphous detritus = 0.10
(95\% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) =
0.1 (95\% PI:: 0.08-0.12), and animal material = 0.7 (95\% PI:
0.56-0.84)(Welch 1968, Benke and Wallace 1980, 1997, Cross et al. 2007,
2011). Variability in \emph{NPE} was incorporated by resampling values
from an assumed beta distribution with median \emph{NPE} = 0.45 (95\% PI
= 0.4-0.5). Beta distributions were fit using the `get.beta.par()'
function within the \emph{rriskDistributions} package (Belgorodski et
al. 2017).

\hypertarget{quantifying-the-distribution-of-food-web-fluxes}{%
\subsection{Quantifying the distribution of food web
fluxes}\label{quantifying-the-distribution-of-food-web-fluxes}}

\hypertarget{evenness-among-consumers}{%
\subsubsection{Evenness Among
consumers}\label{evenness-among-consumers}}

To visualize and quantify how evenly OM fluxes were distributed among
consumers within a stream, we constructed Lorenz curves (Lorenz 1905) on
ordered relative consumption fluxes, such that in a community with \(S\)
species and the relative consumption of species \emph{i}, \(p_i\), is
ordered \(p_1 \leq p_2 \leq ... p_S\). The Lorenz curve plots how a
value, in this

case OM flux, accumulates with increasing cumulative proportion of
species. In a community with perfectly equal distribution of OM
consumption among species, the Lorenz curve is simply a straight
diagonal line. Deviation from perfect equality was calculated as the
Gini coefficient (Gini 1921), normalized for differences in \(S\) among
streams, \(G^*\) (Solomon 1975, Chao and Ricotta 2019):
\[ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)\]

\hypertarget{distribution-along-species-trait-axes}{%
\subsubsection{Distribution along species' trait
axes}\label{distribution-along-species-trait-axes}}

We were interested in how OM fluxes were distributed (randomly
vs.~non-randomly) in relation to species traits (i.e., body size,
\(P:B\) ratio, population biomass) across the temperature gradient. We
used a permutation analyses to test for non-random patterns in OM flux
with species traits. First, we ordered species based on within-stream
ranking of annual population traits (i.e, \(M\), \(P:B\)). We then
calculated a measure of skewness, \(Sk_{flux}\), based on quartiles of
the distribution of OM fluxes in relation to species traits as:

\[Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}\]

where, \(f_{Qx}\), is the cumulative flux at some quantile, \(Qx\), of
the community trait distribution. To determine the probability of
observing the skewness we observe in the data compared to random
ordering, we constructed a distribution of skewness estimates from
random species ordering while maintaining the relative distribution of
OM fluxes. The number of unique orderings of species increases to
computationally intractable numbers very quickly (e.g., \(S!\)),
therefore we permuted 1,000,000 random species orderings and calculating
the skew in the cumulative distribution of annual OM fluxes. We then use
this random distribution to estimate the probability of observing a
skewness as extreme or greater.

\hypertarget{statistical-analyses}{%
\subsection{Statistical Analyses}\label{statistical-analyses}}

Relationships between mean annual temperature (\(^\circ\)C) and mean
community \emph{M} and \emph{P:B} were assessed with bootstrapped linear
regressions. Here, \ensuremath{10^{5}} values of mean \emph{M} or
\emph{P:B} were resampled with replacement from each stream. For each
resampling event, a linear model was fit between
\emph{log\textsubscript{e}}-transformed \emph{M} or \emph{P:B} and mean
annual temperature. Response variables \emph{M} and \emph{P:B} were
transformed to meet assumptions of normality of residuals variation.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{community-om-fluxes}{%
\subsection{Community OM fluxes}\label{community-om-fluxes}}

Annual community energy demand mirrored patterns of secondary production
previously reported (Junker et al. 2020). Community energy demand varied
\textasciitilde44.2-fold across streams (1.005{[}0.556 , 1.555{]} to
44.4 {[}32.4 , 57.8{]}; g AFDM \(m^{-2} y^{-1}\) mean {[}95\% percentile
interval (PI){]}) and was positively related to temperature. Total OM
flux through the consumer community was strongly associated with
community energy demand and varied from 3.9 {[}2.1,6.2{]} to
177.4{[}125.6,236.6{]} g AFDM \(m^{-2} y^{-1}\).

Patterns of OM flux among streams were most closely tied to total
consumer energy demands as consumer diets exhibited high similarity
among streams (Figure SX). Diets composition among all streams were
dominated by diatoms (44.1\% {[}c(\texttt{2.5\%} = 0),c(\texttt{97.5\%}
= 75.5){]}), amorphous detritus (17.4\% {[}c(\texttt{2.5\%} =
0),c(\texttt{97.5\%} = 32.3){]}), and green algae (13.2\%
{[}c(\texttt{2.5\%} = 0),c(\texttt{97.5\%} = 42.6){]}). Within streams,
diet similarity ranged from 0.7 (0.66 -- 0.73) to 0.75 (0.71 -- 0.79).
Among streams, diet overlap was similarly high and mean overlap among
all streams was 0.89\% (0.84 -- 0.92 95\% PI). Diet similarity of
pairwise comparisons among streams showed little differences in diet
among streams and no clear relationship with temperature (Supporting
Materials).

\hypertarget{evenness-of-om-fluxes-within-streams}{%
\subsection{Evenness of OM fluxes within
streams}\label{evenness-of-om-fluxes-within-streams}}

Generally, the material fluxes within a stream were distributed
unequally among consumers, however, this varied among streams (Figure 1;
Figure S1). The calculated inequality, i.e.~Gini coefficient, ranged
from 0.07 {[}0.05 , 0.1{]} to 0.27 {[}0.24 , 0.31{]}; Table 1).
Differences in inequality were partly attributed to consumer species
richness among streams which ranged from 14 to 34 consumers. Patterns of
material fluxes were still unequally distributed among consumers even
after correcting for differences in species richness (Normalized Gini
coefficient: 0.04 {[}0.02 , 0.07{]} to 0.25 {[}0.21 , 0.28{]}; Table 1).

Unequal distributions of fluxes within streams corresponded to very
different patterns in dominance of OM fluxes across streams (Figure 1a).
For example, in an absolute sense, \textasciitilde85\% of total flux was
contributed by 2 to 11 species (0.85\% to 0.85\% of flux, respectively).
Relatively, this flux was attributed by 3\% to 29\% of the species
assemblage.

\hypertarget{om-fluxes-along-species-trait-distributions-among-sites-and-taxa}{%
\subsection{OM fluxes along species trait distributions among sites and
taxa}\label{om-fluxes-along-species-trait-distributions-among-sites-and-taxa}}

The fluxes of OM were distributed differently across body sizes and
turnover rates (\emph{P:B}) among and within streams. Across streams,
mean body size of taxa ranged from 0.13 to 2.66 and mean annual P:B
ranged from 4.23 to 31.67 (Figure 2). Both, \emph{M} and \emph{P:B}
showed associations with mean annual stream temperature that were
negative and positive, respectively. Generally, mean \emph{M} of the
community decreased -9.5\% (95\% PI, -11.1\% -- -8\%) for each increase
in 1\(^\circ\)C. In contrast, mean population \emph{P:B} of the
community increased 18.8\% (95\% IP, 17\% -- 20.7\%) for each
1\(^\circ\)C in mean annual stream temperature. Fluxes were skewed
differentially towards larger body sizes (positive skew) or towards
smaller body sizes (negative skew) among streams, with skew estimates
with body size (\emph{M}) ranging from 0.13 to -0.84 (Figure 3).
Similarly, skew in fluxes towards high turnover taxa varied among
streams ranging from 0.25 to 1 (Figure 3).

When compared to a random ordering while also preserving the relative
distribution of fluxes among taxa, the probability of observing a
similar or more extreme skew of within stream OM fluxes in relation to
species body size ranged from 0.16 to 0.38. Similarly, the probability
of a more extremely skewed distribution in relation to population
biomass turnover ranged from 0.09 to 0.34.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Jeff Wesner and Abe Kanz for code sharing and discussions on modeling
diet proportions.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-allen2005}{}%
Allen, A. P., J. F. Gillooly, and J. H. Brown. 2005. Linking the global
carbon cycle to individual metabolism. Functional Ecology 19:202--213.

\leavevmode\hypertarget{ref-andersen2013}{}%
Andersen, T., P. S. Cranston, and J. H. Epler. 2013. Chironomidae of the
{Holarctic} region: {Keys} and diagnoses, {Part} 1. {Media Tryck},
{Lund, Sweden}.

\leavevmode\hypertarget{ref-arnason1969}{}%
Arnason, B., P. Theodorsson, S. Björnsson, and K. Saemundsson. 1969.
Hengill, a high temperature thermal area in {Iceland}. Bulletin
Volcanologique 33:245--259.

\leavevmode\hypertarget{ref-baiser2019}{}%
Baiser, B., D. Gravel, A. R. Cirtwill, J. A. Dunne, A. K. Fahimipour, L.
J. Gilarranz, J. A. Grochow, D. Li, N. D. Martinez, A. McGrew, T.
Poisot, T. N. Romanuk, D. B. Stouffer, L. B. Trotta, F. S. Valdovinos,
R. J. Williams, S. A. Wood, and J. D. Yeakel. 2019. Ecogeographical
rules and the macroecology of food webs. Global Ecology and Biogeography
28:1204--1218.

\leavevmode\hypertarget{ref-barnes2018}{}%
Barnes, A. D., M. Jochum, J. S. Lefcheck, N. Eisenhauer, C. Scherber, M.
I. O'Connor, P. de Ruiter, and U. Brose. 2018. Energy {Flux}: {The Link}
between {Multitrophic Biodiversity} and {Ecosystem Functioning}. Trends
in Ecology \& Evolution 33:186--197.

\leavevmode\hypertarget{ref-belgorodski2017}{}%
Belgorodski, N., M. Greiner, K. Tolksdorf, and K. Schueller. 2017.
{rriskDistributions}: {Fitting Distributions} to {Given Data} or {Known
Quantiles}.

\leavevmode\hypertarget{ref-benke2017}{}%
Benke, A. C., and A. D. Huryn. 2017. Secondary production and
quantitative food webs. Pages 235--254 Methods in {Stream Ecology}.
{Elsevier}.

\leavevmode\hypertarget{ref-benke1999}{}%
Benke, A. C., A. D. Huryn, L. A. Smock, and J. B. Wallace. 1999.
Length-{Mass Relationships} for {Freshwater Macroinvertebrates} in
{North America} with {Particular Reference} to the {Southeastern United
States}. Journal of the North American Benthological Society
18:308--343.

\leavevmode\hypertarget{ref-benke1980}{}%
Benke, A. C., and J. B. Wallace. 1980. Trophic basis of production among
net-spinning caddisflies in a southern appalachain stream. Ecology
61:108--118.

\leavevmode\hypertarget{ref-benke1997}{}%
Benke, A. C., and J. B. Wallace. 1997. Trophic {Basis} of {Production
Among Riverine Caddisflies}: {Implications} for {Food Web Analysis}.
Ecology 78:1132--1145.

\leavevmode\hypertarget{ref-brose2012}{}%
Brose, U., J. A. Dunne, Montoya José M., O. L. Petchey, F. D. Schneider,
and U. Jacob. 2012. Climate change in size-structured ecosystems.
Philosophical Transactions of the Royal Society B: Biological Sciences
367:2903--2912.

\leavevmode\hypertarget{ref-brown2004}{}%
Brown, J. H., J. F. Gillooly, A. P. Allen, V. M. Savage, and G. B. West.
2004. Toward a {Metabolic Theory} of {Ecology}. Ecology 85:1771--1789.

\leavevmode\hypertarget{ref-burkner2017}{}%
Bürkner, P.-C. 2017. Brms: {An R Package} for {Bayesian Multilevel
Models Using Stan}. Journal of Statistical Software 80:1--28.

\leavevmode\hypertarget{ref-chao2019}{}%
Chao, A., and C. Ricotta. 2019. Quantifying evenness and linking it to
diversity, beta diversity, and similarity. Ecology 100:e02852.

\leavevmode\hypertarget{ref-cross2011}{}%
Cross, W. F., C. V. Baxter, K. C. Donner, E. J. Rosi-Marshall, T. A.
Kennedy, R. O. Hall, H. A. W. Kelly, and R. S. Rogers. 2011. Ecosystem
ecology meets adaptive management: Food web response to a controlled
flood on the {Colorado River}, {Glen Canyon}. Ecological Applications
21:2016--2033.

\leavevmode\hypertarget{ref-cross2007}{}%
Cross, W. F., J. B. Wallace, and A. D. Rosemond. 2007. Nutrient
{Enrichment Reduces Constraints} on {Material Flows} in a
{Detritus}-{Based Food Web}. Ecology 88:2563--2575.

\leavevmode\hypertarget{ref-deruiter1995}{}%
de Ruiter, P. C., A.-M. Neutel, and J. C. Moore. 1995. Energetics,
{Patterns} of {Interaction Strengths}, and {Stability} in {Real
Ecosystems}. Science 269:1257--1260.

\leavevmode\hypertarget{ref-dell2014}{}%
Dell, A. I., S. Pawar, and V. M. Savage. 2014. Temperature dependence of
trophic interactions are driven by asymmetry of species responses and
foraging strategy. Journal of Animal Ecology 83:70--84.

\leavevmode\hypertarget{ref-fordyce2011}{}%
Fordyce, J. A., Z. Gompert, M. L. Forister, and C. C. Nice. 2011. A
{Hierarchical Bayesian Approach} to {Ecological Count Data}: {A Flexible
Tool} for {Ecologists}. PLOS ONE 6:e26785.

\leavevmode\hypertarget{ref-friberg2009}{}%
Friberg, N., J. B. Dybkjær, J. S. Olafsson, G. M. Gislason, S. E.
Larsen, and T. L. Lauridsen. 2009. Relationships between structure and
function in streams contrasting in temperature. Freshwater Biology
54:2051--2068.

\leavevmode\hypertarget{ref-gibert2019}{}%
Gibert, J. P. 2019. Temperature directly and indirectly influences food
web structure. Scientific Reports 9:5312.

\leavevmode\hypertarget{ref-gibert2017}{}%
Gibert, J. P., and J. P. DeLong. 2017. Phenotypic variation explains
food web structural patterns. Proceedings of the National Academy of
Sciences 114:11187--11192.

\leavevmode\hypertarget{ref-gillooly2001}{}%
Gillooly, J. F., J. H. Brown, G. B. West, V. M. Savage, and E. L.
Charnov. 2001. Effects of size and temperature on metabolic rate.
Science (New York, N.Y.) 293:2248--2251.

\leavevmode\hypertarget{ref-gini1921}{}%
Gini, C. 1921. Measurement of {Inequality} of {Incomes}. The Economic
Journal 31:124--126.

\leavevmode\hypertarget{ref-hannesdottir2013}{}%
Hannesdóttir, E. R., G. M. Gíslason, J. S. Ólafsson, Ó. P. Ólafsson, and
E. J. O'Gorman. 2013. Increased {Stream Productivity} with {Warming
Supports Higher Trophic Levels}. Advances in Ecological Research
48:285--342.

\leavevmode\hypertarget{ref-hood2018}{}%
Hood, J. M., J. P. Benstead, W. F. Cross, A. D. Huryn, P. W. Johnson, G.
M. Gíslason, J. R. Junker, D. Nelson, J. S. Ólafsson, and C. Tran. 2018.
Increased resource use efficiency amplifies positive response of aquatic
primary production to experimental warming. Global Change Biology
24:1069--1084.

\leavevmode\hypertarget{ref-huryn1986}{}%
Huryn, A. D., and J. B. Wallace. 1986. A method for obtaining in situ
growth rates of larval {Chironomidae} ({Diptera}) and its application to
studies of secondary Production1. Limnology and Oceanography
31:216--221.

\leavevmode\hypertarget{ref-junker2020}{}%
Junker, J. R., W. F. Cross, J. P. Benstead, A. D. Huryn, J. M. Hood, D.
Nelson, G. M. Gíslason, and J. S. Ólafsson. 2020. Resource supply
governs the apparent temperature dependence of animal production in
stream ecosystems. Ecology Letters 23:1809--1819.

\leavevmode\hypertarget{ref-lorenz1905}{}%
Lorenz, M. O. 1905. Methods of {Measuring} the {Concentration} of
{Wealth}. Publications of the American Statistical Association 9:209.

\leavevmode\hypertarget{ref-may1972}{}%
May, R. M. 1972. Will a {Large Complex System} be {Stable}? Nature
238:413--414.

\leavevmode\hypertarget{ref-mccann1998}{}%
McCann, K., A. Hastings, and G. R. Huxel. 1998. Weak trophic
interactions and the balance of nature. Nature 395:794--798.

\leavevmode\hypertarget{ref-merritt2008}{}%
Merritt, R. W., K. W. Cummins, and M. B. Berg, editors. 2008. An
{Introduction} to the {Aquatic Insects} of {North America}. Fourth.
{Kendall/Hunt Publishing Co.}, {Dubuque, IA}.

\leavevmode\hypertarget{ref-nelson2017}{}%
Nelson, D., J. P. Benstead, A. D. Huryn, W. F. Cross, J. M. Hood, P. W.
Johnson, J. R. Junker, G. M. Gíslason, and J. S. Ólafsson. 2017a. Shifts
in community size structure drive temperature invariance of secondary
production in a stream-warming experiment. Ecology 98:1797--1806.

\leavevmode\hypertarget{ref-nelson2017a}{}%
Nelson, D., J. P. Benstead, A. D. Huryn, W. F. Cross, J. M. Hood, P. W.
Johnson, J. R. Junker, G. M. Gíslason, and J. S. Ólafsson. 2017b.
Experimental whole-stream warming alters community size structure.
Global Change Biology 23:2618--2628.

\leavevmode\hypertarget{ref-oconnor2009}{}%
O'Connor, M. I., M. F. Piehler, D. M. Leech, A. Anton, and J. F. Bruno.
2009. Warming and {Resource Availability Shift Food Web Structure} and
{Metabolism}. PLOS Biology 7:e1000178.

\leavevmode\hypertarget{ref-ogorman2014}{}%
O'Gorman, E. J., J. P. Benstead, W. F. Cross, N. Friberg, J. M. Hood, P.
W. Johnson, B. D. Sigurdsson, and G. Woodward. 2014. Climate change and
geothermal ecosystems: Natural laboratories, sentinel systems, and
future refugia. Global Change Biology 20:3291--3299.

\leavevmode\hypertarget{ref-ogorman2012}{}%
O'Gorman, E. J., D. E. Pichler, G. Adams, J. P. Benstead, H. Cohen, N.
Craig, W. F. Cross, B. O. L. Demars, N. Friberg, G. M. Gíslason, R.
Gudmundsdóttir, A. Hawczak, J. M. Hood, L. N. Hudson, L. Johansson, M.
P. Johansson, J. R. Junker, A. Laurila, J. R. Manson, E. Mavromati, D.
Nelson, J. S. Ólafsson, D. M. Perkins, O. L. Petchey, M. Plebani, D. C.
Reuman, B. C. Rall, R. Stewart, M. S. A. Thompson, and G. Woodward.
2012. Impacts of {Warming} on the {Structure} and {Functioning} of
{Aquatic Communities}. Pages 81--176 Advances in {Ecological Research}.
{Elsevier}.

\leavevmode\hypertarget{ref-padfield2017}{}%
Padfield, D., C. Lowe, A. Buckling, R. Ffrench-Constant, S. Jennings, F.
Shelley, J. S. Ólafsson, and G. Yvon-Durocher. 2017. Metabolic
compensation constrains the temperature dependence of gross primary
production. Ecology Letters 20:1250--1260.

\leavevmode\hypertarget{ref-peterson1977}{}%
Peterson, B. V. 1977. Black flies of {Iceland} ({Diptera}-{Simuliidae}).
Canadian Entomologist 109:449--472.

\leavevmode\hypertarget{ref-rosi-marshall2016}{}%
Rosi-Marshall, E. J., H. A. Wellard Kelly, R. O. Hall, and K. A. Vallis.
2016. Methods for quantifying aquatic macroinvertebrate diets.
Freshwater Science 35:229--236.

\leavevmode\hypertarget{ref-schindelin2012}{}%
Schindelin, J., I. Arganda-Carreras, E. Frise, V. Kaynig, M. Longair, T.
Pietzsch, S. Preibisch, C. Rueden, S. Saalfeld, B. Schmid, J.-Y.
Tinevez, D. J. White, V. Hartenstein, K. Eliceiri, P. Tomancak, and A.
Cardona. 2012. Fiji: An open-source platform for biological-image
analysis. Nature Methods 9:676--682.

\leavevmode\hypertarget{ref-solomon1975}{}%
Solomon, D. L. 1975. A comparative approach to species diversity:7.

\leavevmode\hypertarget{ref-thompson2012}{}%
Thompson, R. M., U. Brose, J. A. Dunne, R. O. Hall, S. Hladyz, R. L.
Kitching, N. D. Martinez, H. Rantala, T. N. Romanuk, D. B. Stouffer, and
J. M. Tylianakis. 2012. Food webs: Reconciling the structure and
function of biodiversity. Trends in Ecology \& Evolution 27:689--697.

\leavevmode\hypertarget{ref-vasseur2005}{}%
Vasseur, D. A., and K. S. McCann. 2005. A {Mechanistic Approach} for
{Modeling Temperature}-{Dependent Consumer}-{Resource Dynamics}. The
American Naturalist 166:184--198.

\leavevmode\hypertarget{ref-walther2002}{}%
Walther, G.-R., E. Post, P. Convey, A. Menzel, C. Parmesan, T. J. C.
Beebee, J.-M. Fromentin, O. Hoegh-Guldberg, and F. Bairlein. 2002.
Ecological responses to recent climate change. Nature 416:389--395.

\leavevmode\hypertarget{ref-welch1968}{}%
Welch, H. E. 1968. Relationships between {Assimiliation Efficiencies}
and {Growth Efficiencies} for {Aquatic Consumers}. Ecology 49:755--759.

\leavevmode\hypertarget{ref-woodward2010b}{}%
Woodward, G., J. P. Benstead, O. S. Beveridge, J. Blanchard, T. Brey, L.
E. Brown, W. F. Cross, N. Friberg, T. C. Ings, U. Jacob, S. Jennings, M.
E. Ledger, A. M. Milner, J. M. Montoya, E. O'Gorman, J. M. Olesen, O. L.
Petchey, D. E. Pichler, D. C. Reuman, M. S. A. Thompson, F. J. F. Van
Veen, and G. Yvon-Durocher. 2010. Ecological {Networks} in a {Changing
Climate}. Pages 71--138 Advances in {Ecological Research}. {Elsevier}.

\leavevmode\hypertarget{ref-zhang2017}{}%
Zhang, L., D. Takahashi, M. Hartvig, and K. H. Andersen. 2017. Food-web
dynamics under climate change. Proceedings of the Royal Society B:
Biological Sciences 284:20171772.

\end{CSLReferences}

\end{document}

### 2021-05-30 R/analyze_diversity.R

@@ -1,0 +1,28 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param production_boots
+analyze_diversity <- function(production_boots) {
+
+  # stream community-level summaries 
+  # interval level community summary
+  int_spp_wide = production_boots[["int_spp_summary"]] %>% bind_rows %>%
+    select(site_id:prod_mg_m_int_mean) %>% replace_na(list(prod_mg_m_int_mean = 0)) %>%
+    pivot_wider(names_from = 'taxon_id', values_from = 'prod_mg_m_int_mean', values_fill = 0)
+  
+  set.seed(123)
+  NMDS = vegan::metaMDS(int_spp_wide %>% ungroup %>%select(-site_id, -date_id))
+  
+  NMDS.scrs = as.data.frame(vegan::scores(NMDS, display = 'sites')) %>% 
+    bind_cols(int_spp_wide %>% select(site_id, date_id)) %>%
+    select(site_id, date_id, everything()) %>%
+    dplyr::mutate(site_id = factor(site_id, levels = names(stream_order_list))) %>%
+    group_by(site_id) %>% dplyr::arrange(date_id)
+  # 
+  # ggplot(NMDS.scrs, aes(x = NMDS1, y = NMDS2)) + 
+  #   geom_point(aes(color = site_id))+
+  #   geom_path(aes(group = site_id, color = site_id))
+  
+  }

### 2021-05-30 R/analyze_skew.R

@@ -77,8 +77,8 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
     named_group_split(site) %>% rlist::list.subset(names(stream_order_list))
   
   # debugonce(skew_probs)
-  PB_skew_probs = map2(stream_PB_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
-  M_skew_probs = map2(stream_M_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
+  PB_skew_probs = future_map2(stream_PB_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
+  M_skew_probs = future_map2(stream_M_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
 
   PB_skew_summ = PB_skew_boots %>%
     group_by(site) %>%
@@ -116,5 +116,5 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
                                                               quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                               quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))))
   
-  return(list(pb_skew_boots = PB_skew_boots, M_skew_boots = M_skew_boots, PB_skew_probs = PB_skew_probs, M_skew_probs = M_skew_probs, PB_skew_summ = PB_skew_summ, M_skew_summ = M_skew_summ))
+  return(list(pb_skew_boots = PB_skew_boots, M_skew_boots = M_skew_boots, pb_skew_probs = PB_skew_probs, M_skew_probs = M_skew_probs, pb_skew_summ = PB_skew_summ, M_skew_summ = M_skew_summ))
 }

### 2021-05-30 R/plan.R

@@ -50,6 +50,8 @@ the_plan <-
   skew_analysis = analyze_skew(lorenz_analysis, random_rankings),
   # diversity analyses
   hill_diversity_analysis = analyze_hill_diversity(flux_summaries[["annual_spp_flux_summary"]]),
+  # community diversity change through time
+  diversity_analysis = analyze_diversity(production_boots),
   #partial dominance
   partial_dominance_analysis = analyze_dominance(flux_summaries[["annual_spp_flux_boots"]]),
   #
@@ -58,7 +60,8 @@ the_plan <-
   diet_similarity = analyze_diet_similarity(gut_lists[["diet_list"]], modeled_diets[["diet_predictions"]]),
   # temperature trait relationships
   temperature_stats = analyze_temp_stats(production_boots[['ann_comm_boots']], gini_analysis[['stream_gini_df']],
-                                         diet_similarity[['among_modeled_overlap']], n_boot = 1e5),
+                                         diet_similarity[['among_modeled_overlap']], skew_analysis, n_boot = 1e5),
+  
 
    ### figures
   #
@@ -66,7 +69,8 @@ the_plan <-
   #
   diet_similarity_analysis = plot_diet_similarity(diet_similarity),
   #
-  annual_spp_flux_fig = plot_spp_flux(flux_summaries[["annual_spp_flux_summary"]], environment_data[["stream_temp_labels"]]),
+  annual_spp_flux_fig = plot_spp_flux(flux_summaries[["annual_spp_flux_summary"]], 
+                                      environment_data[["stream_temp_labels"]]),
   #
   # evenness_profile_fig = plot_evenness_profile(hill_diversity_analysis),
   #
@@ -97,4 +101,11 @@ the_plan <-
   #     file_out("doc/./ms/tables-figures.docx")
   #   }
   # )
+  
+  target_name = target(
+    command = {
+      rmarkdown::render(knitr_in("doc/./coherence_ms/coherence_ms.Rmd"))
+      file_out("doc/./coherence_ms/coherence_ms.docx")
+    }
+  )
 )

### 2021-05-31 doc/ms/ms.Rmd
update writing.

@@
 non-random structure in the community energy fluxes.
-the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
+The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
 Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.
@@
 
-# Discussion
+#Discussion
+
+Changing global temperatures are altering the pathways of energy flow across and within ecosystems.
+Here, we document shifting energy flow pathways across a wide natural temperature gradient, wherein, increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in population biomass turnover.
+Further,
 

### 2021-05-31 R/plan.R

@@ -79,6 +79,8 @@ the_plan <-
   lorenz_trait_fig = plot_trait_lorenz(lorenz_analysis, spp_rankings_summary),
   #
   random_skew_fig = plot_random_skew(skew_analysis, random_rankings),
+  # 
+  temperature_skew_fig = plot_skew_temperatur(temperature_stats),
   
   
   # target_name = target(

### 2021-06-01 doc/ms/ms.Rmd
update manuscript. Almost finalized figures and results. Moving on to discussion.

--- 2021-05-30 doc/ms/ms.Rmd
@@
 drake::loadd(temperature_stats)
+n_boot = temperature_stats[['n_boot']]
 
@@
 
-pb_skew_summ = skew_analysis[["PB_skew_summ"]]
+pb_skew_summ = skew_analysis[["pb_skew_summ"]]
 
@@
 In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% IP, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
+Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
 Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
@@
 We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
-non-random structure in the community energy fluxes.
-the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
-Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.
-The probability that
+non-random structure in community energy fluxes.
+The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean") %>% round(2)` (`r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5") %>% round(2)` -- `r m_skew_summ %>% slice_min(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5") %>% round(2)`) to `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(matches("M.*prob_mean")) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`).
+Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
+The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure SX), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
+This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.
 
@@
 The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` to `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C .
-The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r ((sum(M_skew_temp_coefs < 0)/n_boot)*100)`% of values fell below zero.
+The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero.
 Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
@@
 # Discussion
+
+Changing global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide.
+Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities.
+Further, within consumer communities energy fluxes are skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and smaller
 

### 2021-06-01 R/plan.R

@@ -80,7 +80,7 @@ the_plan <-
   #
   random_skew_fig = plot_random_skew(skew_analysis, random_rankings),
   # 
-  temperature_skew_fig = plot_skew_temperatur(temperature_stats),
+  # temperature_skew_fig = plot_skew_temperature(temperature_stats),
   
   
   # target_name = target(

### 2021-06-01 packages.R

@@ -6,7 +6,7 @@
                     "RCurl","plyr","tidyverse","furrr", "fnmate", "moments",
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
                     "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
-                    "viridis", "broom","bbmle","ggthemes", "ggeffects",
+                    "viridis", "broom","bbmle","ggthemes", "ggeffects", "ggpubr",
                     "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
                     "rstan", "brms", "tidybayes", "parallel", "hillR", "RInSp", "rsample")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
@@ -72,7 +72,7 @@
 source("./R/fluxweb_mod_function.R")
 source("./R/Lorenz.R")
 source("./R/Evenness.R")
-# nboot = 1e3
+nboot = 1e3
 theme_set(theme_mod())
 options(mc.cores = parallel::detectCores()-1)
 rstan_options(auto_write = TRUE)

### 2021-06-06 doc/ms/ms.Rmd
updated skew temp figures

@@
 Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(matches("pb.*prob_mean")) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
-The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure SX), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
+The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure S5), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
 This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.
@@
 Changing global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide.
-Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities.
-Further, within consumer communities energy fluxes are skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and smaller
+Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in mean biomass turnover rates across stream consumer communities, as predicted.
+Further, within consumer communities energy fluxes were skewed systematically toward larger, slower-turnover organisms at cooler stream temperatures and towards smaller, quick turnover populations at warmer temperatures.
+The organization of energy fluxes became less likely due to random chance moving from cooler to warmer temperatures, but this trend reversed at the warmest temperatures.
+The tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests higher population biomass turnover may be selected f temperatures .
 

### 2021-06-06 doc/ms/tables-figures.Rmd
updated skew temp figures

@@
 \newpage
+
+Figure 5.
+Non-random organization of community energy fluxes in relation to population biomass turnover (*P:B*) with mean annual temperature ($^\circ$C).
+Non-random organization is measured by the proportion of randomly generated skew statistics, $Sk_{flux}$, of equal or greater value.
+Observing an empirical value of $Sk_{flux}$ with a low probability of occurrence by random chance suggests non-random organization of community energy fluxes.
+
+```{r echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(temperature_skew_fig)
+grid.draw(pb_probs_plot)
+```
+
+\newpage
 Figure S1. Modeled diet proportions among streams

### 2021-06-06 R/plot_random_skew.R

@@ -53,8 +53,8 @@ random_rankings %>%
   geom_histogram(aes(color = site, y = ..density..), fill = NA, bins = 50)+
   scale_x_continuous(name = expression("Skew statistic"~italic(Sk)))+
   geom_histogram(data = skew_boots, aes(x = pb_y_skew, y = ..density..,color = site, fill = site), linetype = 'dashed', inherit.aes = FALSE, bins = 50, alpha = 0.5)+
-  scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels)+
-  scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels)+
+  scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
+  scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
   guides(linetype = FALSE)+
   theme_tufte(ticks = TRUE) +
   geom_rangeframe(sides = "lb")+

### 2021-06-06 R/plot_skew_temperature.R

@@ -1,0 +1,55 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param temperature_stats
+plot_skew_temperature <- function(temperature_stats, n_id = 2e3) {
+  
+  pb_probs_df = temperature_stats[["pb_probs_df"]]
+  pb_probs_summ = pb_probs_df %>%
+    group_by(site) %>%
+    dplyr::summarise(tempC= unique(tempC),
+                     across(c(pb_skew_prob), list(mean = ~mean(.x, na.rm = TRUE),
+                                                        quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                        quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                        quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                        quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                        quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+    dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+
+  pb_probs_concave_pred = temperature_stats[["pb_probs_concave_pred"]]
+  pb_probs_concave_med = temperature_stats[["pb_probs_concave_med"]]
+
+  set.seed(123)
+  pb_probs_plot =
+    pb_probs_concave_pred %>% 
+    .[sample(1:length(.),n_id, replace = TRUE)] %>%
+    setNames(.,nm = seq(1:n_id)) %>%
+    bind_rows(.id = "n_id") %>% 
+    # dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+  ggplot(aes(x = tempC, y = .fitted, group = n_id)) +
+    geom_line(alpha = 0.1, color = 'lightgrey') +
+    # geom_line(data = pb_probs_concave_med, aes(x= tempC, y = `.fitted`), color = 'black', size = 3, inherit.aes = FALSE)+
+    geom_errorbar(data = pb_probs_summ, aes(x = tempC, ymin = pb_skew_prob_quant2.5, ymax = pb_skew_prob_quant97.5, color = site), size = 1, width = 0, inherit.aes = FALSE)+
[…]

### 2021-07-01 doc/ms/ms.Rmd
updated ms and analysis. hopefully no merge conflicts with other MTU computer.

--- 2021-05-31 doc/ms/ms.Rmd
@@
 empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [@oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017],
-especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010b]. Yet, identifying general effects of temperature is a necessary step
+especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step
 towards understanding how future warming may alter the functioning of ecosystems and the services they provide.\par
@@
 \setlength\parindent{24pt}
-Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010b] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
 The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distributions among species and trophic levels [@may1972; @mccann1998; @barnes2018].
@@
 [@ogorman2012; @hood2018].
-Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2019] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
-We, further expected that increasing temperature would reduce consumer species [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
+Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
+We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
 The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
-Seasonally, warmer streams will lead to earlier food web fluxes in warmer compared to colder streams.
+Further, we predict increasing temperatures
 
@@
 | Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
-Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.
+Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.
 
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
-Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`).
+Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure SX).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
+Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
 Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
-Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature (Supporting Materials).
+Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
 
@@
 The calculated inequality, i.e.
-Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
 Differences in inequality were partly attributed to consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` , `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
 
@@
 Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams.
-Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences among the temperature gradient.
+Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.
 
@@
 The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
-Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
+Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
 Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
 Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
-In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% IP, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3).
-Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
+In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
+Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3).
+Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
+
+The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 5).
+Skew towards larger body sizes was negatively associated with stream temperature.
+The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase.
+The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 5a).
+Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
+The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 5b).
 
 We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
-non-random structure in the community energy fluxes.
-The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`.
-Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.
-The probability that
+non-random structure in community energy fluxes.
+The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`).
+Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
+The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure S5), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
+This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.
 
-The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure XX).
-Skew towards larger body sizes was negatively association with stream temperature.
-The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` to `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C .
-The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero, but `r ((sum(M_skew_temp_coefs < 0)/n_boot)*100)`% of values fell below zero.
-Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
-The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` to `r pb_skew_temp_coef_quant97.5` 95% PI).
+# Discussion
 
-#Discussion
+Rising global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide.
+Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that while increasing mean annual temperatures led to expected reductions in mean community body size and increases in mean biomass turnover rates across stream consumer communities, increasing temperatures also systematically skewed energy fluxes *within* communities.
+Here, energy fluxes were skewed towards smaller, quick turnover populations at warmer temperatures and showed increasingly non-random organization moving from cooler to warmer temperatures.
+but this trend reversed at the warmest temperatures.
+The tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests warming may speed up energy fluxes through ecosystems in both an absolute and relative sense.
 
-Changing global temperatures are altering the pathways of energy flow across and within ecosystems.
-Here, we document shifting energy flow pathways across a wide natural temperature gradient, wherein, increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in population biomass turnover.
-Further,
+Increasing global temperatures
 

### 2021-07-01 doc/ms/tables-figures.Rmd
updated ms and analysis. hopefully no merge conflicts with other MTU computer.

@@
 drake::loadd(gini_analysis)
-gini_analysis[["stream_gini_summary"]] %>% dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+gini_analysis[["stream_gini_summary"]] %>% 
    dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
    dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
-                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>% knitr::kable(align = "lrr")
+                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+   knitr::kable(align = "lrr")
 
@@
 drake::loadd(random_skew_fig)
-grid.draw(random_skew_fig)
+grid.arrange(random_skew_fig[[1]], random_skew_fig[[2]], ncol = 1)
 
@@
 drake::loadd(temperature_skew_fig)
-grid.draw(pb_probs_plot)
+temperature_skew_fig
 ```

### 2021-07-01 R/analyze_skew.R

@@ -40,13 +40,14 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
     rand_skew = rand_skew[,grepl("skew",colnames(rand_skew))]
     skew = unlist(emp_skew[,grepl(skew_var, colnames(emp_skew))])
     extreme_vec = sapply(skew, FUN = function(x){
-      if(x > 0){
-        y = sum(rand_skew >= x, na.rm = TRUE)/rand_tot
-      } else if( x < 0){
-        y = sum(rand_skew <= x, na.rm = TRUE)/rand_tot
-      } else{
-        y = sum(rand_skew ==0, na.rm =TRUE)/rand_tot
-      }
+      y = sum(rand_skew >= x, na.rm = TRUE)/rand_tot
+      # if(x > 0){
+      #   y = sum(rand_skew >= x, na.rm = TRUE)/rand_tot
+      # } else if( x < 0){
+      #   y = sum(rand_skew <= x, na.rm = TRUE)/rand_tot
+      # } else{
+      #   y = sum(rand_skew ==0, na.rm =TRUE)/rand_tot
+      # }
       y
     })
     extreme_vec

### 2021-07-01 R/analyze_temp_stats.R

@@ -86,6 +86,9 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
     purrr::pmap_dbl(~..2 %>% pluck('coefficients') %>% pluck('tempC'))
   
   # estimate the relationship with production skew and temperature
+  
+  new_data = data.frame(tempC = seq((min(stream_temps$tempC)-0.5),(max(stream_temps$tempC)+0.5), 0.5))
+  
   set.seed(123)
   pb_skew_df = skew_analysis[['pb_skew_boots']] %>% named_group_split(site) %>%
     map(~.x %>% slice_sample(n = n_boot, replace = TRUE) %>%
@@ -95,6 +98,10 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
   pb_skew_temp_boots = pb_skew_df %>%
     group_by(n_rep) %>%
     do(model = lm(pb_y_skew ~ tempC, data = .))
+  
+  pb_skew_temp_pred = pb_skew_temp_boots %>%
+  purrr::pmap(~..2 %>% predict(newdata = new_data) %>% data.frame(.fitted = .) %>% dplyr::mutate(tempC = unlist(new_data, use.names = FALSE))) 
+  
   
   pb_skew_temp_coefs = pb_skew_temp_boots %>%
     purrr::pmap_dbl(~..2 %>% pluck('coefficients') %>% pluck('tempC'))
@@ -108,6 +115,9 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
   M_skew_temp_boots = M_skew_df %>%
     group_by(n_rep) %>%
     do(model = lm(M_mg_ind_skew ~ tempC, data = .))
+  
+  m_skew_temp_pred = M_skew_temp_boots %>%
+    purrr::pmap(~..2 %>% predict(newdata = new_data) %>% data.frame(.fitted = .) %>% dplyr::mutate(tempC = unlist(new_data, use.names = FALSE))) 
   
   M_skew_temp_coefs = M_skew_temp_boots %>%
     purrr::pmap_dbl(~..2 %>% pluck('coefficients') %>% pluck('tempC'))
@@ -179,5 +189,7 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
               distance_similarity = distance_similarity, M_skew_temp_coefs = M_skew_temp_coefs,
[…]

### 2021-07-01 R/plot_skew_temperature.R

@@ -4,7 +4,46 @@
 ##'
 ##' @title
 ##' @param temperature_stats
-plot_skew_temperature <- function(temperature_stats, n_id = 2e3) {
+plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
+  
+  pb_skew_summ = temperature_stats[["pb_skew_df"]] %>%
+      group_by(site) %>%
+      dplyr::summarise(tempC= unique(tempC),
+                       across(c(pb_y_skew), list(mean = ~mean(.x, na.rm = TRUE),
+                                                    quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                    quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                    quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                    quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                    quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+      dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+  
+  pb_temp_pred_plot = temperature_stats[["pb_skew_temp_pred"]] %>%
+    .[sample(1:length(.),n_id, replace = TRUE)] %>%
+    setNames(.,nm = seq(1:n_id)) %>%
+    bind_rows(.id = "n_id") %>% 
+    ggplot(aes(x = tempC, y = .fitted, group = n_id)) +
+    geom_line(alpha = 0.1, color = 'lightgrey') +
+    # geom_line(data = pb_probs_concave_med, aes(x= tempC, y = `.fitted`), color = 'black', size = 3, inherit.aes = FALSE)+
+    geom_errorbar(data = pb_skew_summ, aes(x = tempC, ymin = pb_y_skew_quant2.5, ymax = pb_y_skew_quant97.5, color = site), size = 1, width = 0, inherit.aes = FALSE)+
+    geom_errorbar(data = pb_skew_summ, aes(x = tempC, ymin = pb_y_skew_quant25, ymax = pb_y_skew_quant75, color = site), size = 1.5, width = 0, inherit.aes = FALSE)+ 
+    geom_point(data = pb_skew_summ, aes(x = tempC, y = pb_y_skew_mean, fill = site), size = 2, color = 'black', inherit.aes = FALSE) +
[…]

### 2021-07-02 doc/ms/ms.Rmd
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

@@
 
-| Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
+Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
 diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
@@
 
-| To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
 p_S$.
@@
 
-We were interested in how OM fluxes were distributed (randomly vs.
-non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient.
-We used a permutation analyses to test for non-random patterns in OM flux with species traits.
-First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$).
-We then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
+We were interested in the question of how temperature may select for certain species traits (i.e., body size, $P:B$ ratio, population biomass) and therefore OM fluxes would skew towards populations with those traits.
+To detect this, for all bootstrapped estimates of annual OM flux, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
 
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine the probability of observing the skewness we observe in the data compared to random ordering, we constructed a distribution of skewness estimates from random species ordering while maintaining the relative distribution of OM fluxes.
-The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore we permuted 1,000,000 random species orderings and calculating the skew in the cumulative distribution of annual OM fluxes.
-We then use this random distribution to estimate the probability of observing a skewness as extreme or greater.
+To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set; @haegeman2008;], given the number of species and the relative distribution of energy fluxes within a community.
+The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
+Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times.
+The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains.
+This permuted set allowed us to calculate the likelihood of observing the empirical skewness, $Sk_{flux}$, in each stream.
+Further, we estimated the
 
@@
 
-| Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
+Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
 Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
@@
 
-Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1).
-The calculated inequality, i.e.
-Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
-Differences in inequality were partly attributed to consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Generally, OM fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1; Figure S1).
+Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
+Yet, even after accounting for differences in consumer richness,patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
 
@@
 
-Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a).
+Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1a).
 For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
@@
 
+[@diaz2021] SAD are more uneven than their statistical background
+
 # Acknowledgements

### 2021-07-02 doc/ms/tables-figures.Rmd
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

@@
 title: ""
-author: "Report Author"
+author: "JR Junker"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 
-Figure 3.
-Histograms of species trait distributions of (a) log~10~ annual production:biomass ratio (y^-1^), (b) log~10~ mean body mass (mg ind^-1^), and (c) log~10~ annual mean population biomass (mg m^-2^).
+Figure 2.
+Histograms of species trait distributions of (a) log~10~ mean body mass (mg ind^-1^), (b) log~10~ annual production:biomass ratio (y^-1^), and (c) log~10~ annual mean population biomass (mg m^-2^).
 
@@
 
-Figure 4. Relative cumulative fluxes among species in relation to ranked order of (a) annual production:biomass ratio (y^-1^) and (b) mean body size (mg ind^-1^).
+Figure 3. Relative cumulative fluxes among species in relation to ranked order of (a) mean body size (mg ind^-1^) and (b) annual production:biomass ratio (y^-1^).
 
@@
 drake::loadd(lorenz_trait_fig)
-grid.arrange(lorenz_trait_fig[["pb_lorenz_flux_plot"]], lorenz_trait_fig[["M_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
+grid.arrange(lorenz_trait_fig[["M_lorenz_flux_plot"]], lorenz_trait_fig[["pb_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
                          left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))
@@
 Figure 4.
-Bootstrapped distribution of skew statistics from OM fluxes with body size, *M*, and (b) population annual production:biomass ratio relative to the distribution of skew statistics of 100,000 random orderings.
+Fluxes of organic matter were skewed along gradients of the population traits (a) mean individual body size, *M*, and (b) annual population production:biomass, *P:B* ratiopopulation traits.
+Percentile Density of empirical skewness of OM fluxes in relation to .
+relative to the distribution of skew statistics of 100,000 random orderings.
 
@@
 drake::loadd(random_skew_fig)
-grid.arrange(random_skew_fig[[1]], random_skew_fig[[2]], ncol = 1)
+grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))
 
@@
 ```
+
+\newpage
+
+Figure S4.

### 2021-07-02 docs/ms/ms.RMD
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

@@
 
-### Evenness Among consumers
+### Evenness of production among consumers
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
+To visualize and quantify how evenly OM fluxes were distributed throughout consumes within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
 such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
@@
 ### Distribution along species' trait axes
-
-We were interested in how OM fluxes were distributed (randomly vs.
-non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient.
-We used a permutation analyses to test for non-random patterns in OM flux with species traits.
-First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and measured the asymmetry in the distribution of annual OM flux with species traits.
-To determine the probability of observing the empirical asymmetry we constructed a random distribution of asymmetry values.
-The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore chose to permute estimated this by randomly ordering species 10,000,000 times and calculating the skew in the cumulative distribution of annual OM fluxes.
-We then use this random distribution to estimate the probability of observing
 

### 2021-07-02 R/analyze_skew.R

@@ -35,7 +35,7 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
   }
   
   skew_probs = function(emp_skew, rand_skew, skew_var = NULL,...){
-    if(is.null(var)) stop("Error: Must define the skew variable.")
+    if(is.null(skew_var)) stop("Error: Must define the skew variable.")
     rand_tot = nrow(rand_skew)
     rand_skew = rand_skew[,grepl("skew",colnames(rand_skew))]
     skew = unlist(emp_skew[,grepl(skew_var, colnames(emp_skew))])
@@ -53,6 +53,13 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
     extreme_vec
   }
   
+  skew_perc = function(emp_skew, rand_skew, skew_var = NULL,...){
+    if(is.null(skew_var)) stop("Error: Must define the skew variable.")
+    percentile = ecdf(unlist(rand_skew[,grepl("skew",colnames(rand_skew))]))
+    skew = unlist(emp_skew[,grepl(skew_var, colnames(emp_skew))])
+    skew_percs= sapply(skew, percentile)
+    return(skew_percs)
+  }
   ## ++++ End Helper functions ++++ ##
    # debugonce(skew_est)
  
@@ -80,7 +87,11 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
   # debugonce(skew_probs)
   PB_skew_probs = future_map2(stream_PB_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
   M_skew_probs = future_map2(stream_M_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
-
+  
+  debugonce(skew_perc)
+  PB_skew_percs = future_map2(stream_PB_boots, stream_rand_boots, ~skew_perc(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
+  M_skew_percs = future_map2(stream_M_boots, stream_rand_boots, ~skew_perc(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
+  
   PB_skew_summ = PB_skew_boots %>%
     group_by(site) %>%
     dplyr::summarise(across(matches('skew'), list(mean = ~mean(.x, na.rm = TRUE),
[…]

### 2021-07-02 R/plot_random_skew.R

@@ -43,7 +43,40 @@ plot_random_skew <- function(skew_analysis, random_rankings) {
 #   geom_point(aes(color = site, shape = group), size = 3, position = position_dodge(width = 1) ) +
 #   scale_color_manual(values = rev(ocecolors[["temperature"]][oce_temp_pos]), labels = rev(stream_temp_labels))+
 #   facet_grid(~measure)
-
+  
+skew_analysis[['pb_skew_percs']] %>% bind_rows(.id = 'site') %>%
+    pivot_longer(-site, names_to = "boot_id", values_to = "skew_perc") %>%
+    dplyr::select(-boot_id) %>%
+    dplyr::mutate(site = factor(site, levels =names(stream_order_list))) %>%
+    ggplot(aes(x = skew_perc)) +
+    geom_vline(xintercept = c(0.1,0.9), color = 'red', size = 1, alpha = 0.7)+
+    geom_histogram(aes( fill = site, y = ..count..), color = NA, alpha = 0.8, bins = 50)+
+    scale_x_continuous(name = "Percentile of permuted set", limits = c(-0.01,1.01), expand = c(0.01,0.01))+
+    scale_y_continuous(name = "# of observations", expand = c(0.001,0.001))+
+    scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
+    scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
+    theme_tufte(ticks = TRUE) +
+    geom_rangeframe(sides = "lb")+
+    theme(legend.position = 'none', axis.title = element_blank()) +
+    facet_wrap(~site, ncol = , scales = 'free_y') ->pb_perc_plot
+    
+  skew_analysis[['M_skew_percs']] %>% bind_rows(.id = 'site') %>%
+    pivot_longer(-site, names_to = "boot_id", values_to = "skew_perc") %>%
+    dplyr::select(-boot_id) %>%
+    dplyr::mutate(site = factor(site, levels =names(stream_order_list))) %>%
+    ggplot(aes(x = skew_perc)) +
+    geom_vline(xintercept = c(0.1,0.9), color = 'red', size = 1, alpha = 0.7)+
+    geom_histogram(aes( fill = site, y = ..count..), color = NA, alpha = 0.8, bins = 50)+
[…]

### 2021-07-02 R/plot_trait_histogram.R

@@ -28,6 +28,6 @@ plot_trait_histogram <- function(spp_rankings = spp_rankings_summary) {
     scale_fill_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = rev(stream_temp_labels)) +
     theme(axis.title.x = element_blank(), legend.title = element_blank(),legend.position = "none"))
   
-  return(grid.arrange(pb_boxplot, M_boxplot, bio_boxplot, ncol = 3))
+  return(grid.arrange(M_boxplot, pb_boxplot, bio_boxplot, ncol = 3))
 
 }

### 2021-07-02 packages.R

@@ -5,7 +5,7 @@
   package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
                     "RCurl","plyr","tidyverse","furrr", "fnmate", "moments",
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
-                    "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown",
+                    "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown", "MuMIn",
                     "viridis", "broom","bbmle","ggthemes", "ggeffects", "ggpubr",
                     "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
                     "rstan", "brms", "tidybayes", "parallel", "hillR", "RInSp", "rsample")

### 2021-10-13 doc/ms/ms.Rmd
added text and rearranging figures to main text.

@@
 author: 
-- name: James R Junker
-  affiliation: Dept. of Ecology, Montana State University, Bozeman, MT USA
+- name: James R. Junker^[Dept. of Ecology, Montana State University, Bozeman, MT USA]
+- name: Wyatt F. Cross
+- name: James M. Hood
+- name: Jonathan P. Benstead
+- name: Alex D. Huryn
+- name: Daniel Nelson
+- name: Jon S. Olafsson
+- name: Gisli M. Gislason
 output:
@@
 ```{r import general objects, echo=FALSE, message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+source("./packages.R")
+library(knitr)
 
-source("./packages.R")
 drake::loadd(temperature_stats)
@@
 Specifically, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
-Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense/both across and within communities.
+Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense across and within communities.
 
@@
 <!--- warming and effects in food webs --->
-\setlength\parindent{24pt}
 Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
-[@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges [][] and subsequent changes to local and
-regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001]. While a growing body of theoretical and
-empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [@oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017],
-especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step
-towards understanding how future warming may alter the functioning of ecosystems and the services they provide.\par
+[@walther2002].
+Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].
+While a growing body of theoretical and
+empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
+Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
 
 <!--- Speeding up of food web: Species levels--->
-\setlength\parindent{24pt}
-Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
-The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distributions among species and trophic levels [@may1972; @mccann1998; @barnes2018].
-Direct changes through species richness effects [@gibert2019].
-Indirect through the distribution of consumer and prey species and it effects on the acquisition and allocation of resources among species [@zhang2017] --macroecology of food web dynamics and stability are controlled by the .\par
+Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017].
+Importantly,  --macroecology of food web dynamics and stability are controlled by the
 
-\setlength\parindent{24pt}
-Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
+Temperature effects individuals by altering rates of metabolism [@gillooly2001, @brown2004] and biological activity among species [e.g., attack rate, handling time, growth rates,
 etc.; @dell2014].
@@
 [@ogorman2012; @hood2018].
-Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams.
+Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
+As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
 We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
 The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
-Further, we predict increasing temperatures
-
 # Methods
@@
 
-Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500). For taxa which exhibit synchronous growth
+Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000). For taxa which exhibit synchronous growth
 and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
@@
 above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
-replacement (*n* = 500) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
+replacement (*n* = 1000) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
 growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
@@
 using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
-plants (bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
+plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
 contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.
 
-| To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
-hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
-$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
+To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
+hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
+$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
 a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
@@
 
-| From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials).
+From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates.
 Proportional similarities were calculated as:
@@
 p_S$.
-The Lorenz curve plots how a value, in this
-case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
-simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
-[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
+In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is simply a straight diagonal line.
+Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
 
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set; @haegeman2008;], given the number of species and the relative distribution of energy fluxes within a community.
+To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz], given the number of species and the relative distribution of energy fluxes within a community.
 The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
@@
 The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains.
-This permuted set allowed us to calculate the likelihood of observing the empirical skewness, $Sk_{flux}$, in each stream.
-Further, we estimated the
+This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.
+
+### Speed of seasonal energy flux
+
+Lastly, to  we quantified the cumulative
 
@@
 
+```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(gini_analysis)
+tab1_caption = "Table 1. Evenness of energy fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
+gini_analysis[["stream_gini_summary"]] %>% 
+   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
+   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
+                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+   knitr::kable(align = "lrr", caption = tab1_caption)
+
+```
+
 ```{r spp flux summaries, echo = FALSE, warning=FALSE, message=FALSE}
@@
 
-Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1a).
+Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1).
 For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
@@
 Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.
+
+```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450}
+drake::loadd(annual_spp_flux_fig)
+annual_spp_flux_fig
+```
 
@@
 The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
-Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
+Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
 Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
@@
 In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3).
-Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).
+Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
+Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
+
+```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
+drake::loadd(spp_trait_histograms)
+grid.draw(spp_trait_histograms)
+```
 
@@
 The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase.
-The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 5a).
+The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 4).
 Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
-The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 5b).
+The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).
+
+```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
+drake::loadd(lorenz_trait_fig)
+grid.arrange(lorenz_trait_fig[["M_lorenz_flux_plot"]], lorenz_trait_fig[["pb_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
+                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))
+
+```
 
@@
 
+```{r skew statistics, echo=FALSE, warning=FALSE, message=FALSE}
+
+```
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 4. "}
+drake::loadd(random_skew_fig)
+grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))
+
+```
+
+```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(temperature_skew_fig)
+temperature_skew_fig
+```
 # Discussion
@@
 
-[@diaz2021] SAD are more uneven than their statistical background
+[@diaz] SAD are more uneven than their statistical background
 
@@
 
+We are grateful to Sigurður Guðjonsson, Guðni Guðbergsson, and the staff at the Veiðimlastofnun for providing laboratory space and logistical support.
+We are also grateful to Sveinbj€orn Steinþorsson at the University of Iceland for super-jeep transport to our field sites during the winter.
 Jeff Wesner and Abe Kanz for code sharing and discussions on modeling diet proportions.

### 2021-10-13 R/analyze_skew.R

@@ -88,7 +88,7 @@ analyze_skew <- function(lorenz_analysis, random_rankings) {
   PB_skew_probs = future_map2(stream_PB_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
   M_skew_probs = future_map2(stream_M_boots, stream_rand_boots, ~skew_probs(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
   
-  debugonce(skew_perc)
+  # debugonce(skew_perc)
   PB_skew_percs = future_map2(stream_PB_boots, stream_rand_boots, ~skew_perc(emp_skew = .x, rand_skew = .y, skew_var = "pb_y_skew"))
   M_skew_percs = future_map2(stream_M_boots, stream_rand_boots, ~skew_perc(emp_skew = .x, rand_skew = .y, skew_var = "M_mg_ind_skew"))
   

### 2021-10-13 packages.R

@@ -14,10 +14,13 @@
   remotes::install_github("jimjunker1/junkR")
   library(junkR)
   conflict_prefer('count', 'dplyr')
+  conflict_prefer('mutate', 'dplyr')
   remotes::install_github("milesmcbain/dflow")
   # remotes::install_github("MilesMcBain/breakerofchains")
   library(dflow)
   rm("package.list" )
+  
+  source("https://gist.githubusercontent.com/jimjunker1/0ec857c43b1e3a781363c1b1ea7e12ad/raw/4dd2d1078a00500963822d29b2e58ebf39831fb3/geom_flat_violin.R")
   # len <<- function(data)
   # {
   #   result<<-ifelse(is.null(nrow(data)),length(data),nrow(data))

### 2021-10-27 doc/ms/ms.Rmd
updating manuscript adding figure of relationship between PB and M

@@
 [@walther2002].
-Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].
-While a growing body of theoretical and
-empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
-Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
+The effects of temperature on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].
 
@@
 Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+
 The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017].
@@
 As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
-We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
+We further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
 The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
+
 # Methods
@@
 (\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
-For particularly large samples, fine fractions were subsampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
+For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
 the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
@@
 Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @benke2017]. Growth rates were determined using taxon appropriate
-approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., Radix balthica, etc.) were determined using *in situ* chambers [@huryn1986].
+approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
 Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned
@@
 above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
-replacement (*n* = 1000) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
+replacement and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
 growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
 empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
-measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean
+measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration, size-specific growth rates were multiplied by mean
 interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz], given the number of species and the relative distribution of energy fluxes within a community.
+To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021], given the number of species and the relative distribution of energy fluxes within a community.
 The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
@@
 The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
-Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
+Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
 Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
@@
 
-The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 5).
+The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 4).
 Skew towards larger body sizes was negatively associated with stream temperature.
@@
 
-[@diaz] SAD are more uneven than their statistical background
+[@diaz2021] SAD are more uneven than their statistical background
+While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
+Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
 

### 2021-10-27 R/analyze_trait_stats.R

@@ -1,0 +1,11 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param skew_analysis
+analyze_trait_stats <- function(skew_analysis) {
+
+  NULL
+
+}

### 2021-10-27 R/plot_trait_histogram.R

@@ -15,7 +15,7 @@ plot_trait_histogram <- function(spp_rankings = spp_rankings_summary) {
                             geom_flat_violin(position = position_nudge(x = 0.2, y = 0), alpha = 0.8)+
                             geom_point(aes(y = log10(pb_y_mean), color = site), 
                                        position = position_jitter(width = 0.1),
-                                       size = 0.8, alpha = 0.8)+
+                                       size = 0.8, alpha = 0.6)+
                             geom_boxplot(width = 0.1, outlier.shape = NA, alpha = 0.5, show.legend =FALSE)+
                             scale_y_continuous(name = expression(log[10]*"("*italic("P:B")*","~y^{-1}*")"))+
                             scale_x_discrete(labels = rev(stream_temp_labels))+
@@ -30,7 +30,7 @@ plot_trait_histogram <- function(spp_rankings = spp_rankings_summary) {
                            geom_flat_violin(position = position_nudge(x =0.2, y = 0), alpha = 0.8) +
                            geom_point(aes(y = log10(M_mg_ind_mean), color = site), 
                                           position = position_jitter(width = 0.1),
-                                          size = 0.8, alpha = 0.8) +
+                                          size = 0.8, alpha = 0.6) +
                            geom_boxplot(width = 0.1, outlier.shape = NA, alpha = 0.5)+
                            scale_y_continuous(name = expression(log[10]*"("*italic("M")*","~mg^{-ind}*")"))+
                            guides(fill = 'none', color = 'none')+
@@ -44,7 +44,7 @@ plot_trait_histogram <- function(spp_rankings = spp_rankings_summary) {
                              geom_flat_violin(position = position_nudge(x =0.2, y = 0), alpha = 0.8) +
                              geom_point(aes(y = log10(bio_mg_m_mean), color = site), 
                                         position = position_jitter(width = 0.1),
-                                        size = 0.8, alpha = 0.8) +
+                                        size = 0.8, alpha = 0.6) +
                              geom_boxplot(width = 0.1, outlier.shape = NA, alpha = 0.5)+
                              scale_y_continuous(name = expression(log[10]*"("*italic("B")*", mg"~m^{-2}*")"))+
                              scale_x_discrete(labels = rev(stream_temp_labels))+

### 2021-12-15 doc/ms/ms.Rmd
updating ms

@@
 author:
-- name: James R. Junker^[Dept. of Ecology, Montana State University, Bozeman, MT USA]
+  - James R. Junker:
+      email: jrjunker@mtu.edu
+      institute: [msu, glrc]
+      correspondence: true
   - name: Wyatt F. Cross
+    institute: msu
   - name: James M. Hood
+    institute: osu
   - name: Jonathan P. Benstead
+    institute: bama
   - name: Alex D. Huryn
+    institute: bama
   - name: Daniel Nelson
+    institute: usu
   - name: Jon S. Olafsson
+    institute: veidi
   - name: Gisli M. Gislason
+    institute: reyk
+institute:
+  - msu: Dept. of Ecology, Montana State University, Bozeman, MT USA
+  - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
+  - osu: 
+  - bama: 
+  - usu: 
+  - veidi: 
+  - reyk: 
 output:
    word_document:
-     reference_docx: docx_template.docx
+      reference_docx: working_docx_template.docx
+      toc: no
+      pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
    pdf_document:
@@
    html_document: default
+   pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 header-includes:
@@
 Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
-
-The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017].
-Importantly,  --macroecology of food web dynamics and stability are controlled by the
-
-Temperature effects individuals by altering rates of metabolism [@gillooly2001, @brown2004] and biological activity among species [e.g., attack rate, handling time, growth rates,
-etc.; @dell2014].
+Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019].
+Importantly, these effects operate directly through temperature's influence on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017]...
 
@@
 
-Metabolic rates
-
-acquisition of resources by consumer Generally, temperature is predicted to have disproportionately higher effects on consumers relative to resources [@allen2005; @vasseur2005;
-@oconnor2011]
+In fact, reduced organismal body size with warming is considered a 'universal' response of climate change....
 
@@
 study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
-manipulation [see @nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
+manipulation [@nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
 unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021], given the number of species and the relative distribution of energy fluxes within a community.
+To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of energy fluxes within a community.
 The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
@@
 This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.
-
-### Speed of seasonal energy flux
-
-Lastly, to  we quantified the cumulative
 
@@
 Response variables *M* and *P:B* were transformed to meet the assumption of normally distributed residual variation.
+We similarly used a bootstrapped beta regression approach to test for relationships between annual stream temperature and the skewness of fluxes, $Sk_{flux}$, with *M* and *P:B*.
+Skewness coefficients exist in the range [-1, 1], therefore we applied a simple transformation,
+$$ (Sk_{flux} - 1)/2 $$ 
+to standardize the values between 0 and 1 to meet the assumptions of the model.
+Coefficients were back-transformed to estimate effect sizes.
+To detect changes in 'random' vs.
+non-random assembly, we  again used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
+Here, values can take the range between 0 and 1 so no transformation was necessary.
+Because we observed many values near 0 and 1, we implemented a zero-one inflated beta regression in the *zoib* package in R [@]
 
@@
 Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-Yet, even after accounting for differences in consumer richness,patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Yet, even after accounting for differences in consumer richness, patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
 
@@
 Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1).
-For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively).
+For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species.
 Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams.
@@
 
-```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450}
+```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 1."}
 drake::loadd(annual_spp_flux_fig)
@@
 M_skew_temp_coef_mean = round(mean(M_skew_temp_coefs, na.rm = TRUE), 2)
+M_skew_temp_coef_median = round(mean(M_skew_temp_coefs, na.rm = TRUE), 2)
 M_skew_temp_coef_quant2.5 = round(quantile(M_skew_temp_coefs, 0.025, na.rm = TRUE),2)
@@
 
-```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
+```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 2."}
 drake::loadd(spp_trait_histograms)
@@
 
-The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 4).
-Skew towards larger body sizes was negatively associated with stream temperature.
-The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase.
-The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 4).
-Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature.
-The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).
+The skew of energy fluxes towards populations with smaller/larger body sizes showed some systematic variation with stream temperature (Figure 4).
+The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase.
+While the 95% PI contained zero, the estimated effect of temperature on $Sk_{flux}$ towards lower body size populations exhibited a bimodal distribution around zero (Figure SXa), however, `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure SXa).
+Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
+The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4), with `r round((sum(pb_skew_temp_coefs >= 0)/n_boot)*100,1)`% of estimates above zero.
 
-```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
+```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 3."}
 drake::loadd(lorenz_trait_fig)
@@
 The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`).
-Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
+Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
 The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure S5), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
@@
 ```
+
 # Discussion
@@
 
-[@diaz2021] SAD are more uneven than their statistical background
+[@diaz2021a] SAD are more uneven than their statistical background
 While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
@@
 # References
+
+<div id="refs"></div>

### 2021-12-15 R/analyze_temp_stats.R

@@ -13,6 +13,8 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
                                skew_analysis = skew_analysis,
                                n_boot = 1e2) {
   
+  conflicted:::conflicts_reset()
+  
   stream_temps = stream_temp_labels %>% data.frame %>%
     rownames_to_column('site_id') %>% setNames(., c('site_id', 'tempC')) %>%
     dplyr::mutate(tempC = as.numeric(tempC))
@@ -87,40 +89,96 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
   
   # estimate the relationship with production skew and temperature
   
-  new_data = data.frame(tempC = seq((min(stream_temps$tempC)-0.5),(max(stream_temps$tempC)+0.5), 0.5))
+  new_data = data.frame(tempC = seq((min(stream_temps$tempC)-0.5),(max(stream_temps$tempC)+0.5), length.out = 100)) %>%
+    dplyr::mutate(tempC_stand = tempC - mean(tempC, na.rm = TRUE))
   
   set.seed(123)
   pb_skew_df = skew_analysis[['pb_skew_boots']] %>% named_group_split(site) %>%
     map(~.x %>% slice_sample(n = n_boot, replace = TRUE) %>%
           dplyr::mutate(n_rep = 1:n())) %>% bind_rows %>%
-    left_join(stream_temps %>% dplyr::rename(site = 'site_id'))
+    left_join(stream_temps %>% dplyr::rename(site = 'site_id')) %>%
+    dplyr::mutate(tempC_stand = tempC - mean(tempC, na.rm = TRUE),
+                  pb_y_skew_mod = (pb_y_skew + 1)/2)
   
-  pb_skew_temp_boots = pb_skew_df %>%
-    group_by(n_rep) %>%
-    do(model = lm(pb_y_skew ~ tempC, data = .))
+  pb_skew_formula = brms::bf(pb_y_skew_mod ~ tempC_stand,
+                            phi ~ tempC_stand,
+                            zoi ~ 1,
+                            coi ~ 1,
+                            family = brms::zero_one_inflated_beta())
   
+  pb_skew_priors = c(set_prior("normal(0,1.2)", class = "b", coef = "tempC_stand"),
+                    set_prior("normal(0.5,0.5)", class = "Intercept"))
+  
+  pb_skew_temp_boots = brms::brm(formula = pb_skew_formula,
[…]

### 2021-12-15 R/plot_skew_temperature.R

@@ -6,45 +6,49 @@
 ##' @param temperature_stats
 plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
   
+  n_draws = sample(1:6000, n_id, replace = FALSE)
+  
   pb_skew_summ = temperature_stats[["pb_skew_df"]] %>%
       group_by(site) %>%
       dplyr::summarise(tempC= unique(tempC),
                        across(c(pb_y_skew), list(mean = ~mean(.x, na.rm = TRUE),
-                                                    quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                    quant2.5 = ~quantile(.x, 0.05, na.rm = TRUE),
                                                     quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
-                                                    quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                    HPDI_50up = ~rethinking::HPDI(.x, 0.5)[2],
+                                                    HPDI_50dn = ~rethinking::HPDI(.x, 0.5)[1],
+                                                    HPDI_90up = ~rethinking::HPDI(.x, 0.9)[2],
+                                                    HPDI_90dn = ~rethinking::HPDI(.x, 0.9)[1],
+                                                    median = ~median(.x, na.rm = TRUE),
                                                     quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
-                                                    quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+                                                    quant97.5 = ~quantile(.x, 0.95, na.rm = TRUE)))) %>%
       dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
   
-  pb_temp_pred_plot = temperature_stats[["pb_skew_temp_pred"]] %>%
-    .[sample(1:length(.),n_id, replace = TRUE)] %>%
-    setNames(.,nm = seq(1:n_id)) %>%
-    bind_rows(.id = "n_id") %>% 
-    ggplot(aes(x = tempC, y = .fitted, group = n_id)) +
-    geom_line(alpha = 0.1, color = 'lightgrey') +
[…]

### 2021-12-15 R/plot_skew_temperature_old.R

@@ -1,0 +1,276 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param temperature_stats
+plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
+  
+  n_draws = sample(1:6000, n_id, replace = FALSE)
+  
+  # m_skew_summ = temperature_stats[["m_skew_df"]] %>%
+  #   group_by(site) %>%
+  #   dplyr::summarise(tempC= unique(tempC),
+  #                    across(c(M_mg_ind_skew), list(mean = ~mean(.x, na.rm = TRUE),
+  #                                              quant2.5 = ~quantile(.x, 0.05, na.rm = TRUE),
+  #                                              quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+  #                                              HPDI_50up = ~rethinking::HPDI(.x, 0.5)[2],
+  #                                              HPDI_50dn = ~rethinking::HPDI(.x, 0.5)[1],
+  #                                              HPDI_90up = ~rethinking::HPDI(.x, 0.9)[2],
+  #                                              HPDI_90dn = ~rethinking::HPDI(.x, 0.9)[1],
+  #                                              quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+  #                                              quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+  #                                              quant97.5 = ~quantile(.x, 0.95, na.rm = TRUE)))) %>%
+  #   dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+  # 
+  # m_temp_skew_plot = m_skew_summ %>%
+  #   dplyr::mutate(site = factor(site, levels = names(rev(stream_order_list)))) %>%
+  #   ggplot()+
+  #   geom_errorbar( aes(x = site, ymin = M_mg_ind_skew_HPDI_90dn, ymax = M_mg_ind_skew_HPDI_90up, color = site), size = 1, width = 0, inherit.aes = FALSE)+
+  #   geom_errorbar( aes(x = site, ymin = M_mg_ind_skew_HPDI_50dn, ymax = M_mg_ind_skew_HPDI_50up, color = site), size = 1.5, width = 0, inherit.aes = FALSE)+ 
[…]

### 2021-12-15 packages.R

@@ -5,8 +5,8 @@
   package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
                     "RCurl","plyr","tidyverse","furrr", "fnmate", "moments",
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
-                    "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown", "MuMIn",
-                    "viridis", "broom","bbmle","ggthemes", "ggeffects", "ggpubr",
+                    "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown", "MuMIn","zoib",
+                    "viridis", "broom","bbmle","ggthemes", "ggeffects", "ggpubr","betareg",
                     "fluxweb","igraph","ggraph","magick","cowplot","rriskDistributions",
                     "rstan", "brms", "tidybayes", "parallel", "hillR", "RInSp", "rsample")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
@@ -15,6 +15,7 @@
   library(junkR)
   conflict_prefer('count', 'dplyr')
   conflict_prefer('mutate', 'dplyr')
+  conflict_prefer('traceplot', 'coda')
   remotes::install_github("milesmcbain/dflow")
   # remotes::install_github("MilesMcBain/breakerofchains")
   library(dflow)

### 2021-12-28 doc/ms/ms.Rmd
updated results section with new beta regression models.

@@
 
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C).
+Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
 Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
@@
 
-Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @benke2017]. Growth rates were determined using taxon appropriate
+Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR, @benke2017]. Growth rates were determined using taxon appropriate
 approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
@@
 
-Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
+Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method [TBP, @benke1980]. Taxon-specific secondary production estimates were combined with
 diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
@@
 Skewness coefficients exist in the range [-1, 1], therefore we applied a simple transformation,
-$$ (Sk_{flux} - 1)/2 $$ 
+$$ (Sk_{flux} + 1)/2 $$ 
 to standardize the values between 0 and 1 to meet the assumptions of the model.
@@
 Here, values can take the range between 0 and 1 so no transformation was necessary.
-Because we observed many values near 0 and 1, we implemented a zero-one inflated beta regression in the *zoib* package in R [@]
+As necessary, when we observed many values near 0 and 1, we implemented a zero-one inflated beta regressions in brms [@burkner2017] to test if the probability of observing the empirical $Sk_{flux}$ was associated with mean annual temperature across streams.
 
@@
 Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
-Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.
+Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`; `r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)` to `r round((max_demand$flux_mg_m_y_mean/1000),1)`; `r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$ mean; 95% percentile interval (PI)) and was positively related to temperature.
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)`; `r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)`; `r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$.
 
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure SX).
+Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
 Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
@@
 
-```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 1."}
+```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 1.
+Rank ordering of annual population energy flux log~e~(mg m^-2^ y^-1^) in consumer communities across the temperature gradient."}
 drake::loadd(annual_spp_flux_fig)
@@
 
+backtransform_skew = function(x,...){
+  x * 2 - 1
+}
 # analyze skewness with temperature
-M_skew_temp_coefs = temperature_stats[["M_skew_temp_coefs"]]
+M_skew_temp_coefs = backtransform_skew(plogis(temperature_stats[["M_skew_temp_coefs"]]$b_tempC_stand))
 M_skew_temp_coef_mean = round(mean(M_skew_temp_coefs, na.rm = TRUE), 2)
@@
 
-pb_skew_temp_coefs = temperature_stats[["pb_skew_temp_coefs"]]
+pb_skew_temp_coefs = backtransform_skew(plogis(temperature_stats[["pb_skew_temp_coefs"]]$b_tempC_stand))
 pb_skew_temp_coef_mean = round(mean(pb_skew_temp_coefs, na.rm = TRUE),2)
@@
 m_skew_summ = skew_analysis[["M_skew_summ"]]
+
 ```
@@
 grid.draw(spp_trait_histograms)
+
 ```
 
-The skew of energy fluxes towards populations with smaller/larger body sizes showed some systematic variation with stream temperature (Figure 4).
-The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase.
-While the 95% PI contained zero, the estimated effect of temperature on $Sk_{flux}$ towards lower body size populations exhibited a bimodal distribution around zero (Figure SXa), however, `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure SXa).
+The skew of energy fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4).
+The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase.
 Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
-The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4), with `r round((sum(pb_skew_temp_coefs >= 0)/n_boot)*100,1)`% of estimates above zero.
+The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).
 
@@
 
-We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
-non-random structure in community energy fluxes.
-The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)` -- `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`).
-Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`).
-The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed no clear association with temperature (Figure S5), however, there was a trend towards community energy fluxes becoming more organized (less "randomly" structured) in relation to biomass turnover with increasing temperatures (Figure XX).
-This relationship exhibited a concave up relationship with temperature, showing a clear trend toward less-random organization from cool to mid-range temperatures and returning towards a more likely random organization at the warmest stream.
+```{r probs coefs, echo=FALSE, warning=FALSE, message=FALSE}
+m_prob_temp_coef = temperature_stats[["m_probs_temp_coefs"]]$b_tempC_stand
+m_prob_temp_median = median(m_prob_temp_coef, na.rm =TRUE)
+m_prob_temp_quant2.5 = quantile(m_prob_temp_coef, 0.025,na.rm = TRUE)
+m_prob_temp_quant97.5 = quantile(m_prob_temp_coef,0.975, na.rm =TRUE)
 
-```{r skew statistics, echo=FALSE, warning=FALSE, message=FALSE}
+pb_prob_temp_coef = temperature_stats[["pb_probs_temp_coefs"]]$b_tempC_stand
+pb_prob_temp_median = median(pb_prob_temp_coef, na.rm =TRUE)
+pb_prob_temp_quant2.5 = quantile(pb_prob_temp_coef, 0.025,na.rm = TRUE)
+pb_prob_temp_quant97.5 = quantile(pb_prob_temp_coef,0.975, na.rm =TRUE)
 
@@
 
-```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 4. "}
+We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
+non-random structure in community energy fluxes.
+The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI).
+Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI).
+The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 5 top).
+Further, there was a trend towards a more structured energy flux distribution with regard to population *P:B* at higher temperatures.
+The probability of observing such skewed energy fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase.
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 4. Probability distribution of empirical Sk~flux~ measurements compared to random species ordering."}
 drake::loadd(random_skew_fig)
@@
 
-```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE}
+```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.cap="Figure 5.
+Empirical flux measurements (left column), the probability of observing a more Sk~flux~ value more extreme  (middle), and the estimated effect of increasing temperature on the probability of random ordering (right column) for energy flux distributions in relation to body size (top) and population *P:B* (bottom)." }
 drake::loadd(temperature_skew_fig)
- temperature_skew_fig
+ grid.draw(temperature_skew_fig)
 ```
@@
 <div id="refs"></div>
+
+# Appendix
+
+```{r diet figure, echo = FALSE, warning=FALSE, message=FALSE,  dpi = 450, fig.cap="Figure S1. Modeled diet proportions of consumer communities across the temperature gradient."}
+
+drake::loadd(prelim_diet_figures)
+prelim_diet_figures
+
+```
+
+```{r raw lorenz, echo=FALSE, message=FALSE, warning = FALSE, dpi = 400, fig.cap="Figure S2.
+Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (mg AFDM m^-2^ y^-1^)"}
+lorenz_trait_fig[["lorenz_flux_plot"]]
+
+```
+
+```{r biomass lorenze, echo=FALSE, message=FALSE, warning=FALSE, dpi = 400, fig.cap="Figure S3.
+Cumulative plot of relative community flux by species in relation to mean annual population biomass (mg m^-2^)."}
+lorenz_trait_fig[["bio_lorenz_flux_plot"]]
+
+```

### 2021-12-28 R/analyze_temp_stats.R

@@ -322,7 +322,9 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
   #             pb_skew_temp_pred = pb_skew_temp_pred, m_probs_temp_coefs = M_probs_temp_coefs,
   #             pb_probs_temp_coefs = pb_probs_temp_coefs))
   return(list(pb_temp_coefs = pb_temp_coefs, M_temp_coefs = M_temp_coefs, n_boot = n_boot, 
-              distance_similarity = distance_similarity, pb_probs_df = pb_probs_df, 
+              distance_similarity = distance_similarity, M_skew_temp_coefs = M_skew_temp_coefs,
+              pb_skew_temp_coefs = pb_skew_temp_coefs, 
+              pb_probs_df = pb_probs_df, 
               pb_skew_df = pb_skew_df, m_probs_df = M_probs_df, 
               m_skew_df = M_skew_df, m_skew_temp_pred = m_skew_temp_pred,
               pb_probs_temp_pred= pb_probs_temp_pred,

### 2021-12-28 R/plot_skew_temperature.R

@@ -8,6 +8,89 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
   
   n_draws = sample(1:6000, n_id, replace = FALSE)
   
+  m_skew_summ = temperature_stats[["m_skew_df"]] %>%
+    group_by(site) %>%
+    dplyr::summarise(tempC= unique(tempC),
+                     across(c(M_mg_ind_skew), list(mean = ~mean(.x, na.rm = TRUE),
+                                               quant2.5 = ~quantile(.x, 0.05, na.rm = TRUE),
+                                               quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                               HPDI_50up = ~rethinking::HPDI(.x, 0.5)[2],
+                                               HPDI_50dn = ~rethinking::HPDI(.x, 0.5)[1],
+                                               HPDI_90up = ~rethinking::HPDI(.x, 0.9)[2],
+                                               HPDI_90dn = ~rethinking::HPDI(.x, 0.9)[1],
+                                               median = ~median(.x, na.rm = TRUE),
+                                               quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                               quant97.5 = ~quantile(.x, 0.95, na.rm = TRUE)))) %>%
+    dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+  
+  m_temp_skew_plot = ggplotGrob(m_skew_summ %>%
+                                   dplyr::mutate(site = factor(site, levels = names(rev(stream_order_list)))) %>%
+                                   ggplot()+
+                                   geom_errorbar( aes(y = site, xmin = M_mg_ind_skew_HPDI_90dn, xmax = M_mg_ind_skew_HPDI_90up, color = site), size = 1, width = 0)+
+                                   geom_errorbar( aes(y = site, xmin = M_mg_ind_skew_HPDI_50dn, xmax = M_mg_ind_skew_HPDI_50up, color = site), size = 1.5, width = 0)+
+                                   geom_point(aes(y = site, x = M_mg_ind_skew_median), size = 2, color = 'black')+
+                                   scale_x_continuous(name = expression(""*italic(Sk[flux])), limits = c(-1,1), expand = c(0,0.004) ) +
+                                   scale_y_discrete(labels = rev(stream_temp_labels))+
[…]

### 2021-12-28 R/plot_trait_histogram.R

@@ -7,7 +7,7 @@
 plot_trait_histogram <- function(spp_rankings = spp_rankings_summary) {
   
   prod_df = spp_rankings[['prod_spp_rank']] %>% dplyr::filter(prod_mg_m_y_mean > 0 | is.na(prod_mg_m_y_mean)) %>% dplyr::mutate(site = factor(site, levels = rev(stream_order)))
-  pb_df = spp_rankings[['PB_spp_rank']] %>%  dplyr::filter(pb_y_mean >0 | is.na(pb_y_mean)) %>% dplyr::mutate(site = factor(site, levels = rev(stream_order)))
+  pb_df = spp_rankings[['PB_spp_rank']] %>%  dplyr::filter(pb_y_mean >0.001 | is.na(pb_y_mean)) %>% dplyr::mutate(site = factor(site, levels = rev(stream_order)))
   bio_df = spp_rankings[['bio_spp_rank']] %>% dplyr::filter(bio_mg_m_mean >0 | is.na(bio_mg_m_mean)) %>% dplyr::mutate(site = factor(site, levels = rev(stream_order)))
   M_df = spp_rankings[['M_spp_rank']] %>% dplyr::filter(M_mg_ind_mean >0 | is.na(M_mg_ind_mean)) %>% dplyr::mutate(site = factor(site, levels = rev(stream_order)))
   

### 2022-01-14 doc/ms/ms.Rmd
introduction work and incorporating methods/results simplification

@@
 <!--- warming and effects in food webs --->
-Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
-[@walther2002].
-The effects of temperature on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].
-
 <!--- Speeding up of food web: Species levels--->
-Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].
+Increasing global temperatures are altering the provisioning and maintenance of ecosystem services by modifying the network of interactions among species that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
 Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019].
-Importantly, these effects operate directly through temperature's influence on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017]...
+Temperature's effects permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], as an environmental niche filter of community assembly [] and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
 
 <!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
+In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @daufresne2009].
+Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or lastly through reduced body size of warmer individuals [@atkinson1994].
+Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
+These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of organismal biology [@peters1983], influencing life history [@zuess2017; @altermatt2010] and development [@angilleta], diet breadth [], trophic position [], and crucially, metabolic rate [@brown2004].
 
-In fact, reduced organismal body size with warming is considered a 'universal' response of climate change....
+Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by  temperature [@gilooly2001; @arrhenius1898].
+Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019].
+The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2019], consumer-resource interactions [@bideault20149], and food web structure [@gibert2019].
+Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@giloolly2001`], developmental rate [@zuo2012], and population turnover rate [@].
+As such, the emerging picture suggests a smaller, faster world in which warming can "speeds up" ecosystem processes through the compounded effects of smaller body size and higher biological rates.
 
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
+Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs *more*[@woodward2010; @walther2005].
+For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014].
+Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition [] and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012] that can shape life history patterns [i.e., voltinism, @zuess2017].
+and community structure across ecosystems...*better transition here maybe*
+
+These maxmize energy intake when resources are available [@atkinson1997]
+
+- Seasonal systems have unique constraints
+- These seasonal constraints are greater at higher temps
+- This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017],
+2) availability
+
+Here, we measured the patterning and distribution of energy fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
 Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
@@
 Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
-As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
-We further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
+As such, we predicted annual energy fluxes of consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
+We hypothesized temperature to be a strong environmental filter of community assembly and energy flux, especially at the extremes.
+From this we propose a number of predictions regarding the patterning of energy fluxes within and across communities of different temperature, with particular focus on two species traits: body size and population biomass turnover (production:biomass ratios, *P:B*).
+First, we predict warmer temperatures should select for smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities.
+Second, within communities energy fluxes should be dominated by smaller, higher turnover species at warmer temperatures.
+Third,
+
+e further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
+We predicted OM fluxes would be most even at moderate temperatures and dominated by few taxa at the coldest and warmest extremes.
+Lastly, we predicted that temperature is a strong filter of community assembly  Lastly, we quantified how OM fluxes were associated with two key species traits; body size and population production to biomass ratio (P:B) within communities.
+We predicted mean community body size would decrease and mean community P:B ratios would increase at higher temperatures.
 The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
@@
 We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
-characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
+characterized by indirect geothermal heating of groundwater [@arnason1969], leading to natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
 chemistries [@friberg2009]. These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a]. We selected
@@
 manipulation [@nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
-unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
+unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected five Surber samples
 (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
 organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
-(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
+(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15 x magnification).
 For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
@@
 
-**Come back and confirm this section** Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
+Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
 high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
 shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
-= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content
-slides. Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds. Gut content slurries were filtered
+= 3--5) to ensure samples contained enough material for quantification.
+We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification.
+Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds.
+Gut content slurries were filtered
 onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
-microscope slide, cleared with Type B immersion old, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
+microscope slide, cleared with Type B immersion oil, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
 particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
@@
 We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
-$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
-site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
-from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
-values.
+$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value.
+Models were fit in Stan with the 'brms' package in R [@burkner2017].
+For non-dominant taxa, diet proportions were imputed
+from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.
 
@@
 
+drake::loadd(temperature_stats)
+
 ```
+
 ## Community OM fluxes
@@
 Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`; `r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)` to `r round((max_demand$flux_mg_m_y_mean/1000),1)`; `r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$ mean; 95% percentile interval (PI)) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)`; `r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)`; `r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$.
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)`; `r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)`; `r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`
+g AFDM $m^{-2} y^{-1}$.
+
+General patterns of community change and species identity across the gradient.
+Community and population patterns of M and P:B with temperature...
 
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
-Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
-Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
-Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
+**I am strongly considering ditching or appendixing the diet stuff.
+This will become important for the next paper, however, I think it distracts from the story here since we are really just focused on the energy pathways**
 
@@
 
+Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
+Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
+Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
+Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
+
 ```{r diet figure, echo = FALSE, warning=FALSE, message=FALSE,  dpi = 450, fig.cap="Figure S1. Modeled diet proportions of consumer communities across the temperature gradient."}

### 2022-01-14 R/plot_traits_temp.R

@@ -1,0 +1,35 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param spp_rankings_summary
+#' @param temperature_stats
+plot_traits_temp <- function(production_boots,
+                             spp_rankings_summary,
+                             temperature_stats) {
+
+  stream_temps = stream_temp_labels %>% data.frame %>%
+    rownames_to_column('site_id') %>% setNames(., c('site_id', 'tempC')) %>%
+    dplyr::mutate(tempC = as.numeric(tempC))
+  
+  new_data = data.frame(tempC = seq((min(stream_temps$tempC)-0.5),(max(stream_temps$tempC)+0.5), length.out = 100)) %>%
+    dplyr::mutate(tempC_stand = tempC - mean(tempC, na.rm = TRUE))
+  
+  ann_spp_summ = temperature_stats[["sppBootsDf"]] %>%
+    group_by(site_id) %>%
+    dplyr::summarise(across(c(pb_y,M_mg_ind), list(mean = ~mean(.x, na.rm = TRUE),
+                                                   median = ~median(.x, na.rm = TRUE),
+                                                   mode = ~rethinking::chainmode(.x, na.rm = TRUE),
+                                                   quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                   quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                   quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                   quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
+  pb_spp_temp_pred = pb_spp_temp_boots %>%
+    junkR::named_group_split(n_rep) %>%
+    purrr::map(~.x %>% pluck('model'))# %>% predict(unlist(.), newdata = new_data)) %>%
+    bind_rows(.id = n_rep)
+    purrr::pmap()
+ 
+
+}

### 2022-02-14 doc/ms/ms.Rmd
finalizing spp rel flux figure w/ taxonomy. First draft of introduction

@@
 ---
-title: "Manuscript title here"
+title: "Warming non-randomly speeds up food web fluxes in both an absolute and relative sense"
 author:
@@
 institute:
-  - msu: Dept. of Ecology, Montana State University, Bozeman, MT USA
+  - msu: Department of Ecology, Montana State University, Bozeman, MT USA
   - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
-  - osu: 
-  - bama: 
-  - usu: 
-  - veidi: 
-  - reyk: 
+  - osu: Department of Evolution, Ecology, and Organismal Biology, The Ohio State University, Translational Data Analytics Institute, The Aquatic Ecology Laboratory, Columbus, OH 43212, USA
+  - bama: Department of Biological Sciences, University of Alabama, Tuscaloosa, AL  35487, USA
+  - usu: National Aquatic Monitoring Center, Department of Watershed Sciences, Utah State University, Logan, UT 84322, USA
+  - veidi: Institute of Marine and Freshwater Fisheries, Reykjavik, Iceland
+  - reyk: Univeristy of Iceland, Institute of Life and Environmental Sciences, Reykjavik, Iceland
 output:
@@
 
-Energy fluxes through invertebrate food webs restructured in response to temperature.
-Specifically, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
-Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense across and within communities.
+Warming temperatures are altering biological communities and trophic networks globally.
+While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple fundamental ways by 1) decreasing organism body size and 2) increasing metabolic rates.
+These two attributes, body size and metabolic rate, are important drivers of many ecological patterns.
+Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food webs fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly.
+Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a ~25$^\circ$C temperature gradient.
+We then relate patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
+We predicted 1) fluxes would skew towards smaller *M* and higher *P:B* both across and within ecosystems and 2) fluxes would be more skewed at higher temperatures.
+Across the temperature gradient, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
+Additionally, material fluxes of warmer streams were increasingly skewed towards high-turnover populations *within* the community, showing higher temperatures restructured organic matter fluxes in both an absolute and relative sense.
+Lastly, in warmer ecosystems the relative distribution of organic matter fluxes appears to be increasingly 'non-random', evidence of potentially stronger selection for these traits with increasing temperature.
+The emerging picture is a warmer world that is both smaller and faster.
+Our study lends further support to this pattern and also suggests that
 
@@
 Increasing global temperatures are altering the provisioning and maintenance of ecosystem services by modifying the network of interactions among species that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
-Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019].
-Temperature's effects permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], as an environmental niche filter of community assembly [] and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
+Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and fluxes among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019a].
+Temperature's effects permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, as an environmental niche filter of community assembly and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
 
 <!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
-In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @daufresne2009].
-Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or lastly through reduced body size of warmer individuals [@atkinson1994].
+In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @gardner2011; @daufresne2009].
+Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or through reduced body size of warmer individuals [@atkinson1994].
 Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of organismal biology [@peters1983], influencing life history [@zuess2017; @altermatt2010] and development [@angilleta], diet breadth [], trophic position [], and crucially, metabolic rate [@brown2004].
+These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history [@zeuss2017; @altermatt2010; @nelson2020b], development [@angilletta2004], and crucially, basal metabolic rate [@brown2004; @gillooly2001].
 
-Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by  temperature [@gilooly2001; @arrhenius1898].
-Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019].
-The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2019], consumer-resource interactions [@bideault20149], and food web structure [@gibert2019].
-Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@giloolly2001`], developmental rate [@zuo2012], and population turnover rate [@].
-As such, the emerging picture suggests a smaller, faster world in which warming can "speeds up" ecosystem processes through the compounded effects of smaller body size and higher biological rates.
+<!--- Write the main goals of the paragraph--->
+Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by temperature [@gillooly2001].
+Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
+The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
+Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
+As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.
 
-Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs *more*[@woodward2010; @walther2005].
-For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014].
-Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition [] and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012] that can shape life history patterns [i.e., voltinism, @zuess2017].
-and community structure across ecosystems...*better transition here maybe*
-
-These maxmize energy intake when resources are available [@atkinson1997]
-
-- Seasonal systems have unique constraints
-- These seasonal constraints are greater at higher temps
-- This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017],
-2) availability
+Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs [@woodward2010; @walther2002].
+For example, species interactions in food webs may modulate species' TSRs [@delong2014], leading to varied responses among species and trophic levels [@ohlberger2013].
+Additionally, warming-induced body size reductions may act as a stabilizing process in some consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011; @greyson-gaito2022].
+Therefore, food web processes may impart varying selective pressures on the distribution of body sizes and population turnover within communities.
+If strong, these pressures may leave distinct imprints on community structure and the distribution of energy fluxes within food webs with potential implications for the stability and functioning of ecosystems on a warming planet [@petchey1999; @fussmann2014].
 
@@
 As such, we predicted annual energy fluxes of consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
-We hypothesized temperature to be a strong environmental filter of community assembly and energy flux, especially at the extremes.
-From this we propose a number of predictions regarding the patterning of energy fluxes within and across communities of different temperature, with particular focus on two species traits: body size and population biomass turnover (production:biomass ratios, *P:B*).
-First, we predict warmer temperatures should select for smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities.
+We hypothesized temperature to be a strong environmental filter of community assembly and the distribution of energy and organic matter fluxes, especially at the extremes.
+From this we made a number of predictions regarding the patterning of energy fluxes within and across communities of different temperature, with particular focus on two species traits: body size and population biomass turnover (production:biomass ratios, *P:B*).
+First, we predict warmer temperatures should favor smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities.
 Second, within communities energy fluxes should be dominated by smaller, higher turnover species at warmer temperatures.
-Third,
-
-e further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities.
-We predicted OM fluxes would be most even at moderate temperatures and dominated by few taxa at the coldest and warmest extremes.
-Lastly, we predicted that temperature is a strong filter of community assembly  Lastly, we quantified how OM fluxes were associated with two key species traits; body size and population production to biomass ratio (P:B) within communities.
-We predicted mean community body size would decrease and mean community P:B ratios would increase at higher temperatures.
-The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.
+Third, we hypothesized that the selective pressure from environmental temperature on body sizes and population turnover would be greatest at temperature extremes, therefore, the patterning of energy fluxes will be 'non-random' at coldest and warmest temperatures.
 
@@
 particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
-using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
+using image analysis software [@schindelin2012]. We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
 plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
@@
 To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
-hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
+hierarchical multivariate model [@fordyce2011; @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
 $$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
@@
 We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
-$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value.
+$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the assumed concentration value.
 Models were fit in Stan with the 'brms' package in R [@burkner2017].
@@
 
-From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates.
+From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities (*PS*; @whittaker1952) among modeled diet estimates.
 Proportional similarities were calculated as:
@@
 In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is simply a straight diagonal line.
-Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]:
 
-### Distribution along species' trait axes
+$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
 
-We were interested in the question of how temperature may select for certain species traits (i.e., body size, $P:B$ ratio, population biomass) and therefore OM fluxes would skew towards populations with those traits.
-To detect this, for all bootstrapped estimates of annual OM flux, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
+where $G^*$ represents an index of relative evenness of OM fluxes bounded between zero and one--one representing a community with exactly equal proportion of total community OM flux for all species ($1/S$), and a value of zero where total community flux is attributed to a single species.
+
+### Distribution of OM fluxes in relation to species' traits
+
+We predicted that warming would favor species with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
+Across communities, we assessed the relationships between mean annual temperature ($^\circ$C) and mean population *M* and *P:B* of each community with bootstrapped linear regressions.
+Here, `r temperature_stats[['n_boot']]` values of population *M* or *P:B* were resampled with replacement for each species within each stream.
+The mean of all populations within a stream was calculated and a linear model was fit between *log~e~*-transformed *M* or *P:B* and mean annual temperature.
+Response variables *M* and *P:B* were transformed to meet the assumption of normally distributed residual variation.
+
+To quantify the distribution of energy fluxes _**within**_ a community, we assessed if relative OM flux was skewed towards populations with lower or higher relative *M* or  *P:B*.
+To do this, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
 
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of energy fluxes within a community.
+We repeated this analysis for all bootstrapped estimates of OM flux in all communities.
+Skewness coefficients exist in the range [-1, 1], where -1 indicates OM fluxes are skewed perfectly away from a trait and 1 indicates higher relative flux is perfectly associated with higher trait values.
+To determine if $Sk_{flux}$ with population *M* and *P:B* was related to mean annual stream temperature, we use bootstrapped beta regression with a simple transformation to meet the assumptions of the model, $(Sk_{flux} + 1)/2$, thereby standardizing values between 0 and 1.
+Model coefficients were back-transformed to estimate effect sizes.
+
+To assess the strength of environmental filtering of species' traits within a community, we quantified how likely it was to observe such a skewed distribution in OM fluxes by random chance.
+Here, we predicted that communities with strong filtering for traits would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
+In contrast, weak environmental filtering would produce OM fluxes with skew values that are likely due to random chance ('random ordering'.
+To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
 The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
-Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times.
-The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains.
-This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.
-
-## Statistical Analyses
-
-Relationships between mean annual temperature ($^\circ$C) and mean community *M* and *P:B* were assessed with bootstrapped linear regressions.
-Here, `r temperature_stats[['n_boot']]` values of mean *M* or *P:B* were resampled with replacement from each stream.
-For each resampling event, a linear model was fit between *log~e~*-transformed *M* or *P:B* and mean annual temperature.
-Response variables *M* and *P:B* were transformed to meet the assumption of normally distributed residual variation.
-We similarly used a bootstrapped beta regression approach to test for relationships between annual stream temperature and the skewness of fluxes, $Sk_{flux}$, with *M* and *P:B*.
-Skewness coefficients exist in the range [-1, 1], therefore we applied a simple transformation,
-$$ (Sk_{flux} + 1)/2 $$ 
-to standardize the values between 0 and 1 to meet the assumptions of the model.
-Coefficients were back-transformed to estimate effect sizes.
-To detect changes in 'random' vs.
-non-random assembly, we  again used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
+Therefore, we chose to permute a random subset of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times in each stream.
+The number of random orderings was chosen as a balance between characterizing the distribution of skewness values within each feasible set and computational and time constrains.
+This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative OM flux.
+To assess the relationship between the probability of 'non-random ordering' and temperature, we again used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
 Here, values can take the range between 0 and 1 so no transformation was necessary.
 As necessary, when we observed many values near 0 and 1, we implemented a zero-one inflated beta regressions in brms [@burkner2017] to test if the probability of observing the empirical $Sk_{flux}$ was associated with mean annual temperature across streams.
+We predicted increasingly 'non-random' distributions in OM fluxes with increasing temperature.
 
@@
 
+pb_spp_temp_coefs = temperature_stats[["pb_spp_temp_coefs"]]
+m_spp_temp_coefs = temperature_stats[["m_spp_temp_coefs"]]
+
 ```
@@
 Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`; `r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)` to `r round((max_demand$flux_mg_m_y_mean/1000),1)`; `r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$ mean; 95% percentile interval (PI)) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)`; `r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)`; `r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`
-g AFDM $m^{-2} y^{-1}$.
-
-General patterns of community change and species identity across the gradient.
-Community and population patterns of M and P:B with temperature...
+Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` (`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`, 95% PI) to `r round((max_flux$flux_mg_m_y_mean/1000),1)` (`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`, 95% PI) g AFDM $m^{-2} y^{-1}$.
 
@@
 
-**I am strongly considering ditching or appendixing the diet stuff.
-This will become important for the next paper, however, I think it distracts from the story here since we are really just focused on the energy pathways**
+Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
+Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
+Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
+Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
+
+Generally, organic matter fluxes were dominated by insect species from *Simuliidae* and *Chironomidae* families (Figure 1a).
+In warmer streams, OM fluxes shifted toward the pulmonate snail, *Radix balthica*.
+In the warmest stream, where maximum temperatures approach ~40$^\circ$C, OM fluxes were dominated by worms of family *Naididae*, the midge *Cricotpous sylvestris*, and *Radix balthica*.
+
+```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1.
+Patterns of OM flux among populations based on (a) Rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) and (b) relative OM flux among taxaonomic groups in consumer communities and across the temperature gradient."}
+drake::loadd(annual_spp_flux_fig)
+drake::loadd(spp_flux_dist)
+gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
+```
+
+```{r trait df, echo = FALSE, warning = FALSE, message = FALSE}
+drake::loadd(spp_traitsVtemp)
+ann_spp_summ = spp_traitsVtemp[['ann_spp_summ']]
+
+```
 
@@
 
-Generally, OM fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1; Figure S1).
-Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
-Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers.
-Yet, even after accounting for differences in consumer richness, patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).
+Organic matter fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1b; Figure S1).
+Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`; Table 1).
+Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups.
+Yet, even after accounting for differences in consumer richness, patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`; Table 1).
 
@@
 drake::loadd(gini_analysis)
-tab1_caption = "Table 1. Evenness of energy fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
+tab1_caption = "Table 1.
+Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
 gini_analysis[["stream_gini_summary"]] %>% 
@@
 
-Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1).
+Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1b).
 For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species.
@@
 
-```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 1.
-Rank ordering of annual population energy flux log~e~(mg m^-2^ y^-1^) in consumer communities across the temperature gradient."}
-drake::loadd(annual_spp_flux_fig)
-annual_spp_flux_fig
+```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 2.
+The relationships between mean annual stream temperature and (a) average population body size of the community (mg^-ind^) and (b) average population turnover expressed as production to biomass ratios (*P:B*, y^-1^)."}
+
+drake::loadd(spp_traitsVtemp)
+grid.draw(spp_traitsVtemp[['fig1_plot']])
+
+ # drake::loadd(spp_trait_histograms)
+# grid.draw(spp_trait_histograms)
+
 ```
@@
 
-M_temp_coefs = temperature_stats[["M_temp_coefs"]]
+M_temp_coefs = temperature_stats[["m_spp_temp_coefs"]]
+# M_temp_coefs = temperature_stats[["M_temp_coefs"]]
 M_temp_coef_mean = round((exp(mean(M_temp_coefs, na.rm = TRUE)) -1)*100,1)
@@
 
-pb_temp_coefs = temperature_stats[["pb_temp_coefs"]]
+pb_temp_coefs = temperature_stats[["pb_spp_temp_coefs"]] 
+# pb_temp_coefs = temperature_stats[["pb_temp_coefs"]]
 pb_temp_coef_mean = round((exp(mean(pb_temp_coefs, na.rm = TRUE))-1)*100,1)
@@
 
+Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).   
 The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
@@
 In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
+Material fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
 Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
 
-```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 2."}
-drake::loadd(spp_trait_histograms)
-grid.draw(spp_trait_histograms)
+Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 1).
+Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream.
+This decrease corresponded to a `r (exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C.
+In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream.
+This increase corresponded to a `r (exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 1).
 
-```
-
-The skew of energy fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4).
+The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4).
 The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase.
-Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
+Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
 The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).
 
-```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450, fig.cap="Figure 3."}
+```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 3.
+Lorenz curves of cumulative relative organic matter flux with increasing cumulative species.
+Species are ranked along trait axis of (a) mean body size (mg^-ind^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}
+
 drake::loadd(lorenz_trait_fig)
-grid.arrange(lorenz_trait_fig[["M_lorenz_flux_plot"]], lorenz_trait_fig[["pb_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
-                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))
+grid.draw(lorenz_trait_fig[["lorenz_pbM_plot"]])
 
@@
 We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
-non-random structure in community energy fluxes.
+non-random structure in community OM fluxes.
 The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI).
 Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI).
-The probability that energy fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 5 top).
-Further, there was a trend towards a more structured energy flux distribution with regard to population *P:B* at higher temperatures.
-The probability of observing such skewed energy fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase.
-
-```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 4. Probability distribution of empirical Sk~flux~ measurements compared to random species ordering."}
-drake::loadd(random_skew_fig)
-grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))
-
-```
+The probability that OM fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 5 top).
+Further, there was a trend towards a more structured OM flux distribution with regard to population *P:B* at higher temperatures.
+The probability of observing such skewed OM fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase.
 
 ```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.cap="Figure 5.
-Empirical flux measurements (left column), the probability of observing a more Sk~flux~ value more extreme  (middle), and the estimated effect of increasing temperature on the probability of random ordering (right column) for energy flux distributions in relation to body size (top) and population *P:B* (bottom)." }
+Empirical flux measurements (left column), the probability of observing a more Sk~flux~ value more extreme  (middle), and the estimated effect of increasing temperature on the probability of random ordering (right column) for organic matter flux distributions in relation to body size (top) and population *P:B* (bottom)." }
 drake::loadd(temperature_skew_fig)
@@
 
-Rising global temperatures are altering the pathways of energy flow across and within ecosystems with potential consequences for the services they provide.
-Here, we document shifting energy flow pathways across a wide natural temperature gradient to show that while increasing mean annual temperatures led to expected reductions in mean community body size and increases in mean biomass turnover rates across stream consumer communities, increasing temperatures also systematically skewed energy fluxes *within* communities.
-Here, energy fluxes were skewed towards smaller, quick turnover populations at warmer temperatures and showed increasingly non-random organization moving from cooler to warmer temperatures.
-but this trend reversed at the warmest temperatures.
-The tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests warming may speed up energy fluxes through ecosystems in both an absolute and relative sense.
+Rising global temperatures are altering the pathways of energy and material flow across and within ecosystems with potential consequences for the services they provide.
+While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
+Here, we document shifts in the pathways of material flow  across a wide natural temperature gradient and show that increasing temperatures were associated with reductions in mean population body size and increases in mean population *P:B* across stream consumer communities.
+Further, increasing temperatures also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards smaller, quick turnover populations at warmer temperatures.
+Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at temperature extremes and in relation to population *P:B*, suggesting that environmental/niche filtering is especially important in community assembly of both cold and warm communities.
+This tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests warming may speed up energy and material fluxes through ecosystems in both an absolute and relative sense.
 
@@
 [@diaz2021a] SAD are more uneven than their statistical background
-While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
-Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
+
+For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
+Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
+and community structure across ecosystems...*better transition here.
+Trying to get into P:B and why it should be selected*
+
+*Lastly, want to layer in the concepts of niche filtering and neutral processes in community assembly.
+Pull a little thinking from @saito2021.
+This leads into the random vs non-random patterning questions.
+*
+
+These maximize energy intake when resources are available [@atkinson1997]
+
+- Seasonal systems have unique constraints
+- These seasonal constraints are greater at higher temps
+
+This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017],
+2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
 
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
-Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
-Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
-Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
+Recent, models have proposed  However, 
+- both bottom-up (e.g. resource supply) and top-down (e.g., predation) proceesses
+- competition and predation [@delong2014], stabilize c-r dynamics [@osmond2017], optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a]
+-
+
+*Lastly, want to layer in the concepts of niche filtering and neutral processes in community assembly.
+Pull a little thinking from @saito2021.
+This leads into the random vs non-random patterning questions.
+*
+
+These maximize energy intake when resources are available [@atkinson1997]
+
+- Seasonal systems have unique constraints
+- These seasonal constraints are greater at higher temps
+
+This creates a situation where body sizes are selected for that 1) ,
+2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
 
@@
 ```
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure S4. Probability distribution of empirical Sk~flux~ measurements compared to random species ordering."}
+drake::loadd(random_skew_fig)
+grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))
+
+```

### 2022-02-14 R/plan.R

@@ -32,7 +32,9 @@ the_plan <-
   flux_estimates = estimate_flux(diet_matrices, seasonal_boot_split),
   #
   flux_summaries = summarise_fluxes(flux_estimates[["flux_full"]], production_boots[["int_spp_meta"]]),
-  
+  #
+  taxonomic_info = get_taxa_info(ann_spp_flux =
+                                   flux_summaries[["annual_spp_flux_summary"]]), 
    ### trait analyses
   #
   spp_rankings_boots = rank_spp_boots(production_boots[['ann_spp_boots']]),
@@ -85,6 +87,8 @@ the_plan <-
   spp_trait_histograms = plot_trait_histogram(spp_rankings_summary),
   #
   spp_traitsVtemp = plot_traits_temp(production_boots, spp_rankings_summary, temperature_stats),
+  #
+  spp_flux_dist = plot_spp_relFlux(flux_summaries[["annual_spp_flux_summary"]],taxonomic_info),
   #
   lorenz_trait_fig = plot_trait_lorenz(lorenz_analysis, spp_rankings_summary),
   #

### 2022-02-14 R/plot_skew_temperature.R

@@ -194,10 +194,10 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
     
     
   
- top_plot = grid.arrange(grobs = list(m_temp_skew_plot, m_probs_plot, m_temp_coef_plot), 
-                         layout = c(1,1,1,2,2,2,2,3,3), nrow = 1)
- bottom_plot = grid.arrange(grobs = list(pb_temp_skew_plot, pb_probs_plot, pb_temp_coef_plot),
-                         layout = c(1,1,2,2,2,2,2,3,3), nrow = 1)
+ top_plot = grid.arrange(grobs = list(m_temp_skew_plot, m_probs_plot), 
+                         layout = c(1,1,1,2,2,2,2), nrow = 1)
+ bottom_plot = grid.arrange(grobs = list(pb_temp_skew_plot, pb_probs_plot),
+                         layout = c(1,1,1,2,2,2,2), nrow = 1)
  
  full_plot = grid.arrange(top_plot, bottom_plot, nrow = 2)
  return(full_plot)

### 2022-02-14 R/plot_spp_flux.R

@@ -28,6 +28,7 @@ plot_spp_flux <- function(ann_spp_flux =
     scale_x_continuous(name = 'Species rank')+
     scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
     scale_fill_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
+    annotate('text', label = "B", x = Inf, y = Inf, family = 'serif', vjust = 1, hjust = 1, size = 4)+
     theme_tufte(ticks = TRUE) +
     geom_rangeframe(sides = "lb")+
     theme(legend.position = c(0,0),

### 2022-02-14 R/plot_spp_relFlux.R

@@ -1,0 +1,174 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param nameme1
+plot_spp_relFlux <- function(ann_spp_flux =
+                             flux_summaries[["annual_spp_flux_summary"]],
+                             taxaDf = taxonomic_info) {
+  
+  namesDf = taxaDf %>%
+    ungroup %>%
+    dplyr::mutate(taxaGroup = recode(taxaGroup, Oligochaeta = 'Lumbricidae')) %>%
+     dplyr::select(taxon, cleanGroup, taxaGroup) %>% unique
+  
+  taxaDf %>%
+    dplyr::select(site, taxon, cleanGroup, taxaGroup, flux_mg_m_y_mean) %>%
+    dplyr::mutate(site = factor(site, levels = stream_order)) %>%
+    group_by(site) %>%
+    dplyr::mutate(rel_flux_mean = flux_mg_m_y_mean/sum(flux_mg_m_y_mean, na.rm = TRUE)) %>%#,
+                  # rel_flux_mean = case_when(rel_flux_mean <0.01 ~ 0.0101,
+                  #                           TRUE ~ rel_flux_mean)) %>%
+    junkR::named_group_split(site) -> ann_spp_fluxList
+  
+  
+   ann_spp_fluxList = purrr::map(ann_spp_fluxList, function(x){
+     # browser()
+     df = x
+     lowFluxN = x %>% dplyr::filter(rel_flux_mean <= 0.0101) %>% nrow
+     other_label = paste0("Other taxa (n = ",lowFluxN,")")
+     x %>%
+       dplyr::mutate(taxon = case_when(rel_flux_mean > 0.0101 ~ taxon,
+                                       TRUE ~ other_label)) %>%
+       group_by(site, taxon) %>%
+       dplyr::summarise(rel_flux_mean = sum(rel_flux_mean, na.rm = TRUE)) %>%
+       left_join(namesDf, by = "taxon") %>%
+       dplyr::mutate(rel_flux_mean = case_when(rel_flux_mean < 0.01 ~ 0.0101,
+                                               TRUE ~ rel_flux_mean),
+                     taxon = factor(taxon,
+                                    levels = df %>%
+                                      dplyr::filter(taxon != other_label) %>%
+                                      dplyr::arrange(rel_flux_mean) %>%
[…]

### 2022-02-14 R/plot_trait_lorenz.R

@@ -27,6 +27,20 @@ plot_trait_lorenz <- function(lorenz_analysis, spp_rankings_summary) {
           strip.text = element_blank()) +
     facet_wrap(~site, ncol = 2) -> lorenz_flux_plot
     
+    plot_legend = cowplot::get_legend(lorenz_flux_plot + guides(color = guide_legend(byrow = TRUE, nrow = 1)))
+    plot_legend$grobs <- lapply(plot_legend$grobs, function(z) modifyList(z, list(x = unit(0.5, 'npc'), just = "center")))
+    plot_legend$layout
+    
+    pb_label = grid::textGrob(expression("Increasing"~italic("P:B")), x = unit(0.5, 'npc'), just = "centre",
+                             gp = gpar(fontfamily = 'serif', fontsize = 10))
+    pb_box = grid::roundrectGrob(x = unit(0.5, 'npc'), y = unit(0.5, 'npc'),
+                                width = unit(0.55, 'npc'), height = unit(0.8, 'npc'),
+                                just = "centre")
+    pb_arrow = segmentsGrob(x0 = unit(0.1,'npc'), x1 = unit(0.9, 'npc'),
+                           y0 = unit(0.5,'npc'), y1 = unit(0.5, 'npc'),
+                           arrow = arrow(type = 'closed'), gp = gpar(fill = 'black', lex = 0.8))
+    pb_header = grid::grobTree(pb_arrow, pb_box, pb_label)
+    
     lorenz_analysis[["pb_ranking_boots"]] %>%
         ggplot(aes(x = rel_spp, y = rel_flux)) +
         geom_abline(color = "black")+
@@ -38,7 +52,7 @@ plot_trait_lorenz <- function(lorenz_analysis, spp_rankings_summary) {
         scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
         theme_tufte(ticks = TRUE) +
         geom_rangeframe(sides = "lb")+
-        theme(legend.position = c(0,1),
+        theme(legend.position = 'none',
               legend.justification = c("left", "top"), 
               legend.title = element_blank(),
               legend.spacing.y = unit(0.0003,'cm'),
@@ -46,6 +60,17 @@ plot_trait_lorenz <- function(lorenz_analysis, spp_rankings_summary) {
               strip.text = element_blank(), axis.title = element_blank()) +
[…]

### 2022-04-15 doc/ms/ms.Rmd
updated text. commit before st9 updated.

@@
 
-Warming temperatures are altering biological communities and trophic networks globally.
-While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple fundamental ways by 1) decreasing organism body size and 2) increasing metabolic rates.
-These two attributes, body size and metabolic rate, are important drivers of many ecological patterns.
+Warming temperatures are altering communities and trophic networks globally.
+While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple general and fundamental ways: 1) decreasing organism body size and 2) increasing metabolic rates.
+Both body size and metabolic rate are important drivers of many ecological patterns.
 Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food webs fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly.
-Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a ~25$^\circ$C temperature gradient.
-We then relate patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
+Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient.
+We then related patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
 We predicted 1) fluxes would skew towards smaller *M* and higher *P:B* both across and within ecosystems and 2) fluxes would be more skewed at higher temperatures.
@@
 The emerging picture is a warmer world that is both smaller and faster.
-Our study lends further support to this pattern and also suggests that
-
+Our study lends further support to this pattern and suggests that temperature will become an increasingly important environmental filter on warming communities in the future.
 \newpage
@@
 Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history [@zeuss2017; @altermatt2010; @nelson2020b], development [@angilletta2004], and crucially, basal metabolic rate [@brown2004; @gillooly2001].
+These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history patterns [@zeuss2017; @altermatt2010; @nelson2020b], and developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
 
@@
 Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
-As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.
+As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.*possibly simplify the paragraph and combined with above*
 
@@
 using image analysis software [@schindelin2012]. We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
-plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
+plants (e.g., bryophytes), and animal material and then calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
 contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.
@@
 Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`]).
+Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI).
 Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
@@
 Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
-
-Generally, organic matter fluxes were dominated by insect species from *Simuliidae* and *Chironomidae* families (Figure 1a).
-In warmer streams, OM fluxes shifted toward the pulmonate snail, *Radix balthica*.
-In the warmest stream, where maximum temperatures approach ~40$^\circ$C, OM fluxes were dominated by worms of family *Naididae*, the midge *Cricotpous sylvestris*, and *Radix balthica*.
-
-```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1.
-Patterns of OM flux among populations based on (a) Rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) and (b) relative OM flux among taxaonomic groups in consumer communities and across the temperature gradient."}
-drake::loadd(annual_spp_flux_fig)
-drake::loadd(spp_flux_dist)
-gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
-```
-
-```{r trait df, echo = FALSE, warning = FALSE, message = FALSE}
-drake::loadd(spp_traitsVtemp)
-ann_spp_summ = spp_traitsVtemp[['ann_spp_summ']]
-
-```
-
-## Evenness of OM fluxes within streams
 
@@
 gini_summary = gini_analysis[["stream_gini_summary"]] %>% set_names(make.names(names(.)))
-
-```
-
-Organic matter fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1b; Figure S1).
-Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`; Table 1).
-Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups.
-Yet, even after accounting for differences in consumer richness, patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`; Table 1).
-
-```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
-drake::loadd(gini_analysis)
-tab1_caption = "Table 1.
-Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
-gini_analysis[["stream_gini_summary"]] %>% 
-   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
-   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
-                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
-   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
-   knitr::kable(align = "lrr", caption = tab1_caption)
 
@@
 
-Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1b).
-For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species.
-Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams.
-Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.
+## Evenness of OM fluxes within streams
 
-```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 2.
-The relationships between mean annual stream temperature and (a) average population body size of the community (mg^-ind^) and (b) average population turnover expressed as production to biomass ratios (*P:B*, y^-1^)."}
+Generally, organic matter fluxes were dominated by insect species from Simuliidae and Chironomidae families (Figure 1a) and were distributed unevenly (Figure 1b; Figure S1).
+In an absolute sense, ~85% of total flux was contributed by between `r n_dom_min$n_dom` and `r n_dom_max$n_dom` consumer groups.
+Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the consumer assemblage within streams.
+Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups.
+Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1).
+In warmer streams, OM fluxes shifted toward the black fly, *Simuliium vittatum* and the pulmonate snail, *Radix balthica*.
+In the warmest stream, where maximum temperatures approach ~40$^\circ$C, species richness was lowest and OM fluxes were dominated by oligochaete worms of family Naididae, the chironomid *Cricotpous sylvestris*, and *Radix balthica*.
+Yet, even after accounting for differences in consumer richness, patterns of material flux were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1).
+Differences in evenness and dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.
 
+```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1.
+Patterns of OM flux among populations based on (a) relative OM flux among taxonomic groups in consumer communities and descending the temperature gradient from the warmest (27.2$^\\circ$C) on top pane to coldest (5.0$^\\circ$C) on the botthom.
+(b) The rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) of consumer groups.
+In (a), consumer groups fill is based on taxonomic family and the full key of consumer group abbreviations can be found in supporting materials."}
+
+drake::loadd(annual_spp_flux_fig)
+drake::loadd(spp_flux_dist)
+gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
+```
+
+```{r trait df, echo = FALSE, warning = FALSE, message = FALSE}
 drake::loadd(spp_traitsVtemp)
-grid.draw(spp_traitsVtemp[['fig1_plot']])
+ann_spp_summ = spp_traitsVtemp[['ann_spp_summ']]
 
- # drake::loadd(spp_trait_histograms)
-# grid.draw(spp_trait_histograms)
+```
+
+```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
+drake::loadd(gini_analysis)
+tab1_caption = "Table 1.
+Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
+gini_analysis[["stream_gini_summary"]] %>% 
+   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
+   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
+                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+   knitr::kable(align = "lrr", caption = tab1_caption)
 
@@
 
-Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).   
-The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams.
-Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).
-Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
-Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
-In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-Material fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
-Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
+Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 2).
+Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
+This decrease corresponded to a `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C.
+In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
+This increase corresponded to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 2).
 
-Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 1).
-Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream.
-This decrease corresponded to a `r (exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C.
-In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream.
-This increase corresponded to a `r (exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100 %>% round(2)` (`r (exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100 %>% round(2)`--`r (exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100 %>% round(2)`) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 1).
+```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 2.
+The relationships between mean annual stream temperature and (a) average population body size of the community (mg^-ind^) and (b) average population turnover expressed as production to biomass ratios (*P:B*, y^-1^)."}
 
-The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4).
+drake::loadd(spp_traitsVtemp)
+grid.draw(spp_traitsVtemp[['fig1_plot']])
+
+ # drake::loadd(spp_trait_histograms)
+# grid.draw(spp_trait_histograms)
+
+```
+
+Organic matter fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size among streams.
+Skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
+Similarly, skew in fluxes towards high *P:B* taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
+The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4a).
 The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase.
 Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
-The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).
+The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4c).
 
-```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 3.
+```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=4.0, fig.height=7, dpi = 450, fig.cap="Figure 3.
 Lorenz curves of cumulative relative organic matter flux with increasing cumulative species.
-Species are ranked along trait axis of (a) mean body size (mg^-ind^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}
+Species are ranked along trait axis of (a) mean body size (mg ind^-1^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}
 
@@
 non-random structure in community OM fluxes.
-The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI).
-Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI).
-The probability that OM fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 5 top).
+The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI; Figure 4b).
+Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI; Figure 4d).
+The probability that OM fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 4b).
 Further, there was a trend towards a more structured OM flux distribution with regard to population *P:B* at higher temperatures.
-The probability of observing such skewed OM fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase.
+The probability of observing such skewed OM fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase (Figure 4d).
 
-```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.cap="Figure 5.
-Empirical flux measurements (left column), the probability of observing a more Sk~flux~ value more extreme  (middle), and the estimated effect of increasing temperature on the probability of random ordering (right column) for organic matter flux distributions in relation to body size (top) and population *P:B* (bottom)." }
+```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.cap="Figure 4.
+The empirical skew of organic matter fluxes in relation to (a) body size and (c) *P:B*.
+The probability of observing a Sk~flux~ value more extreme by random chance increased slightly with increasing temperature for body size (b).
+The pattern was stronger for population *P:B* (d)." }
 drake::loadd(temperature_skew_fig)
@@
 Rising global temperatures are altering the pathways of energy and material flow across and within ecosystems with potential consequences for the services they provide.
-While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
+While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017]---especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
 Here, we document shifts in the pathways of material flow  across a wide natural temperature gradient and show that increasing temperatures were associated with reductions in mean population body size and increases in mean population *P:B* across stream consumer communities.
 Further, increasing temperatures also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards smaller, quick turnover populations at warmer temperatures.
-Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at temperature extremes and in relation to population *P:B*, suggesting that environmental/niche filtering is especially important in community assembly of both cold and warm communities.
-This tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests warming may speed up energy and material fluxes through ecosystems in both an absolute and relative sense.
-
-Increasing global temperatures
-
-[@diaz2021a] SAD are more uneven than their statistical background
+Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at temperature extremes and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of both cold and warm communities.
+This tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests the speeding up of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of increasing temperature.
 
@@
 Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
-and community structure across ecosystems...*better transition here.
-Trying to get into P:B and why it should be selected*
+and community structure across ecosystems...
+
+[@diaz2021a] SAD are more uneven than their statistical background
 
@@
 
+Spare(d) words
+
 Recent, models have proposed  However, 
@@
 2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
+
+Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).
+Both among and within streams, OM fluxes were distributed differently across body sizes and turnover rates (*P:B*).
+Among streams, mean population body size ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean population annual  P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
+Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
+In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
 

### 2022-04-15 R/plot_random_skew.R

@@ -88,7 +88,7 @@ random_rankings %>%
   geom_histogram(data = skew_boots, aes(x = pb_y_skew, y = ..density..,color = site, fill = site), linetype = 'dashed', inherit.aes = FALSE, bins = 50, alpha = 0.5)+
   scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
   scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
-  guides(linetype = FALSE)+
+  guides(linetype = "none")+
   theme_tufte(ticks = TRUE) +
   geom_rangeframe(sides = "lb")+
   theme(legend.position = 'none') +
@@ -102,11 +102,28 @@ random_rankings %>%
   geom_histogram(data = skew_boots, aes(x = M_mg_ind_skew, y = ..density..,color = site, fill = site), linetype = 'dashed', inherit.aes = FALSE, bins = 50, alpha = 0.5)+
   scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels)+
   scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels)+
-  guides(linetype = FALSE)+
+  guides(linetype = "none")+
   theme_tufte(ticks = TRUE) +
   geom_rangeframe(sides = "lb")+
   theme(legend.position = 'none') +
   facet_wrap(~site, ncol = , scales = 'free_y') -> M_skew_plot
+
+random_summ = random_rankings %>%
+  group_by(site) %>%
+  dplyr::summarise(across(everything(), list(mean = ~mean(.x, na.rm = TRUE),
+                                               median = ~median(.x, na.rm = TRUE),
+                                               quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                               quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE),
+                                               HPDI_25up = ~rethinking::HPDI(.x, prob = 0.25)[2],
+                                               HPDI_25dn = ~rethinking::HPDI(.x, prob = 0.25)[1],
+                                               HPDI_50up = ~rethinking::HPDI(.x, prob = 0.5)[2],
+                                               HPDI_50dn = ~rethinking::HPDI(.x, prob = 0.5)[1]),
[…]

### 2022-04-15 R/plot_skew_temperature.R

@@ -5,7 +5,7 @@
 ##' @title
 ##' @param temperature_stats
 plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
-  
+  set.seed(123)
   n_draws = sample(1:6000, n_id, replace = FALSE)
   
   m_skew_summ = temperature_stats[["m_skew_df"]] %>%
@@ -16,8 +16,8 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
                                                quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                HPDI_50up = ~rethinking::HPDI(.x, 0.5)[2],
                                                HPDI_50dn = ~rethinking::HPDI(.x, 0.5)[1],
-                                               HPDI_90up = ~rethinking::HPDI(.x, 0.9)[2],
-                                               HPDI_90dn = ~rethinking::HPDI(.x, 0.9)[1],
+                                               HPDI_90up = ~rethinking::HPDI(.x, 0.89)[2],
+                                               HPDI_90dn = ~rethinking::HPDI(.x, 0.89)[1],
                                                median = ~median(.x, na.rm = TRUE),
                                                quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                quant97.5 = ~quantile(.x, 0.95, na.rm = TRUE)))) %>%
@@ -31,13 +31,16 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
                                    geom_point(aes(y = site, x = M_mg_ind_skew_median), size = 2, color = 'black')+
                                    scale_x_continuous(name = expression(""*italic(Sk[flux])), limits = c(-1,1), expand = c(0,0.004) ) +
                                    scale_y_discrete(labels = rev(stream_temp_labels))+
+                                   annotate('text', label = "A", x = -Inf, y = 1, family = 'serif', hjust = 0, vjust = 0, size = 4)+
                                    scale_color_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = names(stream_temp_labels))+
                                    theme(legend.position = 'none',
-                                         axis.title.y = element_blank()));#grid.draw(m_temp_skew_plot)
+                                         axis.title.y = element_blank()))#;grid.draw(m_temp_skew_plot)
   
   
[…]

### 2022-04-15 R/plot_spp_flux.R

@@ -20,6 +20,8 @@ plot_spp_flux <- function(ann_spp_flux =
     dplyr::filter(flux_mg_m_y_mean > 1e-5)
   
   evenness_plot= plotting_df %>%
+    na.omit %>%
+    dplyr::filter(log(flux_mg_m_y_mean) > -10) %>%
     ggplot(aes(x = rank, y = log(flux_mg_m_y_mean), group = site))+
     geom_line(aes(color = site), size = 2)+
     geom_point(aes(fill = site), shape = 21, size = 2.3, color = 'black') +

### 2022-04-15 R/plot_trait_lorenz.R

@@ -32,9 +32,9 @@ plot_trait_lorenz <- function(lorenz_analysis, spp_rankings_summary) {
     plot_legend$layout
     
     pb_label = grid::textGrob(expression("Increasing"~italic("P:B")), x = unit(0.5, 'npc'), just = "centre",
-                             gp = gpar(fontfamily = 'serif', fontsize = 10))
+                             gp = gpar(fontfamily = 'serif', fontsize = 8))
     pb_box = grid::roundrectGrob(x = unit(0.5, 'npc'), y = unit(0.5, 'npc'),
-                                width = unit(0.55, 'npc'), height = unit(0.8, 'npc'),
+                                width = unit(0.4, 'npc'), height = unit(0.8, 'npc'),
                                 just = "centre")
     pb_arrow = segmentsGrob(x0 = unit(0.1,'npc'), x1 = unit(0.9, 'npc'),
                            y0 = unit(0.5,'npc'), y1 = unit(0.5, 'npc'),
@@ -61,9 +61,9 @@ plot_trait_lorenz <- function(lorenz_analysis, spp_rankings_summary) {
         facet_wrap(~site, ncol = 1) -> pb_lorenz_flux_plot
     
     M_label = grid::textGrob(expression("Increasing"~italic("M")), x = unit(0.5, 'npc'), just = "centre",
-                             gp = gpar(fontfamily = 'serif', fontsize = 10))
+                             gp = gpar(fontfamily = 'serif', fontsize = 8))
     M_box = grid::roundrectGrob(x = unit(0.5, 'npc'), y = unit(0.5, 'npc'),
-                           width = unit(0.55, 'npc'), height = unit(0.8, 'npc'),
+                           width = unit(0.4, 'npc'), height = unit(0.8, 'npc'),
                            just = "centre")
     M_arrow = segmentsGrob(x0 = unit(0.1,'npc'), x1 = unit(0.9, 'npc'),
                  y0 = unit(0.5,'npc'), y1 = unit(0.5, 'npc'),

### 2022-04-15 R/plot_traits_temp.R

@@ -77,7 +77,7 @@ plot_traits_temp <- function(production_boots,
                        breaks = log(c(5,1,0.5,0.1,0.05, 0.01)), labels = exp(log(c(5,1,0.5,0.1,0.05, 0.01)))) +
     scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
     scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
-    annotate('text', label = 'A', x = Inf, y = Inf, family = 'serif', vjust = 1,hjust = 1, size = 3)+
+    annotate('text', label = 'A', x = Inf, y = Inf, family = 'serif', vjust = 1,hjust = 1, size = 4)+
     theme_tufte(ticks = TRUE) +
     geom_rangeframe(aes(x = tempC, y = log(M_mg_ind_mean)), sides = "lb")+
     theme(legend.position = 'none', axis.title.x = element_blank())) -> comm_m_plot

### 2022-07-08 doc/ms/ms.Rmd
first update after prod fix. Push prior to taxa aggregatation in st7 & oh2

@@
 Warming temperatures are altering communities and trophic networks globally.
-While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter to alter food webs and ecosystems in a couple general and fundamental ways: 1) decreasing organism body size and 2) increasing metabolic rates.
+While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter food webs and ecosystems in a number of general and fundamental ways, among them, 1) decreasing organism body size and 2) increasing metabolic rates.
 Both body size and metabolic rate are important drivers of many ecological patterns.
@@
 
-From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities (*PS*; @whittaker1952) among modeled diet estimates.
+From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities (*PS*; @whittaker1952 among modeled diet estimates.
 Proportional similarities were calculated as:
@@
 filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
-(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
+(bryophytes) = 0.1 (95% PI: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
 incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
@@
 Here, we predicted that communities with strong filtering for traits would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
-In contrast, weak environmental filtering would produce OM fluxes with skew values that are likely due to random chance ('random ordering'.
+In contrast, weak environmental filtering would produce OM fluxes with skew values that are likely due to random chance ('random ordering').
 To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
@@
 This decrease corresponded to a `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C.
-In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
-This increase corresponded to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C (Figure 2).
+In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
+This increase corresponded to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) increase in mean population biomass turnover (P:B y^-1^) for every increase of 1$^\circ$C (Figure 2).
 
@@
 Organic matter fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size among streams.
-Skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
-Similarly, skew in fluxes towards high *P:B* taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
-The skew of OM fluxes towards populations with smaller/larger body sizes showed a small, yet systematic association with stream temperature (Figure 4a).
-The median effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_median` units (`r M_skew_temp_coef_quant2.5`--`r M_skew_temp_coef_quant97.5` 95% PI) for every 1$^\circ$C increase.
+Skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(M_mg_ind_skew_mean) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_mean) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
+Similarly, skew in fluxes towards high *P:B* taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_mean) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_mean) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
+The skew of OM fluxes towards populations with smaller/larger body sizes showed no systematic association with stream temperature (Figure 4a).
 Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
@@
 
-For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
-Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
-and community structure across ecosystems...
-
-[@diaz2021a] SAD are more uneven than their statistical background
-
 *Lastly, want to layer in the concepts of niche filtering and neutral processes in community assembly.
@@
 *
+
+Temperature has long been known to be an important control on ecological process rates [@arrhenius1897; @gillooly2003; @brown2004]
 
@@
 
+For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
+Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
+and community structure across ecosystems...
+
+[@diaz2021a] SAD are more uneven than their statistical background
+
 # Acknowledgements
@@
 We are also grateful to Sveinbj€orn Steinþorsson at the University of Iceland for super-jeep transport to our field sites during the winter.
-Jeff Wesner and Abe Kanz for code sharing and discussions on modeling diet proportions.
+We thank Lauren David, David Hernandez, Amanda Keasberry, Elena Nava, Camille Perrett, Jackie Pitts, Friðþjófur Árnason, Liliana García, Ragnahildur Magnúsdottír, Ryan McClure, Vija Pelekis, Adam Toomey, Chau Tran, Brooke Weigel, Tanner Williamson and many undergraduate workers for field and laboratory help.
+Jeff Wesner and Abe Kanz generously provided R code and discussions on modeling diet proportions.
+This study was supported by the National Science Foundation (DEB-0949774 and DEB-1354624 to JPB and ADH and DEB-0949726 to WFC).
 

### 2022-07-08 R/plot_skew_temperature.R

@@ -31,7 +31,7 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
                                    geom_point(aes(y = site, x = M_mg_ind_skew_median), size = 2, color = 'black')+
                                    scale_x_continuous(name = expression(""*italic(Sk[flux])), limits = c(-1,1), expand = c(0,0.004) ) +
                                    scale_y_discrete(labels = rev(stream_temp_labels))+
-                                   annotate('text', label = "A", x = -Inf, y = 1, family = 'serif', hjust = 0, vjust = 0, size = 4)+
+                                   annotate('text', label = "A", x = -0.99, y = 1, family = 'serif', hjust = 0, vjust = 0, size = 4)+
                                    scale_color_manual(values = rev(ocecolors[['temperature']][oce_temp_pos]), labels = names(stream_temp_labels))+
                                    theme(legend.position = 'none',
                                          axis.title.y = element_blank()))#;grid.draw(m_temp_skew_plot)
@@ -55,13 +55,12 @@ plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
                                                   quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
     dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
   
-    m_probs_plot_df = temperature_stats[["m_probs_temp_pred"]] %>% dplyr::filter(.draw %in% n_draws)
+    m_probs_plot_df = temperature_stats[["m_probs_temp_pred"]] %>% dplyr::filter(.draw %in% 41)#n_draws)
     
   set.seed(123)
   m_probs_plot = ggplotGrob(m_probs_summ %>%
                                ggplot(aes(x = tempC, y = M_skew_prob_median)) +
-                               geom_line(data = m_probs_plot_df, aes( x = tempC, y = .prediction, group = .draw),
-                                         alpha = 0.1, color = 'lightgrey') +
+                                geom_line(data = m_probs_plot_df, aes( x = tempC, y = .prediction, group = .draw))+#, alpha = 0.1, color = 'lightgrey') +
[…]

### 2022-07-20 doc/ms/ms.Rmd
updated figures and added some discussion text

@@
 Here, we document shifts in the pathways of material flow  across a wide natural temperature gradient and show that increasing temperatures were associated with reductions in mean population body size and increases in mean population *P:B* across stream consumer communities.
-Further, increasing temperatures also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards smaller, quick turnover populations at warmer temperatures.
-Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at temperature extremes and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of both cold and warm communities.
+Further, increasing temperature also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards smaller, quick turnover populations at warmer temperatures.
+Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at moderate to warm temperatures and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of warm communities.
 This tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests the speeding up of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of increasing temperature.
+
+Reductions in organism body size with warming has been deemed a "universal" response to warming [@daufresnes2009; @gardner2011; @uszko2022].
+We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 2), corresponding to ~9% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
+While this change represents a community-level shift, the magnitude of change is consistent with recent work on the effects of warming on organism body size across broad taxonomic groups [@deutsch2022].
+This reduction in body size with increasing temperature contrasts results from previous whole-ecosystem warming experiments which observed shifts in community biomass and productivity from smaller to larger organisms following a 3$^\circ$C increase in temperature [@nelson2017; @nelson2017a].
+Our results also counter observational studies in this system that have shown no consistent change in body size within diatom communities at either the population- or community-scale [@adams2013].
+These contrasting results are consistent with deviations from the "universal" response observed across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; fish @rypel2014].
+Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
+Considering the connections between organism body size and many other ecological attributes [@peters1983], reductions in body size with increasing temperatures could have broad implications for ecosystem dynamics with a changing climate [@gibert2019a].
+
+Warmer ecosystems exhibited higher rates of energy flux in both an absolute and relative sense.
+At the community level, we observed a ~7% increase in the mean biomass turnover rate (P:B; y^-1^).
+Temperature has long been recognized as an important driver of ecological rates [@gillooly2001] and the increase in biomass turnover among communities is likely attributed to the thermodynamic effect of temperature--in part.
+Biomass turnover rate is also tightly tied to organism body size [@brown2004; @huryn2007] suggesting that temperature may influence the distribution of *P:B*s both directly through its effects on metabolic rates and indirectly by inducing reductions in organism body size.
+The influence of this interaction between the direct and indirect effect of temperature on metabolic activities in increasingly recognized.
+For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concomitant changes to organism body size are taken into account [@bernhardt2018].
+Further, reduce body sizes stabilize systems by reducing C:R ratios at higher temperatures [@gilbert; @sentis2017; @bideault2019]
 
@@
 
-Temperature has long been known to be an important control on ecological process rates [@arrhenius1897; @gillooly2003; @brown2004]
+Temperature has long been known to be an important control on ecological process rates [@gillooly2003; @brown2004]
 

### 2022-07-20 R/analyze_diversity.R

@@ -19,10 +19,10 @@ analyze_diversity <- function(production_boots) {
     bind_cols(int_spp_wide %>% select(site_id, date_id)) %>%
     select(site_id, date_id, everything()) %>%
     dplyr::mutate(site_id = factor(site_id, levels = names(stream_order_list))) %>%
-    group_by(site_id) %>% dplyr::arrange(date_id)
-  # 
-  # ggplot(NMDS.scrs, aes(x = NMDS1, y = NMDS2)) + 
-  #   geom_point(aes(color = site_id))+
-  #   geom_path(aes(group = site_id, color = site_id))
+    group_by(site_id) %>% dplyr::arrange(date_id) 
+ 
+    return(list(int_spp_wide = int_spp_wide,
+              NMDS = NMDS,
+              NMDS.scrs = NMDS.scrs))
   
   }

### 2022-07-20 R/analyze_temp_stats.R

@@ -135,6 +135,7 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
                             coi ~ 1,
                             family = brms::zero_one_inflated_beta())
   
+  # get_prior(pb_skew_formula, data = pb_skew_df, family = brms::zero_one_inflated_beta())
   pb_skew_priors = c(set_prior("normal(0,1.2)", class = "b", coef = "tempC_stand"),
                     set_prior("normal(0.5,0.5)", class = "Intercept"))
   
@@ -147,18 +148,37 @@ analyze_temp_stats <- function(ann_comm_boots = production_boots[["ann_comm_boot
                                 control = list(adapt_delta = 0.99),
                                 sample_prior = "yes",
                                 file = "./data/derived-data/models/pb_skew_temp_model.rds",
-                                file_refit = 'on_change')
+                                file_refit = 'on_change',
+                                backend = "cmdstanr")
+  pb_skew_temp_boots = add_criterion(pb_skew_temp_boots, "loo", file = "./data/derived-data/models/pb_skew_temp_model.rds")
 
   pb_skew_temp_pred = pb_skew_temp_boots %>%
     add_epred_draws(newdata = new_data) %>%
     dplyr::mutate(new_epred = (.epred - 1)/2)
-  # purrr::pmap(~..2 %>% predict(newdata = new_data) %>% data.frame(.fitted = .) %>% dplyr::mutate(tempC = unlist(new_data, use.names = FALSE))) 
-  # 
-  # 
+
   pb_skew_temp_coefs = pb_skew_temp_boots %>%
     brms::posterior_samples("tempC_stand")
-  #   purrr::pmap_dbl(~..2 %>% pluck('coefficients') %>% pluck('mean') %>% pluck('tempC'))
-  # 
+
+  
+  pb_skew_temp_null = brms::brm(formula = brms::bf(pb_y_skew_mod ~ 1,
+                                                   phi ~ 1,
+                                                   zoi ~ 1,
+                                                   coi ~ 1,
+                                                   family = brms::zero_one_inflated_beta()),
+                                 data = pb_skew_df,
+                                 # prior = pb_skew_priors,
+                                 warmup = 10e3,
+                                 iter = 12e3,
+                                 chains = 3,
+                                 control = list(adapt_delta = 0.99),
+                                 sample_prior = "yes",
+                                 file = "./data/derived-data/models/pb_skew_temp_null.rds",
+                                 file_refit = 'on_change',
+                                backend = "cmdstanr")
[…]

### 2022-07-20 R/plan.R

@@ -93,7 +93,9 @@ the_plan <-
   random_skew_fig = plot_random_skew(skew_analysis, random_rankings),
   # 
   temperature_skew_fig = plot_skew_temperature(temperature_stats, n_id = 2e3),
-  
+  #
+  # diversity_fig = plot_comm_diversity(diversity_analysis),
+  # pbM_fig = plot_spp_ann_trait(production_summaries[['ann_spp_summary']]),
   
   # target_name = target(
     # command = {
@@ -107,7 +109,7 @@ the_plan <-
   #     rmarkdown::render(knitr_in("doc/./ms/ms.Rmd"))
   #     file_out("doc/./ms/ms.docx")
   #   }
-  # ),
+  # )
   # 
   # figure_file = target(
   #   command = {

### 2022-07-20 R/plot_spp_ann_trait.R

@@ -1,0 +1,15 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param nameme1
+plot_spp_ann_trait <- function(sppDf = production_summaries[["ann_spp_summary"]]) {
+
+  sppDf %>%
+    dplyr::mutate(site_id = factor(site_id, levels= stream_order)) %>%
+    ggplot()+
+    geom_point(aes(x = log(M_mg_ind_mean), y = log(pb_y_mean), color = site_id))
+    
+
+}

### 2022-07-20 R/read_clean_guts.R

@@ -15,11 +15,11 @@ read_clean_guts <- function() {
                     c("Tany"),
                     c("Theinem","Theinemanniella"),
                     c("Simuliumvittatum", "Svitt", "Simulium.vittatum"),
-                    c("Oligo", "Lumb 3","Lumb"), 
+                    c("Oligochaeta.A","Oligochaeta.B","Oligo", "Lumb 3","Lumb"), 
                     c("Ofridgidus", "Orthocladius fridgidus","Orthocladius.fridgidus"),
                     c("Rhecricotopus","Rheocricotpus","Rheocricotopus.effusus","Rheocricotopus"),
                     c("Orthoclad"),
-                    c("Ceratopegonid"),
+                    c("Ceratopegonid","Ceratopogonidae.A","Ceratopogonidae.B"),
                     c("Chaetocladius dentiforceps","Odentiformes"),
                     c("Diamesa.bohemani_zernyi"),
                     c("Diamesa.bertrami"),
@@ -45,19 +45,19 @@ read_clean_guts <- function() {
                     "Orthocladius frigidus",
                     "Rheocricotopus effusus",
                     "Orthocladius spp.",
-                    "Ceratopogonidae",
+                    "Ceratopogonid",
                     "Chaetocladius dentiforceps",
                     "Diamesa bohemani_zernyi",
                     "Diamesa bertrami",
-                    "Eukiefferiella claripennis",
-                    "Eukiefferiella minor",
+                    "Eukiefferiella sp.",
+                    "Eukiefferiella sp.",
                     "Micropsectra sp.",
                     "Parochlus sp.",
                     "Potamophylax cingulatus",
                     "Prosimulium ursinum", 
                     "Simulium vernum",
                     "Sperchon glandulosus",
-                    "Oligochaeta A",
+                    "Lumbricidae",
                     "Clinocera stagnalis")
   
   taxon_name_keyval = setNames(rep(new_names, lengths(old_names)), unlist(old_names))

### 2022-07-20 R/read_production.R

@@ -9,12 +9,20 @@ read_production <- function() {
   ####    full raw production, biomass, abundance import and clean    ####
   prod_full_list = readRDS(file = "./data/derived-data/prod_full_fin.rds") %>%
     #rename Tubificid update to Naidid to recognize taxon changes
-    purrr::map(~.x %>% purrr::map(~.x %>% dplyr::mutate(taxon_id = case_when(stringr::str_detect("Tubificid 1",taxon_id) ~ "Naidid 1",
+    furrr::future_map(~.x %>% furrr::future_map(~.x %>% 
+                                    # rename and consolidate a few taxa to maintain resolution among streams
+                                    dplyr::mutate(taxon_id = case_when(grepl("Ceratopogonidae.+", taxon_id) ~ "Ceratopegonid",
+                                                                       grepl("Eukiefferiella.+", taxon_id) ~ "Eukiefferiella sp.",
+                                                                       grepl("Oligochaeta.*",taxon_id) ~ "Lumbricidae",
+                                                                       TRUE ~ taxon_id)) %>%
+                                    dplyr::mutate(taxon_id = case_when(stringr::str_detect("Tubificid 1",taxon_id) ~ "Naidid 1",
                                                                              stringr::str_detect("Tub. 2", taxon_id) ~ "Naidid 2",
                                                                              stringr::str_detect(" Eukiefferiella|Eukiefferiella", taxon_id) ~ "Eukiefferiella sp.",
                                                                              stringr::str_detect("Lumb 3", taxon_id) ~ "Lumbricidae",
                                                                              stringr::str_detect("Orthocladius fridgidus", taxon_id) ~ "Orthocladius frigidus",
-                                                                             TRUE ~ taxon_id )))) %>%
+                                                                             TRUE ~ taxon_id )) %>% group_by(site_id, taxon_id, date_id, boot_id) %>%
+                                    dplyr::summarise(across(where(is.numeric), ~sum(.x))) %>%
+                                    ungroup)) %>%
     rlist::list.subset(names(stream_order_list))
   
   spp_removals = list(hver = c('Homoptera', 'Lepidoptera', 'Limnophora.pupa', 'Midge.pupa', 

### 2022-07-20 packages.R

@@ -2,8 +2,8 @@
 ###load packages and functions
   if(!require("pacman")) install.packages("pacman")
   library(pacman)
-  package.list <- c("conflicted", "dotenv", "drake","data.table","gtools",
-                    "RCurl","plyr","tidyverse","furrr", "fnmate", "moments",
+  package.list <- c("conflicted", "dotenv", "drake","data.table","gtools","rlist",
+                    "RCurl","plyr","tidyverse","furrr", "fnmate", "moments","fuzzySim",
                     "dflow","rmarkdown","tictoc","chron","lubridate","httr","TTR", 
                     "grid","gridExtra", "ggridges", "fluxweb", "rmarkdown", "MuMIn","zoib",
                     "viridis", "broom","bbmle","ggthemes", "ggeffects", "ggpubr","betareg",
@@ -11,8 +11,9 @@
                     "rstan", "brms", "tidybayes", "parallel", "hillR", "RInSp", "rsample",
                     "emmeans")
   p_load(char = package.list, install = TRUE, character.only = TRUE)
-  # p_load_gh("jimjunker1/junkR")
+  # pacman::p_load_gh("jimjunker1/junkR")
   # remotes::install_github("jimjunker1/junkR")
+  devtools::install_github("rmcelreath/rethinking")
   library(junkR)
   conflict_prefer('count', 'dplyr')
   conflict_prefer('mutate', 'dplyr')

### 2022-09-27 doc/ms/Junker_temp-energy-flux_ms.Rmd
ms draft full with round of comments

--- 2022-07-20 doc/ms/ms.Rmd
@@
 ---
-title: "Warming non-randomly speeds up food web fluxes in both an absolute and relative sense"
+title: "Environmental warming increases the absolute and relative importance of high-turnover energy channels in stream food webs"
 author:
@@
     institute: usu
-  - name: Jon S. Olafsson
+  - name: Jón S. Ólafsson
     institute: veidi
-  - name: Gisli M. Gislason
+  - name: Gísli M. Gíslason
     institute: reyk
 institute:
-  - msu: Department of Ecology, Montana State University, Bozeman, MT USA
-  - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
+  - msu: Department of Ecology, Montana State University, Bozeman, MT 59717, USA
+  - glrc: Current `address:` Great Lakes Research Center, Michigan Technological University, Houghton, MI 49931, USA
   - osu: Department of Evolution, Ecology, and Organismal Biology, The Ohio State University, Translational Data Analytics Institute, The Aquatic Ecology Laboratory, Columbus, OH 43212, USA
@@
 <!--- this is a note in Rmarkdown --->
-
 # Abstract
@@
 Warming temperatures are altering communities and trophic networks globally.
-While the influence of warming in food webs is often context-dependent, increasing temperatures are predicted to alter food webs and ecosystems in a number of general and fundamental ways, among them, 1) decreasing organism body size and 2) increasing metabolic rates.
+While the influence of warming on food webs is often context-dependent, increasing temperatures are predicted to influence communities in two fundamental ways: 1) by reducing average body size and 2) by increasing individual metabolic rates.
 Both body size and metabolic rate are important drivers of many ecological patterns.
-Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food webs fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly.
+Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food web fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly.
 Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient.
 We then related patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
-We predicted 1) fluxes would skew towards smaller *M* and higher *P:B* both across and within ecosystems and 2) fluxes would be more skewed at higher temperatures.
+We predicted 1) warmer communities would skew towards smaller *M* and higher *P:B* across ecosystems, 2) organic matter fluxes within communities would increasingly skew towards smaller, higher *P:B* populations at higher temperatures.
 Across the temperature gradient, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
 Additionally, material fluxes of warmer streams were increasingly skewed towards high-turnover populations *within* the community, showing higher temperatures restructured organic matter fluxes in both an absolute and relative sense.
-Lastly, in warmer ecosystems the relative distribution of organic matter fluxes appears to be increasingly 'non-random', evidence of potentially stronger selection for these traits with increasing temperature.
+With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the potential for stronger selection for these traits with increasing temperature.
 The emerging picture is a warmer world that is both smaller and faster.
-Our study lends further support to this pattern and suggests that temperature will become an increasingly important environmental filter on warming communities in the future.
-\newpage
+Our study provides clear empirical support for this pattern in natural communities and suggests that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
 
@@
 <!--- Speeding up of food web: Species levels--->
-Increasing global temperatures are altering the provisioning and maintenance of ecosystem services by modifying the network of interactions among species that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
-Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and fluxes among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019a].
-Temperature's effects permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, as an environmental niche filter of community assembly and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
+Increasing global temperatures can influence the provision and maintenance of ecosystem services by modifying the network of species interactions that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
+The effects of warming permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
+Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and the magnitudes and relative distribution of energy fluxes among species and trophic levels [@may1972; @mccann1998; @barnes2018].
+
+Understanding how warming alters energy fluxes in food webs requires information about how temperature modifies connections between ecosystem structure (i.e.
+biodiversity) and function (BEF).
+The extent to which temperature modifies the relative importance of community assembly processes will mediate changes to ecosystem structure and function with warming within and among ecosystems.
+These processes are varied--from strictly deterministic [\ e.g., environmental/niche filtering, @whittaker1962],  to strictly stochastic [\ e.g., neutral theory, @hubbell2001]--and they operate across multiple scales.
+As such, there are a multitude of possible relationships between warming and species' abundance and trait distributions.
+For example, strong environmental filtering can be expected to mediate the number of species in a community and is likely to skew trait distributions, to some extent, in natural communities [@therriault1999].
+However, the relative distribution of traits can be modified by a number of additional processes beyond environmental filtering that alter species relative abundance distributions [\ e.g., species interactions @therriault1999 and demographic stochasticity @hubbell2001].
+These additional processes can exaggerate or counter any skew in trait distribution imparted through environmental filtering and may therefore be important for understanding the warming response in species and communities and the absolute and relative distribution of organic matter fluxes across gradients in species traits.
+
+Although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e.
+evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
+The implications of these changes on the magnitude and pathways of energy flux in food webs should depend on how warming influences functional trait distributions, as well as how these functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
 
 <!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
-In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @gardner2011; @daufresne2009].
+Body size is a fundamental trait that is strongly influenced by temperature and has great potential to influence energy flux [@atkinson1994; @gardner2011; @daufresne2009].
 Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or through reduced body size of warmer individuals [@atkinson1994].
 Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history patterns [@zeuss2017; @altermatt2010; @nelson2020b], and developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
+These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history patterns [@zeuss2017; @altermatt2010; @nelson2020b], and developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
 
 <!--- Write the main goals of the paragraph--->
-Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by temperature [@gillooly2001].
-Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
-The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
-Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
-As such, the emerging picture suggests a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates.*possibly simplify the paragraph and combined with above*
+Metabolic rate, in addition to being controlled by body size, is a second key trait that is influence by temperature and tied to variation in energy flux through food webs [@gillooly2001; ].
+Warming can influence metabolic indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
+These processes has been shown to modify ecosystem patterns through changes in population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
+Importantly, the kinetic effects of temperature are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
+Taken together, these changes suggest a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates, with potentially lasting imprints on food web structure and energy fluxes [@gibert2019a].
 
-Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs [@woodward2010; @walther2002].
-For example, species interactions in food webs may modulate species' TSRs [@delong2014], leading to varied responses among species and trophic levels [@ohlberger2013].
-Additionally, warming-induced body size reductions may act as a stabilizing process in some consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011; @greyson-gaito2022].
-Therefore, food web processes may impart varying selective pressures on the distribution of body sizes and population turnover within communities.
-If strong, these pressures may leave distinct imprints on community structure and the distribution of energy fluxes within food webs with potential implications for the stability and functioning of ecosystems on a warming planet [@petchey1999; @fussmann2014].
-
-Here, we measured the patterning and distribution of energy fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
-Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
-[@ogorman2012; @hood2018].
+Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
+Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally [@ogorman2012; @hood2018].
 Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
-As such, we predicted annual energy fluxes of consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams.
-We hypothesized temperature to be a strong environmental filter of community assembly and the distribution of energy and organic matter fluxes, especially at the extremes.
-From this we made a number of predictions regarding the patterning of energy fluxes within and across communities of different temperature, with particular focus on two species traits: body size and population biomass turnover (production:biomass ratios, *P:B*).
+As such, we predicted annual organic matter fluxes to consumers would increase with temperature across streams mirroring among-stream patterns in resource availability and consumer energy demand.
+We hypothesized temperature to be a strong environmental filter of community assembly and the distribution of energy and organic matter fluxes.
+From this we made a number of predictions regarding the patterning of organic matter fluxes within and across communities of different temperature, with particular focus on two species traits; body size and population biomass turnover (production:biomass ratios, *P:B*).
 First, we predict warmer temperatures should favor smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities.
-Second, within communities energy fluxes should be dominated by smaller, higher turnover species at warmer temperatures.
-Third, we hypothesized that the selective pressure from environmental temperature on body sizes and population turnover would be greatest at temperature extremes, therefore, the patterning of energy fluxes will be 'non-random' at coldest and warmest temperatures.
+Second, within communities organic matter fluxes should be increasingly dominated by smaller, higher turnover species at warmer temperatures.
+Lastly, we quantify the probability that patterns of organic matter fluxes among populations arise from chance versus the potential for temperature to structure the relative distribution of material fluxes along species trait axes.
 
@@
 lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke1999; @ogorman2012; @hannesdottir2013]. Growth rates (*g*, d^-1^) were
-calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:
+calculated by the changes in mean body size (*M*) over a given time interval (*t*) with the following equation:
 
-$$g = log_e ( W_{t+\Delta t} / W_t) / \Delta t$$
+$$g = log_e ( M_{t+\Delta t} / M_t) / \Delta t$$
 
@@
 above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
-replacement and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
+replacement and growth rates estimated from equation 1.
+We prevented the calculation of negative growth rates by requiring $M_{t + \Delta t}$ \> $M_t$.
+If this condition was not met after 1e^4^ resamplings, a minimum growth rate of 0.001 was set.
+To estimate
 growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
@@
 
-## Diet analysis
-
-Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
-high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
-shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
-= 3--5) to ensure samples contained enough material for quantification.
-We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification.
-Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds.
-Gut content slurries were filtered
-onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
-microscope slide, cleared with Type B immersion oil, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
-particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
-using image analysis software [@schindelin2012]. We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
-plants (e.g., bryophytes), and animal material and then calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
-contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.
-
-To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
-hierarchical multivariate model [@fordyce2011; @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
-$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
-a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
-We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
-$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the assumed concentration value.
-Models were fit in Stan with the 'brms' package in R [@burkner2017].
-For non-dominant taxa, diet proportions were imputed
-from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.
-
-From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities (*PS*; @whittaker1952 among modeled diet estimates.
-Proportional similarities were calculated as:
-
-$$ PS = 1 - 0.5 \sum_{j=1}^S|p_{x,i} - p_{y,i}|$$
-
-where, *p~x,i~* is the proportion of food resource *i* in the diet of taxon *x*, *p~y,i~* is the proportion of food resource *i* in the diet of taxon *y*, and there are *S* food categories.
-Proportional similarity was calculated across all taxa within a stream based on modeled diet contributions from each taxon.
-To calculate *PS* among streams we sampled 1000 estimates of the mean stream-level diet proportions for each stream and calculated *PS* for each.
-
 ## Organic Matter Consumption Estimates
 
-Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method [TBP, @benke1980]. Taxon-specific secondary production estimates were combined with
-diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
+Organic matter fluxes through the community (g m^-2^ t^-1^) were calculated using the trophic basis of production method [TBP, @benke1980].
+Taxon-specific secondary production estimates were combined with
+diet proportions (see Supplemental Materials), diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter.
+For each food
 category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
@@
 a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
-the TBP method using modeled diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
+the TBP method using modeled diet proportions (see *Diet analysis* in Supplemental Materials), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
 incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
@@
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on rank ordered OM fluxes, such that in a community with $S$ species and the relative OM flux of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
 p_S$.
 The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
-In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is simply a straight diagonal line.
+In a community with perfectly equal distribution of OM flux among species, the Lorenz curve is simply a straight diagonal line.
 Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]:
@@
 We predicted that warming would favor species with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
-Across communities, we assessed the relationships between mean annual temperature ($^\circ$C) and mean population *M* and *P:B* of each community with bootstrapped linear regressions.
+To assess the potential effects of environmental filtered across communities, we explored the relationships between mean annual temperature ($^\circ$C) and mean population *M* and *P:B* of each community with bootstrapped linear regressions.
 Here, `r temperature_stats[['n_boot']]` values of population *M* or *P:B* were resampled with replacement for each species within each stream.
@@
 
-To quantify the distribution of energy fluxes _**within**_ a community, we assessed if relative OM flux was skewed towards populations with lower or higher relative *M* or  *P:B*.
-To do this, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
+To quantify how the distribution of organic matter fluxes were modified _**within**_ a community and how this modification was related to temperature, we assessed the extent to which the relative OM fluxes among consumers within a community were skewed towards populations with lower or higher relative *M* or *P:B*.
+To do this, we ordered species based on within-stream ranking of annual population traits (i.e., $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
 
@@
 
-To assess the strength of environmental filtering of species' traits within a community, we quantified how likely it was to observe such a skewed distribution in OM fluxes by random chance.
-Here, we predicted that communities with strong filtering for traits would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
-In contrast, weak environmental filtering would produce OM fluxes with skew values that are likely due to random chance ('random ordering').
+To assess how temperature may structure the skew of OM among populations within a community, we quantified how likely it was to observe such a skewed distribution in OM fluxes by random chance.
+Skewness in OM fluxes may arise through both ecological and random processes.
+Further, the feasible range of skewness values a community can take is inherently tied to the evenness of OM fluxes within a community.
+This dependence on evenness can make it difficult to determine the importance of random versus ecological processes on the distribution of OM fluxes in the community through comparison of raw skewness measures alone.
+Here, we predicted that species' $M$ and $P:B$ would be increasingly important traits structuring OM fluxes within a community and therefore warmer streams would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
+In contrast, cooler streams would exhibit OM fluxes with skew values that are more likely due to random chance ('random ordering'), regardless of raw skewnness values, suggesting other traits govern the distribution of OM fluxes within communities.
 To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
@@
 This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative OM flux.
-To assess the relationship between the probability of 'non-random ordering' and temperature, we again used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
-Here, values can take the range between 0 and 1 so no transformation was necessary.
-As necessary, when we observed many values near 0 and 1, we implemented a zero-one inflated beta regressions in brms [@burkner2017] to test if the probability of observing the empirical $Sk_{flux}$ was associated with mean annual temperature across streams.
-We predicted increasingly 'non-random' distributions in OM fluxes with increasing temperature.
 
@@
 
-## Community OM fluxes
+## Community organic matter fluxes
 
-Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].
-Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`; `r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)` to `r round((max_demand$flux_mg_m_y_mean/1000),1)`; `r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)` g AFDM $m^{-2} y^{-1}$ mean; 95% percentile interval (PI)) and was positively related to temperature.
-Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` (`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`, 95% PI) to `r round((max_flux$flux_mg_m_y_mean/1000),1)` (`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`, 95% PI) g AFDM $m^{-2} y^{-1}$.
+Annual community OM fluxes mirrored patterns of secondary production reported previously [@junker2020].
+Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams (mean [95% percentile interval (PI)]: `r round((min_flux$flux_mg_m_y_mean/1000), 1)`[`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
 
@@
 
-Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Supporting Materials, Figure S1).
-Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%;`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)` 95% PI).
-Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`) among all consumer taxa.
-Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI).
-Diet similarity of pairwise comparisons among streams showed little differences in diet among streams and no clear relationship with temperature.
+Differences in OM flux among streams driven by variation in total energy deman rather than composition of consumed resources, as consumer diets were highly similar among streams (Figure S1).
+Diets were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI).
+Within streams, diet overlap ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)*100`% (`r round(min_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)*100`%) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)`% (`r round(max_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)*100`%) among invertebrate taxa.
+Among streams, diet overlap was similarly high with a mean overlap of `r round(among_overlap_mean,2)*100`% (`r round(among_overlap_quant2.5,2)*100` -- `r round(among_overlap_quant97.5,2)*100`%; 95% PI).
+Diet similarities based on pairwise comparisons among streams showed little difference and no clear relationship with temperature.
 
@@
 
-## Evenness of OM fluxes within streams
+## Evenness of organic matter fluxes
 
-Generally, organic matter fluxes were dominated by insect species from Simuliidae and Chironomidae families (Figure 1a) and were distributed unevenly (Figure 1b; Figure S1).
-In an absolute sense, ~85% of total flux was contributed by between `r n_dom_min$n_dom` and `r n_dom_max$n_dom` consumer groups.
-Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the consumer assemblage within streams.
-Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumer groups.
-Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1).
-In warmer streams, OM fluxes shifted toward the black fly, *Simuliium vittatum* and the pulmonate snail, *Radix balthica*.
-In the warmest stream, where maximum temperatures approach ~40$^\circ$C, species richness was lowest and OM fluxes were dominated by oligochaete worms of family Naididae, the chironomid *Cricotpous sylvestris*, and *Radix balthica*.
-Yet, even after accounting for differences in consumer richness, patterns of material flux were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table 1).
-Differences in evenness and dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.
+In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table S1] and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
+In an absolute sense, and ~85% of total OM flux was contributed by `r n_dom_min$n_dom` and `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness.
+Although differences in evenness among streams were partially attributed to variation in taxon richness (range: `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max`), fluxes wre still highly uneve after accounting for differences in richness (i.e., similar 'Normalized' Gini coefficients, Table S1).
+As average stream temperature increased, OM fluxes shifted from dominance by Simuliidae in the coolest stream to Chironomidae and *R.
+balthica* at moderate temperatures.
+In the warmest stream, where maximum temperatures approach ~40$^\circ$C, taxon richness was lowest and OM fluxes were dominated by oligochaete worms in the family Naididae, the chironomid *Cricotpous sylvestris*, and *R.
+balthica*.
+Among stream differences in evenness and dominance of OM fluxes were not related to temperature ().
 
-```{r figure 1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=6, dpi = 450, fig.cap="Figure 1.
-Patterns of OM flux among populations based on (a) relative OM flux among taxonomic groups in consumer communities and descending the temperature gradient from the warmest (27.2$^\\circ$C) on top pane to coldest (5.0$^\\circ$C) on the botthom.
-(b) The rank ordering of annual population organic matter flux log~e~(mg m^-2^ y^-1^) of consumer groups.
-In (a), consumer groups fill is based on taxonomic family and the full key of consumer group abbreviations can be found in supporting materials."}
-
-drake::loadd(annual_spp_flux_fig)
-drake::loadd(spp_flux_dist)
-gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
-```
+<!-- \newpage -->
 
@@
 
+drake::loadd(gini_analysis)
 ```
 
-```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
-drake::loadd(gini_analysis)
-tab1_caption = "Table 1.
-Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
-gini_analysis[["stream_gini_summary"]] %>% 
-   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
-   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
-                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
-   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
-   knitr::kable(align = "lrr", caption = tab1_caption)
+```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1.
+(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with increasing mean annual temperature.
+Warming stream temperatures also led to (B) a decrease in mean population body size (*M*, mg ind^1^) and (C) an increase in mean population biomass turnover rate (*P:B*, y^-1^)."}
+
+drake::loadd(spp_traitsVtemp)
+grid.draw(spp_traitsVtemp[['fig1_plot']])
+
+ # drake::loadd(spp_trait_histograms)
+# grid.draw(spp_trait_histograms)
 
@@
 
-## OM fluxes along species trait distributions among sites and taxa
+## Organic matter fluxes in relation to body size and biomass turnover rate
 
@@
 
-Across communities, average population body size, *M*, decreased and average biomass turnover, *P:B*, increased with increasing temperature (Figure 2).
-Mean population *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
-This decrease corresponded to a `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)` (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) percent decrease in mean population body size (mg ind^-1^) for every increase of 1$^\circ$C.
-In contrast, the average population *P:B* increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)` 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)` 95% PI) in the warmest stream.
-This increase corresponded to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)` 95% PI) increase in mean population biomass turnover (P:B y^-1^) for every increase of 1$^\circ$C (Figure 2).
+Across stream communities, average population body size (*M* [mg AFDM ind^-1^]) decreased and average population biomass turnover rate (*P:B* [y^-1^]), increased with increasing temperature (Figure 1B, C).
+Average *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)`0 mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the warmest stream, corresponding to an `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)` -- `r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`; 95% PI) decrease in mean body size for every 1$^\circ$C increase in temperature (Figure 1B).
+Average population *P:B* ratio increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the warmest stream corresponding to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)`; 95% PI) increase in *P:B* ratio for every 1$^\circ$C increase (Figure 1C).
 
-```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=5, dpi = 450, fig.cap="Figure 2.
-The relationships between mean annual stream temperature and (a) average population body size of the community (mg^-ind^) and (b) average population turnover expressed as production to biomass ratios (*P:B*, y^-1^)."}
+```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
+(A) Relative contribution (log_10_%) of different taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank ordered organic matter flux (log_e_(mg AFDM m^-2^ y^-1^) by taxon.
+See supporting materials for the full key of taxonomic abbreviations."}
 
-drake::loadd(spp_traitsVtemp)
-grid.draw(spp_traitsVtemp[['fig1_plot']])
-
- # drake::loadd(spp_trait_histograms)
-# grid.draw(spp_trait_histograms)
-
+drake::loadd(annual_spp_flux_fig)
+drake::loadd(spp_flux_dist)
+gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
 ```
 
-Organic matter fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size among streams.
-Skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(M_mg_ind_skew_mean) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_mean) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2).
-Similarly, skew in fluxes towards high *P:B* taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_mean) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_mean) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).
-The skew of OM fluxes towards populations with smaller/larger body sizes showed no systematic association with stream temperature (Figure 4a).
-Similarly, OM fluxes through the community skewed increasingly toward higher turnover (*P:B*) organisms with increasing temperature.
-The median increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5`--`r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4c).
+Within stream communities, OM fluxes skewed towards taxa with larger body sizes (positive skew), smaller body sizes (negative skew), and neutrally with respect to body size (Figure 3A).
+Skew estimates with body size (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_median) %>% select(M_mg_ind_skew_median)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_median) %>% select(M_mg_ind_skew_median) %>% round(2)`; Figure 3B).
+Skew estimates of OM fluxes in relation to body size showed little association with stream temperature except in the warmest stream, where fluxes were heavily skewed toward small-bodied taxa.
+Similarly, skew in OM fluxes in relations to *P:B* ratios varied among streams, ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_median) %>% select(pb_y_skew_median) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_median) %>% select(pb_y_skew_median) %>% round(2)`.
+In this case, OM fluxes to consumers skewed increasingly toward higher turnover (*P:B*) taxa with increasing temperature (Figure 4A, B).
 
-```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=4.0, fig.height=7, dpi = 450, fig.cap="Figure 3.
-Lorenz curves of cumulative relative organic matter flux with increasing cumulative species.
-Species are ranked along trait axis of (a) mean body size (mg ind^-1^) and (b) population turnover (production:biomass ratio, *P:B*, y^-1^), such that x~1~ < x~2~ < x~i~ <...x~S~, where x is the trait value of species *i*."}
+```{r M lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
+The solid line 1:1 line from the origin represents the line of perfect equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
+(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e.
+s) ordering."}
 
-drake::loadd(lorenz_trait_fig)
-grid.draw(lorenz_trait_fig[["lorenz_pbM_plot"]])
+drake::loadd(M_lorenz_skew_fig)
+grid.draw(M_lorenz_skew_fig)
 
@@
 
-We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs.
-non-random structure in community OM fluxes.
-The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)` 95% PI; Figure 4b).
-Similarly, the probability of a more extremely skewed distribution in relation to population *P:B* ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)` 95% PI; Figure 4d).
-The probability that OM fluxes were organized randomly or non-randomly in regards to body size showed a `r round(m_prob_temp_median, 3)*100`% (`r round(m_prob_temp_quant2.5,3)*100`% -- `r round(m_prob_temp_quant97.5,3)*100`% 95% PI) change with 1$^\circ$C change in temperature (Figure 4b).
-Further, there was a trend towards a more structured OM flux distribution with regard to population *P:B* at higher temperatures.
-The probability of observing such skewed OM fluxes randomly became less likely with temperatures, such that the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`% 95% PI) for every 1$^\circ$C increase (Figure 4d).
+We compared our empirical skew estimates (i.e., $Sk_{flux}$) absed on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa were based on random selection (i.e., stochastic) or were truly based on these traits.
+The probability of observing a similar or more extreme skew of OM fluxes in relation to body size was variable among streams and ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI); there was a very weak positive association between this probability and temperature (Figure 3C).
+In contrast, the probability of a similarly or more extreme skew in relation to *P:B* ratios ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI, Figure 4C) and in this case there was a clear trend towards a more structured OM flux distribution--i.e., favoring fluxes through high *P:B* taxa--at warmer temperatures.
+The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`%; 95% PI) for every 1$^\circ$C increase in temperature (Figure 4C).
 
-```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.cap="Figure 4.
-The empirical skew of organic matter fluxes in relation to (a) body size and (c) *P:B*.
-The probability of observing a Sk~flux~ value more extreme by random chance increased slightly with increasing temperature for body size (b).
-The pattern was stronger for population *P:B* (d)." }
-drake::loadd(temperature_skew_fig)
- grid.draw(temperature_skew_fig)
+```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
+The solid line 1:1 line from the origin represents the line of perfect equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
+(B) Empirical estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e.
+stochastic) ordering." }
+
+drake::loadd(PB_lorenz_skew_fig)
+grid.draw(PB_lorenz_skew_fig)
 ```
@@
 Here, we document shifts in the pathways of material flow across a wide natural temperature gradient and show that increasing temperatures were associated with reductions in mean population body size and increases in mean population *P:B* across stream consumer communities.
-Further, increasing temperature also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards smaller, quick turnover populations at warmer temperatures.
-Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at moderate to warm temperatures and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of warm communities.
-This tendency for energy fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests the speeding up of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of increasing temperature.
+Further, increasing temperature also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards  quick turnover populations at warmer temperatures.
+Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at moderate to warm temperatures and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of warm communities--governing both the traits of species present and the relative distribution of energy and materials fluxes among species.
+This tendency for fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests the speeding up of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of increasing temperature.
 
-Reductions in organism body size with warming has been deemed a "universal" response to warming [@daufresnes2009; @gardner2011; @uszko2022].
-We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 2), corresponding to ~9% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
+Reductions in organism body size with warming has been deemed a "universal" response to warming [@daufresne2009; @gardner2011; @uszko2022].
+We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 1B), corresponding to ~`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
 While this change represents a community-level shift, the magnitude of change is consistent with recent work on the effects of warming on organism body size across broad taxonomic groups [@deutsch2022].
@@
 Our results also counter observational studies in this system that have shown no consistent change in body size within diatom communities at either the population- or community-scale [@adams2013].
-These contrasting results are consistent with deviations from the "universal" response observed across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; fish @rypel2014].
+These contrasting results are consistent with deviations from the "universal" response observed across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; @riemer2018; fish @rypel2014].
 Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns [\ i.e., voltinism, @zeuss2017; @nelson2020b; lifespan, @munch2009].
 Considering the connections between organism body size and many other ecological attributes [@peters1983], reductions in body size with increasing temperatures could have broad implications for ecosystem dynamics with a changing climate [@gibert2019a].
 
-Warmer ecosystems exhibited higher rates of energy flux in both an absolute and relative sense.
-At the community level, we observed a ~7% increase in the mean biomass turnover rate (P:B; y^-1^).
+Warmer ecosystems exhibited higher rates of material flux in both an absolute and relative sense.
+At the community level, we observed a ~`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% increase in the mean biomass turnover rate (*P:B*; y^-1^).
 Temperature has long been recognized as an important driver of ecological rates [@gillooly2001] and the increase in biomass turnover among communities is likely attributed to the thermodynamic effect of temperature--in part.
 Biomass turnover rate is also tightly tied to organism body size [@brown2004; @huryn2007] suggesting that temperature may influence the distribution of *P:B*s both directly through its effects on metabolic rates and indirectly by inducing reductions in organism body size.
-The influence of this interaction between the direct and indirect effect of temperature on metabolic activities in increasingly recognized.
-For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concomitant changes to organism body size are taken into account [@bernhardt2018].
-Further, reduce body sizes stabilize systems by reducing C:R ratios at higher temperatures [@gilbert; @sentis2017; @bideault2019]
+The increase in *P:B* we observed across communities was a similar relative magnitude as the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`%, respectively), providing equivocal evidence of the presence and/or importance of this interaction from this broad view.
+Despite this, the influence of this interaction between the direct and indirect effect of temperature on ecological patterns in increasingly recognized.
+For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concurrent changes to organism body size are taken into account [@bernhardt2018].
+Further, there is growing evidence that the interactive effects warming-induced changes to metabolic rates and body size distributions have important implications for the structure and functioning of food webs at higher temperatures [@sentis2017; @bideault2019; @gibert2019a] and may reflect shifting selection for species traits.
 
-*Lastly, want to layer in the concepts of niche filtering and neutral processes in community assembly.
-Pull a little thinking from @saito2021.
-This leads into the random vs non-random patterning questions.
-*
+Temperature was also an important modifier of the relative performance of species and distribution of OM fluxes *within* communities.
+In addition to the observed decrease in mean body size and increase in biomass turnover rates across communities, species' OM fluxes exhibited non-random patterning along species' trait axes.
+Regarding body size, the pattern was equivocal.
+In the coldest and warmest streams, we saw a strong skew in material fluxes towards larger and smaller species, respectively.
+However, at more moderate temperatures (~6--17$^\circ$C), this pattern was not apparent.
+On the other hand, we observed a clearer relationship between the skewness of OM fluxes in relation to biomass turnover with increasing temperatures.
+Fluxes became more skewed and less random in relation to population *P:B* at warmer temperatures (Figure 4B & C).
+The seemingly weak within community patterns with body size and much clearer patterns with *P:B* present a potentially interesting insight into the more proximate processes by which temperature alters ecosystem structure and function.
+For example, despite the general trend of reduced body sizes at higher temperature [e.g., @daufresne2009; @gardner2011; @uszko2022], there is a lack evidence for persistent evolutionary selection within populations for smaller body sizes with warming [@siepielski2019].
+However, warming-induced body size reductions may act as a stabilizing process in consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
 
-Temperature has long been known to be an important control on ecological process rates [@gillooly2003; @brown2004]
+Therefore, the general response of reduced body size with warming or latitudinal temperature gradients may, in fact, mask the true constraints imparted by food web dynamics because of the correlation between body size and other biological traits (e.g., growth rate, mortality rate, lifespan, biomass turnover rate, etc.).
+In high latitude light-driven systems, such as those here, larger and/or slower populations may destabilize consumer-resource dynamics further through more extreme seasonal autocorrelation of resource growth [@greyson-gaito2022], suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [\ e.g., paradox of enrichment, @mccann2011].
+The importance of this dynamic may be under-appreciated in high-latitude ecosystems especially [@mcmeans2020] where warming is beginning to decouple light regimes and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015] likely driving future changes to biodiversity of these systems.
 
-These maximize energy intake when resources are available [@atkinson1997]
+Temperature was not clearly associated with the broad biodiversity metrics of species richness or evenness/dominance of OM fluxes.
+We observed no clear decrease in species richness with increasing temperature found in other works [@petchey1999] beyond the warmest stream having the fewest species.
+However, variability in the taxonomic resolution among groups precludes a more robust analysis of any richness effects.
+Still, generally OM fluxes were unevenly distributed among consumers.
+Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this carries over into energy and material fluxes.
+Interestingly, however, we found important structure in the unevenness of OM fluxes.
+Organic matter fluxes were increasingly skewed towards high *P:B* populations within warmer streams and this pattern was unlikely related to chance (Figure 4C), suggesting temperature may become an increasingly important environmental filter of community assembly and species relative performance.
+That the relative distribution was of OM fluxes was unlikely due to chance reduces that likelihood this pattern could be attributable to demographic stochasticity of consumers.
+This counters recent hypotheses integrating the metabolic theory of ecology [@brown2004] and neutral theory [@hubbell2001] that suggest neutral processes should be more important at higher temperatures [@saito2021].
+The extent to which the patterns we observe here--i.e., the apparent increased importance of environmental/niche filtering at higher temperature--represent general patterns or results from the specific context of this "natural laboratory" [@ogorman2014] remains an open question.
 
-- Seasonal systems have unique constraints
-- These seasonal constraints are greater at higher temps
-
-This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017],
-2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
-
-For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
-Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
-and community structure across ecosystems...
-
-[@diaz2021a] SAD are more uneven than their statistical background
+Here, we documented the important structuring role of temperature in community assembly and the relative distribution of material fluxes across and within streams of a natural temperature gradient.
+Higher temperatures were associated with increased total flux through the food web as well as reductions in average population body size and increases in population biomass turnover.
+Further, biomass turnover rate was an increasingly important structuring trait at warmer temperatures, more so than organism body size.
+Yet, our results give support that warming may reduce organism size and also 'speed up' ecosystem dynamics in both an absolute and relative sense.
+These changes have important implications for the maintenance of biodiversity as well as for the connections between biodiversity and the magnitude and stability of energy and material cycling in ecosystems in a warming world.
 
@@
 
+\newpage
+
 # Appendix
 
-Spare(d) words
+## Appendix 1
 
-Recent, models have proposed  However, 
-- both bottom-up (e.g. resource supply) and top-down (e.g., predation) proceesses
-- competition and predation [@delong2014], stabilize c-r dynamics [@osmond2017], optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a]
--
+### Diet analysis
 
-*Lastly, want to layer in the concepts of niche filtering and neutral processes in community assembly.
-Pull a little thinking from @saito2021.
-This leads into the random vs non-random patterning questions.
-*
+Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
+high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
+shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
+= 3--5) to ensure samples contained enough material for quantification.
+We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification.
+Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds.
+Gut content slurries were filtered onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a microscope slide, cleared with Type B immersion oil, and covered with a cover slip.
+We took 5--10 random photographs under 200--400x magnification, depending on the density of particles, using a digital camera mounted on a compound microscope.
+From these photographs we identified all particles within each field and measured the relative area of particles using image analysis software [@schindelin2012].
+We classified particles into six categories: diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular plants (e.g., bryophytes), and animal material and then calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles.
+Gut contents of many predators were empty or contained unidentifiable, macerated prey.
+For these taxa, we assumed 100% animal material.
 
-These maximize energy intake when resources are available [@atkinson1997]
+To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a hierarchical multivariate model [@fordyce2011; @coblentz2017].
+Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
+$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
+a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
+We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
+$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the assumed concentration value.
+Models were fit in Stan with the 'brms' package in R [@burkner2017].
+For non-dominant taxa, diet proportions were imputed
+from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.
 
-- Seasonal systems have unique constraints
-- These seasonal constraints are greater at higher temps
+From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [\ *PS*, @whittaker1952] among modeled diet estimates.
+Proportional similarities were calculated as:
 
-This creates a situation where body sizes are selected for that 1) ,
-2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
+$$ PS = 1 - 0.5 \sum_{j=1}^S|p_{x,i} - p_{y,i}|$$
 
-Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).
-Both among and within streams, OM fluxes were distributed differently across body sizes and turnover rates (*P:B*).
-Among streams, mean population body size ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean population annual  P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
-Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
-In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
+where, *p~x,i~* is the proportion of food resource *i* in the diet of taxon *x*, *p~y,i~* is the proportion of food resource *i* in the diet of taxon *y*, and there are *S* food categories.
+Proportional similarity was calculated across all taxa within a stream based on modeled diet contributions from each taxon.
+To calculate *PS* among streams we sampled 1000 estimates of the mean stream-level diet proportions for each stream and calculated *PS* for each.
 
@@
 
-```{r raw lorenz, echo=FALSE, message=FALSE, warning = FALSE, dpi = 400, fig.cap="Figure S2.
-Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (mg AFDM m^-2^ y^-1^)"}
-lorenz_trait_fig[["lorenz_flux_plot"]]
+\newpage
+
+## Appendix 2
+
+```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
+tab1_caption = "Table 1.
+Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
+gini_analysis[["stream_gini_summary"]] %>% 
+   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
+   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
+                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
+   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
+   knitr::kable(align = "lrr", caption = tab1_caption)
 
@@
 
-```{r biomass lorenze, echo=FALSE, message=FALSE, warning=FALSE, dpi = 400, fig.cap="Figure S3.
-Cumulative plot of relative community flux by species in relation to mean annual population biomass (mg m^-2^)."}
-lorenz_trait_fig[["bio_lorenz_flux_plot"]]
+```{r raw lorenz, echo=FALSE, message=FALSE, warning = FALSE, dpi = 400, fig.cap="Figure S2.
+Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (mg AFDM m^-2^ y^-1^)"}
+drake::loadd(lorenz_skew_fig)
+lorenz_skew_fig[["lorenz_flux_plot"]]
 
@@
 
-```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure S4. Probability distribution of empirical Sk~flux~ measurements compared to random species ordering."}
+```{r biomass lorenz, echo=FALSE, message=FALSE, warning=FALSE, dpi = 400, fig.cap="Figure S3.
+Cumulative plot of relative community flux by species in relation to mean annual population biomass (mg m^-2^)."}
+lorenz_skew_fig[["bio_lorenz_flux_plot"]]
+
+```
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure S4.
+Probability distribution of empirical Sk~flux~ measurements in relation to (a) mean body size and (b) annual P:B compared to random species ordering.
+The red lines represent the 2.5% and 97.5% percentiles of the Sk~flux~ values from random ordering distributions in each stream community."}
 drake::loadd(random_skew_fig)
@@
 ```
+
+\newpage
+
+### Construction zone
+
+Possible other themes to layer in:
+
+effects of temperature on species evenness, evenness of fluxes, and the statistical and ecological constraints on the organization of energy fluxes in communities (e.g., [@diaz2021a] SAD are more uneven than their statistical background and energy fluxes are also but there is important structure in this unevenness).
+This relates to the random vs non-random patterning questions...pull in the concepts of niche filtering and neutral processes in community assembly.
+Pull a little thinking from @saito2021.
+
+Below is more of a set-up for the next paper but a little foreshadowing and hand waving may find a place in here:
+
+These maximize energy intake when resources are available [@atkinson1997]
+
+- Seasonal systems have unique constraints
+- These seasonal constraints are greater at higher temps
+
+This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017], ecological stability response to warming [@fussmann2014],...
+2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
+
+### Spare(d) words from previous versions. Keeping around for now.
+
+directly kinetic effects and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
+
+environmental filtering of compared the observed distributions of material fluxes among consumer populations to random distributions to quantify the likelihood the patterning of organic matter fluxes arise through random ordering of species or  measure the potential strength of environmental filtering on the relative distribution of organic matter   we tested the potential strength of environmental filtering to determine the distribution of within stream energy fluxes by comparing the  how likely it was  Third, we hypothesized that the selective pressure from environmental temperature on body sizes and population turnover would be greatest at temperature extremes, therefore, the patterning of energy fluxes will be 'non-random' at coldest and warmest temperatures.
+
+Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs [@woodward2010; @walther2002].
+For example, species interactions in food webs may modulate species' TSRs [@delong2014], leading to varied responses among species and trophic levels [@ohlberger2013].
+Additionally, warming-induced body size reductions may act as a stabilizing process in some consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011; @greyson-gaito2022].
+
+For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
+Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
+and community structure across ecosystems...
+
+Recent, models have proposed  However, 
+- both bottom-up (e.g. resource supply) and top-down (e.g., predation) proceesses
+- competition and predation [@delong2014], stabilize c-r dynamics [@osmond2017], optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a]
+
+To assess the relationship between the probability of 'non-random ordering' and temperature, we used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
+Here, values can take the range between 0 and 1 so no transformation was necessary.
+As necessary when we observed many values near 0 and 1, we implemented a zero-one inflated beta regressions in brms [@burkner2017] to test if the probability of observing the empirical $Sk_{flux}$ was associated with mean annual temperature across streams.
+We predicted increasingly 'non-random' distributions in OM fluxes with increasing temperature.
+
+Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).
+Both among and within streams, OM fluxes were distributed differently across body sizes and turnover rates (*P:B*).
+Among streams, mean population body size ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean population annual  P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
+Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
+In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.

### 2022-09-27 R/plot_random_skew.R

@@ -44,22 +44,29 @@ plot_random_skew <- function(skew_analysis, random_rankings) {
 #   scale_color_manual(values = rev(ocecolors[["temperature"]][oce_temp_pos]), labels = rev(stream_temp_labels))+
 #   facet_grid(~measure)
   
+  pb_labs = data.frame(site = stream_order,
+                       labs = c("B",rep(NA_character_,5)))
+  
 skew_analysis[['pb_skew_percs']] %>% bind_rows(.id = 'site') %>%
     pivot_longer(-site, names_to = "boot_id", values_to = "skew_perc") %>%
     dplyr::select(-boot_id) %>%
     dplyr::mutate(site = factor(site, levels =names(stream_order_list))) %>%
-    ggplot(aes(x = skew_perc)) +
+    ggplot(aes(x = skew_perc )) +
     geom_vline(xintercept = c(0.1,0.9), color = 'red', size = 1, alpha = 0.7)+
-    geom_histogram(aes( fill = site, y = ..count..), color = NA, alpha = 0.8, bins = 50)+
+    geom_histogram(aes(fill = site, y = ..count..), color = NA, alpha = 0.8, bins = 50)+
     scale_x_continuous(name = "Percentile of permuted set", limits = c(-0.01,1.01), expand = c(0.01,0.01))+
     scale_y_continuous(name = "# of observations", expand = c(0.001,0.001))+
     scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
     scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
+  geom_text(data = pb_labs, aes(x = 0, y = Inf, vjust = 1, family = 'serif'), label = c("B","","","","",""))+
     theme_tufte(ticks = TRUE) +
     geom_rangeframe(sides = "lb")+
     theme(legend.position = 'none', axis.title = element_blank()) +
-    facet_wrap(~site, ncol = , scales = 'free_y') ->pb_perc_plot
+    facet_wrap(~site, ncol = , scales = 'free_y',labeller = as_labeller(stream_temp_labels)) ->pb_perc_plot
     
+m_labs = data.frame(site = stream_order,
+                    labs = c("A",rep(NA,5)))
+
   skew_analysis[['M_skew_percs']] %>% bind_rows(.id = 'site') %>%
[…]

### 2022-09-27 R/plot_skew_temperaturePB.R

@@ -1,0 +1,156 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param lorenz_analysis
+#' @param spp_rankings_summary
+#' @param temperature_stats
+#' @param n_id
+plot_skew_temperaturePB <- function(lorenz_analysis, spp_rankings_summary,
+                                    temperature_stats, n_id = 2000) {
+
+  pb_label = grid::textGrob(expression("Increasing relative"~italic("P:B")), x = unit(0.5, 'npc'), just = "centre",
+                            gp = gpar(fontfamily = 'serif', fontsize = 8))
+  pb_box = grid::roundrectGrob(x = unit(0.5, 'npc'), y = unit(0.5, 'npc'),
+                               width = unit(0.4, 'npc'), height = unit(0.8, 'npc'),
+                               just = "centre")
+  pb_arrow = segmentsGrob(x0 = unit(0.1,'npc'), x1 = unit(0.9, 'npc'),
+                          y0 = unit(0.5,'npc'), y1 = unit(0.5, 'npc'),
+                          arrow = arrow(type = 'closed'), gp = gpar(fill = 'black', lex = 0.8))
+  pb_header = grid::grobTree(pb_arrow, pb_box, pb_label)
+  
+  lorenz_analysis[["pb_ranking_boots"]] %>%
+    ggplot(aes(x = rel_spp, y = rel_flux)) +
+    geom_abline(color = "black")+
+    geom_abline(intercept = 1, slope = -1, color = "black", linetype = "dotted")+
+    geom_line(aes(group = boot_id), color = "grey", alpha = 0.5) +
+    geom_line(data = spp_rankings_summary[["PB_spp_rank"]], aes(x = rel_spp, y = rel_flux, color = site), size = 1.5) +
+    scale_x_continuous(name = "Cumulative species", limits = c(0,1), expand = c(0,0.03))+
+    scale_y_continuous(name = "Cumulative flux", limits = c(0,1), expand = c(0,0.03))+
+    scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
+    theme_tufte(ticks = TRUE) +
+    geom_rangeframe(sides = "lb")+
+    theme(legend.position = 'none',
+          legend.justification = c("left", "top"), 
+          legend.title = element_blank(),
[…]

### 2022-09-27 R/plot_skew_temperature_old2.R

@@ -1,0 +1,189 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param temperature_stats
+plot_skew_temperature <- function(temperature_stats, n_id = 2e2) {
+  set.seed(123)
+  n_draws = sample(1:6000, n_id, replace = FALSE)
+  
+  m_skew_summ = temperature_stats[["m_skew_df"]] %>%
+    group_by(site) %>%
+    dplyr::summarise(tempC= unique(tempC),
+                     across(c(M_mg_ind_skew), list(mean = ~mean(.x, na.rm = TRUE),
+                                               quant2.5 = ~quantile(.x, 0.05, na.rm = TRUE),
+                                               quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                               HPDI_50up = ~rethinking::HPDI(.x, 0.5)[2],
+                                               HPDI_50dn = ~rethinking::HPDI(.x, 0.5)[1],
+                                               HPDI_90up = ~rethinking::HPDI(.x, 0.89)[2],
+                                               HPDI_90dn = ~rethinking::HPDI(.x, 0.89)[1],
+                                               median = ~median(.x, na.rm = TRUE),
+                                               quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                               quant97.5 = ~quantile(.x, 0.95, na.rm = TRUE)))) %>%
+    dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+  
+  m_temp_skew_plot = ggplotGrob(m_skew_summ %>%
+                                   dplyr::mutate(site = factor(site, levels = names(rev(stream_order_list)))) %>%
+                                   ggplot()+
+                                   geom_errorbar( aes(y = site, xmin = M_mg_ind_skew_HPDI_90dn, xmax = M_mg_ind_skew_HPDI_90up, color = site), size = 1, width = 0)+
+                                   geom_errorbar( aes(y = site, xmin = M_mg_ind_skew_HPDI_50dn, xmax = M_mg_ind_skew_HPDI_50up, color = site), size = 1.5, width = 0)+
+                                   geom_point(aes(y = site, x = M_mg_ind_skew_median), size = 2, color = 'black')+
+                                   scale_x_continuous(name = expression(""*italic(Sk[flux])), limits = c(-1,1), expand = c(0,0.004) ) +
[…]

### 2022-09-27 R/plot_spp_flux.R

@@ -25,7 +25,7 @@ plot_spp_flux <- function(ann_spp_flux =
     ggplot(aes(x = rank, y = log(flux_mg_m_y_mean), group = site))+
     geom_line(aes(color = site), size = 2)+
     geom_point(aes(fill = site), shape = 21, size = 2.3, color = 'black') +
-    scale_y_continuous(name = expression(log[e]~"(Annual flux)[mg"~m^-2~y^-1*"]"),limits = c(-10,NA),
+    scale_y_continuous(name = expression(log[e]~"(Organic matter flux)[mg"~m^-2~y^-1*"]"),limits = c(-10,NA),
                        expand = c(0.03,0))+
     scale_x_continuous(name = 'Species rank')+
     scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+

### 2022-11-04 doc/ms/Junker_temp-energy-flux_ms.Rmd
commit before final kniting of first draft for co-author review

@@
       - '--lua-filter=author-info-blocks.lua'
+      - '--filter=pandoc-crossref.exe'
    pdf_document:
@@
       - '--lua-filter=author-info-blocks.lua'
+      - '--filter=pandoc-crossref.exe'
 header-includes:
@@
 - \usepackage{amsmath}
+- \numberwithin{equation}
 - \usepackage{indentfirst}
@@
 While the influence of warming on food webs is often context-dependent, increasing temperatures are predicted to influence communities in two fundamental ways: 1) by reducing average body size and 2) by increasing individual metabolic rates.
-Both body size and metabolic rate are important drivers of many ecological patterns.
-Therefore, warming-induced changes have the potential to propagate through countless ecosystem processes thereby altering the distribution of food web fluxes, food web stability, and potentially the importance of environmental and biological factors in community assembly.
-Here, we quantify the patterning and relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient.
-We then related patterns in fluxes to species and community traits (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
-We predicted 1) warmer communities would skew towards smaller *M* and higher *P:B* across ecosystems, 2) organic matter fluxes within communities would increasingly skew towards smaller, higher *P:B* populations at higher temperatures.
-Across the temperature gradient, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average.
-Additionally, material fluxes of warmer streams were increasingly skewed towards high-turnover populations *within* the community, showing higher temperatures restructured organic matter fluxes in both an absolute and relative sense.
+These warming-induced changes have the potential to influence the distribution of food web fluxes, food web stability, and the importance of environmental and biological factors in community assembly.
+Here, we quantified patterns and the relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient.
+We then related these patterns to species- and community-level trait distributions (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
+We predicted that 1) communities in warmer streams would skew towards smaller *M* and higher *P:B* and 2) organic matter fluxes within warmer communities would increasingly skew towards smaller, higher *P:B* populations.
+Across the temperature gradient, communities in warmer streams were indeed composed of smaller-bodied and higher biomass-turnover populations on average.
+Additionally, material fluxes within warmer streams were increasingly skewed towards high-turnover populations, demonstrating that warming can restructure organic matter fluxes in both an absolute and relative sense.
 With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the potential for stronger selection for these traits with increasing temperature.
 The emerging picture is a warmer world that is both smaller and faster.
-Our study provides clear empirical support for this pattern in natural communities and suggests that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
+Our study suggests that a warming world will be 'smaller and faster', and that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
 
@@
 The effects of warming permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
-Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and the magnitudes and relative distribution of energy fluxes among species and trophic levels [@may1972; @mccann1998; @barnes2018].
+Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitudes and relative distribution of energy fluxes in food webs[@may1972; @mccann1998; @barnes2018].
 
@@
 biodiversity) and function (BEF).
-The extent to which temperature modifies the relative importance of community assembly processes will mediate changes to ecosystem structure and function with warming within and among ecosystems.
-These processes are varied--from strictly deterministic [\ e.g., environmental/niche filtering, @whittaker1962],  to strictly stochastic [\ e.g., neutral theory, @hubbell2001]--and they operate across multiple scales.
-As such, there are a multitude of possible relationships between warming and species' abundance and trait distributions.
-For example, strong environmental filtering can be expected to mediate the number of species in a community and is likely to skew trait distributions, to some extent, in natural communities [@therriault1999].
-However, the relative distribution of traits can be modified by a number of additional processes beyond environmental filtering that alter species relative abundance distributions [\ e.g., species interactions @therriault1999 and demographic stochasticity @hubbell2001].
-These additional processes can exaggerate or counter any skew in trait distribution imparted through environmental filtering and may therefore be important for understanding the warming response in species and communities and the absolute and relative distribution of organic matter fluxes across gradients in species traits.
-
-Although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e.
+Such connections hinge upon how warming influences functional trait distributions and how these functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
+Additionally, warming may modify both deterministic [e.g., environmental/niche filtering, @whittaker1962] and stochastic [e.g., neutral theory, @hubbell2001] community assembly processes [@saito2021], leading to many possible relationships between warming and species' abundance and trait distributions.
+For example, although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e.
 evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
-The implications of these changes on the magnitude and pathways of energy flux in food webs should depend on how warming influences functional trait distributions, as well as how these functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
+This strong environmental filtering is likely to skew trait distributions, to some extent, in natural communities [@therriault1999].
+However, the relative distribution of traits can be modified by additional processes beyond environmental filtering that alter species relative abundance distributions [e.g., species interactions, @therriault1999; demographic stochasticity, @hubbell2001].
+These additional processes can exaggerate or counter any skew in trait distribution imparted through environmental filtering and may modify the relationship between species' traits and the absolute and relative energy demands in food webs.
 
@@
 Body size is a fundamental trait that is strongly influenced by temperature and has great potential to influence energy flux [@atkinson1994; @gardner2011; @daufresne2009].
-Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or through reduced body size of warmer individuals [@atkinson1994].
-Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of an organism's biology [@peters1983] influencing, life history patterns [@zeuss2017; @altermatt2010; @nelson2020b], and developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
+Body size reductions arise from multiple mechanisms acting at different levels of organization, including the increased relative abundance of smaller species within warmer communities [@bergmann1848], smaller individuals in warmer populations [@james1970], and/or reduced body size of warmer individuals [@atkinson1994].
+These temperature-size relationships are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
+These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of an species life history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b] and,developmental [@angilletta2004] or metabolic rates [@brown2004; @gillooly2001].
 
 <!--- Write the main goals of the paragraph--->
-Metabolic rate, in addition to being controlled by body size, is a second key trait that is influence by temperature and tied to variation in energy flux through food webs [@gillooly2001; ].
-Warming can influence metabolic indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
-These processes has been shown to modify ecosystem patterns through changes in population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
+Metabolic rate, in addition to being controlled by body size, is another key trait that is influence by temperature and tied to variation in energy flux through food webs [@gillooly2001].
+Warming can influence metabolic rates indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
+These processes have been shown to modify ecosystem patterns through changes in population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
 Importantly, the kinetic effects of temperature are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
-Taken together, these changes suggest a smaller, faster world in which warming "speeds up" ecosystem processes through the compounded effects of smaller body size and higher turnover rates, with potentially lasting imprints on food web structure and energy fluxes [@gibert2019a].
+Taken together, these changes suggest that warming shoudl lead to a smaller, faster world in which ecosystem processes 'speed up' through the effects of smaller body size and higher turnover rates, with a potentially strong imprint on food web structure and energy fluxes [@gibert2019a].
 
-Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C).
-Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally [@ogorman2012; @hood2018].
-Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
-As such, we predicted annual organic matter fluxes to consumers would increase with temperature across streams mirroring among-stream patterns in resource availability and consumer energy demand.
-We hypothesized temperature to be a strong environmental filter of community assembly and the distribution of energy and organic matter fluxes.
-From this we made a number of predictions regarding the patterning of organic matter fluxes within and across communities of different temperature, with particular focus on two species traits; body size and population biomass turnover (production:biomass ratios, *P:B*).
-First, we predict warmer temperatures should favor smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities.
-Second, within communities organic matter fluxes should be increasingly dominated by smaller, higher turnover species at warmer temperatures.
-Lastly, we quantify the probability that patterns of organic matter fluxes among populations arise from chance versus the potential for temperature to structure the relative distribution of material fluxes along species trait axes.
+We quantified patterns of organic matter flux in stream food webs across a natural temperature gradient (\~5--28$^\circ$C) in southwestern Iceland.
+Previous research in these streams has shown a strong positive effect of warming on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally [@ogorman2012; @hood2018].
+Invertebrates in these streams rely on autochthonous resources [@ogorman2012; @nelson2020], thus the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
+We, therefore, predicted that annual organic matter fluxes to consumers would increase with stream temperature mirroring patterns in resource availability and consumer energy demand.
+We also hypothesized that temperature would act as a principle environmental filter on community assembly and organic matter fluxes by favoring 'fast' life-history traits.
+Specifically, we predicted that warming temperatures among streams would lead to a decrease in average body size and an increase in average biomass turnover (i.e., *P:B* ratio) of populations, channeling the majority of energy flux through these taxa among stream communities.
+We also predicted that *within* communities, organic matter fluxes would be driven by small-bodied and high *P:B* taxa, and that these would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
+Our results should help refine general predictions about how warming, and its influence on key traits, is likely to shape energy flux through animal food webs.
 
@@
 We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
-characterized by indirect geothermal heating of groundwater [@arnason1969], leading to natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
-chemistries [@friberg2009]. These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a]. We selected
-streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers. In each stream, we measured temperature and water depth
-every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp. Pocasset, MA, USA). Light availability in the watershed was measured every 15
-min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp. Pocasset, MA, USA).
+characterized by indirect geothermal heating of groundwater [@arnason1969], leading to natural variability in stream temperatures (4.5--54.0 $^\circ$C), but similar solute
+chemistries [@friberg2009].
+These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a].
+We selected streams to maximize the temperature range, while minimizing differences in the structural aspects of the primary producer community [@junker2020a].
+In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp.
+Pocasset, MA, USA).
+Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp.
+Pocasset, MA, USA).
 
@@
 
-We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
-study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
-manipulation [@nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
-unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected five Surber samples
-(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
+We sampled macroinvertebrate communities approximately monthly in six streams, four from July 2011 to August 2012 and two from October 2010 to October 2011 (*n* = 6 streams).
+The two streams sampled from 2010--2011 were part of a separate warming manipulation during the reference (i.e., non-manipulated) year [@nelson2017; @nelson2017a].
+Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018].
+We collected five Surber samples (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream.
+Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
 organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
-(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15 x magnification).
-For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
-the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
-taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
+(\>1 mm) and fine (\>250 $\mu$m -- \<1 mm) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15 x magnification).
+For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates.
+Subsamples were scaled to the rest of the sample assuming similar abundance and body size distributions.
+Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson1977; @merritt2008; @andersen2013].
+Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
 
@@
 
-Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR, @benke2017]. Growth rates were determined using taxon appropriate
-approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
-Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned
-chambers for 7--15 days, after which they were again photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
+Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR, @benke2017]. Growth rates were determined using taxon-appropriate
+approaches described in Junker and others [-@junker2020].
+Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [\ *sensu* @huryn1986].
+Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed in the stream within pre-conditioned
+chambers for 7--15 days, and removed and photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
 lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke1999; @ogorman2012; @hannesdottir2013]. Growth rates (*g*, d^-1^) were
@@
 
-$$g = log_e ( M_{t+\Delta t} / M_t) / \Delta t$$
+$$g = log_e ( M_{t+\Delta t} / M_t) / \Delta t$$ {#eq:eqn1}
 
-Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000). For taxa which exhibit synchronous growth
-and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
-using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
-above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
-replacement and growth rates estimated from equation 1.
+Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000).
+For taxa that exhibit synchronous growth and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017].
+Individual lengths were converted to mass (mg AFDM) using published length-mass regression cited above, and size-frequency histograms were visually inspected for directional changes in body size through time.
+For each date, size-frequency distributions were resampled with replacement and growth rates estimated from equation 1.
 We prevented the calculation of negative growth rates by requiring $M_{t + \Delta t}$ \> $M_t$.
-If this condition was not met after 1e^4^ resamplings, a minimum growth rate of 0.001 was set.
-To estimate
-growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
-empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
-measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration, size-specific growth rates were multiplied by mean
-interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
-taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.
+If this condition was not met after 1e^4^ resamplings, a minimum growth rate of 0.001 was used.
+To estimate growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of empirical growth rates against body size and temperature.
+To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled measured growth rates, in addition to abundance and size distributions from individual samples.
+For each iteration, size-specific growth rates were multiplied by mean
+interval biomass for each size class and the number of days between sample dates to estimate size class-specific production.
+For each interval, size classes were summed for each taxon to calculate total population-level production.
+Intervals were summed to estimate annual secondary production (g AFDM m^-2^ y^-1^).
 
@@
 
-Organic matter fluxes through the community (g m^-2^ t^-1^) were calculated using the trophic basis of production method [TBP, @benke1980].
-Taxon-specific secondary production estimates were combined with
-diet proportions (see Supplemental Materials), diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter.
+Organic matter fluxes through the community were calculated using the trophic basis of production method [TBP, @benke1980].
+Taxon-specific secondary production estimates were combined with diet proportions (see Supplemental Materials), diet-specific assimilation efficiencies, *AE~i~*, and net production efficiencies, *NPE* [e.g., @mccullough1975], to estimate consumption of organic matter.
 For each food
 category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
-category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
-matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
-calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
-a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
-the TBP method using modeled diet proportions (see *Diet analysis* in Supplemental Materials), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
-incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
-filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
-(bryophytes) = 0.1 (95% PI: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
-incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
-within the *rriskDistributions* package [@belgorodski2017].
+category.
+The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic matter from each food category by each taxon [@benke1980].
+Consumption was calculated for each taxon across sampling intervals (typically \~1 month).
+Total interval consumption was calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals.
+Variability in consumption estimates was estimated through a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with the TBP method using modeled diet proportions (see *Diet analysis* in Supplemental Materials), diet-specific assimilation efficiencies, and net production efficiency.
+Variability in *AE~i~* was incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36), filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants (bryophytes) = 0.1 (95% PI: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997].
+Variability in *NPE* was incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5).
+Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@belgorodski2017].
 
@@
 
-### Evenness Among consumers
+### Evenness Among taxa
 
-To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on rank ordered OM fluxes, such that in a community with $S$ species and the relative OM flux of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
+To visualize and quantify the evenness of OM fluxes among taxa within each stream, we constructed Lorenz curves [@lorenz1905] on rank-ordered OM fluxes, such that in a community with $S$ species and the relative OM flux of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ...
 p_S$.
-The Lorenz curve plots how a value, in this case OM flux, accumulates with increasing cumulative proportion of species.
-In a community with perfectly equal distribution of OM flux among species, the Lorenz curve is simply a straight diagonal line.
+The Lorenz curve shows how a value, in this case OM flux, accumulates with increasing cumulative proportion of taxa.
+In a community with perfectly equal distribution of OM flux among taxa, the Lorenz curve is simply a straight diagonal line.
 Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]:
 
-$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$ {#eq:eq2}
 
-where $G^*$ represents an index of relative evenness of OM fluxes bounded between zero and one--one representing a community with exactly equal proportion of total community OM flux for all species ($1/S$), and a value of zero where total community flux is attributed to a single species.
+where $G^*$ represents an index of relative evenness of OM fluxes bounded between zero and one; a value of one represents a community with equal proportion of total community OM flux for all species ($1/S$), and a value of zero represents a community in which the total OM flux is attributed to a single taxa.
 
-### Distribution of OM fluxes in relation to species' traits
+### Distribution of OM fluxes in relation to taxa traits
 
-We predicted that warming would favor species with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
-To assess the potential effects of environmental filtered across communities, we explored the relationships between mean annual temperature ($^\circ$C) and mean population *M* and *P:B* of each community with bootstrapped linear regressions.
-Here, `r temperature_stats[['n_boot']]` values of population *M* or *P:B* were resampled with replacement for each species within each stream.
-The mean of all populations within a stream was calculated and a linear model was fit between *log~e~*-transformed *M* or *P:B* and mean annual temperature.
-Response variables *M* and *P:B* were transformed to meet the assumption of normally distributed residual variation.
+We predicted that warming would favor taxa with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
+To assess the potential effects of environmental filtering across communities, we used bootstrapped linear regressions to quantify the relationship between mean annual temperature ($^\circ$C) and mean population body size ($\overline{M}$) and biomass turnover ($\overline{P:B}$) of each stream community.
+Here, `r temperature_stats[['n_boot']]` values of population *M* or *P:B* were resampled with replacement from population secondary production vectors (see *Secondary Production* above) for each taxa within each stream.
+The mean of all populations within a stream was calculated and a linear model was fit between *log~e~*-transformed $\overline{M}$ or $\overline{P:B}$ and mean annual temperature.
+Response variables were transformed to meet the assumption of normally distributed residual variation.
 
-To quantify how the distribution of organic matter fluxes were modified _**within**_ a community and how this modification was related to temperature, we assessed the extent to which the relative OM fluxes among consumers within a community were skewed towards populations with lower or higher relative *M* or *P:B*.
-To do this, we ordered species based on within-stream ranking of annual population traits (i.e., $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:
+To quantify how the distribution of organic matter fluxes were modified *within* a community and whether this modification was related to temperature, we assessed the extent to which the relative OM fluxes among taxa were skewed towards populations with lower or higher relative *M* or *P:B*.
+To do this, we ordered taxa based on within-stream rankings of annual population traits (i.e., *M*, *P:B*) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to taxa traits as:
 
-$$Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}$$
+$$Sk_{flux} = f_{Q0.75} - 2f_{Q0.5} + f_{Q0.25}/ f_{Q0.75}-f_{Q0.25}$$ {#eq:eqn3}
 
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-We repeated this analysis for all bootstrapped estimates of OM flux in all communities.
-Skewness coefficients exist in the range [-1, 1], where -1 indicates OM fluxes are skewed perfectly away from a trait and 1 indicates higher relative flux is perfectly associated with higher trait values.
-To determine if $Sk_{flux}$ with population *M* and *P:B* was related to mean annual stream temperature, we use bootstrapped beta regression with a simple transformation to meet the assumptions of the model, $(Sk_{flux} + 1)/2$, thereby standardizing values between 0 and 1.
+We repeated this analysis for all bootstrapped estimates of OM flux in each stream community.
+Skewness coefficients exist in the range [-1, 1], where -1 indicates that OM fluxes are skewed perfectly away from a trait and 1 indicates that higher relative fluxes are perfectly associated with higher trait values.
+To determine if the skewness of fluxes with *M* and *P:B* was related to mean annual stream temperature, we use bootstrapped beta regression with a simple transformation, $(Sk_{flux} + 1)/2$, to meet the assumptions of the model and standardize values between 0 and 1.
 Model coefficients were back-transformed to estimate effect sizes.
 
-To assess how temperature may structure the skew of OM among populations within a community, we quantified how likely it was to observe such a skewed distribution in OM fluxes by random chance.
-Skewness in OM fluxes may arise through both ecological and random processes.
-Further, the feasible range of skewness values a community can take is inherently tied to the evenness of OM fluxes within a community.
-This dependence on evenness can make it difficult to determine the importance of random versus ecological processes on the distribution of OM fluxes in the community through comparison of raw skewness measures alone.
-Here, we predicted that species' $M$ and $P:B$ would be increasingly important traits structuring OM fluxes within a community and therefore warmer streams would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
-In contrast, cooler streams would exhibit OM fluxes with skew values that are more likely due to random chance ('random ordering'), regardless of raw skewnness values, suggesting other traits govern the distribution of OM fluxes within communities.
-To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
+To examine whether and how temperature influences the skew of OM flux among populations within each community, we quantified the probability of observing the skewed distributions in OM fluxes by random chance.
+The feasible range of skewness values within a community is inherently tied to the evenness of OM fluxes.
+This dependence on evenness can make it difficult to determine the importance of random versus ecological processes on the distribution of OM fluxes by comparison of raw skewness measures alone.
+We predicted that species' $M$ and $P:B$ would be increasingly important traits structuring OM fluxes within a community and therefore warmer streams would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
+In contrast, cooler streams would exhibit OM fluxes with skew values that are more likely due to random chance ('random ordering'), regardless of raw skewness values, suggesting other traits govern the distribution of OM fluxes within communities.
+To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
 The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
-Therefore, we chose to permute a random subset of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times in each stream.
-The number of random orderings was chosen as a balance between characterizing the distribution of skewness values within each feasible set and computational and time constrains.
-This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative OM flux.
+Therefore, we chose to permute a random subset of each stream community's feasible set by randomly ordering species and calculating skewness in the cumulative distribution of annual OM fluxes 100,000 times in each stream.
+This permuted set allowed us to calculate the probability of observing the empirical skewness value, $Sk_{flux}$, compared to a random ordering given the distribution of relative OM flux.
 
@@
 Annual community OM fluxes mirrored patterns of secondary production reported previously [@junker2020].
-Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams (mean [95% percentile interval (PI)]: `r round((min_flux$flux_mg_m_y_mean/1000), 1)`[`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)` to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
+Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams from `r round((min_flux$flux_mg_m_y_mean/1000), 1)`[`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`; mean [95% percentile interval (PI)]:] g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
 
@@
 
-Differences in OM flux among streams driven by variation in total energy deman rather than composition of consumed resources, as consumer diets were highly similar among streams (Figure S1).
-Diets were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`; 95% PI).
+Differences in OM flux among streams were driven by variation in total energy demand rather than composition of consumed resources, as consumer diets were highly similar among streams (Figure S1).
+Diets were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI).
 Within streams, diet overlap ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)*100`% (`r round(min_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)*100`%) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)`% (`r round(max_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)*100`%) among invertebrate taxa.
-Among streams, diet overlap was similarly high with a mean overlap of `r round(among_overlap_mean,2)*100`% (`r round(among_overlap_quant2.5,2)*100` -- `r round(among_overlap_quant97.5,2)*100`%; 95% PI).
+Among streams, diet overlap was similarly high with a mean overlap of `r round(among_overlap_mean,2)*100`% (`r round(among_overlap_quant2.5,2)*100` -- `r round(among_overlap_quant97.5,2)*100`%, 95% PI).
 Diet similarities based on pairwise comparisons among streams showed little difference and no clear relationship with temperature.
@@
 
-In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)` 95% PI; Table S1] and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
-In an absolute sense, and ~85% of total OM flux was contributed by `r n_dom_min$n_dom` and `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness.
-Although differences in evenness among streams were partially attributed to variation in taxon richness (range: `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max`), fluxes wre still highly uneve after accounting for differences in richness (i.e., similar 'Normalized' Gini coefficients, Table S1).
+In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI; Table S1] and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
+In an absolute sense, ~85% of total OM flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness.
+Although differences in evenness among streams were partially attributed to variation in taxon richness (range: `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max`), fluxes were still highly uneven after accounting for differences in richness (i.e., similar 'Normalized' Gini coefficients, Table S1).
 As average stream temperature increased, OM fluxes shifted from dominance by Simuliidae in the coolest stream to Chironomidae and *R.
@@
 balthica*.
-Among stream differences in evenness and dominance of OM fluxes were not related to temperature ().
+Among-stream differences in evenness and dominance of OM fluxes were not related to temperature (Appendix II Table S1).
 
@@
 (A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with increasing mean annual temperature.
-Warming stream temperatures also led to (B) a decrease in mean population body size (*M*, mg ind^1^) and (C) an increase in mean population biomass turnover rate (*P:B*, y^-1^)."}
+Warming stream temperatures also led to (B) a decrease in mean population body size (*M*, mg ind^-1^) and (C) an increase in mean population biomass turnover rate (*P:B*, y^-1^).
+For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
 
@@
 ```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
-(A) Relative contribution (log_10_%) of different taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank ordered organic matter flux (log_e_(mg AFDM m^-2^ y^-1^) by taxon.
+(A) Relative contribution (log~10~%) of different taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
 See supporting materials for the full key of taxonomic abbreviations."}
@@
 
-Within stream communities, OM fluxes skewed towards taxa with larger body sizes (positive skew), smaller body sizes (negative skew), and neutrally with respect to body size (Figure 3A).
-Skew estimates with body size (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_median) %>% select(M_mg_ind_skew_median)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_median) %>% select(M_mg_ind_skew_median) %>% round(2)`; Figure 3B).
+Within stream communities, there were diverse body size--OM flux relationships, with some streams showing skew toward larger-bodied taxa (positive skew), others with most OM fluxes through smaller-bodied sizes (negative skew), and some showed no difference among body sizes (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50) %>% round(2)`, Figure 3A & B).
+Skew estimates with body size ().
 Skew estimates of OM fluxes in relation to body size showed little association with stream temperature except in the warmest stream, where fluxes were heavily skewed toward small-bodied taxa.
-Similarly, skew in OM fluxes in relations to *P:B* ratios varied among streams, ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_median) %>% select(pb_y_skew_median) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_median) %>% select(pb_y_skew_median) %>% round(2)`.
+Similarly, skew in OM fluxes in relation to *P:B* ratios varied among streams, ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_quant50) %>% select(pb_y_skew_quant50) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_quant50) %>% select(pb_y_skew_quant50) %>% round(2)`.
 In this case, OM fluxes to consumers skewed increasingly toward higher turnover (*P:B*) taxa with increasing temperature (Figure 4A, B).
@@
 (C) The probability of observing these skewness values when compared to a random (i.e.
-s) ordering."}
+s) ordering.For panels B and C, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
 
@@
 
-We compared our empirical skew estimates (i.e., $Sk_{flux}$) absed on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa were based on random selection (i.e., stochastic) or were truly based on these traits.
+We compared our empirical skew estimates (i.e., $Sk_{flux}$) based on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa were based on random selection (i.e., stochastic) or were truly based on these traits.
 The probability of observing a similar or more extreme skew of OM fluxes in relation to body size was variable among streams and ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI); there was a very weak positive association between this probability and temperature (Figure 3C).
-In contrast, the probability of a similarly or more extreme skew in relation to *P:B* ratios ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI, Figure 4C) and in this case there was a clear trend towards a more structured OM flux distribution--i.e., favoring fluxes through high *P:B* taxa--at warmer temperatures.
-The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`%; 95% PI) for every 1$^\circ$C increase in temperature (Figure 4C).
+In contrast, the probability of a similar or more extreme skew in relation to *P:B* ratios ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI, Figure 4C) and in this case there was a clear trend towards a more structured OM flux distribution---i.e., favoring fluxes through high *P:B* taxa--at warmer temperatures.
+The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased by `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`%; 95% PI) for every 1$^\circ$C increase in temperature (Figure 4C).
 
@@
 (C) The probability of observing these skewness values when compared to a random (i.e.
-stochastic) ordering." }
+stochastic) ordering.
+For panels B and C, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
 
@@
 
-Rising global temperatures are altering the pathways of energy and material flow across and within ecosystems with potential consequences for the services they provide.
-While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017]---especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010].
-Here, we document shifts in the pathways of material flow across a wide natural temperature gradient and show that increasing temperatures were associated with reductions in mean population body size and increases in mean population *P:B* across stream consumer communities.
-Further, increasing temperature also systematically skewed OM fluxes *within* communities such that, food web fluxes were increasingly skewed towards  quick turnover populations at warmer temperatures.
-Lastly, there was evidence that the distribution of fluxes within communities was non-randomly organized, especially at moderate to warm temperatures and in relation to population *P:B*, suggesting that environmental filtering is especially important in community assembly of warm communities--governing both the traits of species present and the relative distribution of energy and materials fluxes among species.
-This tendency for fluxes to be dominated by relatively higher turnover populations at warmer temperatures and this organization to be increasingly non-random, suggests the speeding up of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of increasing temperature.
+While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [e.g., @oconnor2009], general patterns are elusive and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organization such as communities and food webs [@walther2002; @woodward2010].
+We documented shifts in the pathways of material flows across a wide natural temperature gradient and found that increasing temperatures were associated with reductions in mean population body size and increases in mean population biomass turnover across stream invertebrate communities.
+In addition, we found that warming systematically skewed OM fluxes *within* communities such that, OM flows were increasingly dominated by rapid life-cycle taxa.
+Lastly, we discovered that the distribution of fluxes *within* communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that environmental filtering is especially important in the community assembly of warm communities.
+These patterns suggest that the acceleration of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of environmental warming.
+Further, environmental filtering that is driven by warming is likely governed by both the traits of species present and the ways in which energy and material fluxes are distributed among taxa.
 
-Reductions in organism body size with warming has been deemed a "universal" response to warming [@daufresne2009; @gardner2011; @uszko2022].
-We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 1B), corresponding to ~`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
-While this change represents a community-level shift, the magnitude of change is consistent with recent work on the effects of warming on organism body size across broad taxonomic groups [@deutsch2022].
-This reduction in body size with increasing temperature contrasts results from previous whole-ecosystem warming experiments which observed shifts in community biomass and productivity from smaller to larger organisms following a 3$^\circ$C increase in temperature [@nelson2017; @nelson2017a].
-Our results also counter observational studies in this system that have shown no consistent change in body size within diatom communities at either the population- or community-scale [@adams2013].
-These contrasting results are consistent with deviations from the "universal" response observed across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; @riemer2018; fish @rypel2014].
-Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns [\ i.e., voltinism, @zeuss2017; @nelson2020b; lifespan, @munch2009].
-Considering the connections between organism body size and many other ecological attributes [@peters1983], reductions in body size with increasing temperatures could have broad implications for ecosystem dynamics with a changing climate [@gibert2019a].
+Warming increased rates of materials flux in an absolute sense largely through shifts in community body-size structure.
+At the community level, we observed a ~`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% increase in the mean biomass turnover rate (*P:B*; y^-1^) of populations for each 1$^\circ$C of warming.
+Although this effect among communities may be partially attributed to the thermodynamic influence of temperature [@gillooly2001], biomass turnover rate is also closely related to organism body size [@brown2004; @huryn2007].
+Thus, warming may influence the distributions of *P:B* ratios directly through its effects on metabolic rate and indirectly through reductions in organism body size.
+The increase in *P:B* we observed across communities was similar in magnitude to the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`%, respectively), reinforcing the fundamental connection between organism body size and *P:B*, but also suggesting increases in mean population *P:B* across communities were, may in large part, be attributed to reduced organism body sizes (Figure 1B & C).
+Organism body size is related to a number of other ecological attributes [@peters1983] and changes in body size with increasing temperatures are likely to have broad implications for ecosystems in a changing climate [@gibert2019a].
 
-Warmer ecosystems exhibited higher rates of material flux in both an absolute and relative sense.
-At the community level, we observed a ~`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% increase in the mean biomass turnover rate (*P:B*; y^-1^).
-Temperature has long been recognized as an important driver of ecological rates [@gillooly2001] and the increase in biomass turnover among communities is likely attributed to the thermodynamic effect of temperature--in part.
-Biomass turnover rate is also tightly tied to organism body size [@brown2004; @huryn2007] suggesting that temperature may influence the distribution of *P:B*s both directly through its effects on metabolic rates and indirectly by inducing reductions in organism body size.
-The increase in *P:B* we observed across communities was a similar relative magnitude as the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`%, respectively), providing equivocal evidence of the presence and/or importance of this interaction from this broad view.
-Despite this, the influence of this interaction between the direct and indirect effect of temperature on ecological patterns in increasingly recognized.
-For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concurrent changes to organism body size are taken into account [@bernhardt2018].
-Further, there is growing evidence that the interactive effects warming-induced changes to metabolic rates and body size distributions have important implications for the structure and functioning of food webs at higher temperatures [@sentis2017; @bideault2019; @gibert2019a] and may reflect shifting selection for species traits.
+A general reduction in body size has been deemed a "universal" response to warming [@daufresne2009; @gardner2011; @uszko2022], but notable deviations exists across ecosystems [@thresher2007; @ogorman2012; @ohlberger2013].
+We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 1B), corresponding to ~`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
+While this change is based on community-level shifts (i.e., different sets of taxa), the magnitude of decline is consistent with intra-taxon patterns measured across broad phylogenetic groups [@deutsch2022].
+Interestingly, our results contrast with a previous warming experiment in one of our study streams showing a 3$^\circ$C increase in temperature shifted community biomass and productivity from smaller to larger organisms [@nelson2017; @nelson2017a].
+Moreover, a study of diatom communities across the same temperature gradient in Iceland that reported no consistent change in body size at either the population- or community-level [@adams2013; @ogorman2012].
+Other studies have reported similar deviations from the "universal" response for other taxonomic groups [e.g., invertebrates: @zeuss2017; birds: @geist1987; @riemer2018; fish: @rypel2014].
+While there is certainly a strong propensity for reduced body size with warming, clearly other processes can modify the direction and magnitude of body size shifts and how they play out from individual to ecosystem scales.
 
-Temperature was also an important modifier of the relative performance of species and distribution of OM fluxes *within* communities.
-In addition to the observed decrease in mean body size and increase in biomass turnover rates across communities, species' OM fluxes exhibited non-random patterning along species' trait axes.
-Regarding body size, the pattern was equivocal.
-In the coldest and warmest streams, we saw a strong skew in material fluxes towards larger and smaller species, respectively.
-However, at more moderate temperatures (~6--17$^\circ$C), this pattern was not apparent.
-On the other hand, we observed a clearer relationship between the skewness of OM fluxes in relation to biomass turnover with increasing temperatures.
-Fluxes became more skewed and less random in relation to population *P:B* at warmer temperatures (Figure 4B & C).
-The seemingly weak within community patterns with body size and much clearer patterns with *P:B* present a potentially interesting insight into the more proximate processes by which temperature alters ecosystem structure and function.
-For example, despite the general trend of reduced body sizes at higher temperature [e.g., @daufresne2009; @gardner2011; @uszko2022], there is a lack evidence for persistent evolutionary selection within populations for smaller body sizes with warming [@siepielski2019].
-However, warming-induced body size reductions may act as a stabilizing process in consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
+In addition to community-level responses, temperature was also an important modifier of the relative performance of species *within* communities, causing an increase in the rates of material flux in a *relative* sense with warming.
+Generally speaking, OM fluxes were unevenly distributed among consumers.
+Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this pattern carries over into energy and material fluxes.
+Interestingly, however, we found important structure in the unevenness of OM fluxes with increasing temperature.
+In particular, we found that OM fluxes, to some degree, showed non-random patterning along multiple trait axes.
+First, with respect to body size, the results were equivocal.
+In the coldest and warmest streams, we saw a strong skew in material fluxes towards larger and smaller species, respectively, but this pattern was not apparent at moderate temperatures (~6--17$^\circ$C).
+A much clearer pattern was the increased skewness of OM fluxes towards taxa with high biomass turnover rates at warmer temperatures.
+This pattern also appeared to be increasingly non-random with warming (Figure 4B & C).
+That the relative distribution of OM fluxes was unlikely due to chance reduces the likelihood this pattern could be attributable to demographic stochasticity [e.g., @hubbell2001] and suggests temperature may be a strong environmental filter even at high temperature [e.g., @saito2021].
+Further, warming may filter for taxa with high *P:B* and associated life history traits [\ i.e., multi-voltinism: @zeuss2017; @nelson2020b; short lifespan: @munch2009; high growth rate, @donhauser2020], especially at temperature "extremes" [@donhauser2020].
 
-Therefore, the general response of reduced body size with warming or latitudinal temperature gradients may, in fact, mask the true constraints imparted by food web dynamics because of the correlation between body size and other biological traits (e.g., growth rate, mortality rate, lifespan, biomass turnover rate, etc.).
-In high latitude light-driven systems, such as those here, larger and/or slower populations may destabilize consumer-resource dynamics further through more extreme seasonal autocorrelation of resource growth [@greyson-gaito2022], suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [\ e.g., paradox of enrichment, @mccann2011].
-The importance of this dynamic may be under-appreciated in high-latitude ecosystems especially [@mcmeans2020] where warming is beginning to decouple light regimes and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015] likely driving future changes to biodiversity of these systems.
+A growing body of theoretical and empirical research is beginning to explore the implications of warming for the stability of ecosystems [@fussmann2014].
+'Natural laboratories', such as the geothermal watershed studied here, offer a unique opportunity to isolate the effects of warming and the dominant processes by which it may modulate ecosystem structure and dynamics [@ogorman2014].
+Particularly relevant in our study is the stability and functioning of light-driven ecosystems in response to present and future warming.
+One aspect of climate change that is especially pronounced in high-latitude ecosystems is the decoupling of light regimes---and thereby energy supply regimes---and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015].
+Here, our within-community contrast in how warming skewed fluxes through *P:B* vs.
+body size taxa lends potential insight into the proximate ways in which temperature alters ecosystem structure and function.
+Temperature-size responses vary with a number of ecological factors [@ohlberger2013]; however, warming-induced body size reductions act as a stabilizing process in consumer-resource interactions by reducing consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and consumer energy demand relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
+This gives credence to alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a], a trade-off that may be particularly important in seasonally variable energetic regimes.
+In the absence of other limiting factors, increasing temperatures are likely to make seasonal "boom and bust" cycles of primary production more extreme because of the interactive effects of light and temperature limitation on photosynthetic rates [e.g., @rae1998].
+This process may increase the autocorrelation, as well as, the magnitude (i.e., enrichment) of resource supply, thereby, exaggerating the selection for reduced body sizes because larger and/or slower consumers may destabilize consumer-resource dynamics in the face of increasingly extreme seasonal autocorrelation of resource growth [@greyson-gaito2022].
+This suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [e.g., paradox of enrichment, @mccann2011].
+Therefore, the general response of reduced body size along climactic or geographic temperature gradients may reflect, in part, constraints imparted by food web dynamics, in addition to, physiological mechanisms [e.g., oxygen, @deutsch2022; differential responses of biological process rates, @forster2011].
+The importance of this dynamic may be especially under-appreciated in high-latitude ecosystems [@mcmeans2020].
 
-Temperature was not clearly associated with the broad biodiversity metrics of species richness or evenness/dominance of OM fluxes.
-We observed no clear decrease in species richness with increasing temperature found in other works [@petchey1999] beyond the warmest stream having the fewest species.
-However, variability in the taxonomic resolution among groups precludes a more robust analysis of any richness effects.
-Still, generally OM fluxes were unevenly distributed among consumers.
-Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this carries over into energy and material fluxes.
-Interestingly, however, we found important structure in the unevenness of OM fluxes.
-Organic matter fluxes were increasingly skewed towards high *P:B* populations within warmer streams and this pattern was unlikely related to chance (Figure 4C), suggesting temperature may become an increasingly important environmental filter of community assembly and species relative performance.
-That the relative distribution was of OM fluxes was unlikely due to chance reduces that likelihood this pattern could be attributable to demographic stochasticity of consumers.
-This counters recent hypotheses integrating the metabolic theory of ecology [@brown2004] and neutral theory [@hubbell2001] that suggest neutral processes should be more important at higher temperatures [@saito2021].
-The extent to which the patterns we observe here--i.e., the apparent increased importance of environmental/niche filtering at higher temperature--represent general patterns or results from the specific context of this "natural laboratory" [@ogorman2014] remains an open question.
-
-Here, we documented the important structuring role of temperature in community assembly and the relative distribution of material fluxes across and within streams of a natural temperature gradient.
+We documented the important role of temperature in structuring key functional triats and the relative distribution of material fluxes across natural stream temperature gradient.
 Higher temperatures were associated with increased total flux through the food web as well as reductions in average population body size and increases in population biomass turnover.
-Further, biomass turnover rate was an increasingly important structuring trait at warmer temperatures, more so than organism body size.
-Yet, our results give support that warming may reduce organism size and also 'speed up' ecosystem dynamics in both an absolute and relative sense.
-These changes have important implications for the maintenance of biodiversity as well as for the connections between biodiversity and the magnitude and stability of energy and material cycling in ecosystems in a warming world.
+Further, biomass turnover rate (but not body size) was an increasingly important trait for structuring OM fluxes at warmer temperatures.
+Our results lend support to the idea that warming may reduce organism size and also 'speed up' ecosystem dynamics in both an absolute and relative sense.
+These changes have important implications for the maintenance of biodiversity as well as for the connections between biodiversity and the magnitude and stability of ecosystem energy and material cycles in a warming world.
 
@@
 In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
+
+A general reduction in body size has been deemed a "universal" response to warming [@daufresne2009; @gardner2011; @uszko2022], but notable deviations exists across ecosystems [@thresher2007; @ogorman2012; @ohlberger2013].
+We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 1B), corresponding to ~`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
+While this change is based on community-level shifts (i.e., different sets of taxa), the magnitude of decline is consistent with intra-taxon patterns measured across broad phylogenetic groups [@deutsch2022].
+Interestingly, our results contrast with a previous warming experiment in one of our study streams showing a 3$^\circ$C increase in temperature shifted community biomass and productivity from smaller to larger organisms [@nelson2017; @nelson2017a].
+Moreover, a study of diatom communities across the same temperature gradient in Iceland that reported no consistent change in body size at either the population- or community-level [@adams2013; @ogorman2012].
+Other studies have reported similar deviations from the "universal" response for other taxonomic groups [e.g., invertebrates: @zeuss2017; birds: @geist1987; @riemer2018; fish: @rypel2014].
+Although explanations for these deviations vary [@ohlberger2013], some highlight additional factors that influence body size distributions such as competition and predation [@delong2014], while others have proposed alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns [\ i.e., voltinism: @zeuss2017; @nelson2020b; lifespan: @munch2009].
+Considering the connections between organism body size and many other ecological attributes [@peters1983], changes in body size with increasing temperatures---whether positive or negative---are likely to have broad implications for ecosystems in a changing climate [@gibert2019a].
+
+Although this effect among communities may be partly attributed to the thermodynamic effects of temperature [@gillooly2001], biomass turnover rate is also closely related to organism body size [@brown2004; @huryn2007].
+Thus, warming may influence the distribution of *P:B* ratios directly through its effects on metabolic rate and indirectly through reductions in organism body size.
+The increase in *P:B* we observed across communities was similar in magnitude to the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`%, respectively), reinforcing the fundamental connection between organism body size and *P:B*, but also suggesting increases in mean population *P:B* across communities may be largely attributed to reduced organism body sizes.
+providing equivocal evidence for the presence and/or importance of an interaction between body size and temperature from this broad view.
+Despite this, the influence of this interaction between the direct and indirect effect of temperature on ecological patterns in increasingly recognized.
+For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concurrent changes to organism body size are taken into account [@bernhardt2018].
+
+Further, there is growing evidence that the interactive effects warming-induced changes to metabolic rates and body size distributions have important implications for the structure and functioning of food webs at higher temperatures [@sentis2017; @bideault2019; @gibert2019a] and may reflect shifting selection for species traits.
+
+Temperature was not clearly associated with the broad biodiversity metrics of species richness or evenness/dominance of OM fluxes, yet .
+We observed no clear decrease in species richness with increasing temperature found in other works [@petchey1999] beyond the warmest stream having the fewest species.
+However, variability in the taxonomic resolution among groups precludes a more robust analysis of any richness effects.
+Still, generally OM fluxes were unevenly distributed among consumers.
+Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this pattern carries over into energy and material fluxes.
+Interestingly, however, we found important structure in the unevenness of OM fluxes with increasing temperature.
+As That the relative distribution was of OM fluxes was unlikely due to chance reduces that likelihood this pattern could be attributable to demographic stochasticity of consumers.
+This counters recent hypotheses integrating the metabolic theory of ecology [@brown2004] and neutral theory [@hubbell2001] that suggest neutral processes should be more important at higher temperatures [@saito2021].
+The extent to which the patterns we observe here--i.e., the apparent increased importance of environmental/niche filtering at higher temperature--represent general patterns or results from the specific context of this "natural laboratory" [@ogorman2014] remains an open question.

### 2022-11-18 doc/ms/Junker_temp-energy-flux_ms.Rmd
push before coauthor comments

@@
 
+Submission journal: Ecology
+
+Submission type: Article
+
+Manuscript details:
+
+- Abstract word count: 256/350
+
+- Main text word count (w/ references): 5625
+
+- Page count w/ references: 32/30
+
+- Appendices: 2
+
+Key words: climate change; energy flux; food webs; species traits; warming
+
+Open Research Statement: All data and code used in this work are publicly available at the following link: https://github.com/jimjunker1/temperature_energy-flux.
+
 \newpage
@@
 With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the potential for stronger selection for these traits with increasing temperature.
-The emerging picture is a warmer world that is both smaller and faster.
 Our study suggests that a warming world will be 'smaller and faster', and that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
@@
 The effects of warming permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
-Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitudes and relative distribution of energy fluxes in food webs[@may1972; @mccann1998; @barnes2018].
+Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitudes and relative distribution of energy fluxes in food webs [@may1972; @mccann1998; @barnes2018].
 
 Understanding how warming alters energy fluxes in food webs requires information about how temperature modifies connections between ecosystem structure (i.e.
-biodiversity) and function (BEF).
+biodiversity) and function.
 Such connections hinge upon how warming influences functional trait distributions and how these functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
@@
 Body size is a fundamental trait that is strongly influenced by temperature and has great potential to influence energy flux [@atkinson1994; @gardner2011; @daufresne2009].
-Body size reductions arise from multiple mechanisms acting at different levels of organization, including the increased relative abundance of smaller species within warmer communities [@bergmann1848], smaller individuals in warmer populations [@james1970], and/or reduced body size of warmer individuals [@atkinson1994].
+Body size reductions arise from multiple mechanisms acting at different levels of organization, including the increased relative abundance of smaller species within warmer communities [@bergmann1848] or smaller individuals in warmer populations [@james1970], or reduced absolute body size of warmer individuals [@atkinson1994].
 These temperature-size relationships are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of an species life history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b] and,developmental [@angilletta2004] or metabolic rates [@brown2004; @gillooly2001].
+These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of species life history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b] and, developmental [@angilletta2004] or metabolic rates [@brown2004; @gillooly2001].
 
@@
 Importantly, the kinetic effects of temperature are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
-Taken together, these changes suggest that warming shoudl lead to a smaller, faster world in which ecosystem processes 'speed up' through the effects of smaller body size and higher turnover rates, with a potentially strong imprint on food web structure and energy fluxes [@gibert2019a].
+Taken together, these changes suggest that warming should lead to a smaller, faster world in which ecosystem processes 'speed up' through the effects of smaller body size and higher turnover rates, with a potentially strong imprint on food web structure and energy fluxes [@gibert2019a].
 
@@
 We also hypothesized that temperature would act as a principle environmental filter on community assembly and organic matter fluxes by favoring 'fast' life-history traits.
-Specifically, we predicted that warming temperatures among streams would lead to a decrease in average body size and an increase in average biomass turnover (i.e., *P:B* ratio) of populations, channeling the majority of energy flux through these taxa among stream communities.
-We also predicted that *within* communities, organic matter fluxes would be driven by small-bodied and high *P:B* taxa, and that these would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
+Specifically, we predicted that warming temperatures among streams would lead to a decrease in average body size and an increase in average biomass turnover (i.e., *P:B* ratio) of populations.
+We also predicted that *within* communities, organic matter fluxes would be dominated by small-bodied and high *P:B* taxa at higher temperatures and that these patterns would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
 Our results should help refine general predictions about how warming, and its influence on key traits, is likely to shape energy flux through animal food webs.
@@
 Annual community OM fluxes mirrored patterns of secondary production reported previously [@junker2020].
-Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams from `r round((min_flux$flux_mg_m_y_mean/1000), 1)`[`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`; mean [95% percentile interval (PI)]:] g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
+Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams from `r round((min_flux$flux_mg_m_y_mean/1000), 1)` (`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`; mean [95% percentile interval (PI)]) to `r round((max_flux$flux_mg_m_y_mean/1000),1)` (`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`) g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
 
@@
 
-In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI; Table S1] and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
+In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI; Table S1) and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
 In an absolute sense, ~85% of total OM flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness.
@@
 Within stream communities, there were diverse body size--OM flux relationships, with some streams showing skew toward larger-bodied taxa (positive skew), others with most OM fluxes through smaller-bodied sizes (negative skew), and some showed no difference among body sizes (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50) %>% round(2)`, Figure 3A & B).
-Skew estimates with body size ().
 Skew estimates of OM fluxes in relation to body size showed little association with stream temperature except in the warmest stream, where fluxes were heavily skewed toward small-bodied taxa.
@@
 In addition, we found that warming systematically skewed OM fluxes *within* communities such that, OM flows were increasingly dominated by rapid life-cycle taxa.
-Lastly, we discovered that the distribution of fluxes *within* communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that environmental filtering is especially important in the community assembly of warm communities.
+Lastly, we discovered that the distribution of fluxes within communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that temperature was especially important in structuring the relative performance and resource acquisition among taxa within warm communities.
 These patterns suggest that the acceleration of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of environmental warming.
@@
 Thus, warming may influence the distributions of *P:B* ratios directly through its effects on metabolic rate and indirectly through reductions in organism body size.
-The increase in *P:B* we observed across communities was similar in magnitude to the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`%, respectively), reinforcing the fundamental connection between organism body size and *P:B*, but also suggesting increases in mean population *P:B* across communities were, may in large part, be attributed to reduced organism body sizes (Figure 1B & C).
+The increase in *P:B* we observed across communities was similar in magnitude to the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`%, respectively), reinforcing the fundamental connection between organism body size and *P:B*, but also suggesting increases in mean population *P:B* across communities may, in large part, be attributed to reduced organism body sizes (Figure 1B & C).
 Organism body size is related to a number of other ecological attributes [@peters1983] and changes in body size with increasing temperatures are likely to have broad implications for ecosystems in a changing climate [@gibert2019a].
@@
 One aspect of climate change that is especially pronounced in high-latitude ecosystems is the decoupling of light regimes---and thereby energy supply regimes---and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015].
-Here, our within-community contrast in how warming skewed fluxes through *P:B* vs.
-body size taxa lends potential insight into the proximate ways in which temperature alters ecosystem structure and function.
-Temperature-size responses vary with a number of ecological factors [@ohlberger2013]; however, warming-induced body size reductions act as a stabilizing process in consumer-resource interactions by reducing consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and consumer energy demand relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
+Here, our within-community contrast in how warming skewed fluxes through taxa with respect to *P:B* vs.
+body size may shed light on the proximate ways in which temperature alters ecosystem structure and function.
+Temperature--size responses vary with a number of ecological factors [@ohlberger2013]; however, warming-induced body size reductions act as a stabilizing process in consumer-resource interactions by reducing consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and consumer energy demand relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
 This gives credence to alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
@@
 This process may increase the autocorrelation, as well as, the magnitude (i.e., enrichment) of resource supply, thereby, exaggerating the selection for reduced body sizes because larger and/or slower consumers may destabilize consumer-resource dynamics in the face of increasingly extreme seasonal autocorrelation of resource growth [@greyson-gaito2022].
-This suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [e.g., paradox of enrichment, @mccann2011].
+Thus, suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [e.g., paradox of enrichment, @mccann2011].
 Therefore, the general response of reduced body size along climactic or geographic temperature gradients may reflect, in part, constraints imparted by food web dynamics, in addition to, physiological mechanisms [e.g., oxygen, @deutsch2022; differential responses of biological process rates, @forster2011].
@@
 
-We documented the important role of temperature in structuring key functional triats and the relative distribution of material fluxes across natural stream temperature gradient.
+We documented the important role of temperature in structuring key functional traits and the relative distribution of material fluxes across natural stream temperature gradient.
 Higher temperatures were associated with increased total flux through the food web as well as reductions in average population body size and increases in population biomass turnover.
@@
 ```
-
-\newpage
-
-### Construction zone
-
-Possible other themes to layer in:
-
-effects of temperature on species evenness, evenness of fluxes, and the statistical and ecological constraints on the organization of energy fluxes in communities (e.g., [@diaz2021a] SAD are more uneven than their statistical background and energy fluxes are also but there is important structure in this unevenness).
-This relates to the random vs non-random patterning questions...pull in the concepts of niche filtering and neutral processes in community assembly.
-Pull a little thinking from @saito2021.
-
-Below is more of a set-up for the next paper but a little foreshadowing and hand waving may find a place in here:
-
-These maximize energy intake when resources are available [@atkinson1997]
-
-- Seasonal systems have unique constraints
-- These seasonal constraints are greater at higher temps
-
-This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017], ecological stability response to warming [@fussmann2014],...
-2) optimize for energy availability and demand, 3) and this selection is stronger at extreme temperatures.
-
-### Spare(d) words from previous versions. Keeping around for now.
-
-directly kinetic effects and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].
-
-environmental filtering of compared the observed distributions of material fluxes among consumer populations to random distributions to quantify the likelihood the patterning of organic matter fluxes arise through random ordering of species or  measure the potential strength of environmental filtering on the relative distribution of organic matter   we tested the potential strength of environmental filtering to determine the distribution of within stream energy fluxes by comparing the  how likely it was  Third, we hypothesized that the selective pressure from environmental temperature on body sizes and population turnover would be greatest at temperature extremes, therefore, the patterning of energy fluxes will be 'non-random' at coldest and warmest temperatures.
-
-Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs [@woodward2010; @walther2002].
-For example, species interactions in food webs may modulate species' TSRs [@delong2014], leading to varied responses among species and trophic levels [@ohlberger2013].
-Additionally, warming-induced body size reductions may act as a stabilizing process in some consumer-resource interactions through reduced consumer:resource biomass ratios [@osmond2017] and reductions in consumer growth rates relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011; @greyson-gaito2022].
-
-For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups (e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014).
-Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns (i.e., voltinism, @zeuss2017; @nelson2020b).
-and community structure across ecosystems...
-
-Recent, models have proposed  However, 
-- both bottom-up (e.g. resource supply) and top-down (e.g., predation) proceesses
-- competition and predation [@delong2014], stabilize c-r dynamics [@osmond2017], optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a]
-
-To assess the relationship between the probability of 'non-random ordering' and temperature, we used beta regression on estimates of the probability of seeing the empirical $Sk_{flux}$ value or one more extreme based on random ordering of species in the permuted feasible set.
-Here, values can take the range between 0 and 1 so no transformation was necessary.
-As necessary when we observed many values near 0 and 1, we implemented a zero-one inflated beta regressions in brms [@burkner2017] to test if the probability of observing the empirical $Sk_{flux}$ was associated with mean annual temperature across streams.
-We predicted increasingly 'non-random' distributions in OM fluxes with increasing temperature.
-
-Warmer streams had communities with smaller mean body sizes and faster turnover rates on average (Figure 2).
-Both among and within streams, OM fluxes were distributed differently across body sizes and turnover rates (*P:B*).
-Among streams, mean population body size ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean population annual  P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2).Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively.
-Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C.
-In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature.
-
-A general reduction in body size has been deemed a "universal" response to warming [@daufresne2009; @gardner2011; @uszko2022], but notable deviations exists across ecosystems [@thresher2007; @ogorman2012; @ohlberger2013].
-We observed a clear decrease in the average individual body size of populations from cool to warm communities (Figure 1B), corresponding to ~`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% decline in the mass of individuals for every 1$^\circ$C increase in temperature.
-While this change is based on community-level shifts (i.e., different sets of taxa), the magnitude of decline is consistent with intra-taxon patterns measured across broad phylogenetic groups [@deutsch2022].
-Interestingly, our results contrast with a previous warming experiment in one of our study streams showing a 3$^\circ$C increase in temperature shifted community biomass and productivity from smaller to larger organisms [@nelson2017; @nelson2017a].
-Moreover, a study of diatom communities across the same temperature gradient in Iceland that reported no consistent change in body size at either the population- or community-level [@adams2013; @ogorman2012].
-Other studies have reported similar deviations from the "universal" response for other taxonomic groups [e.g., invertebrates: @zeuss2017; birds: @geist1987; @riemer2018; fish: @rypel2014].
-Although explanations for these deviations vary [@ohlberger2013], some highlight additional factors that influence body size distributions such as competition and predation [@delong2014], while others have proposed alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a] that can shape life history patterns [\ i.e., voltinism: @zeuss2017; @nelson2020b; lifespan: @munch2009].
-Considering the connections between organism body size and many other ecological attributes [@peters1983], changes in body size with increasing temperatures---whether positive or negative---are likely to have broad implications for ecosystems in a changing climate [@gibert2019a].
-
-Although this effect among communities may be partly attributed to the thermodynamic effects of temperature [@gillooly2001], biomass turnover rate is also closely related to organism body size [@brown2004; @huryn2007].
-Thus, warming may influence the distribution of *P:B* ratios directly through its effects on metabolic rate and indirectly through reductions in organism body size.
-The increase in *P:B* we observed across communities was similar in magnitude to the reduction in body size (i.e., +`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% vs -`r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`%, respectively), reinforcing the fundamental connection between organism body size and *P:B*, but also suggesting increases in mean population *P:B* across communities may be largely attributed to reduced organism body sizes.
-providing equivocal evidence for the presence and/or importance of an interaction between body size and temperature from this broad view.
-Despite this, the influence of this interaction between the direct and indirect effect of temperature on ecological patterns in increasingly recognized.
-For example, the effects of temperature on population carrying capacity appear to deviate from metabolic scaling predictions until the effects of concurrent changes to organism body size are taken into account [@bernhardt2018].
-
-Further, there is growing evidence that the interactive effects warming-induced changes to metabolic rates and body size distributions have important implications for the structure and functioning of food webs at higher temperatures [@sentis2017; @bideault2019; @gibert2019a] and may reflect shifting selection for species traits.
-
-Temperature was not clearly associated with the broad biodiversity metrics of species richness or evenness/dominance of OM fluxes, yet .
-We observed no clear decrease in species richness with increasing temperature found in other works [@petchey1999] beyond the warmest stream having the fewest species.
-However, variability in the taxonomic resolution among groups precludes a more robust analysis of any richness effects.
-Still, generally OM fluxes were unevenly distributed among consumers.
-Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this pattern carries over into energy and material fluxes.
-Interestingly, however, we found important structure in the unevenness of OM fluxes with increasing temperature.
-As That the relative distribution was of OM fluxes was unlikely due to chance reduces that likelihood this pattern could be attributable to demographic stochasticity of consumers.
-This counters recent hypotheses integrating the metabolic theory of ecology [@brown2004] and neutral theory [@hubbell2001] that suggest neutral processes should be more important at higher temperatures [@saito2021].
-The extent to which the patterns we observe here--i.e., the apparent increased importance of environmental/niche filtering at higher temperature--represent general patterns or results from the specific context of this "natural laboratory" [@ogorman2014] remains an open question.

### 2022-12-01 doc/coherence_ms/coherence_ms.Rmd
updated manuscript version 2

@@
 </details>
+
+An increasing number of theoretical and empirical studies are beginning to explore the implications of warming for the stability of ecosystems [@fussmann2014].
+'Natural laboratories', such as the geothermal watershed studied here, offer a unique opportunity to isolate the effects of warming and the dominant processes by which it may modulate ecosystem structure and dynamics [@ogorman2014].
+Particularly relevant in our study is the stability and functioning of light-driven ecosystems in response to present and future warming.
+One aspect of climate change that is especially pronounced in high-latitude ecosystems is the decoupling of light regimes---and thereby energy supply regimes---and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015].
+Here, our within-community contrast in how warming skewed fluxes through taxa with respect to *P:B* vs.
+body size may shed light on the proximate ways in which temperature alters ecosystem structure and function.
+Temperature--size responses vary with a number of ecological factors [@ohlberger2013]; however, warming-induced body size reductions act as a stabilizing process in consumer-resource interactions by reducing consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and consumer energy demand relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
+This gives credence to alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
+Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a], a trade-off that may be particularly important in seasonally variable energetic regimes.
+In the absence of other limiting factors, increasing temperatures are likely to make seasonal "boom and bust" cycles of primary production more extreme because of the interactive effects of light and temperature limitation on photosynthetic rates [e.g., @rae1998].
+This process may increase the autocorrelation, as well as, the magnitude (i.e., enrichment) of resource supply, thereby, exaggerating the selection for reduced body sizes because larger and/or slower consumers may destabilize consumer-resource dynamics in the face of increasingly extreme seasonal autocorrelation of resource growth [@greyson-gaito2022].
+Thus, suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [e.g., paradox of enrichment, @mccann2011].
+Therefore, the general response of reduced body size along climactic or geographic temperature gradients may reflect, in part, constraints imparted by food web dynamics, in addition to, physiological mechanisms [e.g., oxygen, @deutsch2022; differential responses of biological process rates, @forster2011].
+The importance of this dynamic may be especially under-appreciated in high-latitude ecosystems [@mcmeans2020].

### 2022-12-01 doc/ms/Junker_temp-energy-flux_ms.Rmd
updated manuscript version 2

@@
 ---
-title: "Environmental warming increases the absolute and relative importance of high-turnover energy channels in stream food webs"
+title: "Environmental warming increases the importance of high-turnover energy channels in stream food webs"
 author:
@@
     institute: bama
-  - name: Alex D. Huryn
+  - name: Alexander D. Huryn
     institute: bama
@@
   - usu: National Aquatic Monitoring Center, Department of Watershed Sciences, Utah State University, Logan, UT 84322, USA
-  - veidi: Institute of Marine and Freshwater Fisheries, Reykjavik, Iceland
-  - reyk: Univeristy of Iceland, Institute of Life and Environmental Sciences, Reykjavik, Iceland
+  - veidi: Institute of Marine and Freshwater Fisheries, Hafnarfjördur, Iceland
+  - reyk: University of Iceland, Institute of Life and Environmental Sciences, Reykjavík, Iceland
 output:
@@
 Warming temperatures are altering communities and trophic networks globally.
-While the influence of warming on food webs is often context-dependent, increasing temperatures are predicted to influence communities in two fundamental ways: 1) by reducing average body size and 2) by increasing individual metabolic rates.
-These warming-induced changes have the potential to influence the distribution of food web fluxes, food web stability, and the importance of environmental and biological factors in community assembly.
+While the overall influence of warming on food webs is often context-dependent, increasing temperatures are predicted to change communities in two fundamental ways: 1) by reducing average body size and 2) by increasing individual metabolic rates.
+These warming-induced changes have the potential to influence the distribution of food web fluxes, food web stability, and the relative importance of ecological and stochastic processes shaping community assembly.
 Here, we quantified patterns and the relative distribution of organic matter fluxes through stream food webs spanning a natural ~25$^\circ$C temperature gradient.
-We then related these patterns to species- and community-level trait distributions (body size, *M* and biomass turnover, *P:B*) within and across ecosystems.
-We predicted that 1) communities in warmer streams would skew towards smaller *M* and higher *P:B* and 2) organic matter fluxes within warmer communities would increasingly skew towards smaller, higher *P:B* populations.
-Across the temperature gradient, communities in warmer streams were indeed composed of smaller-bodied and higher biomass-turnover populations on average.
-Additionally, material fluxes within warmer streams were increasingly skewed towards high-turnover populations, demonstrating that warming can restructure organic matter fluxes in both an absolute and relative sense.
-With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the potential for stronger selection for these traits with increasing temperature.
+We then related these patterns to species- and community-level trait distributions of mean body size and population biomass turnover (*P:B*) within and across ecosystems.
+We predicted that 1) communities in warmer streams would skew towards smaller body size and higher *P:B* and 2) organic matter fluxes within warmer communities would increasingly skew towards smaller, higher *P:B* populations.
+Across the temperature gradient, communities in warmer streams were on average composed of smaller-bodied and higher *P:B* populations.
+Additionally, material fluxes *within* warmer streams were increasingly skewed towards high-turnover populations, demonstrating that warming can restructure organic matter fluxes in both an absolute and relative sense.
+With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the stronger selection for traits driving high turnover with increasing temperature.
 Our study suggests that a warming world will be 'smaller and faster', and that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
@@
 <!--- Speeding up of food web: Species levels--->
-Increasing global temperatures can influence the provision and maintenance of ecosystem services by modifying the network of species interactions that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
+Increasing global temperatures are influencing the provision and maintenance of ecosystem services by modifying the network of species interactions that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
 The effects of warming permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
-Across global climate gradients, these temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitudes and relative distribution of energy fluxes in food webs [@may1972; @mccann1998; @barnes2018].
+Across global climate gradients, such temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitude and relative distribution of energy fluxes in food webs [@may1972; @mccann1998; @barnes2018].
 
-Understanding how warming alters energy fluxes in food webs requires information about how temperature modifies connections between ecosystem structure (i.e.
-biodiversity) and function.
-Such connections hinge upon how warming influences functional trait distributions and how these functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
-Additionally, warming may modify both deterministic [e.g., environmental/niche filtering, @whittaker1962] and stochastic [e.g., neutral theory, @hubbell2001] community assembly processes [@saito2021], leading to many possible relationships between warming and species' abundance and trait distributions.
-For example, although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e.
-evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
-This strong environmental filtering is likely to skew trait distributions, to some extent, in natural communities [@therriault1999].
-However, the relative distribution of traits can be modified by additional processes beyond environmental filtering that alter species relative abundance distributions [e.g., species interactions, @therriault1999; demographic stochasticity, @hubbell2001].
-These additional processes can exaggerate or counter any skew in trait distribution imparted through environmental filtering and may modify the relationship between species' traits and the absolute and relative energy demands in food webs.
+Understanding how warming alters energy fluxes in food webs requires information about how temperature modifies connections between ecosystem structure and function.
+Such connections hinge upon how warming influences functional trait distributions and how functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
+Additionally, warming may modify both deterministic [e.g., environmental/niche filtering, @whittaker1962] and stochastic [e.g., neutral theory, @hubbell2001] community assembly processes [@saito2021], leading to many possible relationships between warming and species abundance and trait distributions.
+For example, although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e., evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
+This strong environmental filtering is likely to skew trait distributions in natural communities [@therriault1999].
+However, the relative distribution of traits can be modified further by additional processes beyond environmental filtering that alter species relative abundance distributions [e.g., species interactions, @therriault1999;\; demographic stochasticity, @hubbell2001].
+These additional processes can exaggerate or counter any skew in trait distributions imparted through environmental filtering and thereby modify the relationship between species' traits and the absolute and relative energy demands in food webs.
 
@@
 Body size reductions arise from multiple mechanisms acting at different levels of organization, including the increased relative abundance of smaller species within warmer communities [@bergmann1848] or smaller individuals in warmer populations [@james1970], or reduced absolute body size of warmer individuals [@atkinson1994].
-These temperature-size relationships are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community.
-These changes can have important implications for ecosystems pattern and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of species life history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b] and, developmental [@angilletta2004] or metabolic rates [@brown2004; @gillooly2001].
+These temperature-size relationships are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and individuals, on average.
+These relationships can have important implications for ecosystems patterns and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of species life-history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b], as well as developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
 
 <!--- Write the main goals of the paragraph--->
-Metabolic rate, in addition to being controlled by body size, is another key trait that is influence by temperature and tied to variation in energy flux through food webs [@gillooly2001].
+Metabolic rate, in addition to being controlled by body size, is another key trait that is influenced by temperature and tied to variation in energy flux through food webs [@gillooly2001].
 Warming can influence metabolic rates indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
@@
 We quantified patterns of organic matter flux in stream food webs across a natural temperature gradient (\~5--28$^\circ$C) in southwestern Iceland.
-Previous research in these streams has shown a strong positive effect of warming on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally [@ogorman2012; @hood2018].
-Invertebrates in these streams rely on autochthonous resources [@ogorman2012; @nelson2020], thus the dynamics of primary production have a strong control on consumer energy demand [@junker2020].
-We, therefore, predicted that annual organic matter fluxes to consumers would increase with stream temperature mirroring patterns in resource availability and consumer energy demand.
-We also hypothesized that temperature would act as a principle environmental filter on community assembly and organic matter fluxes by favoring 'fast' life-history traits.
+Previous research in these streams has shown a strong positive effect of warming on primary production both among streams [@demars2011; @padfield2017] and seasonally within streams [@ogorman2012; @hood2018].
+Invertebrates in these streams rely on autotrophs [@ogorman2012; @nelson2020], thus the dynamics of primary production functions as a strong control on energy flow through consumers [@junker2020].
+We therefore predicted that annual organic matter fluxes to consumers would increase with stream temperature, mirroring patterns in resource availability and consumer energy demand.
+We also hypothesized that temperature would act as a principle environmental filter on community assembly and organic matter fluxes by favoring 'fast' life-history traits associated with small-bodied organisms.
 Specifically, we predicted that warming temperatures among streams would lead to a decrease in average body size and an increase in average biomass turnover (i.e., *P:B* ratio) of populations.
 We also predicted that *within* communities, organic matter fluxes would be dominated by small-bodied and high *P:B* taxa at higher temperatures and that these patterns would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
-Our results should help refine general predictions about how warming, and its influence on key traits, is likely to shape energy flux through animal food webs.
+Our results should help refine general predictions about how ongoing climate warming, and its influence on key traits, is likely to shape energy flux through animal food webs.
 
@@
 
-We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
+We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature from ~5 to 30$^\circ$C. Hengill is
 characterized by indirect geothermal heating of groundwater [@arnason1969], leading to natural variability in stream temperatures (4.5--54.0 $^\circ$C), but similar solute
@@
 We selected streams to maximize the temperature range, while minimizing differences in the structural aspects of the primary producer community [@junker2020a].
-In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp.
-Pocasset, MA, USA).
-Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp.
-Pocasset, MA, USA).
+In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp., Pocasset, MA, USA).
+Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp., Pocasset, MA, USA).
 
@@
 Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018].
-We collected five Surber samples (0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream.
+We collected five Surber samples (0.023 m^2^, 250-$\mu$m mesh) from randomly selected locations within each stream.
 Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
 organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
-(\>1 mm) and fine (\>250 $\mu$m -- \<1 mm) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15 x magnification).
+(\>1 mm) and fine (\>250 $\mu$m--\<1 mm) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15$\times$ magnification).
 For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates.
-Subsamples were scaled to the rest of the sample assuming similar abundance and body size distributions.
 Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with taxonomic keys [@peterson1977; @merritt2008; @andersen2013].
-Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.
+Taxon-specific abundance and biomass were scaled to a per-meter basis by dividing by the Surber sampler area.
 
@@
 Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR, @benke2017]. Growth rates were determined using taxon-appropriate
-approaches described in Junker and others [-@junker2020].
-Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [\ *sensu* @huryn1986].
-Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed in the stream within pre-conditioned
+approaches described in Junker and others [-@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
+Multiple individuals (*n* = 5--15) within small size categories (\~1-mm length range) were photographed next to a field micrometer, placed in the stream within pre-conditioned
 chambers for 7--15 days, and removed and photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
@@
 We prevented the calculation of negative growth rates by requiring $M_{t + \Delta t}$ \> $M_t$.
-If this condition was not met after 1e^4^ resamplings, a minimum growth rate of 0.001 was used.
+If this condition was not met after 10,000 resamplings, a minimum growth rate of 0.001 was used.
 To estimate growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of empirical growth rates against body size and temperature.
@@
 
-Organic matter fluxes through the community were calculated using the trophic basis of production method [TBP, @benke1980].
+Organic matter fluxes through the community were calculated using the trophic basis of production method [TBP\; @benke1980].
 Taxon-specific secondary production estimates were combined with diet proportions (see Supplemental Materials), diet-specific assimilation efficiencies, *AE~i~*, and net production efficiencies, *NPE* [e.g., @mccullough1975], to estimate consumption of organic matter.
@@
 Variability in *NPE* was incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5).
-Beta distributions were fit using the 'get.beta.par()' function within the *rriskDistributions* package [@belgorodski2017].
+Beta distributions were fit in R [@rcoreteam2022] using the 'get.beta.par()' function within the *rriskDistributions* package [@belgorodski2017].
 
@@
 
-### Evenness Among taxa
+### Evenness among taxa
 
@@
 The Lorenz curve shows how a value, in this case OM flux, accumulates with increasing cumulative proportion of taxa.
-In a community with perfectly equal distribution of OM flux among taxa, the Lorenz curve is simply a straight diagonal line.
-Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]:
+In a community with an equal distribution of OM flux among taxa, the Lorenz curve is simply a straight diagonal line.
+Deviation from equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$ [@solomon1975; @chao2019]:
 
@@
 
-where $G^*$ represents an index of relative evenness of OM fluxes bounded between zero and one; a value of one represents a community with equal proportion of total community OM flux for all species ($1/S$), and a value of zero represents a community in which the total OM flux is attributed to a single taxa.
+where $G^*$ represents an index of relative evenness of OM fluxes bounded between zero and one; a value of one represents a community with equal proportion of total community OM flux for all species ($1/S$), and a value of zero represents a community in which the total OM flux is attributed to a single taxon.
 
@@
 We predicted that warming would favor taxa with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
-To assess the potential effects of environmental filtering across communities, we used bootstrapped linear regressions to quantify the relationship between mean annual temperature ($^\circ$C) and mean population body size ($\overline{M}$) and biomass turnover ($\overline{P:B}$) of each stream community.
-Here, `r temperature_stats[['n_boot']]` values of population *M* or *P:B* were resampled with replacement from population secondary production vectors (see *Secondary Production* above) for each taxa within each stream.
+To assess the potential effects of environmental filtering across communities, we used bootstrapped linear regressions to quantify the relationship between mean annual temperature ($^\circ$C) and 1) mean population body size ($\overline{M}$) and 2) biomass turnover ($\overline{P:B}$) of each stream community.
+Here, `r format(temperature_stats[['n_boot']], big.mark = ",", scientific = FALSE)` values of population *M* or *P:B* were resampled with replacement from population secondary production vectors (see *Secondary Production* above) for each taxon within each stream.
 The mean of all populations within a stream was calculated and a linear model was fit between *log~e~*-transformed $\overline{M}$ or $\overline{P:B}$ and mean annual temperature.
@@
 To quantify how the distribution of organic matter fluxes were modified *within* a community and whether this modification was related to temperature, we assessed the extent to which the relative OM fluxes among taxa were skewed towards populations with lower or higher relative *M* or *P:B*.
-To do this, we ordered taxa based on within-stream rankings of annual population traits (i.e., *M*, *P:B*) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to taxa traits as:
+To do this, we ordered taxa based on within-stream rankings of annual population traits (i.e., *M*, *P:B*) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to taxon traits as:
 
@@
 where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution.
-We repeated this analysis for all bootstrapped estimates of OM flux in each stream community.
+We repeated this analysis for all estimates of OM flux used to calculate *M* and *P:B* in each stream community.
 Skewness coefficients exist in the range [-1, 1], where -1 indicates that OM fluxes are skewed perfectly away from a trait and 1 indicates that higher relative fluxes are perfectly associated with higher trait values.
@@
 This dependence on evenness can make it difficult to determine the importance of random versus ecological processes on the distribution of OM fluxes by comparison of raw skewness measures alone.
-We predicted that species' $M$ and $P:B$ would be increasingly important traits structuring OM fluxes within a community and therefore warmer streams would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
-In contrast, cooler streams would exhibit OM fluxes with skew values that are more likely due to random chance ('random ordering'), regardless of raw skewness values, suggesting other traits govern the distribution of OM fluxes within communities.
+We predicted that species $M$ and $P:B$ would be increasingly important traits structuring OM fluxes within a community and therefore warmer streams would exhibit highly skewed OM distributions that would be unlikely due to chance (i.e., 'non-random ordering').
+In contrast, cooler streams would exhibit OM fluxes with skew values that are more likely due to random chance ('random ordering'), regardless of raw skewness values, suggesting other traits or processes govern the distribution of OM fluxes within their communities.
 To accomplish this, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set, @haegeman2008; @diaz2021a], given the number of species and the relative distribution of OM fluxes within a community.
-The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings).
+The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$ for 10 species $\approx 3.6 \times 10^{6}$ unique orderings).
 Therefore, we chose to permute a random subset of each stream community's feasible set by randomly ordering species and calculating skewness in the cumulative distribution of annual OM fluxes 100,000 times in each stream.
 This permuted set allowed us to calculate the probability of observing the empirical skewness value, $Sk_{flux}$, compared to a random ordering given the distribution of relative OM flux.
+We assessed the likelihood of non-random ordering as the distance from the central mass of the random skew distributions within each stream.
+Therefore, observed skew values near the tails of the random distribution where probabilities of observing $Sk_{flux}$ greater or equal ( Pr($Sk_{flux} \geq x$) ) are nearer to zero or one represent communities in which OM fluxes are likely organized non-randomly.
 
@@
 Annual community OM fluxes mirrored patterns of secondary production reported previously [@junker2020].
-Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams from `r round((min_flux$flux_mg_m_y_mean/1000), 1)` (`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`; mean [95% percentile interval (PI)]) to `r round((max_flux$flux_mg_m_y_mean/1000),1)` (`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`) g AFDM $m^{-2} y^{-1}$) and was positively related to temperature (Figure 1A).
+Organic matter flux to invertebrates varied ~`r round((max_flux$flux_mg_m_y_mean/min_flux$flux_mg_m_y_mean),0)`-fold among streams, from `r round((min_flux$flux_mg_m_y_mean/1000), 1)` (`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)` -- `r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`; mean (95% percentile interval [PI])) to `r round((max_flux$flux_mg_m_y_mean/1000),1)` (`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`) g AFDM $m^{-2} y^{-1}$ and was positively related to temperature (Figure 1A).
 
@@
 Differences in OM flux among streams were driven by variation in total energy demand rather than composition of consumed resources, as consumer diets were highly similar among streams (Figure S1).
-Diets were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`, 95% PI).
-Within streams, diet overlap ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)*100`% (`r round(min_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)*100`%) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)`% (`r round(max_within_overlap$meanoverlap_quant2.5,2)*100` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)*100`%) among invertebrate taxa.
-Among streams, diet overlap was similarly high with a mean overlap of `r round(among_overlap_mean,2)*100`% (`r round(among_overlap_quant2.5,2)*100` -- `r round(among_overlap_quant97.5,2)*100`%, 95% PI).
+Across all streams, community-level diets were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%--`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%--`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%; `r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%--`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% dplyr::mutate(across(.fns = ~.x*100)) %>% round(1)`%).
+Within streams, diet overlap ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)*100`% (`r round(min_within_overlap$meanoverlap_quant2.5,2)*100`%--`r round(min_within_overlap$meanoverlap_quant97.5,2)*100`%) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)*100`% (`r round(max_within_overlap$meanoverlap_quant2.5,2)*100`%--`r round(max_within_overlap$meanoverlap_quant97.5,2)*100`%) among invertebrate taxa.
+Among streams, diet overlap was similarly high with a mean overlap of `r round(among_overlap_mean,2)*100`% (`r round(among_overlap_quant2.5,2)*100`%--`r round(among_overlap_quant97.5,2)*100`%).
 Diet similarities based on pairwise comparisons among streams showed little difference and no clear relationship with temperature.
@@
 
-In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI; Table S1) and were dominated by insects in the families Simuliidae and Chironomidae, pulmonated snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
-In an absolute sense, ~85% of total OM flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness.
+In general, OM fluxes were unevenly distributed among taxa (Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`, 95% PI) to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` (`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`; Table S1) and were dominated by insects in the families Simuliidae and Chironomidae, pulmonate snails (*Radix balthica*), and oligochaete worms (Figure 2A & B; Figure S2).
+In  absolute terms, ~85% of total OM flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` taxa, which comprised only `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of total taxon richness among streams.
 Although differences in evenness among streams were partially attributed to variation in taxon richness (range: `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max`), fluxes were still highly uneven after accounting for differences in richness (i.e., similar 'Normalized' Gini coefficients, Table S1).
@@
 balthica* at moderate temperatures.
-In the warmest stream, where maximum temperatures approach ~40$^\circ$C, taxon richness was lowest and OM fluxes were dominated by oligochaete worms in the family Naididae, the chironomid *Cricotpous sylvestris*, and *R.
+In the warmest stream, where maximum temperatures approach ~40$^\circ$C, taxon richness was lowest and OM fluxes were dominated by oligochaete worms in the family Naididae, the chironomid *Cricotopus sylvestris*, and *R.
 balthica*.
@@
 ```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1.
-(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with increasing mean annual temperature.
-Warming stream temperatures also led to (B) a decrease in mean population body size (*M*, mg ind^-1^) and (C) an increase in mean population biomass turnover rate (*P:B*, y^-1^).
+(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature.
+Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
 For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
@@
 
-Across stream communities, average population body size (*M* [mg AFDM ind^-1^]) decreased and average population biomass turnover rate (*P:B* [y^-1^]), increased with increasing temperature (Figure 1B, C).
-Average *M* decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)`0 mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the warmest stream, corresponding to an `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)` -- `r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`; 95% PI) decrease in mean body size for every 1$^\circ$C increase in temperature (Figure 1B).
-Average population *P:B* ratio increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(2)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(2)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the warmest stream corresponding to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(2)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(2)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(2)`; 95% PI) increase in *P:B* ratio for every 1$^\circ$C increase (Figure 1C).
+Across stream communities, average population body size ($\overline{M}$; mg AFDM ind^-1^) decreased and average population biomass turnover rate ($\overline{P:B}$; y^-1^), increased with increasing temperature (Figure 1B & C).
+$\overline{M}$ decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)`0 mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream, corresponding to an `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)` -- `r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`) decrease in mean body size for every 1$^\circ$C increase in temperature (Figure 1B).
+$\overline{P:B}$ ratio increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(1)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(1)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(1)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(1)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(1)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(1)`) in the warmest stream corresponding to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`) increase in $\overline{P:B}$ ratio for every 1$^\circ$C increase (Figure 1C).
 
 ```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
-(A) Relative contribution (log~10~%) of different taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
-See supporting materials for the full key of taxonomic abbreviations."}
+(A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
+Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
+*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*."}
 
@@
 
-Within stream communities, there were diverse body size--OM flux relationships, with some streams showing skew toward larger-bodied taxa (positive skew), others with most OM fluxes through smaller-bodied sizes (negative skew), and some showed no difference among body sizes (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50) %>% round(2)`, Figure 3A & B).
+Within stream communities, there were diverse body size--OM flux relationships, with some streams showing skew toward larger-bodied taxa (positive skew), others with most OM fluxes through smaller-bodied sizes (negative skew), and some showed no difference among body sizes (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50) %>% round(2)`; Figure 3A & B).
 Skew estimates of OM fluxes in relation to body size showed little association with stream temperature except in the warmest stream, where fluxes were heavily skewed toward small-bodied taxa.
 Similarly, skew in OM fluxes in relation to *P:B* ratios varied among streams, ranging from `r pb_skew_summ %>% slice_min(pb_y_skew_quant50) %>% select(pb_y_skew_quant50) %>% round(2)` to `r pb_skew_summ %>% slice_max(pb_y_skew_quant50) %>% select(pb_y_skew_quant50) %>% round(2)`.
-In this case, OM fluxes to consumers skewed increasingly toward higher turnover (*P:B*) taxa with increasing temperature (Figure 4A, B).
+In this case, OM fluxes to consumers skewed increasingly toward higher turnover (*P:B*) taxa with increasing temperature (Figure 4A & B).
 
@@
 (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
-The solid line 1:1 line from the origin represents the line of perfect equality.
+The solid line 1:1 line from the origin represents the line of equality.
 Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
@@
 (B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
-(C) The probability of observing these skewness values when compared to a random (i.e.
-s) ordering.For panels B and C, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
+(C) The probability of observing these skewness values when compared to a random ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
 
@@
 
-We compared our empirical skew estimates (i.e., $Sk_{flux}$) based on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa were based on random selection (i.e., stochastic) or were truly based on these traits.
-The probability of observing a similar or more extreme skew of OM fluxes in relation to body size was variable among streams and ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI); there was a very weak positive association between this probability and temperature (Figure 3C).
-In contrast, the probability of a similar or more extreme skew in relation to *P:B* ratios ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)` -- `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; 95% PI, Figure 4C) and in this case there was a clear trend towards a more structured OM flux distribution---i.e., favoring fluxes through high *P:B* taxa--at warmer temperatures.
-The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased by `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`% -- `r round(pb_prob_temp_quant97.5,3)*100`%; 95% PI) for every 1$^\circ$C increase in temperature (Figure 4C).
+We compared our skew estimates (i.e., $Sk_{flux}$) based on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa could be attributed to random community assembly or likely based on these traits.
+The probability of observing a similar or more extreme skew of OM fluxes in relation to body size was variable among streams and ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`); there was a very weak positive association between this probability and temperature (Figure 3C).
+In contrast, the probability of a similar or more extreme skew in relation to *P:B* ratios ranged from `r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)`--`r pb_skew_summ %>% slice_min(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`) to `r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_mean")) %>% round(2)` (`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant2.5")) %>% round(2)`--`r pb_skew_summ %>% slice_max(pb_skew_prob_mean) %>% select(matches("pb.*prob_quant97.5")) %>% round(2)`; Figure 4C) and in this case there was a clear trend towards a more structured OM flux distribution---i.e., favoring fluxes through high *P:B* taxa--at warmer temperatures.
+The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased by `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`%--`r round(pb_prob_temp_quant97.5,3)*100`%) for every 1$^\circ$C increase in temperature (Figure 4C).
 
@@
 (A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
-The solid line 1:1 line from the origin represents the line of perfect equality.
+The solid 1:1 line from the origin represents the line of equality.
 Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
-The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
-(B) Empirical estimates of *P:B*-related OM flux skewness in relation to stream temperature.
-(C) The probability of observing these skewness values when compared to a random (i.e.
-stochastic) ordering.
-For panels B and C, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
+(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
 
@@
 
-While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [e.g., @oconnor2009], general patterns are elusive and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organization such as communities and food webs [@walther2002; @woodward2010].
-We documented shifts in the pathways of material flows across a wide natural temperature gradient and found that increasing temperatures were associated with reductions in mean population body size and increases in mean population biomass turnover across stream invertebrate communities.
-In addition, we found that warming systematically skewed OM fluxes *within* communities such that, OM flows were increasingly dominated by rapid life-cycle taxa.
-Lastly, we discovered that the distribution of fluxes within communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that temperature was especially important in structuring the relative performance and resource acquisition among taxa within warm communities.
-These patterns suggest that the acceleration of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of environmental warming.
-Further, environmental filtering that is driven by warming is likely governed by both the traits of species present and the ways in which energy and material fluxes are distributed among taxa.
+While a growing body of theoretical and empirical research has enhanced our knowledge of temperature-mediated changes to ecosystems [e.g., @oconnor2009], general patterns are elusive and empirical studies often have idiosyncratic outcomes [@zhang2017; @nelson2017], especially at higher levels of organization such as communities and food webs [@walther2002; @woodward2010].
+Here, we exploit a wide natural gradient of ecosystem temperatures and showed the increasing importance of temperature as an environmental filter of species traits.
+We documented shifts in the pathways of material flows and found that increasing temperatures were associated with reductions in mean population body size and increases in mean population biomass turnover across stream invertebrate communities.
+In addition, we found that warming systematically skewed OM fluxes *within* communities such that, OM flows were increasingly dominated by taxa with rapid life-cycles.
+Lastly, we discovered that the distribution of fluxes within communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that temperature was especially important in structuring relative performance and resource acquisition among taxa within warm communities.
+These patterns show that the acceleration of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of environmental warming.
+Further, environmental filtering that is driven by warming is likely governed by both the traits of species present and the connections between species traits and individual metabolism.
 
-Warming increased rates of materials flux in an absolute sense largely through shifts in community body-size structure.
+Warming-induced shifts in community body size distributions were associated with a community-level increase in the absolute rates of material flux.
 At the community level, we observed a ~`r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(0)`% increase in the mean biomass turnover rate (*P:B*; y^-1^) of populations for each 1$^\circ$C of warming.
@@
 
-In addition to community-level responses, temperature was also an important modifier of the relative performance of species *within* communities, causing an increase in the rates of material flux in a *relative* sense with warming.
+In addition to community-level responses, temperature was also an important modifier of the relative performance of species *within* communities, causing an increase in the rates of material flux in a *relative* sense with warming (i.e., OM fluxes in warmer communities are more skewed towards relatively high *P:B* than cooler ones).
 Generally speaking, OM fluxes were unevenly distributed among consumers.
 Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this pattern carries over into energy and material fluxes.
-Interestingly, however, we found important structure in the unevenness of OM fluxes with increasing temperature.
-In particular, we found that OM fluxes, to some degree, showed non-random patterning along multiple trait axes.
+Interestingly, however, we found important residual structure in the unevenness of OM fluxes with increasing temperature.
+In particular, we found that OM fluxes, to some degree, showed non-random patterning along trait axes.
 First, with respect to body size, the results were equivocal.
@@
 A much clearer pattern was the increased skewness of OM fluxes towards taxa with high biomass turnover rates at warmer temperatures.
-This pattern also appeared to be increasingly non-random with warming (Figure 4B & C).
-That the relative distribution of OM fluxes was unlikely due to chance reduces the likelihood this pattern could be attributable to demographic stochasticity [e.g., @hubbell2001] and suggests temperature may be a strong environmental filter even at high temperature [e.g., @saito2021].
-Further, warming may filter for taxa with high *P:B* and associated life history traits [\ i.e., multi-voltinism: @zeuss2017; @nelson2020b; short lifespan: @munch2009; high growth rate, @donhauser2020], especially at temperature "extremes" [@donhauser2020].
-
-A growing body of theoretical and empirical research is beginning to explore the implications of warming for the stability of ecosystems [@fussmann2014].
-'Natural laboratories', such as the geothermal watershed studied here, offer a unique opportunity to isolate the effects of warming and the dominant processes by which it may modulate ecosystem structure and dynamics [@ogorman2014].
-Particularly relevant in our study is the stability and functioning of light-driven ecosystems in response to present and future warming.
-One aspect of climate change that is especially pronounced in high-latitude ecosystems is the decoupling of light regimes---and thereby energy supply regimes---and the timing of temperature-driven metabolic demands [@huryn2019a; @mcmeans2015].
-Here, our within-community contrast in how warming skewed fluxes through taxa with respect to *P:B* vs.
-body size may shed light on the proximate ways in which temperature alters ecosystem structure and function.
-Temperature--size responses vary with a number of ecological factors [@ohlberger2013]; however, warming-induced body size reductions act as a stabilizing process in consumer-resource interactions by reducing consumer:resource biomass ratios [@osmond2017; @gilbert2014; @sentis2017] and consumer energy demand relative to resource supply [@kozlowski2004; @delong2012a; @mccann2011].
-This gives credence to alternative models of organism body size optimization influenced by, for example, the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012a].
-Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012a], a trade-off that may be particularly important in seasonally variable energetic regimes.
-In the absence of other limiting factors, increasing temperatures are likely to make seasonal "boom and bust" cycles of primary production more extreme because of the interactive effects of light and temperature limitation on photosynthetic rates [e.g., @rae1998].
-This process may increase the autocorrelation, as well as, the magnitude (i.e., enrichment) of resource supply, thereby, exaggerating the selection for reduced body sizes because larger and/or slower consumers may destabilize consumer-resource dynamics in the face of increasingly extreme seasonal autocorrelation of resource growth [@greyson-gaito2022].
-Thus, suggesting a connection between warming responses and a more general food web dynamic of increased relative rates of resource supply and consumer demand [e.g., paradox of enrichment, @mccann2011].
-Therefore, the general response of reduced body size along climactic or geographic temperature gradients may reflect, in part, constraints imparted by food web dynamics, in addition to, physiological mechanisms [e.g., oxygen, @deutsch2022; differential responses of biological process rates, @forster2011].
-The importance of this dynamic may be especially under-appreciated in high-latitude ecosystems [@mcmeans2020].
+This pattern also appeared to arise as a non-random function of warming (Figure 4B & C).
+That the relative distribution of OM fluxes was unlikely due to chance reduces the probability that this pattern was attributable solely to demographic stochasticity [e.g., @hubbell2001; @shoemaker2020] and temperature may be a strong environmental filter for taxa with high *P:B* and associated life-history traits [\ i.e., multi-voltinism: @zeuss2017; @nelson2020b; short lifespan: @munch2009; high growth rate, @donhauser2020], especially at high temperatures [@donhauser2020].
 

### 2022-12-01 R/plot_spp_flux.R

@@ -25,17 +25,17 @@ plot_spp_flux <- function(ann_spp_flux =
     ggplot(aes(x = rank, y = log(flux_mg_m_y_mean), group = site))+
     geom_line(aes(color = site), size = 2)+
     geom_point(aes(fill = site), shape = 21, size = 2.3, color = 'black') +
-    scale_y_continuous(name = expression(log[e]~"(Organic matter flux)[mg"~m^-2~y^-1*"]"),limits = c(-10,NA),
+    scale_y_continuous(name = expression(log[e]~"Organic matter flux (mg"~m^-2~y^-1*")"),limits = c(-10,NA),
                        expand = c(0.03,0))+
     scale_x_continuous(name = 'Species rank')+
-    scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
-    scale_fill_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
+    scale_colour_manual(name = expression("Temperature ("~degree*C~")"), values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
+    scale_fill_manual(name = expression("Temperature ("~degree*C~")"), values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
     annotate('text', label = "B", x = Inf, y = Inf, family = 'serif', vjust = 1, hjust = 1, size = 4)+
     theme_tufte(ticks = TRUE) +
     geom_rangeframe(sides = "lb")+
     theme(legend.position = c(0,0),
           legend.justification = c("left", "bottom"), 
-          legend.title = element_blank(),
+          legend.title = element_text(family = 'serif'),
           legend.spacing.y = unit(0.0003,'cm'),
           legend.key.size = unit(0.4,'cm'));evenness_plot
   

### 2022-12-01 R/plot_traits_temp.R

@@ -23,18 +23,18 @@ plot_traits_temp <- function(flux_summaries,
   
   ann_comm_sum %>%
     ggplot() +
-    geom_errorbar(aes(x = tempC, ymin = log(flux_mg_m_y_quant2.5), ymax = log(flux_mg_m_y_quant97.5), color = site_id), width = 0, size = 1) +
-    geom_errorbar(aes(x = tempC, ymin = log(flux_mg_m_y_quant25), ymax = log(flux_mg_m_y_quant75), color = site_id), width = 0, size = 2) +
+    geom_errorbar(aes(x = tempC, ymin = log(flux_mg_m_y_quant2.5), ymax = log(flux_mg_m_y_quant97.5), color = site_id), width = 0, linewidth = 1) +
+    geom_errorbar(aes(x = tempC, ymin = log(flux_mg_m_y_quant25), ymax = log(flux_mg_m_y_quant75), color = site_id), width = 0, linewidth = 2) +
     geom_point(aes(x = tempC, y = log(flux_mg_m_y_mean), fill = site_id), shape =21, size = 2)+
     scale_x_continuous(name = expression("Temperature ("~degree*C~")"),limits = c(0,30), expand = c(0.01,0.01))+
-    scale_y_continuous(name = expression("Organic matter flux ( g AFDM "~m^-2~y^-1~")"), expand = c(0.01,0.01),
+    scale_y_continuous(name = expression("Organic matter flux ( g AFDM "~m^-2~y^-1*")"), expand = c(0.01,0.01),
                        breaks = log(c(1,5,10,50,100, 500)), labels = exp(log(c(1,5,10,50,100,500)))) +
     scale_color_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
     scale_fill_manual(values = ocecolors[["temperature"]][oce_temp_pos], labels = stream_temp_labels) +
     annotate('text', label = 'A', x = 0.5, y = Inf, family = 'serif', vjust = 1,hjust = 0, size = 4)+
     theme_tufte(ticks = TRUE) +
     geom_rangeframe(aes(x = tempC,y = log(flux_mg_m_y_mean)),sides = "lb")+
-    theme(legend.position = c(1,0),
+    theme(legend.position = "none",
           legend.title = element_blank(),
           legend.justification = c(1,0), axis.title.x = element_blank()) -> ann_comm_flux_plot
     
@@ -68,19 +68,19 @@ plot_traits_temp <- function(flux_summaries,
[…]

### 2022-12-23 doc/ms/Junker_temp-energy-flux_submission.Rmd
getting ready to transfer over to new repo and submit

--- 2022-12-01 doc/ms/Junker_temp-energy-flux_ms.Rmd
@@
    word_document:
-      reference_docx: working_docx_template.docx
+      reference_docx: docx_template.docx
       toc: no
@@
 
-```{r trait v temp, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1.
-(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature.
-Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
-For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
-
-drake::loadd(spp_traitsVtemp)
-grid.draw(spp_traitsVtemp[['fig1_plot']])
-
- # drake::loadd(spp_trait_histograms)
-# grid.draw(spp_trait_histograms)
-
-```
-
 ## Organic matter fluxes in relation to body size and biomass turnover rate
@@
 
-```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
-(A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
-Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
-*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*."}
-
-drake::loadd(annual_spp_flux_fig)
-drake::loadd(spp_flux_dist)
-gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
-```
-
 Within stream communities, there were diverse body size--OM flux relationships, with some streams showing skew toward larger-bodied taxa (positive skew), others with most OM fluxes through smaller-bodied sizes (negative skew), and some showed no difference among body sizes (skew range: `r m_skew_summ %>% slice_min(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50)%>% round(2)` to `r m_skew_summ %>% slice_max(M_mg_ind_skew_quant50) %>% select(M_mg_ind_skew_quant50) %>% round(2)`; Figure 3A & B).
@@
 In this case, OM fluxes to consumers skewed increasingly toward higher turnover (*P:B*) taxa with increasing temperature (Figure 4A & B).
-
-```{r M lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3.
-(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
-The solid line 1:1 line from the origin represents the line of equality.
-Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
-The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
-(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
-(C) The probability of observing these skewness values when compared to a random ordering.
-For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
-
-drake::loadd(M_lorenz_skew_fig)
-grid.draw(M_lorenz_skew_fig)
-
-```
 
@@
 The likelihood of elevated fluxes among high *P:B* taxa became much more likely with warming, and the probability of random ordering decreased by `r round(pb_prob_temp_median, 3)*100`% (`r round(pb_prob_temp_quant2.5,3)*100`%--`r round(pb_prob_temp_quant97.5,3)*100`%) for every 1$^\circ$C increase in temperature (Figure 4C).
-
-```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4.
-(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
-The solid 1:1 line from the origin represents the line of equality.
-Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
-The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
-(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
-(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
-For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
-
-drake::loadd(PB_lorenz_skew_fig)
-grid.draw(PB_lorenz_skew_fig)
-```
 
@@
 <div id="refs"></div>
+
+\newpage
+
+# Figure captions
+
+Figure 1.
+(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature.
+Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
+For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds.
+
+Figure 2.
+(A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
+Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
+*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*.
+
+Figure 3.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
+The solid line 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
+(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^{th} and 75^{th} percentile bounds, and narrow bars represent the 2.5^{th} and 97.5^{th} percentile bounds.
+
+Figure 4.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^{-1}).
+The solid 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
+(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^{th} and 75^{th} percentile bounds, and narrow bars represent the 2.5^{th} and 97.5^{th} percentile bounds.
+
+\newpage
+
+## Figure 1
+
+```{r figure 1, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1.
+(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature.
+Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
+For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
+
+drake::loadd(spp_traitsVtemp)
+grid.draw(spp_traitsVtemp[['fig1_plot']])
+
+ # drake::loadd(spp_trait_histograms)
+# grid.draw(spp_trait_histograms)
+
+```
+
+\newpage
+
+## Figure 2
+
+```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
+(A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
+Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
+*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*."}
+
+drake::loadd(annual_spp_flux_fig)
+drake::loadd(spp_flux_dist)
+gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
+```
+
+\newpage
+
+## Figure 3
+
+```{r figure 3, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
+The solid line 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
+(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
+
+drake::loadd(M_lorenz_skew_fig)
+grid.draw(M_lorenz_skew_fig)
+
+```
+
+\newpage
+
+## Figure 4
+
+```{r figure 4, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
+The solid 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
+(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
+
+drake::loadd(PB_lorenz_skew_fig)
+grid.draw(PB_lorenz_skew_fig)
+
+```
 

### 2022-12-23 doc/ms/Junker_temp-energy-flux_submission_v2.Rmd
getting ready to transfer over to new repo and submit

--- 2022-12-01 doc/ms/Junker_temp-energy-flux_ms.Rmd
@@
 
-Key words: climate change; energy flux; food webs; species traits; warming
+Open Research Statement: All data and code used in this work are publicly available at the following link: https://github.com/jimjunker1/temperature_energy-flux.
 
-Open Research Statement: All data and code used in this work are publicly available at the following link: https://github.com/jimjunker1/temperature_energy-flux.
+Key words: energy flux; climate change; food webs; species traits; warming
 
@@
 We predicted that 1) communities in warmer streams would skew towards smaller body size and higher *P:B* and 2) organic matter fluxes within warmer communities would increasingly skew towards smaller, higher *P:B* populations.
-Across the temperature gradient, communities in warmer streams were on average composed of smaller-bodied and higher *P:B* populations.
-Additionally, material fluxes *within* warmer streams were increasingly skewed towards high-turnover populations, demonstrating that warming can restructure organic matter fluxes in both an absolute and relative sense.
-With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting the stronger selection for traits driving high turnover with increasing temperature.
-Our study suggests that a warming world will be 'smaller and faster', and that warming has the potential to shape pathways of energy and material flows in food webs in ways that may be predictable.
+Across the temperature gradient, warmer communities were characterized by smaller (~9% per $^\circ$C) body size and (~7% faster per $^\circ$C) *P:B* populations on average.
+Additionally, organic matter fluxes *within* warmer streams were increasingly skewed towards higher *P:B* populations, demonstrating that warming can restructure organic matter fluxes in both an absolute and relative sense.
+With warming, the relative distribution of organic matter fluxes also appeared to be increasingly 'non-random', suggesting stronger selection for traits driving high turnover with increasing temperature.
+Our study suggests that a warming world will favor energy fluxes through 'smaller and faster' populations, and that these changes may be more predictable than previously thought.
 
@@
 <!--- Speeding up of food web: Species levels--->
-Increasing global temperatures are influencing the provision and maintenance of ecosystem services by modifying the network of species interactions that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
-The effects of warming permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity (e.g., attack rate, handling time, growth rates, etc.; @dell2014, to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
+Increasing global temperatures influence the provision and maintenance of ecosystem services by modifying the network of species interactions that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012].
+Warming effects permeate across multiple levels of biological organization, from control on individual metabolic rates [@gillooly2001; @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.\; @dell2014], to broad-scale shifts in community assembly and structure [@saito2021; @gibert2019a; @nelson2017a].
 Across global climate gradients, such temperature-induced changes have the potential to mediate food web stability [@baiser2019] by altering the acquisition and allocation of resources [@zhang2017] and the magnitude and relative distribution of energy fluxes in food webs [@may1972; @mccann1998; @barnes2018].
 
-Understanding how warming alters energy fluxes in food webs requires information about how temperature modifies connections between ecosystem structure and function.
-Such connections hinge upon how warming influences functional trait distributions and how functional traits translate to energy demands [@loreau2001; @norberg2001; @norberg2004].
-Additionally, warming may modify both deterministic [e.g., environmental/niche filtering, @whittaker1962] and stochastic [e.g., neutral theory, @hubbell2001] community assembly processes [@saito2021], leading to many possible relationships between warming and species abundance and trait distributions.
-For example, although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming may have profound effects on the dominance structure (i.e., evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
+Understanding how warming alters energy flux in food webs requires information about how temperature modifies relationships between ecosystem structure and function.
+Such connections likely depend upon how warming influences functional trait distributions and how functional traits translate to patterns of energy demand [@loreau2001; @norberg2001; @norberg2004].
+Additionally, warming can modify community assembly processes [@saito2021]---both deterministic [e.g., environmental/niche filtering, @whittaker1962] and stochastic [e.g., neutral theory, @hubbell2001]---leading to many possible relationships between warming, the relative abundance of species, and dominance of particular functional traits.
+For example, although temperature appears to have minimal control on species richness across taxonomic groups [e.g., @bastazini2021], warming can have profound effects on the dominance structure (i.e., evenness) of ecological communities, often by reducing community evenness and favoring a few well-adapted species [@hillebrand2008].
 This strong environmental filtering is likely to skew trait distributions in natural communities [@therriault1999].
-However, the relative distribution of traits can be modified further by additional processes beyond environmental filtering that alter species relative abundance distributions [e.g., species interactions, @therriault1999;\; demographic stochasticity, @hubbell2001].
-These additional processes can exaggerate or counter any skew in trait distributions imparted through environmental filtering and thereby modify the relationship between species' traits and the absolute and relative energy demands in food webs.
+However, the relative distribution of traits can be further modified by additional processes unrelated to environmental filtering that alter species relative abundances [e.g., species interactions, @therriault1999;\; demographic stochasticity, @hubbell2001].
+These additional processes can exaggerate or counter any skew in trait distributions driven by environmental filtering and thereby modify the relationship between species' traits and the absolute and relative energy demands in food webs.
 
 <!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
-Body size is a fundamental trait that is strongly influenced by temperature and has great potential to influence energy flux [@atkinson1994; @gardner2011; @daufresne2009].
-Body size reductions arise from multiple mechanisms acting at different levels of organization, including the increased relative abundance of smaller species within warmer communities [@bergmann1848] or smaller individuals in warmer populations [@james1970], or reduced absolute body size of warmer individuals [@atkinson1994].
-These temperature-size relationships are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and individuals, on average.
-These relationships can have important implications for ecosystems patterns and processes that control energy and material fluxes in ecosystems because body size is a strong determinant of species life-history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b], as well as developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
+Body size is a fundamental trait that is influenced by temperature and has great potential to influence energy flux [@atkinson1994; @gardner2011; @daufresne2009].
+Reduced body size in response to warming can arise at multiple levels of organization, including increased relative abundance of smaller species in warmed communities [@bergmann1848] or smaller individuals in warmer populations [@james1970], or reduced absolute body size of warmed individuals [@atkinson1994].
+Thus, warmer communities are likely to contain both smaller species and individuals.
+These relationships can have important implications for energy and material flux in ecosystems because body size is a strong determinant of species life-history patterns [@peters1983; @zeuss2017; @altermatt2010; @nelson2020b], as well as developmental [@angilletta2004] and metabolic rates [@brown2004; @gillooly2001].
 
 <!--- Write the main goals of the paragraph--->
-Metabolic rate, in addition to being controlled by body size, is another key trait that is influenced by temperature and tied to variation in energy flux through food webs [@gillooly2001].
+Metabolic rate, in addition to being controlled by body size, is another key trait that is influenced by temperature and tied to variation in energy flux through food webs [@gillooly2001; @barnes2018].
 Warming can influence metabolic rates indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019; @osmond2017].
-These processes have been shown to modify ecosystem patterns through changes in population abundance [@bernhardt2018], consumer-resource interactions [@bideault2019], and food web structure [@gibert2019a].
-Importantly, the kinetic effects of temperature are tied to many biological processes [@dell2014], among them growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and population turnover rate [@huryn2007; @brown2004].
-Taken together, these changes suggest that warming should lead to a smaller, faster world in which ecosystem processes 'speed up' through the effects of smaller body size and higher turnover rates, with a potentially strong imprint on food web structure and energy fluxes [@gibert2019a].
+These processes can modify ecosystem patterns through changes in population carrying capacity [@bernhardt2018], species' relative abundances and consequent effects on consumer-resource interactions or food web structure [@gibert2019a; @bideault2019].
+Moreover, metabolic rates are also tied to many biological processes [@dell2014], including growth rate [@gillooly2001], developmental rate [@zuo2012; @nelson2020b], voltinism [@zeuss2017], and biomass turnover rate [@huryn2007; @brown2004].
+Taken together, these changes suggest that warming should lead to a smaller, faster world in which ecosystem processes accelerate through the effects of smaller body size and higher turnover rates, with a potentially strong imprint on food web structure and energy fluxes [@gibert2019a].
 
@@
 We also hypothesized that temperature would act as a principle environmental filter on community assembly and organic matter fluxes by favoring 'fast' life-history traits associated with small-bodied organisms.
-Specifically, we predicted that warming temperatures among streams would lead to a decrease in average body size and an increase in average biomass turnover (i.e., *P:B* ratio) of populations.
-We also predicted that *within* communities, organic matter fluxes would be dominated by small-bodied and high *P:B* taxa at higher temperatures and that these patterns would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
+Specifically, we predicted that warming temperatures would lead to reduced average body size and increased average biomass turnover (i.e., *P:B* ratio) of populations among streams.
+We also predicted that *within* communities, organic matter fluxes would be dominated by small-bodied and high *P:B* taxa at higher temperatures, and that these patterns would not arise by random change [i.e., a 'selection effect' *sensu* @huston1997].
 Our results should help refine general predictions about how ongoing climate warming, and its influence on key traits, is likely to shape energy flux through animal food webs.
@@
 In each stream, we measured temperature and water depth every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp., Pocasset, MA, USA).
-Light availability in the watershed was measured every 15 min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp., Pocasset, MA, USA).
+Light availability in the watershed was measured every 15 minutes from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp., Pocasset, MA, USA).
 
@@
 Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR, @benke2017]. Growth rates were determined using taxon-appropriate
-approaches described in Junker and others [-@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
+approaches described in Junker and others [-@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were measured using *in situ* chambers [@huryn1986].
 Multiple individuals (*n* = 5--15) within small size categories (\~1-mm length range) were photographed next to a field micrometer, placed in the stream within pre-conditioned
@@
 
-Organic matter fluxes through the community were calculated using the trophic basis of production method [TBP\; @benke1980].
+Organic matter fluxes (mg AFDM m^-2^ y^-1^) through the community were calculated using the trophic basis of production method [TBP\; @benke1980].
 Taxon-specific secondary production estimates were combined with diet proportions (see Supplemental Materials), diet-specific assimilation efficiencies, *AE~i~*, and net production efficiencies, *NPE* [e.g., @mccullough1975], to estimate consumption of organic matter.
@@
 We predicted that warming would favor taxa with smaller body size and higher population turnover and therefore OM fluxes would be skewed towards small body size (*M*) and higher *P:B* across and within communities.
-To assess the potential effects of environmental filtering across communities, we used bootstrapped linear regressions to quantify the relationship between mean annual temperature ($^\circ$C) and 1) mean population body size ($\overline{M}$) and 2) biomass turnover ($\overline{P:B}$) of each stream community.
+To assess the potential importance of environmental filtering across communities, we used bootstrapped linear regressions to quantify the relationship between mean annual temperature ($^\circ$C) and either mean population body size ($\overline{M}$) or biomass turnover ($\overline{P:B}$) of each stream community.
 Here, `r format(temperature_stats[['n_boot']], big.mark = ",", scientific = FALSE)` values of population *M* or *P:B* were resampled with replacement from population secondary production vectors (see *Secondary Production* above) for each taxon within each stream.
@@
 We assessed the likelihood of non-random ordering as the distance from the central mass of the random skew distributions within each stream.
-Therefore, observed skew values near the tails of the random distribution where probabilities of observing $Sk_{flux}$ greater or equal ( Pr($Sk_{flux} \geq x$) ) are nearer to zero or one represent communities in which OM fluxes are likely organized non-randomly.
+Therefore, communities in which OM fluxes are likely organized non-randomly are indicated by observed skew values near the tails of these random distributions.
 
@@
 
-Across stream communities, average population body size ($\overline{M}$; mg AFDM ind^-1^) decreased and average population biomass turnover rate ($\overline{P:B}$; y^-1^), increased with increasing temperature (Figure 1B & C).
+Across stream communities, average population body size ($\overline{M}$; mg AFDM ind^-1^) decreased and average population biomass turnover rate ($\overline{P:B}$; y^-1^) increased with increasing temperature (Figure 1B & C).
 $\overline{M}$ decreased from `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% max %>% round(2)` mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_max(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`; 95% PI) in the coldest stream to `r ann_spp_summ %>% dplyr::select(M_mg_ind_mean) %>% min %>% round(2)`0 mg AFDM ind^-1^ (`r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant2.5) %>% round(2)` -- `r ann_spp_summ %>% dplyr::slice_min(M_mg_ind_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(2)`) in the warmest stream, corresponding to an `r ((exp(mean(m_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(m_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)` -- `r ((exp(quantile(m_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`) decrease in mean body size for every 1$^\circ$C increase in temperature (Figure 1B).
 $\overline{P:B}$ ratio increased from `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% min %>% round(1)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(1)` -- `r ann_spp_summ %>% dplyr::slice_min(pb_y_mean) %>% dplyr::select(pb_y_quant97.5) %>% round(1)`) in the coldest stream to `r ann_spp_summ %>% dplyr::select(pb_y_mean) %>% max %>% round(1)` y^-1^ (`r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(pb_y_quant2.5) %>% round(1)` -- `r ann_spp_summ %>% dplyr::slice_max(pb_y_mean) %>% dplyr::select(M_mg_ind_quant97.5) %>% round(1)`) in the warmest stream corresponding to a `r ((exp(mean(pb_spp_temp_coefs, na.rm = TRUE)) - 1)*100) %>% round(1)`% (`r ((exp(quantile(pb_spp_temp_coefs,0.025, na.rm = TRUE)) - 1)*100) %>% round(1)`--`r ((exp(quantile(pb_spp_temp_coefs,0.975, na.rm = TRUE)) - 1)*100) %>% round(1)`) increase in $\overline{P:B}$ ratio for every 1$^\circ$C increase (Figure 1C).
-
-```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
-(A) Log~10~ percent contribution of taxa to OM flux in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
-Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
-*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*."}
-
-drake::loadd(annual_spp_flux_fig)
-drake::loadd(spp_flux_dist)
-gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
-```
 
@@
 
-We compared our skew estimates (i.e., $Sk_{flux}$) based on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa could be attributed to random community assembly or likely based on these traits.
+We compared our skew estimates (i.e., $Sk_{flux}$) of OM flux based on ordered data (i.e., ordered from small to large *M* or low to high *P:B* ratios; Figure 3B and Figure 4B) to skew estimates based on randomly sorted data to detect whether OM fluxes through smaller and higher *P:B* taxa could be attributed to these traits vs.
+random community assembly processes.
 The probability of observing a similar or more extreme skew of OM fluxes in relation to body size was variable among streams and ranged from `r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_min(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`; 95% PI) to `r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_mean")) %>% round(2)` (`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant2.5")) %>% round(2)`--`r m_skew_summ %>% slice_max(M_skew_prob_mean) %>% select(matches("M.*prob_quant97.5")) %>% round(2)`); there was a very weak positive association between this probability and temperature (Figure 3C).
@@
 
-```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4.
-(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
-The solid 1:1 line from the origin represents the line of equality.
-Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
-The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
-(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
-(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
-For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
-
-drake::loadd(PB_lorenz_skew_fig)
-grid.draw(PB_lorenz_skew_fig)
-```
-
 # Discussion
 
-While a growing body of theoretical and empirical research has enhanced our knowledge of temperature-mediated changes to ecosystems [e.g., @oconnor2009], general patterns are elusive and empirical studies often have idiosyncratic outcomes [@zhang2017; @nelson2017], especially at higher levels of organization such as communities and food webs [@walther2002; @woodward2010].
-Here, we exploit a wide natural gradient of ecosystem temperatures and showed the increasing importance of temperature as an environmental filter of species traits.
-We documented shifts in the pathways of material flows and found that increasing temperatures were associated with reductions in mean population body size and increases in mean population biomass turnover across stream invertebrate communities.
+While a growing body of theoretical and empirical research has enhanced our knowledge of temperature-mediated changes to ecosystems [e.g., @oconnor2009], general patterns remain elusive and empirical studies often show idiosyncratic outcomes [@zhang2017; @nelson2017], especially at higher levels of biological organization [@walther2002; @woodward2010].
+Here, we leveraged a wide natural gradient of ecosystem temperatures and demonstrated that temperature acts as a strong environmental filter of species traits.
+In particular, we found that increasing temperatures were associated with reduced population body size and increased population biomass turnover among stream invertebrate communities, leading to higher organic matter fluxes through these populations.
 In addition, we found that warming systematically skewed OM fluxes *within* communities such that, OM flows were increasingly dominated by taxa with rapid life-cycles.
-Lastly, we discovered that the distribution of fluxes within communities was non-randomly organized, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that temperature was especially important in structuring relative performance and resource acquisition among taxa within warm communities.
-These patterns show that the acceleration of energy and material fluxes through ecosystems in both an absolute and relative sense may be a general effect of environmental warming.
-Further, environmental filtering that is driven by warming is likely governed by both the traits of species present and the connections between species traits and individual metabolism.
+Lastly, we discovered that the distribution of fluxes within communities was non-random, especially with respect to *P:B* ratios at moderate to high temperatures, suggesting that temperature was especially important in structuring relative performance and resource acquisition within warm communities.
+These patterns show that the acceleration of energy and material fluxes through ecosystems in both an absolute (among ecosystems) and relative (within ecosystems) sense may be a general effect of environmental warming.
 
@@
 
-In addition to community-level responses, temperature was also an important modifier of the relative performance of species *within* communities, causing an increase in the rates of material flux in a *relative* sense with warming (i.e., OM fluxes in warmer communities are more skewed towards relatively high *P:B* than cooler ones).
-Generally speaking, OM fluxes were unevenly distributed among consumers.
-Given the systematic unevenness in the distribution of individuals among species [@diaz2021a], it may not be surprising that this pattern carries over into energy and material fluxes.
-Interestingly, however, we found important residual structure in the unevenness of OM fluxes with increasing temperature.
-In particular, we found that OM fluxes, to some degree, showed non-random patterning along trait axes.
-First, with respect to body size, the results were equivocal.
+In addition to cross-ecosystem effects of temperature on patterns of species traits and organic matter flux, we found that temperature had strong effects on the relative performance of species *within* communities, leading to an increase OM fluxes through populations with high biomass turnover rates.
+Generally speaking, OM fluxes were unevenly distributed among populations within communities, which may be expected given the systematic unevenness in the distribution of individuals among species [@diaz2021a].
+However, we found important residual structure in the unevenness of OM fluxes that appeared to be related to functional trait axes.
+With respect to body size, the results were somewhat equivocal.
 In the coldest and warmest streams, we saw a strong skew in material fluxes towards larger and smaller species, respectively, but this pattern was not apparent at moderate temperatures (~6--17$^\circ$C).
-A much clearer pattern was the increased skewness of OM fluxes towards taxa with high biomass turnover rates at warmer temperatures.
-This pattern also appeared to arise as a non-random function of warming (Figure 4B & C).
-That the relative distribution of OM fluxes was unlikely due to chance reduces the probability that this pattern was attributable solely to demographic stochasticity [e.g., @hubbell2001; @shoemaker2020] and temperature may be a strong environmental filter for taxa with high *P:B* and associated life-history traits [\ i.e., multi-voltinism: @zeuss2017; @nelson2020b; short lifespan: @munch2009; high growth rate, @donhauser2020], especially at high temperatures [@donhauser2020].
+In contrast, we found a much clearer pattern with respect to biomass turnover rates, in which OM fluxes were increasingly skewed towards taxa with high turnover within warmer streams.
+We also foudn that this pattern was clearly non-random, suggesting that it cannot be attributed to simple demographic stochasticity [e.g., @hubbell2001; @shoemaker2020].
+These results suggest that temperature may be a strong environmental filter---and therefore natural selection agent---for taxa with high turnover rates and associated life-history traits [\ e.g., multi-voltinism: @zeuss2017; @nelson2020b; short lifespan: @munch2009; high growth rate, @donhauser2020], especially at relatively high temperatures.
 
-We documented the important role of temperature in structuring key functional traits and the relative distribution of material fluxes across natural stream temperature gradient.
-Higher temperatures were associated with increased total flux through the food web as well as reductions in average population body size and increases in population biomass turnover.
-Further, biomass turnover rate (but not body size) was an increasingly important trait for structuring OM fluxes at warmer temperatures.
-Our results lend support to the idea that warming may reduce organism size and also 'speed up' ecosystem dynamics in both an absolute and relative sense.
+We documented the important role of temperature in structuring key functional traits and the relative distribution of material fluxes across a natural stream temperature gradient.
+Higher temperatures were associated with increased total flux through the food web, as well as reductions in average population body size and increases in population biomass turnover.
+Further, biomass turnover rate---but not body size---was increasingly important for structuring OM fluxes at warmer temperatures.
+Our results support the idea that warming may reduce organism size and also 'speed up' ecosystem dynamics in both an absolute and relative sense.
 These changes have important implications for the maintenance of biodiversity as well as for the connections between biodiversity and the magnitude and stability of ecosystem energy and material cycles in a warming world.
@@
 
+# Conflict of Interest
+
+The authors have no conflict of interest to declare.
+
 # References
@@
 
+# Figure captions
+
+Figure 1.
+(A) Total organic matter flux (mg AFDM m^-2^ y^-1^) increased with mean annual temperature.
+Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
+For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds.
+
+Figure 2.
+(A) Percent contribution of taxa to OM flux (log~e~[mg AFDM m^-2^ y^-1^])in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~[g AFDM m^-2^ y^-1^]) by taxon.
+Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
+*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*.
+
+Figure 3.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
+The solid line 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical Lorenz curve.
+(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^{th} and 75^{th} percentile bounds, and narrow bars represent the 2.5^{th} and 97.5^{th} percentile bounds.
+
+Figure 4.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^{-1}).
+The solid 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
+(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds.
+
+\newpage
+
+Figure 1
+
+```{r figure 1, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5, dpi = 450, fig.cap="Figure 1.
+(A) Total organic matter flux (g AFDM m^-2^ y^-1^) increased with mean annual temperature.
+Higher stream temperatures also led to (B) a decrease in mean population body size ($\\overline{M}$, mg ind^-1^) and (C) an increase in mean population biomass turnover rate ($\\overline{P:B}$, y^-1^).
+For all panels, points represent the mean value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
+
+drake::loadd(spp_traitsVtemp)
+grid.draw(spp_traitsVtemp[['fig1_plot']])
+
+ # drake::loadd(spp_trait_histograms)
+# grid.draw(spp_trait_histograms)
+
+```
+
+\newpage
+
+Figure 2
+
+```{r figure 2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=7.5, fig.height=8, dpi = 450, fig.cap="Figure 2.
+(A) Percent contribution of taxa to OM flux (log~e~[g AFDM m^-2^ y^-1^])in each stream; colors correspond to mean annual temperature shown in the legend; (B) rank-ordered organic matter flux (log~e~(mg AFDM m^-2^ y^-1^) by taxon.
+Taxa abbreviations: F:Naid, Family Naididae; N comm, *Nais communis*; C syl, *Cricotopus sylvestris*; R balt, *Radix balthica*; Macro sp., *Macropelopia* sp.; C dent, *Chaetocladius dentiforceps*; S vitt, *Simulium vittatum*; Euk spp., *Eukiefferiella* spp.; O obl, *Orthocladius oblidens*; Micro sp.
+*Micropsectra* sp.; D bert, *Diamesa bertrami*; D boh-zer, *Diamesa bohemani-zernyi*; F: Lumb, Family Lumbricidae; P cing, *Potamophylax cingulatus*; S gland, *Sperchon glandulosus*; P urs, *Prosimulium ursinum*; SC: Cope, Subclass Copepoda; R eff, *Rheocricotopus effusus*; S vern, *Simulium vernum*; Chaet sp., *Chaetocladius* sp.; Thien sp., *Thienemanniella*  sp.; O frig, *Orthocladius frigidus*; Limn rip, *Limnophora riparia*; Dicra, *Dicranota* sp.; C: Ost, Class Ostracoda; S aur, *Simulium aurem*."}
+
+drake::loadd(annual_spp_flux_fig)
+drake::loadd(spp_flux_dist)
+gridExtra::grid.arrange( spp_flux_dist,annual_spp_flux_fig, ncol = 2, layout_matrix = cbind(1,1,1,1,2,2,2))
+```
+
+\newpage
+
+Figure 3
+
+```{r figure 3, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 3.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing body size (from left to right; *M*, mg AFDM ind^-1^).
+The solid line 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to body size.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the empirical lorenz curve.
+(B) Empirical estimates of body size-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds."}
+
+drake::loadd(M_lorenz_skew_fig)
+grid.draw(M_lorenz_skew_fig)
+
+```
+
+\newpage
+
+Figure 4
+
+```{r figure 4, echo = FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=4, dpi = 450, fig.cap="Figure 4.
+(A) Lorenz curves showing cumulative relative organic matter flux among taxa with increasing *P:B* ratio (from left to right; y^-1^).
+The solid 1:1 line from the origin represents the line of equality.
+Distributions near this line suggest minimal structuring of OM fluxes in relation to *P:B* ratio.
+The dotted line allows for visualization of skewness in OM fluxes based on its intersection with the Lorenz curve.
+(B) Estimates of *P:B*-related OM flux skewness in relation to stream temperature.
+(C) The probability of observing these skewness values when compared to a random (i.e., stochastic) ordering.
+For panels B and C, points represent the median value, wide bars represent the 25^th^ and 75^th^ percentile bounds, and narrow bars represent the 2.5^th^ and 97.5^th^ percentile bounds." }
+
+drake::loadd(PB_lorenz_skew_fig)
+grid.draw(PB_lorenz_skew_fig)
+
+```
+
+\newpage
+
 # Appendix
 
-## Appendix 1
+## Appendix S1
+
+Appendix S1: Supporting information for Junker, J.
+R., W.
+F.
+Cross, J.
+M.
+Hood, J.
+P.
+Benstead, A.
+D.
+Huryn, D.
+Nelson, J.
+S.
+Ólafsson, and G.
+M.
+Gíslason, "*Environmental warming increases the importance of high-turnover energy channels in stream food webs*" for review and publication in *Ecology*.
 
@@
 
- ```{r diet figure, echo = FALSE, warning=FALSE, message=FALSE,  dpi = 450, fig.cap="Figure S1. Modeled diet proportions of consumer communities across the temperature gradient."}
+ ```{r diet figure, echo = FALSE, warning=FALSE, message=FALSE,  dpi = 450, fig.cap="Appendix S1:Figure S1.
+Posterior distributions of site-level diet proportions for consumer communities across the temperature gradient."}
 
@@
 
-## Appendix 2
+## Appendix S2
+
+Appendix S2: Supporting information for Junker, J.
+R., W.
+F.
+Cross, J.
+M.
+Hood, J.
+P.
+Benstead, A.
+D.
+Huryn, D.
+Nelson, J.
+S.
+Ólafsson, and G.
+M.
+Gíslason, "*Environmental warming increases the importance of high-turnover energy channels in stream food webs*" for review and publication in *Ecology*.
 
 ```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
-tab1_caption = "Table 1.
+tab1_caption = "Appendix S2:Table S1.
 Evenness of organic matter fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
@@
 
-```{r raw lorenz, echo=FALSE, message=FALSE, warning = FALSE, dpi = 400, fig.cap="Figure S2.
-Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (mg AFDM m^-2^ y^-1^)"}
+\newpage
+
+```{r raw lorenz, echo=FALSE, message=FALSE, warning = FALSE, dpi = 400, fig.cap="Appendix S2:Figure S1.
+Lorenz plot of relative community flux by species in ascending order of annual population organic matter flux (g AFDM m^-2^ y^-1^)"}
 drake::loadd(lorenz_skew_fig)
@@
 
-```{r biomass lorenz, echo=FALSE, message=FALSE, warning=FALSE, dpi = 400, fig.cap="Figure S3.
+\newpage
+
+```{r biomass lorenz, echo=FALSE, message=FALSE, warning=FALSE, dpi = 400, fig.cap="Appendix S2:Figure S2.
 Cumulative plot of relative community flux by species in relation to mean annual population biomass (mg m^-2^)."}
@@
 
-```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure S4.
+\newpage
+
+```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Appendix S2:Figure S3.
 Probability distribution of empirical Sk~flux~ measurements in relation to (a) mean body size and (b) annual P:B compared to random species ordering.
